### 2023-09-08 paper1_figures.Rmd
sabina's version 08.09.23

---
title: "paper1_figures"
output: html_document
date: "2023-09-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

FIGURE 1: diagram of papers' selection process
``` {r}
library(DiagrammeR)
library(webshot)
DiagrammeR::grViz("digraph {
graph [layout = dot, rankdir = TB]

node [shape = rectangle]        
rec1 [label = 'Papers identified from search engines
n = 5210']
rec2 [label = 'Duplicates
n = 624']
rec3 [label = 'Papers screened based on titles and abstracts
n = 4586']
rec4 [label = 'Papers not suitable
n = 4321']
rec5 [label = 'Papers read completely
n = 265']
rec6 [label = 'Papers not suitable
n = YYY']
rec7 [label = 'Studies included
n = XXX']

# edge definitions with the node IDs
rec1 -> rec2
rec3 -> rec4
rec5 -> rec6
rec1 -> rec3 -> rec5 -> rec7
}",
height = 500)
```

### 2023-09-08 paper1_markdown.Rmd
sabina's version 08.09.23

---
title             : "Cooperation in commons and social dilemmas: A scoping review"
shorttitle        : "Cooperation in commons and social dilemmas"

author: 
  - name          : "Pedrazzini Sabina"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University of Bern, Centre for Development and Environment (CDE), Mittelstrasse 43, CH-3012 Bern"
    email         : "sabina.pedrazzini@unibe.ch"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "University of Bern"

authornote: |

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "cooperation, social dilemmas, commons"
#wordcount         : ""

bibliography      : CommonPaths.json

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_word

---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
Classical economic theories have described human being as "homo economicus". This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954]. Therefore, according to these theories, human beings are not supposed to show altruistic behaviours, i.e. behaviours that involve costs for the self while benefiting others [@Wittek2015]. However, prosocial acts are often observed in human interactions (**FIND REFERENCES**), and many theories have been developed to explain them.
An example is the theory of competitive altruism [@Roberts1998], that says that acting for the good of others could be a signal of a person's prosociality and therefore improve this person's reputation. Moreover, in the evolutionary perspective, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
Adding something on cooperation norms? Maybe this could be the link between altruism and cooperation? See also the article in Zotero that says that altruism is one of the seven forms that cooperation could have, so maybe is it better to talk about cooperation from the beginning???

**??? CONNECTING ALTRUISM WITH COOPERATION ???**
Cooperation = sacrificing for the grater good at a personal cost (Kollock, 1998)
The study of cooperation is particularly interesting in social dilemmas, i. e. situations in which short-term individual and long-term collective interests are at odds [@Hardin1968]. add Dawes' definition

where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980]. **<- EXPLAIN BETTER!!!**

Thus, the most rational behaviour for everyone would be to defect, because it would ensure the maximum outcome independently of other individuals' choices. ADD NASH EQUILIBRIUM??? (@Colman2018 = at page 2 good definition of Nash) However, as with altruism, cooperative decisions are often made in social dilemmas, showing that human beings are not always rational in the economic, individual sense [@Kollock1998] and that there are multiple factors that can influence people's decisions in such situations (see for example @VanLange2013 for a review).

b.	Moreover, some studies consider cooperation to be the intuitive option, while defection needs more thinking (Kieslich & Hilbig, 2014)
c.	A deeper understanding of mechanisms underlying cooperation in social dilemma is therefore necessary
+ cooperation even more fragile when scarce resources (De Luca et al.) => importance of understanding it

Reaching a better understanding of mechanism underlying cooperation in social dilemmas is even more important when considering that many everyday situations have a social dilemma structure. An example is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous than acting without worrying about environment [@Griskevicius2010]. However, if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic. Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody pays it, then public television will stop existing. + @Kollock1998: page 183, many of the problems that we face are, at their core, social dilemmas.
A third example of real-life social dilemmas are commons.

-	This is even more important if we consider the practical implication that social dilemmas have in our society: social dilemmas could be translated into commons
a.	Climate change as social dilemmas
b.	Definition of commons  commons as social dilemmas
c.	Article that says that social dilemmas are not the same as commons (Cole & Grossman, 2010)
d.	But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
e.	Existing theory about the commons = similar structure than for social dilemmas: rational human beings are supposed to fail (TOC, Hardin, 1986), but in reality cooperation is often observed (for example Ostrom, 1990 + find others)
-	Importance of commons: Pacheco et al. (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons
-	Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of group organization groups can set to improve a cooperation of all members
a.	?? Is it to mention that I focus on what a group can do, without focusing on how external institutions can influence cooperation?? If so, see @Larsson2016
-	Research questions (see if not too redundant with the previous phrase)

+ introducing free-riding concept somewhere

# Methods
To conduct this scoping review, different papers published in academic journals were analyzed in response to the research questions. 
To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect. The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust" **, "intergroup"**, and they were paired with "AND" and "OR" Boolean operators. The research was made during the month of August, 2023.
According with @Munn2022, the type of source was not a selection criteria, therefore experimental and qualitative studies, as well as meta-analysis and systematic reviews are included. This allows us to have an idea as complete as possible about the existing literature on cooperation in commons and social dilemmas. Moreover, there were not chronological or geographical limitations, once again to provide a broader vision on the topic.
There were however some selection criteria concerning the papers' content. First of all, as mentioned in the introduction, this review will focus on individual and group dynamic that can enhance or decrease cooperation in a social dilemma situation (i. e. commons). For this reason, all the papers investigating how an external entity/institution can shape cooperation were not included. Secondly, papers that studied social dilemmas with an agent-based model methodology were also excluded. **include explication**

Criteria developed during screening:
- no papers about agent-based model
- no ethical/religious/philosophical papers
- adult participants

Initially, 5210 papers emerged from the key phrases search. After deleting the duplicates, the count was of 4586. Based on titles and abstracts, 4321 articles were eliminated, leaving 265 (**with emotions**) texts to examine. After a full-text evaluation of the remaining papers, XXX were selected for the present review. Figure 1 resumes this selection procedure.

## Papers' description

# Individual factors
## Gender
The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results: sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], and sometimes there was no difference between genders. In general, meta-analysis found a non significant effect size for this difference [e.g. @Balliet2011; @Spadaro2023]. This indicates that gender differences in cooperation are very flexible and can vary depending on the context [@Spadaro2023]. Therefore, when a significant effect is observed, it means that gender has somewhat been made salient by the situation [@Sell2009].

One of the most observed moderator of this effect is the interaction partners. In fact, in a social dilemma experiment, women are more cooperative toward strangers than men are, while men cooperate more in a group of friends. Moreover, after a socialization phase where strangers could interact, men cooperated more than women [@Peshkovskaya2017]. These results seem to indicate that men accord more importance at the relationship with other members than women. @Gomez-Ruiz2020 also got to the same conclusion by showing that the creation of a team identity enhanced men's cooperation, but had no effects on women. Moreover, in a social dilemma with many iterations, men, but not women, tended to increase their cooperation over time [@Balliet2011].

The partners' gender also have an impact on women's and men's cooperation. In general, groups composed only by men are more cooperative than only-women groups. This is explained by the fact that women are less achievement oriented and more socially oriented than men: they are therefore less concerned by the maximization of their personal payoff and more about relative payoff. Thus, the defection strategy allows them to play defensively and to avoid earning less than the other players [@Colman2018]. Moreover, men displayed higher levels of gratitude and trust in same-sex groups than women [@Peshkovskaya2019]. On the other side, women cooperate more in mixed group. In fact, when both men and women are present, gender stereotypes are activated and people tend to adapt their behaviour to them. This leads women to behave in a more prosocial, altruistic way and men to be more self-oriented and competitive [@Balliet2011]. The same result is also found by @Peshkovskaya2019, who also demonstrated that women reported a stronger social connection with their partners in mixed than in same-sex groups.
The overall group composition also have an impact on cooperation: in general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023]. However, @Barrero-Amortegui2021 showed that the level of resource exploitation is linked to the number of women in a group, but that this link is mediated by the signature of an agreement about extraction. More precisely, in their experiment, groups with a majority of women extracted more resources from a common good (and thus cooperated less) before the signature of the agreement, but also showed the largest reduction of the exploitation level after the agreement was signed. Therefore, even the effect of group composition seems to be subjected to moderator variables.

Another reason why gender differences in cooperation are often very small is that fear and greed motives are confused in a classical social dilemma situation [@Simpson2003]. In this contexts, a feeling of fear arises when one's cooperation could be exploited by others' free-riding, while greed is the feeling associated with the temptation to free-ride on others' cooperation. According to social psychology and evolutionary theories, the author expected women to defect more when fear incentives were present, and men to defect more with greed incentives. Although he could corroborate only the second hypothesis, his intuition about women being more sensitive to the fear of being exploited is confirmed by other studies. For example, women level of cooperation is predicted by their trust in their interaction partner, while men's trust and cooperation are not linked [@Irwin2015]. Moreover, women's lower cooperation is explained by the fact that they expected their partner to contribute less to the common good [@Dorrough2019].

Finally, some of the analyzed papers presented interesting secondary results. First, against their authors' expectations, some intercultural studies showed that the gender difference in cooperation is not explained by the level of gender equality of the country [@Dorrough2019; @Spadaro2023]. Secondly, in an experiment not involving a social dilemma, women were significantly more altruistic than men [@Dorrough2019]. According to the authors, this underlines the importance of distinguishing between prosociality and strategic interactions that characterize social dilemmas. Therefore, in a situation where classical attributes of social dilemmas are not explicit, gender difference in cooperation could not be subjected to the same moderator effects described above. Lastly, according to @Sell2009, it is not possible to think about gender without relying it to social status, with men representing the high-status group. Therefore, gender differences in cooperation could also be caused by social status: to have a better understanding of this hypothesis, it would be interesting to investigate the difference in cooperation between two other social groups with a different status (e.g. high and low socioeconomic status).

In conclusion, "at times women are more cooperative than men, less cooperative than men, or equally as cooperative as men. These variations are explained, in large part, by structural differences and identities triggered by those differences" [@Sell2009]. The context in which men and women interact is therefore essential to predict if a gender will cooperate more than the other, and which one.

## Group identity
@Gomez-Ruiz2020: even if study about gender differences, they found a main effect of team identity on cooperation

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2023-09-11 paper1_markdown.Rmd
Update paper1_markdown.Rmd
test
Sabina 11.09

@@
 output            : papaja::apa6_word
-
 ---
@@
 ```
+
 Classical economic theories have described human being as "homo economicus".
@@
 
-**??? CONNECTING ALTRUISM WITH COOPERATION ???**
-Cooperation = sacrificing for the grater good at a personal cost (Kollock, 1998)
-The study of cooperation is particularly interesting in social dilemmas, i.
+**???
+CONNECTING ALTRUISM WITH COOPERATION ???** Cooperation = sacrificing for the grater good at a personal cost (Kollock, 1998) The study of cooperation is particularly interesting in social dilemmas, i.
 e.
@@
 where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980].
-**<- EXPLAIN BETTER!!!**
+**\<- EXPLAIN BETTER!!!**
 
@@
 c.  A deeper understanding of mechanisms underlying cooperation in social dilemma is therefore necessary
-+ cooperation even more fragile when scarce resources (De Luca et al.) => importance of understanding it
+
+-   cooperation even more fragile when scarce resources (De Luca et al.) =\> importance of understanding it
 
@@
 -   This is even more important if we consider the practical implication that social dilemmas have in our society: social dilemmas could be translated into commons
+
 a.  Climate change as social dilemmas
@@
 c.  Article that says that social dilemmas are not the same as commons (Cole & Grossman, 2010)
-d.	But: Reindl et al.
+d.
+But: Reindl et al.
 (2019) and Rommel et al.
 (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
-e.	Existing theory about the commons = similar structure than for social dilemmas: rational human beings are supposed to fail (TOC, Hardin, 1986), but in reality cooperation is often observed (for example Ostrom, 1990 + find others)
+e.
+Existing theory about the commons = similar structure than for social dilemmas: rational human beings are supposed to fail (TOC, Hardin, 1986), but in reality cooperation is often observed (for example Ostrom, 1990 + find others)
+
 -   Importance of commons: Pacheco et al.
@@
 -   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of group organization groups can set to improve a cooperation of all members
+
 a.  ?? Is it to mention that I focus on what a group can do, without focusing on how external institutions can influence cooperation?? If so, see @Larsson2016
+
 -   Research questions (see if not too redundant with the previous phrase)
 
-+ introducing free-riding concept somewhere
+-   introducing free-riding and defection concept somewhere (see @Gomez-Ruiz2020 introduction for free-riding)
 
 # Methods
+
 To conduct this scoping review, different papers published in academic journals were analyzed in response to the research questions.
@@
 
-Criteria developed during screening:
-- no papers about agent-based model
-- no ethical/religious/philosophical papers
-- adult participants
+Criteria developed during screening: - no papers about agent-based model - no ethical/religious/philosophical papers - adult participants
 
@@
 # Individual factors
+
 ## Gender
+
 The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results: sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], and sometimes there was no difference between genders.
@@
 ## Group identity
+
 @Gomez-Ruiz2020: even if study about gender differences, they found a main effect of team identity on cooperation
+@Arora2016: baseline = reciprocity: participants respond with defection to defection and with cooperation to cooperation, but in-group identification can change this --> main effect of identification on cooperation
+faced to an in-group defector, high identifiers cooperate more than low (no difference between high and low when the partner cooperates) = compensation + this compensation comes with lower trust toward the partner who defected, so the cooperation is not driven by in-group favoritism
+@Torsvik2011: group identity as mediator of anticipating a discussion (see if useful or not to add it here)
+@VanVugt2009: mention that it happens that high-identifying members compensate for free-riders + when people identify with a social group the are more concerned about their in-group reputation
+boost of social identity through inducing competition between groups, but not helpful --> promote a superordinate social identity
+group member that strongly identify with their community do not need an economic incentive to cooperate
+@Puurtinen2009: between group competition enhances cooperation (even between unrelated individuals) by aligning individual and group interest --> investements in public good higher in the group competition vs normal condition + in the group competition there was more anger toward in-group free-rider and guilt toward its own lack of cooperation --> ingroup identification can be enhanced via intergroup competition
+@Noonan2016: study about commons = dog parks --> "having a strong sens of community is related to increased voluntarism" + re-read to see if others parts could be interesting
+@Zhang2019: collective risk as operationalization of group identity: (1) cooperation decreased with time when the risk was individual, but not when it was collective; (2) beliefs about others' cooperation formed similarly under the two conditions = these beliefs are interpreted in a different way according to the condition
+@Dorrough2015: ingroup favoritism increase with time and it is mediated by expectations of others' contributions + the increment is due to the change between ingroup and outgroup as interaction partners, it is not gradual
 
-# Discussion
+@Bardsley2005: paper about conformity (see if it can be useful in this section)
+
+#D
 

### 2023-09-11 paper1_markdown.Rmd
11.09
test
test2
final version 11.09

@@
 
++ @Kramer1984: see the phrases underlined in the introduction
+
 Thus, the most rational behaviour for everyone would be to defect, because it would ensure the maximum outcome independently of other individuals' choices.
@@
 A third example of real-life social dilemmas are commons.
+
+@Jackson2012: according to economist, cooperation is an irrational response in social dilemmas (see the articles that he cites)
 
@@
 faced to an in-group defector, high identifiers cooperate more than low (no difference between high and low when the partner cooperates) = compensation + this compensation comes with lower trust toward the partner who defected, so the cooperation is not driven by in-group favoritism
-@Torsvik2011: group identity as mediator of anticipating a discussion (see if useful or not to add it here)
 @VanVugt2009: mention that it happens that high-identifying members compensate for free-riders + when people identify with a social group the are more concerned about their in-group reputation
@@
 @Dorrough2015: ingroup favoritism increase with time and it is mediated by expectations of others' contributions + the increment is due to the change between ingroup and outgroup as interaction partners, it is not gradual
+@Jackson2011 + @Jackson2012: group performance and group identity on cooperation
+@Nockur2020: positive effect of intergroup competition (but not of dispositional competitiveness) on cooperation in social dilemmas
+@Kramer1984: a superordinate identity enhances cooperation
 
 @Bardsley2005: paper about conformity (see if it can be useful in this section)   
+@Torsvik2011: group identity as mediator of anticipating a discussion (see if useful or not to add it here)
 
-#D
+#Discussion
 

### 2023-09-12 paper1_markdown.Rmd
12.09: first version of the "group identity" section

--- 2023-09-11 paper1_markdown.Rmd
@@
 keywords          : "cooperation, social dilemmas, commons"
-#wordcount         : ""
+wordcount         : ""
 
@@
 output            : papaja::apa6_word
+#bibliography: references.bib
 ---
@@
 
+@Torsvik2011: in the introduction says that people in social dilemma are confused and can make random choices = argument against the completely rational human (see wich papers they cited)
+
 **???
@@
 **\<- EXPLAIN BETTER!!!**
+
+-   @Kramer1984: see the phrases underlined in the introduction
 
@@
 One of the most observed moderator of this effect is the interaction partners.
-In fact, in a social dilemma experiment, women are more cooperative toward strangers than men are, while men cooperate more in a group of friends.
+In fact, in a social dilemma experiment, women were more cooperative toward strangers than men, while men cooperated more in a group of friends.
 Moreover, after a socialization phase where strangers could interact, men cooperated more than women [@Peshkovskaya2017].
@@
 
-@Gomez-Ruiz2020: even if study about gender differences, they found a main effect of team identity on cooperation
-@Arora2016: baseline = reciprocity: participants respond with defection to defection and with cooperation to cooperation, but in-group identification can change this --> main effect of identification on cooperation
-faced to an in-group defector, high identifiers cooperate more than low (no difference between high and low when the partner cooperates) = compensation + this compensation comes with lower trust toward the partner who defected, so the cooperation is not driven by in-group favoritism
-@Torsvik2011: group identity as mediator of anticipating a discussion (see if useful or not to add it here)
-@VanVugt2009: mention that it happens that high-identifying members compensate for free-riders + when people identify with a social group the are more concerned about their in-group reputation
-boost of social identity through inducing competition between groups, but not helpful --> promote a superordinate social identity
-group member that strongly identify with their community do not need an economic incentive to cooperate
-@Puurtinen2009: between group competition enhances cooperation (even between unrelated individuals) by aligning individual and group interest --> investements in public good higher in the group competition vs normal condition + in the group competition there was more anger toward in-group free-rider and guilt toward its own lack of cooperation --> ingroup identification can be enhanced via intergroup competition
-@Noonan2016: study about commons = dog parks --> "having a strong sens of community is related to increased voluntarism" + re-read to see if others parts could be interesting
-@Zhang2019: collective risk as operationalization of group identity: (1) cooperation decreased with time when the risk was individual, but not when it was collective; (2) beliefs about others' cooperation formed similarly under the two conditions = these beliefs are interpreted in a different way according to the condition
-@Dorrough2015: ingroup favoritism increase with time and it is mediated by expectations of others' contributions + the increment is due to the change between ingroup and outgroup as interaction partners, it is not gradual
+Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group (e.g.
+@Arora2016; @Noonan2016; @Gomez-Ruiz2020).
+For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions.
+This is explained by the fact that, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016].
+A strong social identity also maintains a high level of cooperation over time [@Zhang2019].
+Moreover, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015].
 
-@Bardsley2005: paper about conformity (see if it can be useful in this section)
+However, the fact that not all members identify with their group to the same extent can lead to inequalities on cooperation.
+For example, @VanVugt2009 mentioned that high identified individual can even compensate, by cooperating more, for other in-group members' defection.
+The same result was also found by @Arora2016: high identified individuals cooperated more than low identified ones when faced to an in-group participant who defected (this difference was not found when the defector was not a group member).
+However, this compensation came with a cost, since participants who compensated for an in-group defector reported lower trust toward this person.
 
-#D
+Another well replicated result is the positive effect of intergroup competition on intragroup cooperation.
+In fact, in-group identification can be enhanced via a competition between different groups because in such a context individual's and group's interests are aligned [@Puurtinen2009].
+In a social dilemma experiment, these authors demonstrated that cooperation was higher in an intergroup-competition condition than in a non-competitive condition.
+Moreover, when participants had to compete against other groups, they reported higher levels of anger toward in-group free-riders and they felt more guilty after a defection decision.
+In another experiment, intergroup competition reduced resources consumption (and therefore enhanced cooperation), while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
+This shows that the increase of cooperation via competition is due to group membership factors, and not to competition per se.
+
+However, despite the observed beneficial effects of inducing an intergroup competition, in a real-life situation this could be harmful.
+This is especially true in case of resources that are shared between several groups, which are at greater risk of over-exploitation in case of intergroup competition [@VanVugt2009].
+A possible solution to maintain the positive effects of group identification, while eliminating the risk of over-exploitation caused by intergroup competition, is to prime a superordinate identity [@VanVugt2009].
+In fact, intergroup cooperation can be enhanced by making salient the common characteristics of the different groups, instead of their differences [@Kramer1984].
+Another effective way to create a superordinate identity is to induce the feeling of a common fate, for example through a collective risk.
+In fact, a common fate allows a group to become real [@Zhang2019], and can therefore erase intergroup competition.
+
+Finally, social identity does not only have a main effect on people's cooperation, but can also moderate other factors' impact.
+For example, monetary incentive are more effective at enhancing cooperation of low identified individual than of high identified ones [@VanVugt2009].
+Moreover, a previous group failure can decrease cooperation between low identified member, but this effect is not observed in people who have a strong identification with their group [@Jackson2011; @Jackson2012].
+
+In general, social identity seems to have a positive and largely observed effect on individuals' cooperation.
+This is due to the fact that humans have a very developed sense of belonging to social groups, and that this has an impact on their willingness to help other members of their group [@VanVugt].
+Since priming a common social identity is quite simple (e.g.
+@Kramer1984; @Zhang2019), this could be a very powerful method to enhance cooperation in an easy and cheap way.
+
+# Discussion
 

### 2023-09-12 paper1_markdown.Rmd
final version 12.09

@@
 @Torsvik2011: in the introduction says that people in social dilemma are confused and can make random choices = argument against the completely rational human (see wich papers they cited)
+doi:10.1098/rstb.2010.0135: in the introduction they cite papers that have observed cooperation
 
@@
 A strong social identity also maintains a high level of cooperation over time [@Zhang2019].
-Moreover, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015].
+Moreover, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].
 
@@
 Since priming a common social identity is quite simple (e.g.
-@Kramer1984; @Zhang2019), this could be a very powerful method to enhance cooperation in an easy and cheap way.
+@Kramer1984; @Zhang2019), this could be a very powerful technique to enhance cooperation in an easy and cheap way.
+
+## Personal values and attitudes
+
+@Kieslich2014: HEXACO factor Humility Honesty predicts cooperation
+@Emonds2011: interaction pro-self/pro-social x type of game
+@Liu2009: independent vs interdependent self
+@Probst1999: different patterns of cooperation based on culture (vertical individualist, vertical collectivist, HI, HC)
 

### 2023-09-13 paper1_markdown.Rmd
13.09

@@
 
++ @VanLange1998: many behaviours that tend to serve our personal well-being are detrimental to the environment
+
 @Jackson2012: according to economist, cooperation is an irrational response in social dilemmas (see the articles that he cites)
@@
 (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
++ @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited)
 e.
@@
 
+Personality plays a substantial role in predicting cooperation [@Hilbig2018]
+
 @Kieslich2014: HEXACO factor Humility Honesty predicts cooperation
+  @Hilbig2018: this link is explained by greed (temptation to exploit others' cooperation)
 @Emonds2011: interaction pro-self/pro-social x type of game
-@Liu2009: independent vs interdependent self
+@Liu2009a: independent vs interdependent self
 @Probst1999: different patterns of cooperation based on culture (vertical individualist, vertical collectivist, HI, HC)
+@Sussman2016: pro-env values predict less harvesting only when a resource is scarce
+@VanLange1998: field study on commuting --> proself accord more importance to the perceived efficacy of the behaviour (= personal well-being) than prosocial + prosocial with high trust expressed significantly more preference for a common transport/carpooling than the other three groups
+@DeKwaadsteniet2008: interaction between group size (un)certainity and SVO, and the self-restraining effect observed in prosocial under uncertainity condition is explained by the motive to have a maximal joint outcome (but not by equality, even if this motive is more important for prosocial than proself)
+@Balliet2009: meta-analysis: SVO has a general positive effect on cooperation + 2 mediators = paid vs unpaid (in unpaid situations SVO effect was stronger) and take-some vs give-some dilemmas (in give-some SVO effect was stronger)
+@Kocher2017: self control and risk aversion impact cooperation
 
 # Discussion
+
+observation: majority of papers included are about SD, and very few studies about commons are quantitative --> future research: quantitative approach to investigate cooperation in common initiatives
 

### 2023-09-14 paper1_markdown.Rmd
14.09

--- 2023-09-12 paper1_markdown.Rmd
@@
 
-@Torsvik2011: in the introduction says that people in social dilemma are confused and can make random choices = argument against the completely rational human (see wich papers they cited)
+@Torsvik2011: in the introduction says that people in social dilemma are confused and can make random choices = argument against the completely rational human (see wich papers they cited) <doi:10.1098/rstb.2010.0135>: in the introduction they cite papers that have observed cooperation
 
@@
 
+-   @VanLange1998: many behaviours that tend to serve our personal well-being are detrimental to the environment
+
 @Jackson2012: according to economist, cooperation is an irrational response in social dilemmas (see the articles that he cites)
@@
 (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
+
+-   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited)
+
 e.
@@
 A strong social identity also maintains a high level of cooperation over time [@Zhang2019].
-Moreover, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015].
+Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect.
+Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].
 
@@
 For example, @VanVugt2009 mentioned that high identified individual can even compensate, by cooperating more, for other in-group members' defection.
-The same result was also found by @Arora2016: high identified individuals cooperated more than low identified ones when faced to an in-group participant who defected (this difference was not found when the defector was not a group member).
+The same result was also found by @Arora2016: high identified individuals cooperated more than low identified ones when faced to an in-group participant who defected (and this difference was not found when the defector was not a group member).
 However, this compensation came with a cost, since participants who compensated for an in-group defector reported lower trust toward this person.
@@
 Another well replicated result is the positive effect of intergroup competition on intragroup cooperation.
-In fact, in-group identification can be enhanced via a competition between different groups because in such a context individual's and group's interests are aligned [@Puurtinen2009].
+In fact, in-group identification can be enhanced via a competition between different groups, because in such a context individual's and group's interests are aligned [@Puurtinen2009].
 In a social dilemma experiment, these authors demonstrated that cooperation was higher in an intergroup-competition condition than in a non-competitive condition.
 Moreover, when participants had to compete against other groups, they reported higher levels of anger toward in-group free-riders and they felt more guilty after a defection decision.
-In another experiment, intergroup competition reduced resources consumption (and therefore enhanced cooperation), while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
+In another experiment using a public resource game, intergroup competition reduced resources consumption (and therefore enhanced cooperation), while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
 This shows that the increase of cooperation via competition is due to group membership factors, and not to competition per se.
@@
 This is especially true in case of resources that are shared between several groups, which are at greater risk of over-exploitation in case of intergroup competition [@VanVugt2009].
-A possible solution to maintain the positive effects of group identification, while eliminating the risk of over-exploitation caused by intergroup competition, is to prime a superordinate identity [@VanVugt2009].
+A possible solution to maintain the positive effects of group identification, while eliminating the risk of over-exploitation caused by the competitive context, is to prime a superordinate identity [@VanVugt2009].
 In fact, intergroup cooperation can be enhanced by making salient the common characteristics of the different groups, instead of their differences [@Kramer1984].
@@
 In general, social identity seems to have a positive and largely observed effect on individuals' cooperation.
-This is due to the fact that humans have a very developed sense of belonging to social groups, and that this has an impact on their willingness to help other members of their group [@VanVugt].
+This is due to the fact that humans have a very developed sense of belonging to social groups, and that this has an impact on their willingness to help other members of their group [@VanVugt2009].
 Since priming a common social identity is quite simple (e.g.
-@Kramer1984; @Zhang2019), this could be a very powerful method to enhance cooperation in an easy and cheap way.
+@Kramer1984; @Zhang2019), this could be a very powerful technique to enhance cooperation in an easy and cheap way.
+
+## Values and personality traits
+
+Personal values and personality traits can play an important role in predicting cooperative behaviour [@Hilbig2018].
+One of the most studied is the Social Value Orientation (SVO), that divides people in pro-social and pro-self based on how much they value their own and others' outcomes in situations of interdependence [@Balliet2009].
+The effect of SVO on cooperation is very consensual: in a meta-analysis, 81 out of the 82 papers examined reported than pro-social cooperated significantly more that pro-self [@Balliet2009].
+
+However, this general effect is subjected to several moderators.
+For example, pro-self individuals cooperated more in a game where incentives to cooperation were present than in a game without such incentives, while pro-social did not displayed this difference and showed high levels of cooperation in both contexts [@Emonds2011].
+A similar effect is also described by @Balliet2009, who found a stronger effect of SVO in unpaid games than in paid ones, because, when monetary rewards were present, pro-self increased their cooperation.
+Therefore, pro-self individuals also cooperate, but only when cooperation serves their personal interest.
+In fact, in a study about commuting habits, the extent to which the cooperative behaviour (i.e.
+choosing to commute by public transportation or carpooling) was perceived as efficient impacted pro-self individual's decision more than pro-social's [@VanLange1998].
+
+Moreover, SVO has a stronger effect if there is an uncertainty about the number of individuals having access to a common resource: when the number of other participants was not known, pro-social, but not pro-self, reduced their harvesting comparing to a group-size certainty condition [@DeKwaadsteniet2008].
+The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self only think at their own personal interest.
+Finally, SVO effect is partly explained by trust, i.e.
+the extent to which people think that their interaction partners will also cooperate.
+In fact, in @VanLange1998, pro-social individuals with a low level of trust did not make different decisions than pro-self individuals, while the most cooperative were pro-social with an high level of trust.
+
+Other studies also focused on how much people are self- or social-oriented by using other constructs.
+For example, @Liu2009a demonstrated that priming a common fate to induce a context of interdependence significantly increased the cooperation level of participants with an independent self, but had no effect on participants with an interdependent self (who already displayed high levels of cooperation).
+Moreover, in a social dilemma experiment, competitive, individualistic people were motivated just by personal gain, while people who saw themselves as a part of a group were more interested on maximizing the income of each member, even at the cost to have a smaller personal payoff [@Probst1999].
+Also, high allocentric (i.e collectivist) individuals cooperated more than low allocentric ones when the perceived social norms are cooperative: this means that they are more sensitive to social cues and therefore they adapt their behaviour to social norms [@Chen2007].
+
+Finally, there are other personal values and traits that can affect cooperation.
+For example, pro-environmental values are negatively correlated with harvesting from a common resource, but only when the resource is scarce; therefore these values are more likely to motivate difficult, rather than easy, ecological behaviours [@Sussman2016].
+Levels of harvesting from a common resource are also lower between left-wingers than right-wingers [@Fosgaard2019].
+Moreover, humility and honesty are significant predictor of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018].
+Lastly, self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017].
+
+In conclusion, values and personality traits have a large impact on human cooperation, and it is thus very important to take them into account when investigating this phenomenon.
+Interestingly, some social psychological techniques (e.g.
+elaboration) allow to modify an individual's values [@Sussman2016].
+Such techniques could therefore be used to improve cooperation.
 
 # Discussion
+
+observation: majority of papers included are about SD, and very few studies about commons are quantitative --\> future research: quantitative approach to investigate cooperation in common initiatives
 

### 2023-09-18 paper1_markdown.Rmd
18.09 version

@@
 
+introduction of the societal problem = cooperation (= renonce to the individual most advantageous choice for the common good) is the key to resolve many societal problems (e.g.
+covid vaccination, climate change)
+
 Classical economic theories have described human being as "homo economicus".
@@
 A third example of real-life social dilemmas are commons.
+(**USE THIS AT THE VERY BEGINNING TO INTRODUCE THE SOCIETAL PROBLEM?**)
 
@@
 This allows us to have an idea as complete as possible about the existing literature on cooperation in commons and social dilemmas.
-Moreover, there were not chronological or geographical limitations, once again to provide a broader vision on the topic.
+Moreover, there were not chronological or geographical limitations, once again to provide a broader vision of the topic.
 There were however some selection criteria concerning the papers' content.
@@
 
-Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group (e.g.
-@Arora2016; @Noonan2016; @Gomez-Ruiz2020).
+Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group [e.g.
+@Arora2016; @Noonan2016; @Gomez-Ruiz2020].
 For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions.
@@
 Moreover, when participants had to compete against other groups, they reported higher levels of anger toward in-group free-riders and they felt more guilty after a defection decision.
-In another experiment using a public resource game, intergroup competition reduced resources consumption (and therefore enhanced cooperation), while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
+In another experiment using a public resource game, intergroup competition reduced resources consumption, while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
 This shows that the increase of cooperation via competition is due to group membership factors, and not to competition per se.
@@
 
+## Social status???
+
+retrieve work on gender that says that gender effects are probably in part impacted by status?
+
+# Group factors
+
+## Reward and punishment
+
+Possible introduction: Incentives are divided in reward and punishments.
+Punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2016].
+The positive effect of punishment in promoting cooperation is well confirmed ...
+
+On the other side, results about rewarding are not so consensual ...
+
+@Chen2022: reward, but not punishment, increased cooperation in the following round for both high and low benefit members
+
+@Nockur2021: punishment (three different types) increase cooperation + the presence of a punishment system increased the perception of fairness + satisfaction was higher in peer and democratic punishment than in centralized and no punishment condition
+
+@Kingsley2016: the possibility of punish others increased the cooperation in homogeneous groups (= where all members started with the same endowment), but not in heterogeneous groups
+
+@Milinski2012: punishment is worthy on the long run (straight after, the ones who punished are the ones with the lowest income) + reward is less efficient than punishment (punish: at the beginning, to establish cooperation, reward is a cost all along because once cooperation is established you always have to continue rewarding it) + punishment can however entail a second-order social dilemma (defection = do not punish but having advantages for the fact that everybody cooperates thanks to punishers)
+
+@Xiao2016: higher cooperation if only the cooperator can punish the defector (vs everybody can punish), and in particular for deterministic (vs stochastic) game\
+when both can punish, anti-social punishment is present --\> effect = a person who cooperated and received a punishment in t is less likely to cooperate in t+1 (proportional)\
+in stochastic games, the occurrence of a negative event is not a predictor for punishing (= based on other's defection, independently of the outcome)\
+punishment of non-investor is smaller in stochastic (vs deterministic) games
+
+@Balliet2011a: PUN: positive effect on cooperation in social dilemmas\
+stronger if the punishment was costly (vs free)\
+stronger if decentralized (vs centralized)\
+stronger if SD with partners (vs strangers)\
+stronger if iterated (vs one-shot)\
+REWARD: positive effect on cooperation in social dilemmas\
+stronger if costly vs free\
+no effect of de-centralized\
+stronger if iterated (vs one-shot)\
+stronger in the resource dilemma (vs public good or prisoner dilemma)\
+OVERALL: no difference on the strength of these effects
+
+@Jacquet2011: the expectation of honour and shame enhance cooperation
+
+@Rockenbach2019: successful groups punish, but with caution and not in early stages (see Excel for more results)
+
+@VanDijk2016: results are both in the introduction and result case
+
+exclusion as a form of punishment
+
+## Communication
+
+## Group size
+
+## Social Norms
+
 # Discussion

### 2023-09-21 paper1_markdown.Rmd
Update paper1_markdown.Rmd
change intro

@@
 
+Many societal problems that humans are facing nowadays are social dilemmas, i.
+e.
+situations in which short-term individual and long-term collective interests are at odds [@Hardin1968].
+More specifically, independently of others' actions, every individual obtains a better individual payoff by acting in an egoistic, non-cooperative way.
+However, if everybody did so, the worst possible outcome is obtained ????
+
+where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980].
+
+Reaching a better understanding of mechanism underlying cooperation in social dilemmas is even more important when considering that many everyday situations have a social dilemma structure.
+An example is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous than acting without worrying about environment [@Griskevicius2010].
+However, if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic.
+Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody pays it, then public television will stop existing.
++ @Kollock1998: page 183, many of the problems that we face are, at their core, social dilemmas.
+A third example of real-life social dilemmas are commons.
+(**USE THIS AT THE VERY BEGINNING TO INTRODUCE THE SOCIETAL PROBLEM?**)
+
 introduction of the societal problem = cooperation (= renonce to the individual most advantageous choice for the common good) is the key to resolve many societal problems (e.g.
@@
 
-**???
-CONNECTING ALTRUISM WITH COOPERATION ???** Cooperation = sacrificing for the grater good at a personal cost (Kollock, 1998) The study of cooperation is particularly interesting in social dilemmas, i.
-e.
-situations in which short-term individual and long-term collective interests are at odds [@Hardin1968].
-add Dawes' definition
-
-where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980].
-**\<- EXPLAIN BETTER!!!**
+**??? CONNECTING ALTRUISM WITH COOPERATION ???** Cooperation = sacrificing for the grater good at a personal cost (Kollock, 1998)  **\<- EXPLAIN BETTER!!!**
 
@@
 -   cooperation even more fragile when scarce resources (De Luca et al.) =\> importance of understanding it
-
-Reaching a better understanding of mechanism underlying cooperation in social dilemmas is even more important when considering that many everyday situations have a social dilemma structure.
-An example is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous than acting without worrying about environment [@Griskevicius2010].
-However, if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic.
-Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody pays it, then public television will stop existing.
-+ @Kollock1998: page 183, many of the problems that we face are, at their core, social dilemmas.
-A third example of real-life social dilemmas are commons.
-(**USE THIS AT THE VERY BEGINNING TO INTRODUCE THE SOCIETAL PROBLEM?**)
 

### 2023-09-21 paper1_markdown.Rmd
Update paper1_markdown.Rmd
21.09

--- 2023-09-18 paper1_markdown.Rmd
@@
 
-introduction of the societal problem = cooperation (= renonce to the individual most advantageous choice for the common good) is the key to resolve many societal problems (e.g.
-covid vaccination, climate change)
+Many societal problems that humans are facing nowadays have a social dilemma structure [@Kollock1998], i.
+e.
+they are situations in which short-term, individual interests are at odds with long-term, collective ones [@Hardin1968].
+More specifically, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
+However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
+
+An example of real-life social dilemma is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous than acting without worrying about environment [@Griskevicius2010].
+However, since behaviours that serve our personal well-being tend to be detrimental to the environment [@VanLange1998], if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic.
+Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody paid it, public television would no longer exist.
+Cooperation (i.e.
+sacrificing for the grater good at a personal cost, [@Kollock1998]) is therefore essential to avoid the worst collective outcome in social dilemma situations, and that is why a deep comprehension of this phenomenon is needed.
 
@@
 This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954].
-Therefore, according to these theories, human beings are not supposed to show altruistic behaviours, i.e.
+Therefore, according to these theories, individuals are not supposed to show altruistic behaviours, i.e.
 behaviours that involve costs for the self while benefiting others [@Wittek2015].
-However, prosocial acts are often observed in human interactions (**FIND REFERENCES**), and many theories have been developed to explain them.
-An example is the theory of competitive altruism [@Roberts1998], that says that acting for the good of others could be a signal of a person's prosociality and therefore improve this person's reputation.
-Moreover, in the evolutionary perspective, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
-Adding something on cooperation norms?
-Maybe this could be the link between altruism and cooperation?
-See also the article in Zotero that says that altruism is one of the seven forms that cooperation could have, so maybe is it better to talk about cooperation from the beginning???
+Instead, the evolutionary perspective suggests that individuals can cooperate when doing so bring them a personal advantage.
+For example, the theory of competitive altruism [@Roberts1998] says that acting for the others' good could be a signal of a person's prosociality, and therefore improve this person's reputation.
+Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
+In sum, according to economic and evolutionary theories, individuals are always pursuing their self-interest.
 
-@Torsvik2011: in the introduction says that people in social dilemma are confused and can make random choices = argument against the completely rational human (see wich papers they cited) <doi:10.1098/rstb.2010.0135>: in the introduction they cite papers that have observed cooperation
+However, in social dilemma experiments, a significant amount of people are "strong reciprocators": they are willing to use their personal resources to "be kind to those who are being kind and to punish those who are being unkind", even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009].
+This shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare[@Torsvik2011; @VanVugt2009].
+In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational cooperative or non-cooperative decision.
+In fact, cooperation seems to be the intuitive option in social dilemma experiments, while defection needs more thinking [@Kieslich2014].
+Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995].
+Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [@VanLange2013].
 
-**???
-CONNECTING ALTRUISM WITH COOPERATION ???** Cooperation = sacrificing for the grater good at a personal cost (Kollock, 1998) The study of cooperation is particularly interesting in social dilemmas, i.
-e.
-situations in which short-term individual and long-term collective interests are at odds [@Hardin1968].
-add Dawes' definition
+## Commons as social dilemmas
 
-where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980].
-**\<- EXPLAIN BETTER!!!**
+Commons are a very specific kind of social dilemma.
+**FIND A DEFINITION (lol) that shows the similarity with social dilemmas (common resource, ...) !!** + Since, as in social dilemmas, a conflict between individual and collective interest is present @Sussman2016 used the term of "commons dilemmas" to speak about commons.
 
--   @Kramer1984: see the phrases underlined in the introduction
+Predictions about cooperations in commons are also similar to the social dilemma context: according to @Hardin1968 and his "Tragedy of the Commons", since individuals are likely to maximize their individual gain, commons are inevitably destined to failure due to the over exploitation of resources.
+However, successfully managed commons are often observed [e.g.
+@Ostrom1990] and, as discussed in the previous section, human beings are not motivated just by their personal interests.
 
-Thus, the most rational behaviour for everyone would be to defect, because it would ensure the maximum outcome independently of other individuals' choices.
-ADD NASH EQUILIBRIUM???
-(@Colman2018 = at page 2 good definition of Nash) However, as with altruism, cooperative decisions are often made in social dilemmas, showing that human beings are not always rational in the economic, individual sense [@Kollock1998] and that there are multiple factors that can influence people's decisions in such situations (see for example @VanLange2013 for a review).
+@Reindl2019: cooperation and defection in lab experiments are predictive of behaviours in a real public good (where individuals have to give resources to contribute to a public good)
 
-b.  Moreover, some studies consider cooperation to be the intuitive option, while defection needs more thinking (Kieslich & Hilbig, 2014)
-c.  A deeper understanding of mechanisms underlying cooperation in social dilemma is therefore necessary
-
--   cooperation even more fragile when scarce resources (De Luca et al.) =\> importance of understanding it
-
-Reaching a better understanding of mechanism underlying cooperation in social dilemmas is even more important when considering that many everyday situations have a social dilemma structure.
-An example is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous than acting without worrying about environment [@Griskevicius2010].
-However, if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic.
-Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody pays it, then public television will stop existing.
-+ @Kollock1998: page 183, many of the problems that we face are, at their core, social dilemmas.
-A third example of real-life social dilemmas are commons.
-(**USE THIS AT THE VERY BEGINNING TO INTRODUCE THE SOCIETAL PROBLEM?**)
-
--   @VanLange1998: many behaviours that tend to serve our personal well-being are detrimental to the environment
-
-@Jackson2012: according to economist, cooperation is an irrational response in social dilemmas (see the articles that he cites)
-
--   This is even more important if we consider the practical implication that social dilemmas have in our society: social dilemmas could be translated into commons
-
-a.  Climate change as social dilemmas
-b.  Definition of commons  commons as social dilemmas
-c.  Article that says that social dilemmas are not the same as commons (Cole & Grossman, 2010)
-d.
-But: Reindl et al.
+-   But: Reindl et al.
 (2019) and Rommel et al.
@@
 
--   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited)
-
-e.
-Existing theory about the commons = similar structure than for social dilemmas: rational human beings are supposed to fail (TOC, Hardin, 1986), but in reality cooperation is often observed (for example Ostrom, 1990 + find others)
-
+```{=html}
+<!-- -->
+```
+-   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
 -   Importance of commons: Pacheco et al.
 (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons
+
+@Pacheco2014: "global coordination for a common good should be attempted by segmenting tasks in many small to medium sized groups, in which perception of risk is high and uncertainty in collective goals is minimized"
+
+ideal = decentralized agreements between smaller groups, possibly focused on regional issues are prone to significantly raise the probability of success in coordinating to tame the planet's climate
+
 -   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of group organization groups can set to improve a cooperation of all members
@@
 a.  ?? Is it to mention that I focus on what a group can do, without focusing on how external institutions can influence cooperation?? If so, see @Larsson2016
-
--   Research questions (see if not too redundant with the previous phrase)
-
--   introducing free-riding and defection concept somewhere (see @Gomez-Ruiz2020 introduction for free-riding)
+b.
 
@@
 To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect.
-The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust" **, "intergroup"**, and they were paired with "AND" and "OR" Boolean operators.
+The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust", and they were paired with "AND" and "OR" Boolean operators.
 The research was made during the month of August, 2023.
@@
 This allows us to have an idea as complete as possible about the existing literature on cooperation in commons and social dilemmas.
-Moreover, there were not chronological or geographical limitations, once again to provide a broader vision of the topic.
+Moreover, there was any chronological or geographical limitation, once again to provide a broader vision of the topic.
 There were however some selection criteria concerning the papers' content.
@@
 Possible introduction: Incentives are divided in reward and punishments.
-Punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2016].
+Punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015].
 The positive effect of punishment in promoting cooperation is well confirmed ...
@@
 
-@VanDijk2016: results are both in the introduction and result case
+@VanDijk2015: results are both in the introduction and result case
 

### 2023-09-22 paper1_markdown.Rmd
22.09

@@
 (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
-
-```{=html}
-<!-- -->
-```
 -   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
@@
 
-## Reward and punishment
+## Incentives
 
-Possible introduction: Incentives are divided in reward and punishments.
-Punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015].
-The positive effect of punishment in promoting cooperation is well confirmed ...
+Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^1].
+In the litterature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
+In general, when there is the possibility for participants to punish others members based on their contributions, cooperation is higher than when this is not possible [e.g.
+@Pfattheicher2018; @Balliet2011a].
 
-On the other side, results about rewarding are not so consensual ...
+[^1]: Since the present paper's interest is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
 
-@Chen2022: reward, but not punishment, increased cooperation in the following round for both high and low benefit members
+However, this main results is subjected to several moderator factors.
+First, the punishment have a bigger impact on cooperation if its implementation is costly for the punishers than if it is free [@Balliet2011a], but at the same time the cost should not be too high [@Egas2008].
+Moreover, punishments are more effective if the interaction is among friends than among strangers, and if people know that they will have to interact repeatedly with each other [@Balliet2011a].
+Also, an experiment showed that a punishment system increased cooperation in groups where all members had the same amount of resources, but not in groups where income was heterogeneous [@Kingsley2016].
+To add: @Chen2022 low members do not punish others low members --\> solidarity that encourages free-riding??
 
-@Nockur2021: punishment (three different types) increase cooperation + the presence of a punishment system increased the perception of fairness + satisfaction was higher in peer and democratic punishment than in centralized and no punishment condition
+moderators:
 
-@Kingsley2016: the possibility of punish others increased the cooperation in homogeneous groups (= where all members started with the same endowment), but not in heterogeneous groups
-
-@Milinski2012: punishment is worthy on the long run (straight after, the ones who punished are the ones with the lowest income) + reward is less efficient than punishment (punish: at the beginning, to establish cooperation, reward is a cost all along because once cooperation is established you always have to continue rewarding it) + punishment can however entail a second-order social dilemma (defection = do not punish but having advantages for the fact that everybody cooperates thanks to punishers)
+@Egas2008: punishment must be not too costly and highly effective
 
@@
 
-@Balliet2011a: PUN: positive effect on cooperation in social dilemmas\
-stronger if the punishment was costly (vs free)\
-stronger if decentralized (vs centralized)\
-stronger if SD with partners (vs strangers)\
-stronger if iterated (vs one-shot)\
+after the moderators: say that we must be cautious and cite rockenbach + cite the problems
+
+@Rockenbach2019: successful groups punish, but with caution and not in early stages (see Excel for more results)
+
+problem:
+
+-   second order social dilemma @Milinski2012
+
+-   anti social punishment
+
+solution = democratic, rather than peer, punishment: @Nockur2021: punishment (three different types) increase cooperation + the presence of a punishment system increased the perception of fairness + satisfaction was higher in peer and democratic punishment than in centralized and no punishment condition
+
+However, a system in which every individual has the possibility to assign a punishment to others can entail a second-order social dilemma [@Milinski2012], since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators
+
+@Milinski2012: punishment is worthy on the long run (straight after, the ones who punished are the ones with the lowest income) + punishment can however entail a second-order social dilemma (defection = do not punish but having advantages for the fact that everybody cooperates thanks to punishers)
+
+On the other side, results about rewarding are not so consensual ...
+
+@Chen2022: reward, but not punishment, increased cooperation in the following round for both high and low benefit members
+
+@Milinski2012:  + reward is less efficient than punishment (punish: at the beginning, to establish cooperation, reward is a cost all along because once cooperation is established you always have to continue rewarding it)
+
+@Balliet2011a: \
 REWARD: positive effect on cooperation in social dilemmas\
@@
 
-@Jacquet2011: the expectation of honour and shame enhance cooperation
-
-@Rockenbach2019: successful groups punish, but with caution and not in early stages (see Excel for more results)
-
 @VanDijk2015: results are both in the introduction and result case
 
+@Pfattheicher2018: democratic (vs peer) punishment showed lower punishment level, less antisocial punishment and higher final payoff and higher cooperation levels + the payoff was highest in a control condition, so higher cooperation cannot fully compensate punishment cost (although democratic could be worthy on the long run)
+
+@Irwin2014: punishment and reward have detrimental effects on cooperation + trust
+
 exclusion as a form of punishment
+
+@Nelissen2013: social punishment = disapproval is better than financial because cooperation rates do not drop after the removal
+
+@Jacquet2011: the expectation of honour and shame enhance cooperation
 

### 2023-09-25 paper1_markdown.Rmd
25.09

@@
 This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954].
-Therefore, according to these theories, individuals are not supposed to show altruistic behaviours, i.e.
-behaviours that involve costs for the self while benefiting others [@Wittek2015].
+Therefore, according to these theories, individuals are not supposed to show altruistic behaviours, defined as behaviours that involve costs for the self while benefiting others [@Wittek2015].
 Instead, the evolutionary perspective suggests that individuals can cooperate when doing so bring them a personal advantage.
@@
 Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995].
-Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [@VanLange2013].
+Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].
 
@@
 
+## Belief
+
 # Group factors
@@
 @Pfattheicher2018; @Balliet2011a].
+Moreover, the presence of a punishment system increases the perception of fairness [@Nockur2021].
 
 [^1]: Since the present paper's interest is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
+Incentives given by third party have also an effect on cooperation, but they are not included in this review.
 
@@
 Moreover, punishments are more effective if the interaction is among friends than among strangers, and if people know that they will have to interact repeatedly with each other [@Balliet2011a].
+In fact, in short interactions, if punishment is costly, individuals who punish others are the ones with the lowest personal income [@Milinski2012], and this could discourage the application of the fine.
 Also, an experiment showed that a punishment system increased cooperation in groups where all members had the same amount of resources, but not in groups where income was heterogeneous [@Kingsley2016].
-To add: @Chen2022 low members do not punish others low members --\> solidarity that encourages free-riding??
+In fact, @Chen2022 found that, in groups where the initial endowment was heterogeneous, participants that received less didn't punish the others "low-status" members.
+This solidarity could therefore encourage free-riding.
+Moreover, the effect of punishment is stronger if only cooperators have the power to punish defectors, than if everybody can punish [@Xiao2016].
+Finally, a plain situation is also needed to have a stronger effect of punishment: the link between behaviour and outcome must be clear, without random factors affecting the final outcome [@Xiao2016], and the punishment must be highly effective [@Egas2008].
 
-moderators:
+However, punishment must be applied with carefulness: @Rockenbach2019 compared the punishment strategy of different groups, and found that the most successful ones (whose members had the highest payoff at the end of the experiment) punished with caution and not in early stages of the game.
+In these groups, a norm of when and how punishment should be applied seems to exist.
+Moreover, punishment can also have two main negative sides.
+First, it could entails a second-order social dilemma [@Milinski2012], since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators.
+Secondly, anti-social punishment can arise.
+This term refer to the punishment of cooperators by non-cooperators, and it is present when all participants can punish independently of their contributions [@Xiao2016].
+In this context, defectors can see cooperators as rule breakers, and anti-social punishment is a sort of retaliation [@VanDijk2015].
 
-@Egas2008: punishment must be not too costly and highly effective
+A possible solution could be to implement a system of democratic punishment, where a fine is given only if a majority of participants agree.
+In fact, compared to a peer punishment system where participants decide individually if and who punish, in a democratic system anti-social punishment is less present, general punishment level is lower, and final payoff and cooperation rates are higher [@Pfattheicher2018].
 
-@Xiao2016: higher cooperation if only the cooperator can punish the defector (vs everybody can punish), and in particular for deterministic (vs stochastic) game\
-when both can punish, anti-social punishment is present --\> effect = a person who cooperated and received a punishment in t is less likely to cooperate in t+1 (proportional)\
-in stochastic games, the occurrence of a negative event is not a predictor for punishing (= based on other's defection, independently of the outcome)\
-punishment of non-investor is smaller in stochastic (vs deterministic) games
+Rewarding systems, on the other side, are less investigated.
+Globally, they have a positive effect on cooperation[@Balliet2011a].
+However, some studies found that they were more efficient than punishment [e.g.
+@Chen2022], while others came to the opposite conclusion [e.g.
+@Milinski2012] or found no difference between the two systems [e.g.
+@Balliet2011a].
 
-after the moderators: say that we must be cautious and cite rockenbach + cite the problems
+In a meta-analysis, @Balliet2011a found that rewards had a stronger effect on cooperation if their implementation was costly rather than free, and in iterated, rather than single, interactions.
+Moreover, rewarding was more effective in situations where participants had to decide how much take from a common resource, compared to when they had to decide how much contribute to a common good.
 
-@Rockenbach2019: successful groups punish, but with caution and not in early stages (see Excel for more results)
+In general, incentives seem to be a powerful tool to enhance cooperation, but they have a dark side.
+In fact, they reduce participants' intrinsic motivation [@VadDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+Also, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members[@Irwin2014], and especially the trust in the fact that others are internally motivated to cooperate [@Mulder2006].
+Therefore, if incentives are removed, cooperation drops [@Irwin2014; @Mulder2006].
 
-problem:
+Finally, incentives are often studied in economic formats, but they can also be social.
+For example, the expectiation of honour or shame (after cooperating or defecting, respectively) is enough to enhance cooperation [@Jacquet2011].
+Moreover, expressing disapproval toward defectors can boost cooperation by inducing more compliance to the cooperative social norm [@Nelissen2013].
+Even an ostracism system where participants can vote to exclude other members from the game is very effective in increasing cooperation [@Jarungrattanapong2022].
+In general, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
 
--   second order social dilemma @Milinski2012
-
--   anti social punishment
-
-solution = democratic, rather than peer, punishment: @Nockur2021: punishment (three different types) increase cooperation + the presence of a punishment system increased the perception of fairness + satisfaction was higher in peer and democratic punishment than in centralized and no punishment condition
-
-However, a system in which every individual has the possibility to assign a punishment to others can entail a second-order social dilemma [@Milinski2012], since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators
-
-@Milinski2012: punishment is worthy on the long run (straight after, the ones who punished are the ones with the lowest income) + punishment can however entail a second-order social dilemma (defection = do not punish but having advantages for the fact that everybody cooperates thanks to punishers)
-
-On the other side, results about rewarding are not so consensual ...
-
-@Chen2022: reward, but not punishment, increased cooperation in the following round for both high and low benefit members
-
-@Milinski2012:  + reward is less efficient than punishment (punish: at the beginning, to establish cooperation, reward is a cost all along because once cooperation is established you always have to continue rewarding it)
-
-@Balliet2011a: \
-REWARD: positive effect on cooperation in social dilemmas\
-stronger if costly vs free\
-no effect of de-centralized\
-stronger if iterated (vs one-shot)\
-stronger in the resource dilemma (vs public good or prisoner dilemma)\
-OVERALL: no difference on the strength of these effects
-
-@VanDijk2015: results are both in the introduction and result case
-
-@Pfattheicher2018: democratic (vs peer) punishment showed lower punishment level, less antisocial punishment and higher final payoff and higher cooperation levels + the payoff was highest in a control condition, so higher cooperation cannot fully compensate punishment cost (although democratic could be worthy on the long run)
-
-@Irwin2014: punishment and reward have detrimental effects on cooperation + trust
-
-exclusion as a form of punishment
-
-@Nelissen2013: social punishment = disapproval is better than financial because cooperation rates do not drop after the removal
-
-@Jacquet2011: the expectation of honour and shame enhance cooperation
+To conclude, economic incentives can have a positive effect on cooperation, but their efficient implementation must be insured all along the interaction, otherwise cooperation rates would drop.
+On the other hand, social incentives seem to have the same positive effect, and their removal do not cause a reduction of cooperation.
+However, there is a lack of studies focusing on this kind of sanctions.
 
@@
 
-## Group size
+@Torsvik2011:
+
+opposite to hypothesis: anticipating a discussion reduced contributions to a public good (social norm enhanced by anticipating a discussion is probably one of conditional cooperation and not of inconditional cooperation =\> cond coop is also a moral norm)
+
+in a PGG, people are also confused and make random choice: forcing to think about a discussion lead them to reflect more on the situation and act more rational + if the norm is of conditional cooperation, then rational = do not cooperate
+
+study 2: if participants are told that they're part of a social group and that those who don't contribute are free-riders, anticipating a discussion increased contributions
+
+if a discussion is announced, labelling defectors as free-riders has a big impact = communicates that there is a normative expectation to cooperate, so so anticipating a discussion enhances a norm of unconditional cooperation
+
+@Balliet2010:
+
+\- overall strong and positive effect of communication on cooperation
+
+\- stronger effect for the talking (vs written) communication =\> more norms during face-to-face + nonverbal communication (video or phone calls also have this effect)
+
+\- no difference of the effect if the communication was prior (vs during) the game, both are effective: communication before can create a social norm of keeping promise that sustain cooperation even if the communication is interrupted
+
+\- communication has a stronger effect on bigger (vs smaller) groups: big group = less cooperation, communication buffers this negative effect + evolutionary theories = more efficient to send a generosity signal if many (vs few) others are present
+
+@Bicchieri2002: norms are more important than group identity to explain the benefits of communication on cooperation
+
+@Kumakawa2013: just knowing that ex-post communication will be possible does not affect cooperation, but receiving an actual feedback does + negative feedback increased cooperation, while positive ones had no effect
+
+@Feinberg2014: gossip increased cooperation, especially when ostracize a person based on gossip content was possible, by facilitating partner selection
+
+@Giardini2021: gossip can also be a way to increase own reputation (by telling the truth)
+
+@Adams2022: qualitative analysis of communication contents in social dilemma --\> see page 29 of the paper to see which contents are associated with (un)successful groups
+
+## Group size --\> link with anonymity?
 
 ## Social Norms
+
+## Commitment
 

### 2023-09-26 paper1_markdown.Rmd
26.09

@@
 
-@Torsvik2011:
+Communication has a global positive effect on cooperation [e.g.
+@Balliet2010; @Bicchieri2002], but this effect is subjected to several moderators.
+First, talking is more powerful than sending written messages, because it allows non-verbal communication and facilitates the social norms formation process.
+Moreover, communication's effect is stronger in large groups: when many people are present cooperation rates are lower, so communication between members can buffer this negative effect [@Balliet2010].
+Finally, if communicate with others requires a personal cost, the effect is weaker than if communication is free [@Janssen2014].
 
-opposite to hypothesis: anticipating a discussion reduced contributions to a public good (social norm enhanced by anticipating a discussion is probably one of conditional cooperation and not of inconditional cooperation =\> cond coop is also a moral norm)
+The content of the messages is also essential.
+@Koessler2021 identified four steps that need to be present when participants in a social dilemma situation communicate: problem awareness, identification of strategies, agreement and ratification.
+In another study, groups who used communication to foster a common social identity, promote cooperative social norms and ensure that all the players publicly committed displayed higher rates of cooperation than other groups [@Adams2022].
+However, casual chit-chat also plays a very important role in increasing cooperation [@Koessler2021].
+Also, the increase of cooperation through communication can be explained by the normative content that people are shaping while exchanging messages [@Janssen2014].
+Moreover, even if communication also helps to create a social identity, the effect of social norms is a stronger mediator of the link between communication and cooperation [@Bicchieri2002].
 
-in a PGG, people are also confused and make random choice: forcing to think about a discussion lead them to reflect more on the situation and act more rational + if the norm is of conditional cooperation, then rational = do not cooperate
+Another factor that influences the effect that communication has on cooperation is whether individuals exchange messages before, during or after the cooperative interaction phase.
+Concerning the post-game communication, @Kumakawa2013 found that receiving a feedback about the cooperation choice made previously can increase cooperation in the following interactions, especially if the feedback is negative.
+However, just the fact of knowing that a discussion will follow is not enough to enhance cooperation, and can even have a counterproductive effect, because forcing people to think about a future discussion make them reflect more on the situation and thus act more rationally [@Torsvik2011].
+On the other hand, communication before or during the interaction have both a positive impact on cooperation, and the difference between their effect is not significant [@Balliet2010].
 
-study 2: if participants are told that they're part of a social group and that those who don't contribute are free-riders, anticipating a discussion increased contributions
+Finally, several studies investigated the effect of gossip as a form of communication that can increase cooperation.
+Gossip is defined as a spread of reputational information about another person [@Feinberg2014], and it increases cooperation in two ways: first, if people know that gossip is possible, they tend to cooperate more to avoid the risk of being the target of such gossip and therefore of being excluded from following interactions.
+Secondly, having information about the past behaviour of potential cooperation partners can help to select the most cooperative people in an interaction situation [@Feinberg2014].
+Moreover, the same authors found that pro-social individuals gossiped more than pro-self.
+This shows that gossip can have the pro-social function of protecting others from a potential exploitation [@Feinberg2012].
+However, gossip has also some self-interest effects: for instance, observing another subject being exploited, and having the opportunity to gossip about the exploiter significantly reduced negative affects in @Feinberg2012 's participants.
+Moreover, providing correct information while gossiping helps to build a positive reputation [@Giardini2021].
 
-if a discussion is announced, labelling defectors as free-riders has a big impact = communicates that there is a normative expectation to cooperate, so so anticipating a discussion enhances a norm of unconditional cooperation
-
-@Balliet2010:
-
-\- overall strong and positive effect of communication on cooperation
-
-\- stronger effect for the talking (vs written) communication =\> more norms during face-to-face + nonverbal communication (video or phone calls also have this effect)
-
-\- no difference of the effect if the communication was prior (vs during) the game, both are effective: communication before can create a social norm of keeping promise that sustain cooperation even if the communication is interrupted
-
-\- communication has a stronger effect on bigger (vs smaller) groups: big group = less cooperation, communication buffers this negative effect + evolutionary theories = more efficient to send a generosity signal if many (vs few) others are present
-
-@Bicchieri2002: norms are more important than group identity to explain the benefits of communication on cooperation
-
-@Kumakawa2013: just knowing that ex-post communication will be possible does not affect cooperation, but receiving an actual feedback does + negative feedback increased cooperation, while positive ones had no effect
-
-@Feinberg2014: gossip increased cooperation, especially when ostracize a person based on gossip content was possible, by facilitating partner selection
-
-@Giardini2021: gossip can also be a way to increase own reputation (by telling the truth)
-
-@Adams2022: qualitative analysis of communication contents in social dilemma --\> see page 29 of the paper to see which contents are associated with (un)successful groups
+In conclusion, when people have the possibility to communicate before, during or after a cooperative interaction, the cooperation level increases.
+Even if the strength of this effect can vary depending on the situation, communication never seems to have a negative impact on cooperation.
 

### 2023-10-02 paper1_markdown.Rmd
02.10

@@
 
+what is the connection between commons and social dilemmas? --\> well argument
+
+paper goal?
+
+-   if commons --\> very important to make the link SD - commons: why social dilemma research could be useful for commons community
+
+-   if not commons --\> not so important
+
+-   commons are gaining always more interest because they could be a solution --\> start from this and then say that SD could be useful to understand + lack of quantitative studies about cooperation in commons
+
+-   discussion: critiques at SD because it is artificial, does not take into account all real-life factors --\> so it is good to keep it as a base, but investigations in commons are needed
+
 Many societal problems that humans are facing nowadays have a social dilemma structure [@Kollock1998], i.
@@
 they are situations in which short-term, individual interests are at odds with long-term, collective ones [@Hardin1968].
-More specifically, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
+More specifically, in such situations, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
 However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
 
-An example of real-life social dilemma is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous than acting without worrying about environment [@Griskevicius2010].
+An example of real-life social dilemma is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous for the self than acting without worrying about environment [@Griskevicius2010].
 However, since behaviours that serve our personal well-being tend to be detrimental to the environment [@VanLange1998], if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic.
@@
 Therefore, according to these theories, individuals are not supposed to show altruistic behaviours, defined as behaviours that involve costs for the self while benefiting others [@Wittek2015].
-Instead, the evolutionary perspective suggests that individuals can cooperate when doing so bring them a personal advantage.
-For example, the theory of competitive altruism [@Roberts1998] says that acting for the others' good could be a signal of a person's prosociality, and therefore improve this person's reputation.
+However, there are individual differences in the level of rationality, i.e.
+the ability to think analytically at the situation.
+@Lang2018 showed that individuals scoring low in rationality cooperated more than individuals with an high score.
+This shows that, when investigating a phenomenon like cooperation, individual differences must be taken into account.
+
+Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage.
+For example, the theory of competitive altruism [@Roberts1998] says that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation.
 Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
-In sum, according to economic and evolutionary theories, individuals are always pursuing their self-interest.
+@Vanvugt2010a confirmed this assumptions in a social dilemma setting, by showing that people contributed more to a public resource when their action was visible by others, even if the public good was already provided or unattainable.
+In lines with hypothesis, participants who wasted their resources in the public good were perceived with an higher social status.
+This means that cooperation can also serve a self-interested goal, by improving the reputation of cooperators.
 
+According to economic and evolutionary theories, individuals are always pursuing their self-interest, either by maximizing their personal payoff by defecting, either by cooperating to increase their social status and reputation.
 However, in social dilemma experiments, a significant amount of people are "strong reciprocators": they are willing to use their personal resources to "be kind to those who are being kind and to punish those who are being unkind", even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009].
 This shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare[@Torsvik2011; @VanVugt2009].
+GEF hypothesis: @VonBorgstede2018
+
 In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational cooperative or non-cooperative decision.
@@
 Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995].
+In fact, @Fosgaard2017 showed that, in public good games, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff.
+Moreover, these misperceptions can vary depending on how the game is presented.
+
 Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].
+Understanding how these different factors impact and shape cooperation is therefore essential to try to solve many of the societal problems that we are facing.
+**???**
 
@@
 (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
+-   @Ros-Galvez2015: those who donated more in a game are those who post more in an online forum (= cooperation)
 -   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
@@
 
--   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of group organization groups can set to improve a cooperation of all members
+-   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of organization groups can set to improve a cooperation of all members
 
@@
 Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect.
+Group identification can also esaily be implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992].
 Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].
@@
 However, this general effect is subjected to several moderators.
-For example, pro-self individuals cooperated more in a game where incentives to cooperation were present than in a game without such incentives, while pro-social did not displayed this difference and showed high levels of cooperation in both contexts [@Emonds2011].
+For example, pro-self individuals cooperated more in a game where economic incentives to cooperation were present than in a game without such incentives, while pro-social did not displayed this difference and showed high levels of cooperation in both contexts [@Emonds2011].
 A similar effect is also described by @Balliet2009, who found a stronger effect of SVO in unpaid games than in paid ones, because, when monetary rewards were present, pro-self increased their cooperation.
@@
 The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self only think at their own personal interest.
-Finally, SVO effect is partly explained by trust, i.e.
+Also, SVO effect is partly explained by trust, i.e.
 the extent to which people think that their interaction partners will also cooperate.
 In fact, in @VanLange1998, pro-social individuals with a low level of trust did not make different decisions than pro-self individuals, while the most cooperative were pro-social with an high level of trust.
+Finally, @Lu2019 showed that the intuitive choice of pro-social individuals is cooperation, while for pro-self is defection.
+However, pro-self can cooperate more if they have the possibility to deliberate about the situation, because they can realize that the best strategy to maximize the joint (and thus personal) outcome is cooperation.
 
@@
 Moreover, humility and honesty are significant predictor of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018].
-Lastly, self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017].
+Self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017].
+Lastly, people with an higher justice sensitivity make bigger contributions to a public good [@Schlosser2018].
 
@@
 In fact, they reduce participants' intrinsic motivation [@VadDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+In fact, @Schlosser2018 demonstrated that people's level of justice sensitivity could predict their contributions to a public good game, but this link disappeared when a punishment system was introduced.
 Also, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members[@Irwin2014], and especially the trust in the fact that others are internally motivated to cooperate [@Mulder2006].

### 2023-10-05 paper1_figures.Rmd
final numbers 04.10

@@
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
 
@@
 rec4 [label = 'Papers not suitable
-n = 4321']
+n = 4333']
 rec5 [label = 'Papers read completely
-n = 265']
+n = 253']
 rec6 [label = 'Papers not suitable
-n = YYY']
+n = 157']
 rec7 [label = 'Studies included
-n = XXX']
+n = 96']
 

### 2023-10-05 paper1_markdown.Rmd
05.10

@@
 ---
-title             : "Cooperation in commons and social dilemmas: A scoping review"
-shorttitle        : "Cooperation in commons and social dilemmas"
+title             : "Improving the understanding of cooperation in commons through social dilemmas' literature: A scoping review"
+shorttitle        : "Improving the understanding of cooperation in commons"
 
@@
 
+**once selected the journal, re-organize all the introduction!!!**
+
 what is the connection between commons and social dilemmas? --\> well argument
@@
 -   commons are gaining always more interest because they could be a solution --\> start from this and then say that SD could be useful to understand + lack of quantitative studies about cooperation in commons
+
+    -   to make the link: list of papers that studied a common in a social dilemma perspective (ex: Hartl & Hofmann, 2022)
 
@@
 
+@Franzen2019: example that commons can work (outlets in Swiss farms)
+
 @Reindl2019: cooperation and defection in lab experiments are predictive of behaviours in a real public good (where individuals have to give resources to contribute to a public good)
@@
 
+@Munn2018: reason to conduct a scoping review
+
 To conduct this scoping review, different papers published in academic journals were analyzed in response to the research questions.
@@
 After deleting the duplicates, the count was of 4586.
-Based on titles and abstracts, 4321 articles were eliminated, leaving 265 (**with emotions**) texts to examine.
-After a full-text evaluation of the remaining papers, XXX were selected for the present review.
+Based on titles and abstracts, 4321 articles were eliminated, leaving 253 texts to examine.
+After a full-text evaluation of the remaining papers, 92were selected for the present review.
 Figure 1 resumes this selection procedure.
@@
 ## Papers' description
+
+The included papers were published between 1984 and 2023, with a median of 2015.
+
+A majority of the studies was conducted in Europe (*N*=40) (especially in Germany (*N*=12) and in the Netherlands (*N*=9)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=10, of which *N*=7 in China).
+Moreover, *N*=7 studies were set in more than one country, and *N*=13 were meta-analysis or literature reviews.
+The two remaining studies took place in Australia and in Colombia, respectively.
+
+Almost all of the selected texts were journal articles. The only exceptions were a conference paper and a book chapter.
+
+still to do:
+
+-   main topic: social dilemma or commons? social dilemma to conceptualize a specific commons? social dilemma applied to real-life situations?
+
+-   methodology: lab vs meta-analysis vs review vs qualitative vs other?
 
@@
 The context in which men and women interact is therefore essential to predict if a gender will cooperate more than the other, and which one.
+
+## Social status
+
+Few studies have investigate how social status impact cooperation, and their results do not allow to draw a clear conclusion about this effect.
+
+For instance, advantaged members (i.e.
+high-status class) tended to cooperate less than disadvantaged ones [@Aksoy2019].
+In fact, when participants did not receive the same endowment at the beginning of the experiment, contributions of "rich" and "poor" members converged [@Kingsley2016].
+In other words, proportionally to their resources, low-status participants cooperated more.
+However, in their review, @VanLange2013 identified some studies that observed the opposite effect, namely that wealthier people (or those who benefitted more from a common resource) contributed more to the common good than the other.
+
+Social status can also create inter-class conflicts.
+In fact, people cooperated more with the members of the same social class than with other classes' members [@Aksoy2019].
+Moreover, a form of solidarity is observed between low-status members: in a study where participants had the opportunity to punish others for a non-cooperative behaviour, low-status members punished significantly less other low-status participants [@Chen2022].
+Also, in an experiment where participants were randomly advantaged during the interaction, @Camera2020 found that subjects who received a lot of advantages were discriminated by others, and especially by the ones who were rarely advantaged.
+
+Regarding the overall group composition, results are not consensual.
+On one hand, @Aksoy2019 found that groups with an inequality of status between members displayed lower levels of cooperation than homogeneous groups.
+On the other hand, economic and socio-cultural heterogeneity, although being negatively correlated with in-group trust, does not have a direct effect on a common-pool resource well-being [@VanKlingeren2021].
+
+In conclusion, social status impacts cooperation, but it seems to have multiple effects.
+Moreover, as mentioned in the previous section, @Sell2009 affirmed that, when investigating gender differences in cooperation, it is impossible to disentangle the effect of social status.
+Similarly, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
+This shows that social identity and social status are deeply connected, and that therefore it is difficult to separate their effects on cooperation.
 
@@
 
-## Social status???
+## Trust and beliefs about others' contribution
 
-retrieve work on gender that says that gender effects are probably in part impacted by status?
+In social dilemma situations, trust can be defined as the "expectations of others' benevolent motives in situations that involve a conflict between self and collective interests" [@Balliet2013, p.1].
+Trust can be dispositional or a state; the former is an individual's general trait, and is usually measured with personality scales, the latter is linked to the context, and can be operazionalized by expectations about a partner's behaviour in a specific situation [@Balliet2013].
+The two are positevely correlated [@Lubke2021], and therefore both have a positive general effect on cooperation [@VanLange2013; @Balliet2013].
+In fact, high levels of trust are associated with more contributions to a public good [@Kocher2015], and a participant's contribution in a public good game can be predicted by her beliefs about others' contributions [@Smith2013].
+These beliefs are linked with SVO orientation [@Ackermann2019].
 
-## Belief
+Several studied confirmed this relationship.
+For instance, @Chaudhuri2002 demonstrated that people who cooperated more in a first public good game trusted more their partner in a following interaction than people whose main strategy was defecting.
+Moreover, people that were pessimistic about others' contribution cooperated significantly less than the optimistic [@Oyediran2018], and those who free-rode in a public good game, compared to cooperators, believed that others contributed less [@Kocher2015].
+Also, people were more willing to purchase actions for a CO2 mitigation initiative when they believed that the majority of others had also bought them [@Sturm2019].
+Finally, in a study about self-administered outlets in Swiss farms (i.e.
+outlets where nobody monitors if people pay or not their purchase), @Franzen2019 found that a farmer's general trust in other people is a significant predictor of the probability of having such an outlet.
+Concerning the moderators, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
+
+People can also display different levels of trust in the "reliability, effectiveness and legitimacy of public institutions" [@Rompf2017, p.2].
+This authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to adapt to norms.
+Moreover, the effects of perceived costs and benefits of the action are less predictive in people with high institutional trust.
+
+Finally, trusting others (and the institutions) is essential to display higher level of cooperation.
+However, general beliefs about others' cooperation are quite low compared to the actual behaviours, and this trust gap can undermine cooperation, since people's actions are significantly predicted by their beliefs [@Lubke2021].
+Therefore it is essential to provide people with reliable information about others' behaviour, to increase trust and, as a consequence, cooperation.
 
@@
 Rewarding systems, on the other side, are less investigated.
-Globally, they have a positive effect on cooperation[@Balliet2011a].
+Globally, they have a positive effect on cooperation [@Balliet2011a].
 However, some studies found that they were more efficient than punishment [e.g.
@@
 Finally, incentives are often studied in economic formats, but they can also be social.
-For example, the expectiation of honour or shame (after cooperating or defecting, respectively) is enough to enhance cooperation [@Jacquet2011].
+For example, the expectation of honour or shame (after cooperating or defecting, respectively) is enough to enhance cooperation [@Jacquet2011].
 Moreover, expressing disapproval toward defectors can boost cooperation by inducing more compliance to the cooperative social norm [@Nelissen2013].
@@
 However, casual chit-chat also plays a very important role in increasing cooperation [@Koessler2021].
-Also, the increase of cooperation through communication can be explained by the normative content that people are shaping while exchanging messages [@Janssen2014].
+Also, the increase of cooperation through communication can be explained by the normative content that people are shaping while exchanging messages [@Janssen2014], and by the fact that it allows participant to reach a consensus about the best strategy [@Hopthrow2005].
 Moreover, even if communication also helps to create a social identity, the effect of social norms is a stronger mediator of the link between communication and cooperation [@Bicchieri2002].
@@
 This shows that gossip can have the pro-social function of protecting others from a potential exploitation [@Feinberg2012].
-However, gossip has also some self-interest effects: for instance, observing another subject being exploited, and having the opportunity to gossip about the exploiter significantly reduced negative affects in @Feinberg2012 's participants.
+However, gossip has also some self-interest effects: for instance, observing another subject being exploited and having the opportunity to gossip about the exploiter significantly reduced negative affects in @Feinberg2012 's participants.
 Moreover, providing correct information while gossiping helps to build a positive reputation [@Giardini2021].
@@
 
-## Group size --\> link with anonymity?
-
 ## Social Norms
 
-## Commitment
+Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour [@Borgstede2018].
+@Thogersen2008 studied the effect of social norms on daily social dilemma situations such as environmental behaviours, and found that both injunctive (what others approve) and descriptive (what others do) are positively related to behaviours.
+Moreover, cooperation can be maintained via social norms, because people who do not respect them are susceptible of social sanctions.
+In fact, if social approval is possible, people cooperate more [@Rege2004].
+
+There are several explanations of social norms' effect on cooperation.
+Firstly, according to the appropriateness framework, when taking a decision people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
+Therefore they need to define the situation as a cooperative task and to strongly identify with the group [@VanLange2013].
+This leads to a greater accessibility of group's norms and consequently (if the norms are cooperative) to more cooperation.
+Testing this assumption, @Arora2012 showed that a greater identification with social group lead to higher levels of cooperation.
+The second explanation concerns conformity: in general people adapt their cooperation to others' behaviour, but this is usually explained by the reciprocity principle (cooperate enhances the probability that others will do the same, and therefore that the final payoff will be higher) [@Bardsley2005].
+However, these authors demonstrated that people conform to others' behaviour even if this has no impact on their personal payoff.
+Therefore, people have a general tendency to imitate others to follow social norms.
+
+Finally, social norms can be modified by participants.
+For instance, @Weber2008 demonstrated that in several social dilemma experiment there are consistent cooperators, i.e.
+people who always cooperate.
+The presence of these people can increase other members' cooperation, and this effect is mediated by the perception of the social norms.
+Moreover, social norms can also be shaped via communication [@Bicchieri2002].
+
+In conclusion, social norms have a significant effect on people's cooperation in social dilemma situations.
+Since they are quite easily modified [@Weber2008], shaping cooperative norms can be a powerful instrument to improve cooperation.
+
+## Anonymity
+
+There are not many studies on the influence of anonymity on cooperation, but, according to @Wang2017, most of the factors that can increase cooperation rely on a reduction of anonymity.
+For instance, it is not possible to punish defectors without knowing who they are.
+Therefore, in general it seems that non-anonymous situations can significantly increase cooperation rates.
+In fact, when anonymity is removed in a social dilemma situation, cooperation increases and defection is reduced [@Wang2017].
+This can be explained by the fact that, when their actions are visible, people worry about others' approval [@Rege2004] and that, in non-anonymous situations, contributions can be a self-presentation strategy, because being perceived as pro-social can increase one's social status [@VanVugt2010a].
+There are therefore more social incentives to cooperate in non-anonymous, rather than anonymous, situations.
+
+Moreover, this effect is displayed especially in situations when individuals face a cost when cooperating and know that they will not get any personal benefit.
+For instance, @Butz2021 demonstrated that, in a public good game where a part of contributions was donated to a charity association, disclosing identity increased cooperation, but only if the donation was deducted from participants' payoff.
+In the same direction, @VanVugt2010a found that, when actions were public, contributions were higher if the public good was already attained or unattainable, and therefore if participants did not have a personal interest in cooperating.
+
+Reducing anonymity in cooperative interactions can be very effective to encourage people to contribute more.
+A possible way to do this is to reduce group's size.
+In fact, according to @Romano2016, a larger group leads to de-individuation, because it is more difficult to understand who is defecting.
+Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable.
+Moreover, communicate is easier in smaller groups [@Borgstede2018].
+This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good.
+Increasing cooperation through the reduction of anonymity is also possible by giving public feedbacks about people's cooperation [@Przepiorka2020].
+
+Another effective method to reduce anonymity is to make people publicly promise to cooperate before the cooperative interaction.
+For instance, in a laboratory experiment modeling a common pool resource, people who publicly committed exploited significantly less the resource than people who committed in private, even if after committing they were not restricted in their harvesting possibilities [@Mosler1993].
+This results was also confirmed by @Przepiorka2020, who showed that non-binding promises increased cooperation.
+Moreover, even a compulsory commitment has a beneficial effect on cooperation, even if the most efficient groups are those where all participants signed voluntary the pledge [@Koessler2021a].
+
+In conclusion, reducing anonymity during interactions is essential to improve cooperation, because this can facilitate the implementation of others cooperation-enhancing techniques [@Wang2017].
+Moreover, it exists several low-cost method to make situations non-anonymous.
 
@@
 
+individual factor: gender is interpretable by social status and ss is interpretable by group identity
+
+group factors: communication linked to social norms and social identity + anonymity underlies all the others + incentives has dark sides
+
+## Limitation
+
 observation: majority of papers included are about SD, and very few studies about commons are quantitative --\> future research: quantitative approach to investigate cooperation in common initiatives
+
+60/92 papers in Europe and North America + reviews also based on studies in these countries =\> bias (talk about cultural differences in cooperation)
 

### 2023-10-06 paper1_markdown.Rmd
06.10

@@
 
+  According to PRISMA-ScR: Provide a structured summary that includes (as applicable) background, objectives, eligibility criteria, sources of evidence, charting methods, results, and conclusions that relate to the review questions and objectives
+
   <!-- https://tinyurl.com/ybremelq -->
@@
 
+PRISMA-ScR:
+
+-   Describe the rationale for the review in the context of what is already known. Explain why the review questions/objectives lend themselves to a scoping review approach
+
+    many studies on cooperation, but just a few focus on commons =\> similar aspects between commons and social dilemmas, so literature on social dilemma can be a powerful tool to investigate which factors could impact cooperation in commons
+
+-   Provide an explicit statement of the questions and objectives being addressed with reference to their key elements (e.g., population or participants, concepts, and context) or other relevant key elements used to conceptualize the review questions and/or objectives.
+
+PLAN OF THE INTRODUCTION:
+
+-   COMMONS: what they are, why they become more and more popular and their main challenge = cooperation
+
+    -   commons' definition
+
+    -   more and more interest in commons because they could be a solution (see @Pacheco2014)
+
+    -   cooperation =\> provide example of the Tragedy of the Commons
+
+In a commons situation individual, short-term interests are at odds with collective, long-term ones [@Hardin1968].
+To ensure the success of a commons, people have therefore to sacrifice a part of their personal benefits for the collective good.
+For instance, a fisher could be tempted to fish in large quantity from a common basin, but if every other fisher did the same, fishes would not be enough to reproduce, and therefore there would be less fish for the following season.
+
+Cooperation, defined as a personal sacrifice for the greater good [@Kollock1998], is thus essential to in commons, and that is why a deeper understanding of how it works in this context is essential.
+Cooperation has often been studied with social dilemma experiments XXX.
+
+=\> existing literature on cooperation =\> retake the text below
+
+-   cooperation: often studied in social dilemma situation, while there is a lack of (quantitative) studies in commons
+
+-   similarities between commons and social dilemma, that justify why taking SD to investigate commons is pertinent + to make the link: list of papers that studied a common in a social dilemma perspective (ex: Hartl & Hofmann, 2022)
+
 **once selected the journal, re-organize all the introduction!!!**
-
-what is the connection between commons and social dilemmas? --\> well argument
-
-paper goal?
-
--   if commons --\> very important to make the link SD - commons: why social dilemma research could be useful for commons community
-
--   if not commons --\> not so important
-
--   commons are gaining always more interest because they could be a solution --\> start from this and then say that SD could be useful to understand + lack of quantitative studies about cooperation in commons
-
-    -   to make the link: list of papers that studied a common in a social dilemma perspective (ex: Hartl & Hofmann, 2022)
-
--   discussion: critiques at SD because it is artificial, does not take into account all real-life factors --\> so it is good to keep it as a base, but investigations in commons are needed
 
@@
 Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
-@Vanvugt2010a confirmed this assumptions in a social dilemma setting, by showing that people contributed more to a public resource when their action was visible by others, even if the public good was already provided or unattainable.
+@VanVugt2010a confirmed this assumptions in a social dilemma setting, by showing that people contributed more to a public resource when their action was visible by others, even if the public good was already provided or unattainable.
 In lines with hypothesis, participants who wasted their resources in the public good were perceived with an higher social status.
@@
 (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons
+-   @Gomez-Ruiz2020: see part about free-riders in the introduction
 
@@
 
-@Munn2018: reason to conduct a scoping review
+@Munn2018: reason to conduct a scoping review =\> maybe in the introduction?
 
-To conduct this scoping review, different papers published in academic journals were analyzed in response to the research questions.
+To conduct this scoping review, different scientific publications were analyzed in response to the research questions.
 To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect.
@@
 The research was made during the month of August, 2023.
-According with @Munn2022, the type of source was not a selection criteria, therefore experimental and qualitative studies, as well as meta-analysis and systematic reviews are included.
+According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included.
 This allows us to have an idea as complete as possible about the existing literature on cooperation in commons and social dilemmas.
 Moreover, there was any chronological or geographical limitation, once again to provide a broader vision of the topic.
-There were however some selection criteria concerning the papers' content.
+There were however some selection criteria concerning the papers' methodology and content.
 First of all, as mentioned in the introduction, this review will focus on individual and group dynamic that can enhance or decrease cooperation in a social dilemma situation (i.
@@
 Secondly, papers that studied social dilemmas with an agent-based model methodology were also excluded.
-**include explication**
-
-Criteria developed during screening: - no papers about agent-based model - no ethical/religious/philosophical papers - adult participants
+**include explication** Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.
 
@@
 Based on titles and abstracts, 4321 articles were eliminated, leaving 253 texts to examine.
-After a full-text evaluation of the remaining papers, 92were selected for the present review.
+After a full-text evaluation of the remaining papers, 91 were selected for the present review.
 Figure 1 resumes this selection procedure.
@@
 
-The included papers were published between 1984 and 2023, with a median of 2015.
+The 91 included papers were published between 1984 and 2023, with a median of 2015.
+Almost all of the selected texts were journal articles, with the only exception being a book chapter.
+Most of them were experimental studies (*N*=62), followed by literature review and meta-analysis (*N*=14) and correlational studies[^1] (*N*=14).
+The remaining paper was a qualitative study.
 
-A majority of the studies was conducted in Europe (*N*=40) (especially in Germany (*N*=12) and in the Netherlands (*N*=9)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=10, of which *N*=7 in China).
+[^1]: With "experimental studies" are intended all the studies were at least a variable is manipulated by researchers, while "correlational studies" refers to papers using quantitative analysis, but without manipulations.
+
+The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=77) refers to high controlled laboratory experiments where participants have to take cooperative decision.
+Usually some variables are manipulated to investigate the influence of a specific factor on cooperation [e.g.
+@Zhang2019].
+The type of paradigm used was most of the time a public good game (where participants can decide how much to contribute to a public good, e.g.
+@Torsvik2011) or a common resource game (where participants can decide how much to take from a common resource, e.g.
+@Nockur2020).
+Moreover, the type of game could change vary during the experiment [e.g.
+@Fosgaard2019].
+The second category is "real-life social dilemma situation" (*N*=7), and investigate cooperation in different real-life situations that have a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
+Thirdly, "real-life commons" (*N*=4) refers to studies that investigate cooperation within participants that are members of a commons in their everyday life.
+Finally, papers in the category "commons modeled by a social dilemma experiment" (*N*=3) use a laboratory social dilemma paradigm, but with clear references to a concrete common.
+For instance, in @Mosler1993, participants had to imagine to be fishermen who shared a common basin.
+
+Most of the papers concerned psychology and economic.
+In fact, thirty-five papers were published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin*, and fourteen in economic journals (e.g.
+*Experimental Economics*).
+Additionally, some papers (*N*=8) were published in interdisciplinary journals such as *Journal of Economic Psychology.*
+
+Finally, most of the studies were conducted in Europe (*N*=40) (especially in Germany (*N*=12) and in the Netherlands (*N*=9)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=9, of which *N*=6 in China).
 Moreover, *N*=7 studies were set in more than one country, and *N*=13 were meta-analysis or literature reviews.
 The two remaining studies took place in Australia and in Colombia, respectively.
-
-Almost all of the selected texts were journal articles. The only exceptions were a conference paper and a book chapter.
-
-still to do:
-
--   main topic: social dilemma or commons? social dilemma to conceptualize a specific commons? social dilemma applied to real-life situations?
-
--   methodology: lab vs meta-analysis vs review vs qualitative vs other?
 
@@
 
-Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^1].
+Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^2].
 In the litterature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
@@
 
-[^1]: Since the present paper's interest is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
+[^2]: Since the present paper's interest is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
 Incentives given by third party have also an effect on cooperation, but they are not included in this review.
@@
 In general, incentives seem to be a powerful tool to enhance cooperation, but they have a dark side.
-In fact, they reduce participants' intrinsic motivation [@VadDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+In fact, they reduce participants' intrinsic motivation [@VanDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
 In fact, @Schlosser2018 demonstrated that people's level of justice sensitivity could predict their contributions to a public good game, but this link disappeared when a punishment system was introduced.
@@
 Moreover, expressing disapproval toward defectors can boost cooperation by inducing more compliance to the cooperative social norm [@Nelissen2013].
-Even an ostracism system where participants can vote to exclude other members from the game is very effective in increasing cooperation [@Jarungrattanapong2022].
+Even an ostracism system where participants can vote to exclude other members from the game is very effective in increasing cooperation [@Maier-Rigaud2010].
 In general, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
@@
 
-Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour [@Borgstede2018].
+Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour [@VonBorgstede2018].
 @Thogersen2008 studied the effect of social norms on daily social dilemma situations such as environmental behaviours, and found that both injunctive (what others approve) and descriptive (what others do) are positively related to behaviours.
@@
 Testing this assumption, @Arora2012 showed that a greater identification with social group lead to higher levels of cooperation.
-The second explanation concerns conformity: in general people adapt their cooperation to others' behaviour, but this is usually explained by the reciprocity principle (cooperate enhances the probability that others will do the same, and therefore that the final payoff will be higher) [@Bardsley2005].
+The second explanation concerns conformity: in general people adapt their cooperation to others' behaviour, but this is usually explained by the reciprocity principle (cooperate enhances the probability that others will do the same, and therefore that the final payoff will be higher) [@Bardsley2005a].
 However, these authors demonstrated that people conform to others' behaviour even if this has no impact on their personal payoff.
@@
 Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable.
-Moreover, communicate is easier in smaller groups [@Borgstede2018].
+Moreover, communicate is easier in smaller groups [@VonBorgstede2018].
 This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good.
@@
 
-60/92 papers in Europe and North America + reviews also based on studies in these countries =\> bias (talk about cultural differences in cooperation)
+critiques at SD because it is artificial, does not take into account all real-life factors --\> so it is good to keep it as a base, but investigations in commons are needed
+
+60/91 papers in Europe and North America + reviews also based on studies in these countries =\> bias (talk about cultural differences in cooperation)
 

### 2023-10-10 paper1_figures.Rmd
10.10

@@
 DiagrammeR::grViz("digraph {
-graph [layout = dot, rankdir = TB]
+graph [layout = neato, rankdir = TB]
 
@@
 rec1 [label = 'Papers identified from search engines
-n = 5210']
+n = 5210', pos='0,0!']
 rec2 [label = 'Duplicates
-n = 624']
+n = 624', pos='3,0!']
 rec3 [label = 'Papers screened based on titles and abstracts
-n = 4586']
+n = 4586', pos='0,-1!']
 rec4 [label = 'Papers not suitable
-n = 4333']
+n = 4333', pos='3,-1!']
 rec5 [label = 'Papers read completely
-n = 253']
+n = 253', pos='0,-2!']
 rec6 [label = 'Papers not suitable
-n = 157']
+n = 157', pos='3,-2!']
 rec7 [label = 'Studies included
-n = 96']
+n = 96', pos='0,-3!']
 
@@
 ```
+
+``` {r}
+library(DiagrammeR)
+library(webshot)
+DiagrammeR::grViz("digraph {
+  graph [layout = fdp, rankdir = LR]
+
+  node [shape = rectangle]
+  rec1 [label = 'social identity', pos='0,0!']
+  rec2 [label = 'cooperation', pos='4,0!']
+  rec3 [label = 'social norms']
+  rec4 [label = 'communication']
+  rec5 [label = 'trust']
+
+  rec1 -> rec2
+  rec1 -> rec3 -> rec2
+  rec4 -> rec3
+  rec4 -> rec1
+  rec1 -> rec5 -> rec2
+}", height = 500)
+```

### 2023-10-10 paper1_markdown.Rmd
10.10

@@
 
-PRISMA-ScR:
+During last years, the interest in alternative ways of social organization augmented drastically because of the social and ecological crises we are facing [@Euler2018].
+Commons are one of this possible solutions, since they represent an alternative way of organizing resources who does not involve the classic private and public model [@Ostrom1990].
+In her seminal work, Ostrom refers to commons (or "common-pool resource") as a resource system equally shared between a self-managed community of users, because of the difficulty of excluding somebody from benefiting from its use [@Ostrom1990].
+Beyond the resource aspect of the commons, the notion of social practices (referred as commoning) is also essential [@Euler2018].
+Commoning is the process through which people manage to find solutions for their needs by self-organizing independently from the state or the market.
+Community is therefore engaged in defining rules to successfully manage a shared resource [@Meroni2022], and that is why taking into account the specific community who is commoning is also essential to fully understand a commons [@Dove2019].
+@Bollier2019 are even more radical: for them, the term "commons" should not be defined as a resource at all, but as "living social systems" who allow people to self-organize to address shared problems.
+Finally, "commons can thus be understood as collaborative arrangements for value production processes that are based on participatory principles" [@Seravalli2018a, p.
+1].
 
--   Describe the rationale for the review in the context of what is already known. Explain why the review questions/objectives lend themselves to a scoping review approach
+Commons are currently receiving more and more attention because they function outside of the capitalist system, they respect the Earth by giving mutual benefits to their members [@Meroni2022], and they could be the needed change toward more sustainable and fair economy and society [@Seravalli2018a].
+In fact, having small groups with a high perception of risk and a minimal uncertainty in collective goal, possibly focused on regional issues, could significantly improve the probability of success in attaining common goals related to sustainability [@Pacheco2014].
+Moreover, it is easier to coordinate on a local, rather than global, level [@Carpenter2011].
+Broadly, commons represent a possible solution simply by showing that alternatives to the classic model are possible [@Baibarac-Duignan2023].
 
-    many studies on cooperation, but just a few focus on commons =\> similar aspects between commons and social dilemmas, so literature on social dilemma can be a powerful tool to investigate which factors could impact cooperation in commons
+However, in order for the commons to be successful its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998], but this cooperation can be difficult to achieve [@Carpenter2011].
+This is explained by two characteristics of the commons' social dynamics.
+First, there is a strong asymmetry, in the sense that the collectivity has a strong impact on the individual, but a person's decisions have a smaller effect on the collective [@Kramer1984].
+Therefore, if people are uncertain about others' cooperation, the best solution is pursuing their personal self-interest.
+Secondly, in a commons situation, every member faces a conflict between individual, short-term interests and collective, long-term ones [@Hardin1968].
+For instance, a fisher could be tempted to fish in large quantity from a common basin, but if every other fisher did the same there would not be enough fish for the following seasons.
+According to @Hardin1968 and his "Tragedy of the Commons", individuals' greed to maximize their personal payoff will inevitably lead to the destruction of the common resource.
+For these reasons, it is essential to understand why people do (not) cooperate in commons, and which factors can impact cooperation.
 
--   Provide an explicit statement of the questions and objectives being addressed with reference to their key elements (e.g., population or participants, concepts, and context) or other relevant key elements used to conceptualize the review questions and/or objectives.
+## The study of cooperation
 
-PLAN OF THE INTRODUCTION:
+It exists different approaches to the study of cooperation.
+For instance, classical economic theories consider individuals as completely rational and always maximizing (expected) utility [@Edwards1954].
+Thus, according to these theories, individuals are not supposed to behave altruistically, namely to incur a personal cost while benefiting others [@Wittek2015].
+Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage.
+For example, the theory of competitive altruism says that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation [@Roberts1998].
+Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
 
--   COMMONS: what they are, why they become more and more popular and their main challenge = cooperation
+Cooperation has also extensively been studied through social dilemma.
+In such situations, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
+However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
+This approach is very useful to gain insights into how cooperation works because it provides a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
 
-    -   commons' definition
+While economic and evolutionary theories say that individuals are always pursuing their self-interest (either by defecting to maximize their personal payoff, either by cooperating to increase their social status and reputation), social dilemma experiments' results show that it is not always the case.
+First, it is observed that a significant amount of people are "strong reciprocators": they are willing to use their personal resources to reward cooperators and punish defectors, even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009].
+Moreover, according to the Greed Efficiency Fairness hypothesis, people's greed to pursuit their personal interest is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
+These results shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare [@Torsvik2011; @VanVugt2009].
 
-    -   more and more interest in commons because they could be a solution (see @Pacheco2014)
-
-    -   cooperation =\> provide example of the Tragedy of the Commons
-
-In a commons situation individual, short-term interests are at odds with collective, long-term ones [@Hardin1968].
-To ensure the success of a commons, people have therefore to sacrifice a part of their personal benefits for the collective good.
-For instance, a fisher could be tempted to fish in large quantity from a common basin, but if every other fisher did the same, fishes would not be enough to reproduce, and therefore there would be less fish for the following season.
-
-Cooperation, defined as a personal sacrifice for the greater good [@Kollock1998], is thus essential to in commons, and that is why a deeper understanding of how it works in this context is essential.
-Cooperation has often been studied with social dilemma experiments XXX.
-
-=\> existing literature on cooperation =\> retake the text below
-
--   cooperation: often studied in social dilemma situation, while there is a lack of (quantitative) studies in commons
-
--   similarities between commons and social dilemma, that justify why taking SD to investigate commons is pertinent + to make the link: list of papers that studied a common in a social dilemma perspective (ex: Hartl & Hofmann, 2022)
-
-**once selected the journal, re-organize all the introduction!!!**
-
-Many societal problems that humans are facing nowadays have a social dilemma structure [@Kollock1998], i.
-e.
-they are situations in which short-term, individual interests are at odds with long-term, collective ones [@Hardin1968].
-More specifically, in such situations, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
-However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
-
-An example of real-life social dilemma is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous for the self than acting without worrying about environment [@Griskevicius2010].
-However, since behaviours that serve our personal well-being tend to be detrimental to the environment [@VanLange1998], if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic.
-Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody paid it, public television would no longer exist.
-Cooperation (i.e.
-sacrificing for the grater good at a personal cost, [@Kollock1998]) is therefore essential to avoid the worst collective outcome in social dilemma situations, and that is why a deep comprehension of this phenomenon is needed.
-
-Classical economic theories have described human being as "homo economicus".
-This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954].
-Therefore, according to these theories, individuals are not supposed to show altruistic behaviours, defined as behaviours that involve costs for the self while benefiting others [@Wittek2015].
-However, there are individual differences in the level of rationality, i.e.
-the ability to think analytically at the situation.
-@Lang2018 showed that individuals scoring low in rationality cooperated more than individuals with an high score.
-This shows that, when investigating a phenomenon like cooperation, individual differences must be taken into account.
-
-Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage.
-For example, the theory of competitive altruism [@Roberts1998] says that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation.
-Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
-@VanVugt2010a confirmed this assumptions in a social dilemma setting, by showing that people contributed more to a public resource when their action was visible by others, even if the public good was already provided or unattainable.
-In lines with hypothesis, participants who wasted their resources in the public good were perceived with an higher social status.
-This means that cooperation can also serve a self-interested goal, by improving the reputation of cooperators.
-
-According to economic and evolutionary theories, individuals are always pursuing their self-interest, either by maximizing their personal payoff by defecting, either by cooperating to increase their social status and reputation.
-However, in social dilemma experiments, a significant amount of people are "strong reciprocators": they are willing to use their personal resources to "be kind to those who are being kind and to punish those who are being unkind", even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009].
-This shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare[@Torsvik2011; @VanVugt2009].
-GEF hypothesis: @VonBorgstede2018
-
-In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational cooperative or non-cooperative decision.
+In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational decision.
 In fact, cooperation seems to be the intuitive option in social dilemma experiments, while defection needs more thinking [@Kieslich2014].
 Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995].
-In fact, @Fosgaard2017 showed that, in public good games, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff.
-Moreover, these misperceptions can vary depending on how the game is presented.
+In fact, @Fosgaard2017 showed that, in public good games, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff, and these misconceptions can vary depending on how the game is presented.
+Moreover, there are individual differences in the level of rationality, i.e.
+the ability to think analytically at the situation [@Lang2018]: individuals scoring low in rationality cooperate more than individuals with an high score.
+Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].
 
-Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].
-Understanding how these different factors impact and shape cooperation is therefore essential to try to solve many of the societal problems that we are facing.
-**???**
+## Current review
 
-## Commons as social dilemmas
+Like social dilemma experiments challenge economic and evolutionary assumptions about cooperation, so do observations of real-life commons with Hardin's "Tragedy of the Commons": in fact, there are many examples of successful commons [e.g.
+@Ostrom1990; @Franzen2019].
+However, cooperation in commons has not been systematically studied like it has been in social dilemmas, and there is therefore a lack of knowledge about the factors that could enhance cooperation in this context.
+A way to start to fill this gap is to apply results of social dilemma to the commons.
+Linking this two topics is pertinent for at least three reasons.
+First, social dilemmas and commons share the same basic conflict between personal and collective interests [@Hardin1968; @Dawes1980].
+For this reason, @Sussman2016 used the term of "commons dilemma" and considered commons to be a particular case of social dilemma.
+Secondly, cooperation and defection in social dilemma laboratory experiments can predict people's behaviour in a commons situation [e.g.
+@Reindl2019; @Ros-Galvez2015].
+Finally, others studies already used the social dilemma framework to study real-life commons [e.g.
+@Hartl2022].
 
-Commons are a very specific kind of social dilemma.
-**FIND A DEFINITION (lol) that shows the similarity with social dilemmas (common resource, ...) !!** + Since, as in social dilemmas, a conflict between individual and collective interest is present @Sussman2016 used the term of "commons dilemmas" to speak about commons.
-
-Predictions about cooperations in commons are also similar to the social dilemma context: according to @Hardin1968 and his "Tragedy of the Commons", since individuals are likely to maximize their individual gain, commons are inevitably destined to failure due to the over exploitation of resources.
-However, successfully managed commons are often observed [e.g.
-@Ostrom1990] and, as discussed in the previous section, human beings are not motivated just by their personal interests.
-
-@Franzen2019: example that commons can work (outlets in Swiss farms)
-
-@Reindl2019: cooperation and defection in lab experiments are predictive of behaviours in a real public good (where individuals have to give resources to contribute to a public good)
-
--   But: Reindl et al.
-(2019) and Rommel et al.
-(2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
--   @Ros-Galvez2015: those who donated more in a game are those who post more in an online forum (= cooperation)
--   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
--   Importance of commons: Pacheco et al.
-(2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons
--   @Gomez-Ruiz2020: see part about free-riders in the introduction
-
-@Pacheco2014: "global coordination for a common good should be attempted by segmenting tasks in many small to medium sized groups, in which perception of risk is high and uncertainty in collective goals is minimized"
-
-ideal = decentralized agreements between smaller groups, possibly focused on regional issues are prone to significantly raise the probability of success in coordinating to tame the planet's climate
-
--   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of organization groups can set to improve a cooperation of all members
-
-a.  ?? Is it to mention that I focus on what a group can do, without focusing on how external institutions can influence cooperation?? If so, see @Larsson2016
-b.
+Based on these evidences, the aim of the present review is to use social dilemma literature to gain insights into cooperation in commons by (a) identifying individual factors that can shape it and (b) understanding which techniques groups can implement to encourage their members to cooperate.
+It is important to note that the point (b) will focus exclusively on bottom-up strategies that groups can adopt, and not on top-down solutions like privatization or centralized control of the resource.
+In fact, it well demonstrated that members of a commons can efficiently manage it without the intervention of an external institution [@Larsson2016].
+Moreover, bottom-up solutions are often more efficient than the two others [@Ostrom1990].
 
@@
 
-@Munn2018: reason to conduct a scoping review =\> maybe in the introduction?
-
-To conduct this scoping review, different scientific publications were analyzed in response to the research questions.
+Given the exploratory nature of this paper, a scoping review approach is used [@Munn2018].
+To conduct it, different scientific publications were analyzed in response to the research questions.
 To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect.
@@
 According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included.
-This allows us to have an idea as complete as possible about the existing literature on cooperation in commons and social dilemmas.
-Moreover, there was any chronological or geographical limitation, once again to provide a broader vision of the topic.
+This allows us to have an idea as complete as possible about the existing literature on cooperation in social dilemmas and commons.
+Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision of the topic.
 There were however some selection criteria concerning the papers' methodology and content.
-First of all, as mentioned in the introduction, this review will focus on individual and group dynamic that can enhance or decrease cooperation in a social dilemma situation (i.
-e.
-commons).
-For this reason, all the papers investigating how an external entity/institution can shape cooperation were not included.
+First, as mentioned in the introduction, papers investigating how an external entity/institution shapes cooperation were not included.
 Secondly, papers that studied social dilemmas with an agent-based model methodology were also excluded.
-**include explication** Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.
+Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.
 
@@
 
-[^1]: With "experimental studies" are intended all the studies were at least a variable is manipulated by researchers, while "correlational studies" refers to papers using quantitative analysis, but without manipulations.
+[^1]: Studies were at least a variable is manipulated by researchers are part of the category of "experimental studies", while "correlational studies" refers to papers using quantitative analysis, but without manipulations.
 
@@
 @Nockur2020).
-Moreover, the type of game could change vary during the experiment [e.g.
+Moreover, the type of game could vary during the experiment [e.g.
 @Fosgaard2019].
 The second category is "real-life social dilemma situation" (*N*=7), and investigate cooperation in different real-life situations that have a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
-Thirdly, "real-life commons" (*N*=4) refers to studies that investigate cooperation within participants that are members of a commons in their everyday life.
+Thirdly, "real-life commons" (*N*=4) refers to studies that investigate cooperation with participants that are members of a commons in their everyday life.
 Finally, papers in the category "commons modeled by a social dilemma experiment" (*N*=3) use a laboratory social dilemma paradigm, but with clear references to a concrete common.
@@
 
-Most of the papers concerned psychology and economic.
+Most of the papers concerned psychology and economy.
 In fact, thirty-five papers were published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin*, and fourteen in economic journals (e.g.
@@
 
-People can also display different levels of trust in the "reliability, effectiveness and legitimacy of public institutions" [@Rompf2017, p.2].
+People can also display different levels of trust in the "reliability, effectiveness and legitimacy of public institutions" [@Rompf2017, p.
+2].
 This authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to adapt to norms.
@@
 For instance, it is not possible to punish defectors without knowing who they are.
-Therefore, in general it seems that non-anonymous situations can significantly increase cooperation rates.
-In fact, when anonymity is removed in a social dilemma situation, cooperation increases and defection is reduced [@Wang2017].
+Therefore, in general it seems that non-anonymous situations can significantly increase cooperation and reduce defection [@Wang2017].
 This can be explained by the fact that, when their actions are visible, people worry about others' approval [@Rege2004] and that, in non-anonymous situations, contributions can be a self-presentation strategy, because being perceived as pro-social can increase one's social status [@VanVugt2010a].
@@
 Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable.
-Moreover, communicate is easier in smaller groups [@VonBorgstede2018].
+Moreover, communication is easier in smaller groups [@VonBorgstede2018].
 This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good.
@@
 
+This review identified some factors that could impact people's cooperation in social dilemmas and in commons.
+
+-   individual factors: some of them can be manipulated to improve cooperation, some of them must just be taken into account when "planning"
+
+-   group factors = strategies that groups can implement to improve cooperation
+
+-   =\> talk about the practical implication of this (interventions, ...)
+
+Previous theories
+
+Ostrom's (1990) eight principles for successfully managing a common (the 8th not pertinent):
+
+1\.
+Clearly defined boundaries =\>Individuals or households who have rights to withdraw resource units from the, CPR must be clearly defined, as must the boundaries of the CPR itself.
+**SOCIAL IDENTITY: since it defines an in-group and an out-group social identity becomes salient** @Tajfel1974
+
+2\.
+Congruence between appropriation and provision rules and local conditions =\> Appropriation rules restricting time, place, technology, and/or quantity of resource units are related to local conditions and to provision rules requiring labor, material, and/or money.
+
+3\. Collective-choice arrangements =\> Most individuals affected by the operational rules can participate in modifying the operational rules. **COMMUNICATION, SOCIAL NORMS**
+
+4\. Monitoring =\> Monitors, who actively audit CPR conditions and appropriator behavior, are accountable to the appropriators or are the appropriators. **INCENTIVES**
+
+5\.
+Graduated sanctions =\> Appropriators who violate operational rules are likely to be assessed graduated sanctions (depending on the seriousness and context of the offense) by other appropriators, by officials accountable to these appropriators, or by both.
+**INCENTIVES**
+
+6\.
+Conflict-resolution mechanisms =\> Appropriators and their officials have rapid access to low-cost local arenas to resolve conflicts among appropriators or between appropriators and officials.
+**COMMUNICATION**
+
+7\.
+Minimal recognition of rights to organize =\> The rights of appropriators to devise their own institutions are not challenged by external governmental authorities.
+**NOT APPLICABLE BECAUSE NO FOCUS ON EXTERNAL INSTITUTIONS**
+
+At a certain point say that these factors are not independent, but interconnected =\> prepare a model/framework
+
+@Tajfel1974: classic TIS, explanation of why more group identity = more cooperation, see also experiments with minimal groups paradigm
+
+SIMPEA model: [https://www.researchgate.net/profile/Michael-Brenner-Fliesser/publication/368219709/figure/fig2/AS:11431281117565450\@1675469130812/SIMPEA-model-Fritsche-et-al-2018.jpg](https://www.researchgate.net/profile/Michael-Brenner-Fliesser/publication/368219709/figure/fig2/AS:11431281117565450@1675469130812/SIMPEA-model-Fritsche-et-al-2018.jpg)
+
+SIMCA model: [https://www.researchgate.net/profile/Fouad-Bou-Zeineddine/publication/351515886/figure/fig1/AS:1042875005542400\@1625652185052/an-Zomeren-et-al-2008-Social-Identity-Model-of-Collective-Action-SIMCA-with.png](https://www.researchgate.net/profile/Fouad-Bou-Zeineddine/publication/351515886/figure/fig1/AS:1042875005542400@1625652185052/an-Zomeren-et-al-2008-Social-Identity-Model-of-Collective-Action-SIMCA-with.png)
+
+@Chou2013: link between trust and collective efficacy, so that trust could also fit in SIMPEA and SIMCA
+
+bystander effect =\> anonymity
+
+@Aksoy2019: see if class or group had a stronger impact =\> could be a reference to say that it is important to create a common social identity that makes weaker the effect of previous belongings **???**
+
+@Hogg2006: communication and social identity
+
+@Navarro-Carillo2018: high status more generalized trust, low status more in-group depersonalized trust (because more social networks)
+
 individual factor: gender is interpretable by social status and ss is interpretable by group identity
+
+social status: low cooperate more than high =\> theories of Iacoviello etc!!!
 

### 2023-10-11 paper1_figures.Rmd
11.10

@@
 rec1 [label = 'Papers identified from search engines
-n = 5210', pos='0,0!']
+n = 5210', pos='0,0!', width = 4, height = 0.5]
 rec2 [label = 'Duplicates
-n = 624', pos='3,0!']
+n = 624', pos='4,0!', width = 2, height = 0.5]
 rec3 [label = 'Papers screened based on titles and abstracts
-n = 4586', pos='0,-1!']
+n = 4586', pos='0,-1!', width = 4, height = 0.5]
 rec4 [label = 'Papers not suitable
-n = 4333', pos='3,-1!']
+n = 4333', pos='4,-1!', width = 2, height = 0.5]
 rec5 [label = 'Papers read completely
-n = 253', pos='0,-2!']
+n = 253', pos='0,-2!', width = 4, height = 0.5]
 rec6 [label = 'Papers not suitable
-n = 157', pos='3,-2!']
+n = 157', pos='4,-2!', width = 2, height = 0.5]
 rec7 [label = 'Studies included
-n = 96', pos='0,-3!']
+n = 90', pos='0,-3!', width = 4, height = 0.5]
 

### 2023-10-11 paper1_markdown.Rmd
11.10

@@
 output            : papaja::apa6_word
+always_allow_html : true
 #bibliography: references.bib
@@
 Based on titles and abstracts, 4321 articles were eliminated, leaving 253 texts to examine.
-After a full-text evaluation of the remaining papers, 91 were selected for the present review.
+After a full-text evaluation of the remaining papers, 90 were selected for the present review.
 Figure 1 resumes this selection procedure.
+
+```{r}
+library(DiagrammeR)
+library(webshot2)
+DiagrammeR::grViz("digraph {
+graph [layout = neato, rankdir = TB]
+
+node [shape = rectangle]       
+rec1 [label = 'Papers identified from search engines
+n = 5210', pos='0,0!', width = 4, height = 0.5]
+rec2 [label = 'Duplicates
+n = 624', pos='4,0!', width = 2, height = 0.5]
+rec3 [label = 'Papers screened based on titles and abstracts
+n = 4586', pos='0,-1!', width = 4, height = 0.5]
+rec4 [label = 'Papers not suitable
+n = 4333', pos='4,-1!', width = 2, height = 0.5]
+rec5 [label = 'Papers read completely
+n = 253', pos='0,-2!', width = 4, height = 0.5]
+rec6 [label = 'Papers not suitable
+n = 163', pos='4,-2!', width = 2, height = 0.5]
+rec7 [label = 'Studies included
+n = 90', pos='0,-3!', width = 4, height = 0.5]
+
+# edge definitions with the node IDs
+rec1 -> rec2
+rec3 -> rec4
+rec5 -> rec6
+rec1 -> rec3 -> rec5 -> rec7
+}",
+height = 500)
+```
 
@@
 
-The 91 included papers were published between 1984 and 2023, with a median of 2015.
+The 90 included papers were published between 1984 and 2023, with a median of 2015.
 Almost all of the selected texts were journal articles, with the only exception being a book chapter.
-Most of them were experimental studies (*N*=62), followed by literature review and meta-analysis (*N*=14) and correlational studies[^1] (*N*=14).
+Most of them were experimental studies (*N*=61), followed by literature review and meta-analysis (*N*=14) and correlational studies[^1] (*N*=14).
 The remaining paper was a qualitative study.
@@
 
-The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=77) refers to high controlled laboratory experiments where participants have to take cooperative decision.
+The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=76) refers to high controlled laboratory experiments where participants have to take cooperative decision.
 Usually some variables are manipulated to investigate the influence of a specific factor on cooperation [e.g.
@@
 
-Finally, most of the studies were conducted in Europe (*N*=40) (especially in Germany (*N*=12) and in the Netherlands (*N*=9)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=9, of which *N*=6 in China).
+Finally, most of the studies were conducted in Europe (*N*=39) (especially in Germany (*N*=12) and in the Netherlands (*N*=9)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=9, of which *N*=6 in China).
 Moreover, *N*=7 studies were set in more than one country, and *N*=13 were meta-analysis or literature reviews.
@@
 In other words, proportionally to their resources, low-status participants cooperated more.
-However, in their review, @VanLange2013 identified some studies that observed the opposite effect, namely that wealthier people (or those who benefitted more from a common resource) contributed more to the common good than the other.
+However, in their review, @VanLange2013 identified some studies that observed the opposite effect, namely that wealthier people (or those who benefited more from a common resource) contributed more to the common good than the other.
 
@@
 In fact, high levels of trust are associated with more contributions to a public good [@Kocher2015], and a participant's contribution in a public good game can be predicted by her beliefs about others' contributions [@Smith2013].
-These beliefs are linked with SVO orientation [@Ackermann2019].
 
@@
 However, general beliefs about others' cooperation are quite low compared to the actual behaviours, and this trust gap can undermine cooperation, since people's actions are significantly predicted by their beliefs [@Lubke2021].
-Therefore it is essential to provide people with reliable information about others' behaviour, to increase trust and, as a consequence, cooperation.
+In order to increase trust and, consequentely, cooperation, it is therefore it is essential to provide people with reliable information about others' behaviour.
 
@@
 This solidarity could therefore encourage free-riding.
-Moreover, the effect of punishment is stronger if only cooperators have the power to punish defectors, than if everybody can punish [@Xiao2016].
+Moreover, the effect of punishment is stronger when only cooperators have the power to punish defectors, than when everybody can punish [@Xiao2016].
 Finally, a plain situation is also needed to have a stronger effect of punishment: the link between behaviour and outcome must be clear, without random factors affecting the final outcome [@Xiao2016], and the punishment must be highly effective [@Egas2008].
@@
 In these groups, a norm of when and how punishment should be applied seems to exist.
-Moreover, punishment can also have two main negative sides.
+Moreover, punishment has also two main negative sides.
 First, it could entails a second-order social dilemma [@Milinski2012], since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators.
@@
 
-This review identified some factors that could impact people's cooperation in social dilemmas and in commons.
+Through a scoping review approach, the current study identified some factors that could impact cooperation in social dilemmas and in commons.
+Some of the this elements can be related to Ostrom's principles to successfully manage a commons [@Ostrom1990].
+In fact, her first statement says that commons need clearly defined boundaries: therefore, it must be clear who has the right to benefit from the common resource and who does not.
+This could be linked to the social identity construct, since only when an in- and an out-group exist social identity is salient and therefore an identification is possible [@Tajfel1974].
+Even if Ostrom developed this principle on a more organizational level, the secondary effect of creating a social identity for commons' members can also contribute to improve cooperation.
+Moreover, individuals who are part of the group, and who are therefore affected by the commons' rules, must be able to participate in modifying them (principle 3).
+This statement shows the importance of social norms, and especially of injunctive ones, namely what is morally approved in a social group [@Cialdini1990].
+Moreover, in order to modify such norms, people have to communicate [@Bicchieri2002].
+Communication is also essential for principle 6, who posits that members of a commons must have access to low-cost arenas to resolve conflicts.
+In fact, communication helps to reach an agreement to the strategy that needs to be followed [@Hopthrow2005].
+Finally, Ostrom's principles 4 and 5 underline the importance of incentives, especially in the form of a monitoring system implemented by members them-selves and a graduate sanctions system toward violators of the rules.
+The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they are worried about others' approval [@Nelissen2013; @Rege2004].
+On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^3]
 
--   individual factors: some of them can be manipulated to improve cooperation, some of them must just be taken into account when "planning"
+[^3]: Principles 2, 7 and 8 refer to elements that are not pertinent to the current review, and therefore do not match any of the factors identified.
 
--   group factors = strategies that groups can implement to improve cooperation
+Ostrom's assumptions are therefore confirmed, especially by factors at the organizational level.
+This is understandable when considering her economic approach to the study of the commons.
+However, taking into account the social dynamics and the individuals who interact within the commons is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
+For this reason, this paper makes a step further by identifying some individual factors that affect the efficiency of commons.
 
--   =\> talk about the practical implication of this (interventions, ...)
-
-Previous theories
-
-Ostrom's (1990) eight principles for successfully managing a common (the 8th not pertinent):
-
-1\.
-Clearly defined boundaries =\>Individuals or households who have rights to withdraw resource units from the, CPR must be clearly defined, as must the boundaries of the CPR itself.
-**SOCIAL IDENTITY: since it defines an in-group and an out-group social identity becomes salient** @Tajfel1974
-
-2\.
-Congruence between appropriation and provision rules and local conditions =\> Appropriation rules restricting time, place, technology, and/or quantity of resource units are related to local conditions and to provision rules requiring labor, material, and/or money.
-
-3\. Collective-choice arrangements =\> Most individuals affected by the operational rules can participate in modifying the operational rules. **COMMUNICATION, SOCIAL NORMS**
-
-4\. Monitoring =\> Monitors, who actively audit CPR conditions and appropriator behavior, are accountable to the appropriators or are the appropriators. **INCENTIVES**
-
-5\.
-Graduated sanctions =\> Appropriators who violate operational rules are likely to be assessed graduated sanctions (depending on the seriousness and context of the offense) by other appropriators, by officials accountable to these appropriators, or by both.
-**INCENTIVES**
-
-6\.
-Conflict-resolution mechanisms =\> Appropriators and their officials have rapid access to low-cost local arenas to resolve conflicts among appropriators or between appropriators and officials.
-**COMMUNICATION**
-
-7\.
-Minimal recognition of rights to organize =\> The rights of appropriators to devise their own institutions are not challenged by external governmental authorities.
-**NOT APPLICABLE BECAUSE NO FOCUS ON EXTERNAL INSTITUTIONS**
+@Tajfel1974: classic TIS, explanation of why more group identity = more cooperation, see also experiments with minimal groups paradigm + @Fritsche2018: The collectively interchangeable state of "social identity" makes people susceptible to adopt collective appraisals, goals, and behavior tendencies that are shared within their ingroup as their own
 
@@
 
-@Tajfel1974: classic TIS, explanation of why more group identity = more cooperation, see also experiments with minimal groups paradigm
+@Ackermann2019: link between SVO and trust
 
 SIMPEA model: [https://www.researchgate.net/profile/Michael-Brenner-Fliesser/publication/368219709/figure/fig2/AS:11431281117565450\@1675469130812/SIMPEA-model-Fritsche-et-al-2018.jpg](https://www.researchgate.net/profile/Michael-Brenner-Fliesser/publication/368219709/figure/fig2/AS:11431281117565450@1675469130812/SIMPEA-model-Fritsche-et-al-2018.jpg)
+
+environmental goals are usually collective goals and can therefore be attained just through a collective action (SIMPEA, @Fritsche2018a) =\> link with the fact that commons are successful only if people cooperate, "These crises, such as climate change, are large-scale and have the structure of common good dilemmas"
+
+in order to evaluate the climate crisis as relevant for the self, individuals need a connection with others who are more likely to be affected by it
+
+4 elements that affect appraisal of environmental crisis + pro-environmental behaviours:
+
+-   in-group identification
+
+-   collective efficacy beliefs =\> trust: since trust are the belief in others' contribution, it must be linked to the perceived collective efficacy (no trust = no collective efficacy, because if one thinks that the others are not contributing as they should then they can not believe that a collective action can be efficient)
+
+-   in-group norms and goals
 
@@
 
-social status: low cooperate more than high =\> theories of Iacoviello etc!!!
+social status: low cooperate more than high =\> theories of Iacoviello etc!!!\
+@Vargas-Salfate2018: more system justification in high-status individuals!
 
 group factors: communication linked to social norms and social identity + anonymity underlies all the others + incentives has dark sides
+
+-   individual factors: some of them can be manipulated to improve cooperation, some of them must just be taken into account when "planning"
+
+-   group factors = strategies that groups can implement to improve cooperation
+
+-   =\> talk about the practical implication of this (interventions, ...)
 

### 2023-10-12 paper1_markdown.Rmd
12.10

@@
 Commons are one of this possible solutions, since they represent an alternative way of organizing resources who does not involve the classic private and public model [@Ostrom1990].
-In her seminal work, Ostrom refers to commons (or "common-pool resource") as a resource system equally shared between a self-managed community of users, because of the difficulty of excluding somebody from benefiting from its use [@Ostrom1990].
-Beyond the resource aspect of the commons, the notion of social practices (referred as commoning) is also essential [@Euler2018].
+In her seminal work, Ostrom refers to commons (or "common-pool resource") as a resource system equally shared between a self-managed community of users, also because of the difficulty of excluding somebody from benefiting from its use [@Ostrom1990].
+Beyond the material aspect of the commons, the notion of social practices (referred as commoning) is also essential [@Euler2018].
 Commoning is the process through which people manage to find solutions for their needs by self-organizing independently from the state or the market.
@@
 @Bollier2019 are even more radical: for them, the term "commons" should not be defined as a resource at all, but as "living social systems" who allow people to self-organize to address shared problems.
-Finally, "commons can thus be understood as collaborative arrangements for value production processes that are based on participatory principles" [@Seravalli2018a, p.
+Finally, "commons can [...] be understood as collaborative arrangements for value production processes that are based on participatory principles" [@Seravalli2018a, p.
 1].
@@
 This approach is very useful to gain insights into how cooperation works because it provides a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
-
 While economic and evolutionary theories say that individuals are always pursuing their self-interest (either by defecting to maximize their personal payoff, either by cooperating to increase their social status and reputation), social dilemma experiments' results show that it is not always the case.
@@
 First, as mentioned in the introduction, papers investigating how an external entity/institution shapes cooperation were not included.
-Secondly, papers that studied social dilemmas with an agent-based model methodology were also excluded.
+Secondly, human participants were needed, so papers who studied social dilemmas with an agent-based model methodology were also excluded.
 Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.
@@
 n = 163', pos='4,-2!', width = 2, height = 0.5]
-rec7 [label = 'Studies included
+rec7 [label = 'Papers included
 n = 90', pos='0,-3!', width = 4, height = 0.5]
@@
 
-The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=76) refers to high controlled laboratory experiments where participants have to take cooperative decision.
-Usually some variables are manipulated to investigate the influence of a specific factor on cooperation [e.g.
+The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=76) refers to high controlled laboratory experiments where participants had to take cooperative decision.
+Usually some variables were manipulated to investigate the influence of a specific factor on cooperation [e.g.
 @Zhang2019].
-The type of paradigm used was most of the time a public good game (where participants can decide how much to contribute to a public good, e.g.
-@Torsvik2011) or a common resource game (where participants can decide how much to take from a common resource, e.g.
+The type of paradigm used was most of the time a public good game (where participants could decide how much to contribute to a public good, e.g.
+@Torsvik2011) or a common resource game (where participants could decide how much to take from a common resource, e.g.
 @Nockur2020).
@@
 @Fosgaard2019].
-The second category is "real-life social dilemma situation" (*N*=7), and investigate cooperation in different real-life situations that have a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
-Thirdly, "real-life commons" (*N*=4) refers to studies that investigate cooperation with participants that are members of a commons in their everyday life.
-Finally, papers in the category "commons modeled by a social dilemma experiment" (*N*=3) use a laboratory social dilemma paradigm, but with clear references to a concrete common.
+The second category is "real-life social dilemma situation" (*N*=7), and investigated cooperation in different real-life situations with a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
+Thirdly, "real-life commons" (*N*=4) refers to papers who studied cooperation with participants that were members of a commons in their everyday life.
+Finally, papers in the category "commons modeled by a social dilemma experiment" (*N*=3) used a laboratory social dilemma paradigm, but with clear references to a concrete common.
 For instance, in @Mosler1993, participants had to imagine to be fishermen who shared a common basin.
@@
 
-Finally, most of the studies were conducted in Europe (*N*=39) (especially in Germany (*N*=12) and in the Netherlands (*N*=9)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=9, of which *N*=6 in China).
-Moreover, *N*=7 studies were set in more than one country, and *N*=13 were meta-analysis or literature reviews.
+Finally, most of the studies were conducted in Europe (*N*=39) (especially in Germany (*N*=12) and in the Netherlands (*N*=9)), followed by North America (*N*=20, *N*=19 of which in the USA) and Asia (*N*=9, *N*=6 of which in China).
+Moreover, *N*=6 studies were set in more than one country, and *N*=14 were meta-analysis or literature reviews.
 The two remaining studies took place in Australia and in Colombia, respectively.
@@
 In general, groups composed only by men are more cooperative than only-women groups.
-This is explained by the fact that women are less achievement oriented and more socially oriented than men: they are therefore less concerned by the maximization of their personal payoff and more about relative payoff.
+This is explained by the fact that, in general, women are less achievement oriented and more socially oriented than men: they are therefore less concerned by the maximization of their personal payoff and more about relative payoff.
 Thus, the defection strategy allows them to play defensively and to avoid earning less than the other players [@Colman2018].
@@
 This leads women to behave in a more prosocial, altruistic way and men to be more self-oriented and competitive [@Balliet2011].
-The same result is also found by @Peshkovskaya2019, who also demonstrated that women reported a stronger social connection with their partners in mixed than in same-sex groups.
+The same result is also found by @Peshkovskaya2019, who addiotionally demonstrated that women reported a stronger social connection with their partners in mixed than in same-sex groups.
 The overall group composition also have an impact on cooperation: in general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023].
@@
 
-## Group identity
+## Group identification
 
@@
 One of the most studied is the Social Value Orientation (SVO), that divides people in pro-social and pro-self based on how much they value their own and others' outcomes in situations of interdependence [@Balliet2009].
-The effect of SVO on cooperation is very consensual: in a meta-analysis, 81 out of the 82 papers examined reported than pro-social cooperated significantly more that pro-self [@Balliet2009].
+The effect of SVO on cooperation is very consensual: in a meta-analysis, 81 out of the 82 papers examined reported than pro-social cooperated significantly more than pro-self [@Balliet2009].
 
@@
 
-Through a scoping review approach, the current study identified some factors that could impact cooperation in social dilemmas and in commons.
-Some of the this elements can be related to Ostrom's principles to successfully manage a commons [@Ostrom1990].
+Through a scoping review approach, the current study identified several factors that could impact cooperation in social dilemmas and in commons.
+Some of this elements can be related to Ostrom's principles to successfully manage a commons [@Ostrom1990].
 In fact, her first statement says that commons need clearly defined boundaries: therefore, it must be clear who has the right to benefit from the common resource and who does not.
@@
 In fact, communication helps to reach an agreement to the strategy that needs to be followed [@Hopthrow2005].
-Finally, Ostrom's principles 4 and 5 underline the importance of incentives, especially in the form of a monitoring system implemented by members them-selves and a graduate sanctions system toward violators of the rules.
+Finally, Ostrom's principles 4 and 5 underline the importance of incentives, more precisely in the form of a monitoring system implemented by members them-selves and a graduate sanctions system toward violators of the rules.
 The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they are worried about others' approval [@Nelissen2013; @Rege2004].
@@
 However, taking into account the social dynamics and the individuals who interact within the commons is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
-For this reason, this paper makes a step further by identifying some individual factors that affect the efficiency of commons.
+For this reason, this paper makes a step further by identifying some individual characteristics affecting the efficiency of commons.
+The effects of these factors seem to be coherent with the existing literature.
 
-@Tajfel1974: classic TIS, explanation of why more group identity = more cooperation, see also experiments with minimal groups paradigm + @Fritsche2018: The collectively interchangeable state of "social identity" makes people susceptible to adopt collective appraisals, goals, and behavior tendencies that are shared within their ingroup as their own
+For instance, the effect of trust on cooperation
 
-At a certain point say that these factors are not independent, but interconnected =\> prepare a model/framework
+-   link of every individual factor with the existing literature
 
-@Ackermann2019: link between SVO and trust
+    -   trust: being trusted increase the level of oxytocin, and this impact in turn the cooperative behaviour toward the person who trusted first @Campbell2010 + dispositional trust predicted pro social behaviour + mediated the relation between early-life experience and pro social behaviour @Wu2020 + conditional reciprocity = cooperate just if others do so (strong reciprocity, @Fehr2022, @VanLange1999): if no information on others, we must base our choice in trust
+
+    -   SVO: pro-socials cooperate more because they accord more importance at others' outcome + joint outcome (vs pro-selves = competitors and individualist) @VanLange1999, integrative model of social value orientation (by according importance at the role of equality in outcomes for pro-social, this model allows to explain why pro-social can behave even less cooperatively than pro-self when reciprocity is violated)
+
+    -   @Tajfel1974: classic TIS, explanation of why more group identity = more cooperation, see also experiments with minimal groups paradigm + @Fritsche2018: The collectively interchangeable state of "social identity" makes people susceptible to adopt collective appraisals, goals, and behavior tendencies that are shared within their ingroup as their own
+
+    -   social status: low cooperate more than high =\> theories of Iacoviello etc!!!\
+        @Vargas-Salfate2018: more system justification in high-status individuals!
+
+    -   @Janssen2015: confirmation of several factors (to read!!!)
+
+-   group factors: communication linked to social norms and social identity + anonymity underlies all the others + incentives has dark sides
+
+-   saying that these factors are not independent, but interconnected
+
+    -   For example, women level of cooperation is predicted by their trust in their interaction partner, while men's trust and cooperation are not linked [@Irwin2015].
+Moreover, women's lower cooperation is explained by the fact that they expected their partner to contribute less to the common good [@Dorrough2019].
+
+    -   @Ackermann2019: link between SVO and trust
+
+    -   @Navarro-Carillo2018: high status more generalized trust, low status more in-group depersonalized trust (because more social networks) =\> link with gender and trust
+
+    -   link between gender and social status, and between social status and social identity
+
+    -   @Aksoy2019: see if class or group had a stronger impact =\> could be a reference to say that it is important to create a common social identity that makes weaker the effect of previous belongings **???**
+
+    -   @Hogg2006: communication and social identity
+
+    -   @Chou2013: link between trust and collective efficacy, so that trust could also fit in SIMPEA and SIMCA
+
+    -   de-individualized trust = more trust in people of in-group just because they are in-group
+
+    -   @VanLange1999 =\> women were more prevalent between pro-socials and less between pro-selves (secondary result)
+
+-   in-group identification is also the main predictor of collective action in SIMCA and SIMPEA
 
@@
 
-@Chou2013: link between trust and collective efficacy, so that trust could also fit in SIMPEA and SIMCA
-
-bystander effect =\> anonymity
-
-@Aksoy2019: see if class or group had a stronger impact =\> could be a reference to say that it is important to create a common social identity that makes weaker the effect of previous belongings **???**
-
-@Hogg2006: communication and social identity
-
-@Navarro-Carillo2018: high status more generalized trust, low status more in-group depersonalized trust (because more social networks)
-
-individual factor: gender is interpretable by social status and ss is interpretable by group identity
-
-social status: low cooperate more than high =\> theories of Iacoviello etc!!!\
-@Vargas-Salfate2018: more system justification in high-status individuals!
-
-group factors: communication linked to social norms and social identity + anonymity underlies all the others + incentives has dark sides
-
 -   individual factors: some of them can be manipulated to improve cooperation, some of them must just be taken into account when "planning"
@@
 
-## Limitation
+## Limitations, future perspectives and conclusion
 
-observation: majority of papers included are about SD, and very few studies about commons are quantitative --\> future research: quantitative approach to investigate cooperation in common initiatives
+This review's aim was to provide an overview of the factors that affect cooperation in social dilemma situations such as commons.
+However, most of the studies included had a laboratory social dilemma setting, who do not allow to exactly reproduce the dynamics present in a commons [@Cole2010].
+Therefore, this papers offers a good basis about elements influencing cooperation in commons, but future studies should confirm this results in real-life settings.
+Moreover, this review is not informative about the relative importance of each factor.
+To shed light on this topic, quantitative studies are needed.
 
-critiques at SD because it is artificial, does not take into account all real-life factors --\> so it is good to keep it as a base, but investigations in commons are needed
+Another limitation of the current review is the lack of representation of the global population.
+In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews were also mostly based on studies from Global North.
+The current results apply therefore to Western societies and should not be generalized to Global South.
+In fact, there are cultural differences in the levels of individualism and collectivism: generally, North American and European cultures are more individualistic while South American, African and Asian ones are more collective [@Triandis1989].
+These differences affect the extent to which individuals define them-selves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g.
+@Kuwabara2014].
+For this reason, it is likely that underlying mechanism of cooperation are different for Global South and North: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.
 
-60/91 papers in Europe and North America + reviews also based on studies in these countries =\> bias (talk about cultural differences in cooperation)
+Finally, the papers included in this review did not provide a longitudinal perspective on the study of cooperation, leaving therefore some open questions: which factors are more important in the early or in the late stages of cooperation?
+How the different factors evolve and influence each-others over time?
+That is why longitudinal investigations about the evolution of commons are needed.
+
+To conclude, this paper offers a first draft of why people do (not) cooperate in commons, and highlights a lack of systematic studies about cooperation in commons.
+However, it is not without limitations, thus further researches are necessary to reach a deeper understanding of the topic.
++ say the first important practical implication that we can already deduce (social identity, ...)
 

### 2023-10-17 paper1_markdown.Rmd
17.10

@@
 Commons are one of this possible solutions, since they represent an alternative way of organizing resources who does not involve the classic private and public model [@Ostrom1990].
-In her seminal work, Ostrom refers to commons (or "common-pool resource") as a resource system equally shared between a self-managed community of users, also because of the difficulty of excluding somebody from benefiting from its use [@Ostrom1990].
-Beyond the material aspect of the commons, the notion of social practices (referred as commoning) is also essential [@Euler2018].
+In her seminal work, Ostrom refers to commons as a resource system equally shared between a self-managed community of users, also because of the difficulty of excluding somebody from benefiting from its use [@Ostrom1990].
+Commons can also be understood "as collaborative arrangements for value production processes that are based on participatory principles" [@Seravalli2018a, p.
+1].
+Therefore, beyond the material aspect of the commons, the notion of social practices (referred as commoning) is also essential [@Euler2018].
 Commoning is the process through which people manage to find solutions for their needs by self-organizing independently from the state or the market.
-Community is therefore engaged in defining rules to successfully manage a shared resource [@Meroni2022], and that is why taking into account the specific community who is commoning is also essential to fully understand a commons [@Dove2019].
+Community is therefore engaged in defining rules to successfully manage a shared resource [@Meroni2022], and that is why taking into account the specific community who is commoning is crucial to fully understand a commons [@Dove2019].
 @Bollier2019 are even more radical: for them, the term "commons" should not be defined as a resource at all, but as "living social systems" who allow people to self-organize to address shared problems.
-Finally, "commons can [...] be understood as collaborative arrangements for value production processes that are based on participatory principles" [@Seravalli2018a, p.
-1].
+These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look to the people who form these communities and to their organization.
 
-Commons are currently receiving more and more attention because they function outside of the capitalist system, they respect the Earth by giving mutual benefits to their members [@Meroni2022], and they could be the needed change toward more sustainable and fair economy and society [@Seravalli2018a].
+Commons are currently receiving more and more attention because they function outside of the capitalist system, they respect the Earth by giving mutual benefits to their members, and they could be the needed change toward more sustainable and fair economy and society [@Meroni2022; @Seravalli2018a].
 In fact, having small groups with a high perception of risk and a minimal uncertainty in collective goal, possibly focused on regional issues, could significantly improve the probability of success in attaining common goals related to sustainability [@Pacheco2014].
@@
 
-However, in order for the commons to be successful its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998], but this cooperation can be difficult to achieve [@Carpenter2011].
+In order for the commons to be successful, its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998].
+However, this cooperation can be difficult to achieve.
 This is explained by two characteristics of the commons' social dynamics.
-First, there is a strong asymmetry, in the sense that the collectivity has a strong impact on the individual, but a person's decisions have a smaller effect on the collective [@Kramer1984].
+First, there is a strong asymmetry between individual and collective: the latter has a strong impact on the individual, while personal decisions have a smaller effect on the collective [@Kramer1984].
 Therefore, if people are uncertain about others' cooperation, the best solution is pursuing their personal self-interest.
@@
 Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage.
-For example, the theory of competitive altruism says that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation [@Roberts1998].
+For example, the theory of competitive altruism posits that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation [@Roberts1998].
 Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
@@
 This approach is very useful to gain insights into how cooperation works because it provides a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
-While economic and evolutionary theories say that individuals are always pursuing their self-interest (either by defecting to maximize their personal payoff, either by cooperating to increase their social status and reputation), social dilemma experiments' results show that it is not always the case.
+While according to economic and evolutionary theories individuals are always pursuing their self-interest (either by defecting to maximize their personal payoff, either by cooperating to increase their social status and reputation), social dilemma experiments' results show that it is not always the case.
 First, it is observed that a significant amount of people are "strong reciprocators": they are willing to use their personal resources to reward cooperators and punish defectors, even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009].
-Moreover, according to the Greed Efficiency Fairness hypothesis, people's greed to pursuit their personal interest is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
-These results shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare [@Torsvik2011; @VanVugt2009].
-
-In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational decision.
-In fact, cooperation seems to be the intuitive option in social dilemma experiments, while defection needs more thinking [@Kieslich2014].
-Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995].
-In fact, @Fosgaard2017 showed that, in public good games, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff, and these misconceptions can vary depending on how the game is presented.
+Moreover, social dilemma experiments provided evidences suggesting that people do not always thoroughly analyze the context to take a rational decision.
+In fact, cooperation seems to be the intuitive option, while defection needs more thinking [@Kieslich2014].
+Additionally, people can also cooperate in part because they are confused about the situation [@Andreoni1995].
+In fact, @Fosgaard2017 showed that, in some experiments, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff, and these misconceptions can vary depending on how the game is presented.
 Moreover, there are individual differences in the level of rationality, i.e.
 the ability to think analytically at the situation [@Lang2018]: individuals scoring low in rationality cooperate more than individuals with an high score.
-Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].
+These evidences suggest that people are not always rational in the economic, individualistic way [@Kollock1998], and that there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].
 
@@
 @Ostrom1990; @Franzen2019].
+A possible explanation is the Greed Efficiency Fairness hypothesis: people's greed to pursuit their personal interest is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
+Thus, cooperation is not always driven by personal interest, and people care about others' and environment's welfare [@Torsvik2011; @VanVugt2009].
+
 However, cooperation in commons has not been systematically studied like it has been in social dilemmas, and there is therefore a lack of knowledge about the factors that could enhance cooperation in this context.
@@
 First, social dilemmas and commons share the same basic conflict between personal and collective interests [@Hardin1968; @Dawes1980].
-For this reason, @Sussman2016 used the term of "commons dilemma" and considered commons to be a particular case of social dilemma.
+For this reason, commons can be considered as a particular case of social dilemma (for example, @Sussman2016 used the term of "commons dilemma").
 Secondly, cooperation and defection in social dilemma laboratory experiments can predict people's behaviour in a commons situation [e.g.
@@
 It is important to note that the point (b) will focus exclusively on bottom-up strategies that groups can adopt, and not on top-down solutions like privatization or centralized control of the resource.
-In fact, it well demonstrated that members of a commons can efficiently manage it without the intervention of an external institution [@Larsson2016].
+In fact, it is well demonstrated that members of a commons can efficiently manage it without the intervention of an external institution [@Larsson2016].
 Moreover, bottom-up solutions are often more efficient than the two others [@Ostrom1990].
@@
 
-Given the exploratory nature of this paper, a scoping review approach is used [@Munn2018].
+Given the exploratory nature of this paper, a scoping review approach is adopted [@Munn2018].
 To conduct it, different scientific publications were analyzed in response to the research questions.
-To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect.
+To gather the papers, a Boolean search methodology was used in several scientific search engines such as Scopus, Web of Science and ScienceDirect.
 The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust", and they were paired with "AND" and "OR" Boolean operators.
@@
 According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included.
-This allows us to have an idea as complete as possible about the existing literature on cooperation in social dilemmas and commons.
+This allows to have an idea as complete as possible about the existing literature on cooperation in social dilemmas and commons.
 Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision of the topic.
@@
 rec6 [label = 'Papers not suitable
-n = 163', pos='4,-2!', width = 2, height = 0.5]
+n = 164', pos='4,-2!', width = 2, height = 0.5]
 rec7 [label = 'Papers included
-n = 90', pos='0,-3!', width = 4, height = 0.5]
+n = 89', pos='0,-3!', width = 4, height = 0.5]
 
@@
 
-The 90 included papers were published between 1984 and 2023, with a median of 2015.
+The 89 included papers were published between 1984 and 2023, with a median of 2015.
 Almost all of the selected texts were journal articles, with the only exception being a book chapter.
-Most of them were experimental studies (*N*=61), followed by literature review and meta-analysis (*N*=14) and correlational studies[^1] (*N*=14).
+Most of them were experimental studies (*N*=60), followed by literature review and meta-analysis (*N*=14) and correlational studies[^1] (*N*=14).
 The remaining paper was a qualitative study.
 
-[^1]: Studies were at least a variable is manipulated by researchers are part of the category of "experimental studies", while "correlational studies" refers to papers using quantitative analysis, but without manipulations.
+[^1]: Studies where at least a variable is manipulated by researchers are part of the category "experimental studies", while "correlational studies" refers to papers using quantitative analysis, but without manipulations.
 
-The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=76) refers to high controlled laboratory experiments where participants had to take cooperative decision.
+The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=75) refers to high controlled laboratory experiments where participants had to take cooperative decision.
 Usually some variables were manipulated to investigate the influence of a specific factor on cooperation [e.g.
@@
 Most of the papers concerned psychology and economy.
-In fact, thirty-five papers were published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin*, and fourteen in economic journals (e.g.
+In fact, thirty-four papers were published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin*, and fourteen in economic journals (e.g.
 *Experimental Economics*).
@@
 
-Finally, most of the studies were conducted in Europe (*N*=39) (especially in Germany (*N*=12) and in the Netherlands (*N*=9)), followed by North America (*N*=20, *N*=19 of which in the USA) and Asia (*N*=9, *N*=6 of which in China).
+Finally, most of the studies were conducted in Europe (*N*=38) (especially in Germany (*N*=12) and in the Netherlands (*N*=8)), followed by North America (*N*=20, *N*=19 of which in the USA) and Asia (*N*=9, *N*=6 of which in China).
 Moreover, *N*=6 studies were set in more than one country, and *N*=14 were meta-analysis or literature reviews.
@@
 
-The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results: sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], and sometimes there was no difference between genders.
-In general, meta-analysis found a non significant effect size for this difference [e.g.
+The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results: sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], and sometimes there was no differences.
+In general, meta-analysis found a non significant effect size [e.g.
 @Balliet2011; @Spadaro2023].
@@
 The partners' gender also have an impact on women's and men's cooperation.
-In general, groups composed only by men are more cooperative than only-women groups.
-This is explained by the fact that, in general, women are less achievement oriented and more socially oriented than men: they are therefore less concerned by the maximization of their personal payoff and more about relative payoff.
+In general, groups composed by men only are more cooperative than only-women groups.
+This is explained by the fact that women are generally less achievement oriented and more socially oriented than men: they are therefore less concerned by the maximization of their personal payoff and more about relative payoff.
 Thus, the defection strategy allows them to play defensively and to avoid earning less than the other players [@Colman2018].
@@
 In fact, when both men and women are present, gender stereotypes are activated and people tend to adapt their behaviour to them.
-This leads women to behave in a more prosocial, altruistic way and men to be more self-oriented and competitive [@Balliet2011].
-The same result is also found by @Peshkovskaya2019, who addiotionally demonstrated that women reported a stronger social connection with their partners in mixed than in same-sex groups.
+This leads women to behave in a more pro-social, altruistic way and men to be more self-oriented and competitive [@Balliet2011].
+The same result is also found by @Peshkovskaya2019, who additionally demonstrated that women reported a stronger social connection with their partners in mixed than in same-sex groups.
 The overall group composition also have an impact on cooperation: in general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023].
@@
 For instance, advantaged members (i.e.
-high-status class) tended to cooperate less than disadvantaged ones [@Aksoy2019].
+high-status class) tend to cooperate less than disadvantaged ones [@Aksoy2019].
 In fact, when participants did not receive the same endowment at the beginning of the experiment, contributions of "rich" and "poor" members converged [@Kingsley2016].
@@
 Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect.
-Group identification can also esaily be implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992].
+Group identification can also easily be implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992].
 Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].
@@
 
-# Group factors
+# Organizational factors
 
@@
 
-Through a scoping review approach, the current study identified several factors that could impact cooperation in social dilemmas and in commons.
-Some of this elements can be related to Ostrom's principles to successfully manage a commons [@Ostrom1990].
+Through a scoping review approach, the current paper identified several factors that could impact cooperation in social dilemmas and in commons.
+Some of this elements can be related to the principles to successfully manage a common resource that Ostrom drew after the observation of several communities [@Ostrom1990].
 In fact, her first statement says that commons need clearly defined boundaries: therefore, it must be clear who has the right to benefit from the common resource and who does not.
@@
 In fact, communication helps to reach an agreement to the strategy that needs to be followed [@Hopthrow2005].
-Finally, Ostrom's principles 4 and 5 underline the importance of incentives, more precisely in the form of a monitoring system implemented by members them-selves and a graduate sanctions system toward violators of the rules.
+Finally, Ostrom's principles 4 and 5 underline the importance of incentives, more precisely in the form of a monitoring system implemented by members themselves and a graduate sanctions system toward violators of the rules.
 The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they are worried about others' approval [@Nelissen2013; @Rege2004].
@@
 
-Ostrom's assumptions are therefore confirmed, especially by factors at the organizational level.
+Ostrom's principles are therefore in line with the results of this review, especially concerning factors at the organizational level.
 This is understandable when considering her economic approach to the study of the commons.
 However, taking into account the social dynamics and the individuals who interact within the commons is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
-For this reason, this paper makes a step further by identifying some individual characteristics affecting the efficiency of commons.
+For this reason, this paper made a step further and identified some individual characteristics affecting the efficiency of commons.
 The effects of these factors seem to be coherent with the existing literature.
 
-For instance, the effect of trust on cooperation
+First, according to the analyzed papers, trust has a positive effect on cooperation.
+In fact, since cooperation involves the risk that others will defect, trusting others is essential [@Henry2011].
+Moreover, according to the principle of reciprocity, people cooperate more when facing cooperative partners [@Fehr2022; @VanLange1999].
+However, in real-life situation it is not always possible to know exactly others' contributions, and therefore trust (i.e.
+beliefs about how much others cooperate) become essential to decide how to behave [@Vuolevi2012].
+Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can (not) be successful.
+These evidences fit well with the more general result showing that dispositional trust is a predictor of pro-social behaviour [@Wu2020].
+Finally, this link has a biological grounding: being trusted increases the level of oxytocin (a hormone that helps creating attachment between individuals), and this, in turn, improve the cooperative behaviour toward the person who first showed trust [@Campbell2010].
 
--   link of every individual factor with the existing literature
+Secondly, Social Value Orientation has also an impact on cooperation: in fact, there are individual differences in motivation when people have to decide how to allocate a resource between themselves and others [@Murphy2011].
+More specifically, pro-social individuals accord more importance to others' and joint outcome than pro-self, and they are therefore more cooperative [@VanLange1999].
+This is also confirmed experimentally by @Fiedler2013, who showed that pro-social and pro-self processed the situation in a similar way, but accorded different weights to the outcome for themselves and others.
+Finally, since they value more the equality in outcomes, pro-social can behave even less cooperatively than pro-self when reciprocity is violated [@VanLange1999].
 
-    -   trust: being trusted increase the level of oxytocin, and this impact in turn the cooperative behaviour toward the person who trusted first @Campbell2010 + dispositional trust predicted pro social behaviour + mediated the relation between early-life experience and pro social behaviour @Wu2020 + conditional reciprocity = cooperate just if others do so (strong reciprocity, @Fehr2022, @VanLange1999): if no information on others, we must base our choice in trust
+Concerning gender effect on cooperation, the existing literature about gender stereotypes would predict that women cooperate more than men.
+In fact, according to the stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012], and this lead to the perception that women's intentions are more benevolent than those of men [@Ellemers2017].
+In line with these predictions, @Westermann2005 found that, managing a natural resource, groups where women were present displayed more solidarity and collaboration comparing to all-men groups.
+Despite these evidences, this review found that there is no general gender effect on cooperation and that a lot of moderator are at stake.
+Moreover, gender is always embedded with social status dynamics [@Sell2009], and it is therefore difficult to separate the two effects.
+The analyzed studies about social status and cooperation showed that usually members of low-status groups cooperated more and showed more solidarity with others low-status members than high-status.
+Although the effect of social status on cooperation has not been extensively studied, these results seem to be consistent with the existing literature on social status.
+For instance, members of high-status groups are more individualistic, because their group belonging does not reduce individual characteristics as it does with low-status [@Lorenzi-Cioldi2002].
+Moreover, high-status individuals display more system justification than low status, i.e.
+they see the social system as fair and secure [@Caricati2012], and higher levels of Social Dominance Orientation [@Vargas-Salfate2018], that is the personal preference for inequality between social groups and that is negatively correlated with concern about others and altruism [@Pratto1994].
+Finally, although the differences between social statuses, people tend to cooperate more with individuals of their same social class than with others, and this effect is manly due to group identification [@Aksoy2019].
+Social status is therefore deeply connected to the last of the identified individual factors, group identification.
 
-    -   SVO: pro-socials cooperate more because they accord more importance at others' outcome + joint outcome (vs pro-selves = competitors and individualist) @VanLange1999, integrative model of social value orientation (by according importance at the role of equality in outcomes for pro-social, this model allows to explain why pro-social can behave even less cooperatively than pro-self when reciprocity is violated)
+The reviewed results showed that the more individuals identify with their group, the more they are likely to act for the group's good.
+In fact, people's identity is also composed by their group affiliations, and the stronger they identify a social group, the more important this group becomes for their identity and the more their personal interests aligns with group's ones [@Tajfel1974].
+Also, within a social group, individuals perceive themselves are more similar to other members [@Turner1984], and therefore they are more susceptible to adopt collective goals and behaviours [@Fritsche2018].
+Moreover, strongly identified people are less likely to leave a social group in case of failure or difficulties [@Ellemers1997].
+Thus, in order for a social group to be successful, its members must strongly identify with it.
+In fact, in-group identification is the main predictor of collective action in the Social Identity Model of Collective Action [SIMCA, @VanZomeren2008].
+Moreover, @Fritsche2018 apply this social identity approach to environmentalism with the Social Identity Model of Pro-Environmental Action (SIMPEA).
+According to its authors, the climate crisis has the structure of common good dilemmas, because environmental goals can be attained only if everybody cooperates.
+Group identification is once again the main predictor of such collective actions.
 
-    -   @Tajfel1974: classic TIS, explanation of why more group identity = more cooperation, see also experiments with minimal groups paradigm + @Fritsche2018: The collectively interchangeable state of "social identity" makes people susceptible to adopt collective appraisals, goals, and behavior tendencies that are shared within their ingroup as their own
+## Factors' interactions
 
-    -   social status: low cooperate more than high =\> theories of Iacoviello etc!!!\
-        @Vargas-Salfate2018: more system justification in high-status individuals!
+Until now, the identified factors has been discussed separately. However,
 
-    -   @Janssen2015: confirmation of several factors (to read!!!)
+-
+
+    -   @Janssen2015: confirmation of several factors
+
+        -   cheap talk (= communication who does not affect the payoff of the game) can also improve cooperation because it signals intentions and trustworthiness
+
+        -   Behavior motivated by moral obligations and social preferences can be undermined by economic interventions
+
+        -   Larger groups will make it more difficult to evaluate the trustworthiness of all other participants and make it easier to free ride on actions of others
 
@@
 
--   saying that these factors are not independent, but interconnected
+Finally, all of the group and individual factors identified are deeply interconnected.
 
@@
 
-    -   @Ackermann2019: link between SVO and trust
+    -   @Ackermann2019: link between SVO and trust + @Bogaert2008
 
     -   @Navarro-Carillo2018: high status more generalized trust, low status more in-group depersonalized trust (because more social networks) =\> link with gender and trust
-
-    -   link between gender and social status, and between social status and social identity
 
@@
 
--   in-group identification is also the main predictor of collective action in SIMCA and SIMPEA
+    -
 
-SIMPEA model: [https://www.researchgate.net/profile/Michael-Brenner-Fliesser/publication/368219709/figure/fig2/AS:11431281117565450\@1675469130812/SIMPEA-model-Fritsche-et-al-2018.jpg](https://www.researchgate.net/profile/Michael-Brenner-Fliesser/publication/368219709/figure/fig2/AS:11431281117565450@1675469130812/SIMPEA-model-Fritsche-et-al-2018.jpg)
-
-environmental goals are usually collective goals and can therefore be attained just through a collective action (SIMPEA, @Fritsche2018a) =\> link with the fact that commons are successful only if people cooperate, "These crises, such as climate change, are large-scale and have the structure of common good dilemmas"
-
-in order to evaluate the climate crisis as relevant for the self, individuals need a connection with others who are more likely to be affected by it
-
-4 elements that affect appraisal of environmental crisis + pro-environmental behaviours:
-
--   in-group identification
-
--   collective efficacy beliefs =\> trust: since trust are the belief in others' contribution, it must be linked to the perceived collective efficacy (no trust = no collective efficacy, because if one thinks that the others are not contributing as they should then they can not believe that a collective action can be efficient)
-
--   in-group norms and goals
-
-SIMCA model: [https://www.researchgate.net/profile/Fouad-Bou-Zeineddine/publication/351515886/figure/fig1/AS:1042875005542400\@1625652185052/an-Zomeren-et-al-2008-Social-Identity-Model-of-Collective-Action-SIMCA-with.png](https://www.researchgate.net/profile/Fouad-Bou-Zeineddine/publication/351515886/figure/fig1/AS:1042875005542400@1625652185052/an-Zomeren-et-al-2008-Social-Identity-Model-of-Collective-Action-SIMCA-with.png)
-
+```{=html}
+<!-- -->
+```
 -   individual factors: some of them can be manipulated to improve cooperation, some of them must just be taken into account when "planning"
@@
 
--   =\> talk about the practical implication of this (interventions, ...)
+-   =\> talk about the practical implication of this (interventions, ...) + say that a factor will have not only an impact on cooperation, but also on other factors
 
-## Limitations, future perspectives and conclusion
+# Limitations, future perspectives and conclusion
 
-This review's aim was to provide an overview of the factors that affect cooperation in social dilemma situations such as commons.
-However, most of the studies included had a laboratory social dilemma setting, who do not allow to exactly reproduce the dynamics present in a commons [@Cole2010].
+To conclude, this review's aim was to provide an overview of the factors that affect cooperation in social dilemma situations such as commons.
+While attaining this goal, the current paper has also highlighted a lack of systematic studies about cooperation in commons.
++ say the first important practical implication that we can already deduce (social identity, ...)
+
+@Janssen2015: In contrast to lab experiments, studies find that cultural factors, experiences with specific institutional arrangements and ecological conditions can affect the way participants make decisions in those experiments.
+This demonstrates that effectiveness of interventions is context specific.
+
+However, it is not without limitations, thus further researches are necessary to reach a deeper understanding of the topic.
+First, most of the studies included had a laboratory social dilemma setting, who do not allow to exactly reproduce the dynamics present in a commons [@Cole2010].
 Therefore, this papers offers a good basis about elements influencing cooperation in commons, but future studies should confirm this results in real-life settings.
@@
 
+-   @Henry2011: Such a theory must build on research in less complex contexts, but must also give attention to the added effects of evolving networks and information-sharing amongst those making decisions relevant to sustainability and global environmental change (their study was on trust, but it can be applied to this review in general)
+
 Another limitation of the current review is the lack of representation of the global population.
-In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews were also mostly based on studies from Global North.
+In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Global North.
 The current results apply therefore to Western societies and should not be generalized to Global South.
-In fact, there are cultural differences in the levels of individualism and collectivism: generally, North American and European cultures are more individualistic while South American, African and Asian ones are more collective [@Triandis1989].
-These differences affect the extent to which individuals define them-selves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g.
+In fact, there are cultural differences in the levels of individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989].
+These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g.
 @Kuwabara2014].
@@
 
-To conclude, this paper offers a first draft of why people do (not) cooperate in commons, and highlights a lack of systematic studies about cooperation in commons.
-However, it is not without limitations, thus further researches are necessary to reach a deeper understanding of the topic.
-+ say the first important practical implication that we can already deduce (social identity, ...)
-
 \newpage

### 2023-10-18 paper1_markdown.Rmd
18.10 mac

@@
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - "Conceptualization"
-      - "Writing - Original Draft Preparation"
-      - "Writing - Review & Editing"
+     # - "Conceptualization"
+     # - "Writing - Original Draft Preparation"
+     # - "Writing - Review & Editing"
 
@@
 In conclusion, social status impacts cooperation, but it seems to have multiple effects.
-Moreover, as mentioned in the previous section, @Sell2009 affirmed that, when investigating gender differences in cooperation, it is impossible to disentangle the effect of social status.
-Similarly, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
+Moreover, similarly to what @Sell2009 affirmed about the effects of gender and social status, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
 This shows that social identity and social status are deeply connected, and that therefore it is difficult to separate their effects on cooperation.
@@
 However, in real-life situation it is not always possible to know exactly others' contributions, and therefore trust (i.e.
-beliefs about how much others cooperate) become essential to decide how to behave [@Vuolevi2012].
+beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012].
 Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can (not) be successful.
@@
 For instance, members of high-status groups are more individualistic, because their group belonging does not reduce individual characteristics as it does with low-status [@Lorenzi-Cioldi2002].
-Moreover, high-status individuals display more system justification than low status, i.e.
-they see the social system as fair and secure [@Caricati2012], and higher levels of Social Dominance Orientation [@Vargas-Salfate2018], that is the personal preference for inequality between social groups and that is negatively correlated with concern about others and altruism [@Pratto1994].
+Moreover, high-status individuals display more system justification than low status [@Caricati2012], and higher levels of Social Dominance Orientation [@Vargas-Salfate2018].
+Therefore, they see the social system as fair and secure and they have a preference for inequality between social groups.
+This is negatively correlated with concern about others and altruism [@Pratto1994].
 Finally, although the differences between social statuses, people tend to cooperate more with individuals of their same social class than with others, and this effect is manly due to group identification [@Aksoy2019].
@@
 The reviewed results showed that the more individuals identify with their group, the more they are likely to act for the group's good.
-In fact, people's identity is also composed by their group affiliations, and the stronger they identify a social group, the more important this group becomes for their identity and the more their personal interests aligns with group's ones [@Tajfel1974].
-Also, within a social group, individuals perceive themselves are more similar to other members [@Turner1984], and therefore they are more susceptible to adopt collective goals and behaviours [@Fritsche2018].
+In fact, people's identity is also composed by their group affiliations, and the stronger they identify with a social group, the more important this group becomes for their identity and the more their personal interests aligns with group's ones [@Tajfel1974].
+Also, within a social group, individuals perceive themselves as more similar to other members [@Turner1984], and therefore they are more susceptible to adopt collective goals and behaviours [@Fritsche2018].
 Moreover, strongly identified people are less likely to leave a social group in case of failure or difficulties [@Ellemers1997].
@@
 
-Until now, the identified factors has been discussed separately. However,
+Until now, the identified factors has been discussed separately.
+However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.
+For instance, incentives are more useful to improve cooperation of low-, rather than high-identified, group members [@VanVugt2009]; trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019].
+These connections are also confirmed in the litterature.
 
@@
 -   group factors: communication linked to social norms and social identity + anonymity underlies all the others + incentives has dark sides
-
-Finally, all of the group and individual factors identified are deeply interconnected.
-
--   For example, women level of cooperation is predicted by their trust in their interaction partner, while men's trust and cooperation are not linked [@Irwin2015].
-Moreover, women's lower cooperation is explained by the fact that they expected their partner to contribute less to the common good [@Dorrough2019].
 
@@
 
-@Janssen2015: In contrast to lab experiments, studies find that cultural factors, experiences with specific institutional arrangements and ecological conditions can affect the way participants make decisions in those experiments.
-This demonstrates that effectiveness of interventions is context specific.
-
 However, it is not without limitations, thus further researches are necessary to reach a deeper understanding of the topic.
-First, most of the studies included had a laboratory social dilemma setting, who do not allow to exactly reproduce the dynamics present in a commons [@Cole2010].
+First, most of the studies included had a laboratory social dilemma setting, who are simplier than real-life situations and do not allow to exactly reproduce the dynamics present in a commons [@Henry2011; @Cole2010].
+In fact, some elements such as cultural factors and specific ecological conditions affect the decision making process, and cannot be reproducted in lab experiments [@Janssen2015].
 Therefore, this papers offers a good basis about elements influencing cooperation in commons, but future studies should confirm this results in real-life settings.
@@
 To shed light on this topic, quantitative studies are needed.
-
--   @Henry2011: Such a theory must build on research in less complex contexts, but must also give attention to the added effects of evolving networks and information-sharing amongst those making decisions relevant to sustainability and global environmental change (their study was on trust, but it can be applied to this review in general)
 

### 2023-11-03 paper1_markdown.Rmd
03.11

@@
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
+    #corresponding : yes    # Define only one corresponding author
     address       : "University of Bern, Centre for Development and Environment (CDE), Mittelstrasse 43, CH-3012 Bern"
@@
   - id            : "1"
-    institution   : "University of Bern"
+    institution   : "Centre for Development and Environment, University of Bern"
 
-authornote: |
+#authornote: |
 
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+  Commons represent an alternative social organization outside the classical capitalist model, therefore they could be the needed change toward more sustainable societies and economy.
+However, in order for a common to be successful, its members must cooperate, i.e.
+incur a personal sacrifice for the collective good.
+Despite the importance of cooperation, there is a lack of studies that investigated this topic in commons context.
+On the other hand, cooperation has been extensively studied in social dilemma experiments, where personal and collective interests are at odds.
+Since the two contexts share some structural characteristics, the results of social dilemma experiments could be used to gain insights on cooperation in commons.
+  The goal of the current scoping review is to identify the factors that impact cooperation in social dilemma situations, to gain a better understanding of what could shape cooperation in commons.
+A key-word search and a subsequent selection lead to the inclusion of 89 papers, who are used to identify 9 factors that influence cooperation both at the individual and group level.
+These factors are discussed within the existing literature on commons and cooperation.
+Finally, the practical implication of this work for commons' organization, as well as the review's limitations, are highlighted.
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  According to PRISMA-ScR: Provide a structured summary that includes (as applicable) background, objectives, eligibility criteria, sources of evidence, charting methods, results, and conclusions that relate to the review questions and objectives
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "cooperation, social dilemmas, commons"
-wordcount         : ""
+#keywords          : "cooperation, social dilemmas, commons"
+#wordcount         : ""
 
@@
 always_allow_html : true
-#bibliography: references.bib
 ---
@@
 
-During last years, the interest in alternative ways of social organization augmented drastically because of the social and ecological crises we are facing [@Euler2018].
-Commons are one of this possible solutions, since they represent an alternative way of organizing resources who does not involve the classic private and public model [@Ostrom1990].
+During last years, the interest in alternative ways of social organization increased drastically because of the social and ecological crises we are facing [@Euler2018].
+Commons are a possible solution, since they represent an alternative way of organizing resources not involving the classic private and public model [@Ostrom1990].
 In her seminal work, Ostrom refers to commons as a resource system equally shared between a self-managed community of users, also because of the difficulty of excluding somebody from benefiting from its use [@Ostrom1990].
@@
 Commoning is the process through which people manage to find solutions for their needs by self-organizing independently from the state or the market.
-Community is therefore engaged in defining rules to successfully manage a shared resource [@Meroni2022], and that is why taking into account the specific community who is commoning is crucial to fully understand a commons [@Dove2019].
+The community is therefore engaged in defining rules to successfully manage a shared resource [@Meroni2022], and that is why taking into account the specific community who is commoning is crucial to fully understand a common [@Dove2019].
 @Bollier2019 are even more radical: for them, the term "commons" should not be defined as a resource at all, but as "living social systems" who allow people to self-organize to address shared problems.
@@
 
-Commons are currently receiving more and more attention because they function outside of the capitalist system, they respect the Earth by giving mutual benefits to their members, and they could be the needed change toward more sustainable and fair economy and society [@Meroni2022; @Seravalli2018a].
+Commons are currently receiving more and more attention because they function outside of the capitalist system, they respect the planet by giving mutual benefits to their members, and they could be the needed change toward more sustainable and fair economy and society [@Meroni2022; @Seravalli2018a].
 In fact, having small groups with a high perception of risk and a minimal uncertainty in collective goal, possibly focused on regional issues, could significantly improve the probability of success in attaining common goals related to sustainability [@Pacheco2014].
@@
 
-In order for the commons to be successful, its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998].
+In order for a common to be successful, its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998].
 However, this cooperation can be difficult to achieve.
 This is explained by two characteristics of the commons' social dynamics.
-First, there is a strong asymmetry between individual and collective: the latter has a strong impact on the individual, while personal decisions have a smaller effect on the collective [@Kramer1984].
-Therefore, if people are uncertain about others' cooperation, the best solution is pursuing their personal self-interest.
-Secondly, in a commons situation, every member faces a conflict between individual, short-term interests and collective, long-term ones [@Hardin1968].
+First, there is a strong asymmetry between individual and collective, with collectivity having a strong impact on the individuals and personal decisions having a smaller effect on the group [@Kramer1984].
+Therefore, if people are uncertain about others' intentions, the best solution is pursuing their personal self-interest.
+Secondly, in a common, every member faces a conflict between individual, short-term interests and collective, long-term ones [@Hardin1968].
 For instance, a fisher could be tempted to fish in large quantity from a common basin, but if every other fisher did the same there would not be enough fish for the following seasons.
@@
 
-It exists different approaches to the study of cooperation.
+There are different approaches to the study of cooperation.
 For instance, classical economic theories consider individuals as completely rational and always maximizing (expected) utility [@Edwards1954].
@@
 
-Like social dilemma experiments challenge economic and evolutionary assumptions about cooperation, so do observations of real-life commons with Hardin's "Tragedy of the Commons": in fact, there are many examples of successful commons [e.g.
+Like social dilemma experiments challenge economic and evolutionary assumptions about cooperation, so do observations of real-life commons with Hardin's "Tragedy of the Commons": there are many examples of successful commons [e.g.
 @Ostrom1990; @Franzen2019].
 A possible explanation is the Greed Efficiency Fairness hypothesis: people's greed to pursuit their personal interest is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
-Thus, cooperation is not always driven by personal interest, and people care about others' and environment's welfare [@Torsvik2011; @VanVugt2009].
+Thus, cooperation is not always driven by personal interest, and people care about others and environment [@Torsvik2011; @VanVugt2009].
 
@@
 A way to start to fill this gap is to apply results of social dilemma to the commons.
-Linking this two topics is pertinent for at least three reasons.
+Linking these two topics is pertinent for at least three reasons.
 First, social dilemmas and commons share the same basic conflict between personal and collective interests [@Hardin1968; @Dawes1980].
@@
 @Reindl2019; @Ros-Galvez2015].
-Finally, others studies already used the social dilemma framework to study real-life commons [e.g.
+Finally, others studies already used a social dilemma framework to study real-life commons [e.g.
 @Hartl2022].
 
-Based on these evidences, the aim of the present review is to use social dilemma literature to gain insights into cooperation in commons by (a) identifying individual factors that can shape it and (b) understanding which techniques groups can implement to encourage their members to cooperate.
+Based on these evidences, the aim of the present review is to use social dilemma literature to gain insights into cooperation in commons by (a) identifying individual factors that can shape it and (b) understanding which strategies groups can implement to encourage their members to cooperate.
 It is important to note that the point (b) will focus exclusively on bottom-up strategies that groups can adopt, and not on top-down solutions like privatization or centralized control of the resource.
-In fact, it is well demonstrated that members of a commons can efficiently manage it without the intervention of an external institution [@Larsson2016].
+In fact, it is well demonstrated that members of a common can efficiently manage it without the intervention of an external institution [@Larsson2016].
 Moreover, bottom-up solutions are often more efficient than the two others [@Ostrom1990].
@@
 
-Given the exploratory nature of this paper, a scoping review approach is adopted [@Munn2018].
+Given the exploratory nature of this paper, a scoping review approach is used [@Munn2018].
 To conduct it, different scientific publications were analyzed in response to the research questions.
@@
 The research was made during the month of August, 2023.
-According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included.
-This allows to have an idea as complete as possible about the existing literature on cooperation in social dilemmas and commons.
-Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision of the topic.
+According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included, to have an idea as complete as possible about the existing literature on the topic.
+Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision.
 There were however some selection criteria concerning the papers' methodology and content.
 First, as mentioned in the introduction, papers investigating how an external entity/institution shapes cooperation were not included.
-Secondly, human participants were needed, so papers who studied social dilemmas with an agent-based model methodology were also excluded.
+Secondly, human participants were needed, so papers who studied social dilemmas with an agent-based model were also excluded.
 Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.
@@
 After deleting the duplicates, the count was of 4586.
-Based on titles and abstracts, 4321 articles were eliminated, leaving 253 texts to examine.
-After a full-text evaluation of the remaining papers, 90 were selected for the present review.
-Figure 1 resumes this selection procedure.
-
-```{r}
-library(DiagrammeR)
-library(webshot2)
-DiagrammeR::grViz("digraph {
-graph [layout = neato, rankdir = TB]
-
-node [shape = rectangle]       
-rec1 [label = 'Papers identified from search engines
-n = 5210', pos='0,0!', width = 4, height = 0.5]
-rec2 [label = 'Duplicates
-n = 624', pos='4,0!', width = 2, height = 0.5]
-rec3 [label = 'Papers screened based on titles and abstracts
-n = 4586', pos='0,-1!', width = 4, height = 0.5]
-rec4 [label = 'Papers not suitable
-n = 4333', pos='4,-1!', width = 2, height = 0.5]
-rec5 [label = 'Papers read completely
-n = 253', pos='0,-2!', width = 4, height = 0.5]
-rec6 [label = 'Papers not suitable
-n = 164', pos='4,-2!', width = 2, height = 0.5]
-rec7 [label = 'Papers included
-n = 89', pos='0,-3!', width = 4, height = 0.5]
-
-# edge definitions with the node IDs
-rec1 -> rec2
-rec3 -> rec4
-rec5 -> rec6
-rec1 -> rec3 -> rec5 -> rec7
-}",
-height = 500)
-```
+Based on titles and abstracts, 4333 articles were eliminated, leaving 253 texts to examine.
+After a full-text evaluation of the remaining papers, 89 were selected for the present review.
+Figure 1 resumes this selection process.
 
@@
 @Zhang2019].
-The type of paradigm used was most of the time a public good game (where participants could decide how much to contribute to a public good, e.g.
+The type of paradigm could be a public good game (where participants could decide how much to contribute to a public good, e.g.
 @Torsvik2011) or a common resource game (where participants could decide how much to take from a common resource, e.g.
@@
 The second category is "real-life social dilemma situation" (*N*=7), and investigated cooperation in different real-life situations with a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
-Thirdly, "real-life commons" (*N*=4) refers to papers who studied cooperation with participants that were members of a commons in their everyday life.
+Thirdly, "real-life commons" (*N*=4) refers to papers who studied cooperation with participants that were members of a common in their everyday life.
 Finally, papers in the category "commons modeled by a social dilemma experiment" (*N*=3) used a laboratory social dilemma paradigm, but with clear references to a concrete common.
@@
 
-The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results: sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], and sometimes there was no differences.
-In general, meta-analysis found a non significant effect size [e.g.
+The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results.
+Sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], but, in general, meta-analysis found a non significant effect size [e.g.
 @Balliet2011; @Spadaro2023].
@@
 
-One of the most observed moderator of this effect is the interaction partners.
+Interaction partners can moderate this effect.
 In fact, in a social dilemma experiment, women were more cooperative toward strangers than men, while men cooperated more in a group of friends.
@@
 These results seem to indicate that men accord more importance at the relationship with other members than women.
-@Gomez-Ruiz2020 also got to the same conclusion by showing that the creation of a team identity enhanced men's cooperation, but had no effects on women.
+In fact, the creation of a team identity enhances men's, but not women's, cooperation [@Gomez-Ruiz2020].
 Moreover, in a social dilemma with many iterations, men, but not women, tended to increase their cooperation over time [@Balliet2011].
@@
 In general, groups composed by men only are more cooperative than only-women groups.
-This is explained by the fact that women are generally less achievement oriented and more socially oriented than men: they are therefore less concerned by the maximization of their personal payoff and more about relative payoff.
-Thus, the defection strategy allows them to play defensively and to avoid earning less than the other players [@Colman2018].
-Moreover, men displayed higher levels of gratitude and trust in same-sex groups than women [@Peshkovskaya2019].
+This is explained by the fact that women, compared to men, are generally less concerned by the maximization of their personal payoff and more about relative payoff.
+Thus, the defection strategy allows them to avoid earning less than the other players [@Colman2018].
+Moreover, men display higher levels of gratitude and trust in same-sex groups than women [@Peshkovskaya2019].
 On the other side, women cooperate more in mixed group.
@@
 The overall group composition also have an impact on cooperation: in general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023].
-However, @Barrero-Amortegui2021 showed that the level of resource exploitation is linked to the number of women in a group, but that this link is mediated by the signature of an agreement about extraction.
-More precisely, in their experiment, groups with a majority of women extracted more resources from a common good (and thus cooperated less) before the signature of the agreement, but also showed the largest reduction of the exploitation level after the agreement was signed.
+However, @Barrero-Amortegui2021 showed that groups with a majority of women were more cooperative only after the signature of an agreement against excessive harvesting of a common resource.
 Therefore, even the effect of group composition seems to be subjected to moderator variables.
@@
 According to social psychology and evolutionary theories, the author expected women to defect more when fear incentives were present, and men to defect more with greed incentives.
-Although he could corroborate only the second hypothesis, his intuition about women being more sensitive to the fear of being exploited is confirmed by other studies.
+Although only the second hypothesis was corroborated, his intuition about women being more sensitive to the fear of being exploited is confirmed by other studies.
 For example, women level of cooperation is predicted by their trust in their interaction partner, while men's trust and cooperation are not linked [@Irwin2015].
@@
 In conclusion, "at times women are more cooperative than men, less cooperative than men, or equally as cooperative as men.
-These variations are explained, in large part, by structural differences and identities triggered by those differences" [@Sell2009].
+These variations are explained, in large part, by structural differences and identities triggered by those differences" [@Sell2009, p.
+322].
 The context in which men and women interact is therefore essential to predict if a gender will cooperate more than the other, and which one.
@@
 
-Few studies have investigate how social status impact cooperation, and their results do not allow to draw a clear conclusion about this effect.
-
+Few studies have investigated how social status impact cooperation, and their results do not allow to draw a clear conclusion about this effect.
 For instance, advantaged members (i.e.
@@
 Moreover, a form of solidarity is observed between low-status members: in a study where participants had the opportunity to punish others for a non-cooperative behaviour, low-status members punished significantly less other low-status participants [@Chen2022].
-Also, in an experiment where participants were randomly advantaged during the interaction, @Camera2020 found that subjects who received a lot of advantages were discriminated by others, and especially by the ones who were rarely advantaged.
+Also, in another experiment, participants were randomly advantaged during the interaction: subjects who received a lot of advantages were discriminated by others, and especially by the ones who were rarely advantaged [@Camera2020].
 
@@
 Moreover, similarly to what @Sell2009 affirmed about the effects of gender and social status, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
-This shows that social identity and social status are deeply connected, and that therefore it is difficult to separate their effects on cooperation.
+This shows that social identity and social status are deeply connected, and that it is difficult to separate their effects on cooperation.
 
@@
 Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect.
-Group identification can also easily be implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992].
+Group identification can also be easily implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992].
 Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].
@@
 However, the fact that not all members identify with their group to the same extent can lead to inequalities on cooperation.
-For example, @VanVugt2009 mentioned that high identified individual can even compensate, by cooperating more, for other in-group members' defection.
-The same result was also found by @Arora2016: high identified individuals cooperated more than low identified ones when faced to an in-group participant who defected (and this difference was not found when the defector was not a group member).
+For example, @VanVugt2009 mentioned that high-identified individual can even compensate, by cooperating more, for other in-group members' defection.
+The same result was also found by @Arora2016: high-identified individuals cooperated more than low-identified ones when faced to an in-group participant who defected (and this difference was not found when the defector was not a group member).
 However, this compensation came with a cost, since participants who compensated for an in-group defector reported lower trust toward this person.
@@
 In fact, in-group identification can be enhanced via a competition between different groups, because in such a context individual's and group's interests are aligned [@Puurtinen2009].
-In a social dilemma experiment, these authors demonstrated that cooperation was higher in an intergroup-competition condition than in a non-competitive condition.
+In fact, these authors demonstrated that cooperation was higher in an intergroup-competition condition than in a non-competitive condition.
 Moreover, when participants had to compete against other groups, they reported higher levels of anger toward in-group free-riders and they felt more guilty after a defection decision.
 In another experiment using a public resource game, intergroup competition reduced resources consumption, while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
-This shows that the increase of cooperation via competition is due to group membership factors, and not to competition per se.
+This shows that the increase of cooperation via competition is due to group membership factors, and not to competition in itself.
 
-However, despite the observed beneficial effects of inducing an intergroup competition, in a real-life situation this could be harmful.
+However, despite the observed beneficial effects of inducing an intergroup competition, this could be harmful in real-life situations.
 This is especially true in case of resources that are shared between several groups, which are at greater risk of over-exploitation in case of intergroup competition [@VanVugt2009].
@@
 Finally, social identity does not only have a main effect on people's cooperation, but can also moderate other factors' impact.
-For example, monetary incentive are more effective at enhancing cooperation of low identified individual than of high identified ones [@VanVugt2009].
-Moreover, a previous group failure can decrease cooperation between low identified member, but this effect is not observed in people who have a strong identification with their group [@Jackson2011; @Jackson2012].
+For example, monetary incentive are more effective at enhancing cooperation of low-identified individual than of high-identified ones [@VanVugt2009].
+Moreover, a previous group failure can decrease cooperation between low-identified member, but this effect is not observed in people who have a strong identification with their group [@Jackson2011; @Jackson2012].
 
@@
 One of the most studied is the Social Value Orientation (SVO), that divides people in pro-social and pro-self based on how much they value their own and others' outcomes in situations of interdependence [@Balliet2009].
-The effect of SVO on cooperation is very consensual: in a meta-analysis, 81 out of the 82 papers examined reported than pro-social cooperated significantly more than pro-self [@Balliet2009].
+The effect of SVO on cooperation is very consensual: in a meta-analysis, 81 out of the 82 papers examined reported that pro-social cooperated significantly more than pro-self [@Balliet2009].
 
 However, this general effect is subjected to several moderators.
-For example, pro-self individuals cooperated more in a game where economic incentives to cooperation were present than in a game without such incentives, while pro-social did not displayed this difference and showed high levels of cooperation in both contexts [@Emonds2011].
+For example, pro-self individuals cooperated more in a game where economic incentives to cooperation were present than in a game without such incentives, while pro-social did not display this difference and showed high levels of cooperation in both contexts [@Emonds2011].
 A similar effect is also described by @Balliet2009, who found a stronger effect of SVO in unpaid games than in paid ones, because, when monetary rewards were present, pro-self increased their cooperation.
@@
 Moreover, SVO has a stronger effect if there is an uncertainty about the number of individuals having access to a common resource: when the number of other participants was not known, pro-social, but not pro-self, reduced their harvesting comparing to a group-size certainty condition [@DeKwaadsteniet2008].
-The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self only think at their own personal interest.
+The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self mainly think at their own personal interest.
 Also, SVO effect is partly explained by trust, i.e.
@@
 In fact, in @VanLange1998, pro-social individuals with a low level of trust did not make different decisions than pro-self individuals, while the most cooperative were pro-social with an high level of trust.
-Finally, @Lu2019 showed that the intuitive choice of pro-social individuals is cooperation, while for pro-self is defection.
-However, pro-self can cooperate more if they have the possibility to deliberate about the situation, because they can realize that the best strategy to maximize the joint (and thus personal) outcome is cooperation.
+Finally, the intuitive choice is to cooperate for pro-social individuals, while it is to defect for pro-self [@Lu2019].
+However, pro-self can cooperate more if they have the possibility to deliberate about the situation, because they realize that the best strategy to maximize the joint (and thus personal) outcome is cooperation.
 
@@
 Levels of harvesting from a common resource are also lower between left-wingers than right-wingers [@Fosgaard2019].
-Moreover, humility and honesty are significant predictor of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018].
+Moreover, humility and honesty are significant predictors of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018].
 Self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017].
@@
 
-In social dilemma situations, trust can be defined as the "expectations of others' benevolent motives in situations that involve a conflict between self and collective interests" [@Balliet2013, p.1].
+Trust can be defined as the "expectations of others' benevolent motives in situations that involve a conflict between self and collective interests" [@Balliet2013, p.1].
 Trust can be dispositional or a state; the former is an individual's general trait, and is usually measured with personality scales, the latter is linked to the context, and can be operazionalized by expectations about a partner's behaviour in a specific situation [@Balliet2013].
-The two are positevely correlated [@Lubke2021], and therefore both have a positive general effect on cooperation [@VanLange2013; @Balliet2013].
+The two are positively correlated [@Lubke2021], and both have a positive general effect on cooperation [@VanLange2013; @Balliet2013].
 In fact, high levels of trust are associated with more contributions to a public good [@Kocher2015], and a participant's contribution in a public good game can be predicted by her beliefs about others' contributions [@Smith2013].
@@
 Finally, in a study about self-administered outlets in Swiss farms (i.e.
-outlets where nobody monitors if people pay or not their purchase), @Franzen2019 found that a farmer's general trust in other people is a significant predictor of the probability of having such an outlet.
+outlets where nobody monitors if people pay or not their purchases), @Franzen2019 found that a farmer's general trust in other people is a significant predictor of the probability of having such an outlet.
 Concerning the moderators, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
@@
 2].
-This authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to adapt to norms.
+These authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to comply to norms.
 Moreover, the effects of perceived costs and benefits of the action are less predictive in people with high institutional trust.
@@
 However, general beliefs about others' cooperation are quite low compared to the actual behaviours, and this trust gap can undermine cooperation, since people's actions are significantly predicted by their beliefs [@Lubke2021].
-In order to increase trust and, consequentely, cooperation, it is therefore it is essential to provide people with reliable information about others' behaviour.
+In order to increase trust and, consequently, cooperation, it is therefore essential to provide people with reliable information about others' behaviour.
 
@@
 Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^2].
-In the litterature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
+In the literature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
 In general, when there is the possibility for participants to punish others members based on their contributions, cooperation is higher than when this is not possible [e.g.
@@
 
-[^2]: Since the present paper's interest is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
+[^2]: Since the interest of the present review is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
 Incentives given by third party have also an effect on cooperation, but they are not included in this review.
 
-However, this main results is subjected to several moderator factors.
+However, this main results is subjected to several moderators.
 First, the punishment have a bigger impact on cooperation if its implementation is costly for the punishers than if it is free [@Balliet2011a], but at the same time the cost should not be too high [@Egas2008].
@@
 
-However, punishment must be applied with carefulness: @Rockenbach2019 compared the punishment strategy of different groups, and found that the most successful ones (whose members had the highest payoff at the end of the experiment) punished with caution and not in early stages of the game.
+However, punishment must be applied with carefulness: @Rockenbach2019 compared the strategies of different groups, and found that the most successful ones (whose members had the highest payoff at the end of the experiment) punished with caution and not in early stages of the game.
 In these groups, a norm of when and how punishment should be applied seems to exist.
@@
 @Balliet2011a].
-
 In a meta-analysis, @Balliet2011a found that rewards had a stronger effect on cooperation if their implementation was costly rather than free, and in iterated, rather than single, interactions.
@@
 In general, incentives seem to be a powerful tool to enhance cooperation, but they have a dark side.
-In fact, they reduce participants' intrinsic motivation [@VanDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+First, they reduce participants' intrinsic motivation [@VanDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
 In fact, @Schlosser2018 demonstrated that people's level of justice sensitivity could predict their contributions to a public good game, but this link disappeared when a punishment system was introduced.
-Also, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members[@Irwin2014], and especially the trust in the fact that others are internally motivated to cooperate [@Mulder2006].
-Therefore, if incentives are removed, cooperation drops [@Irwin2014; @Mulder2006].
+Secondly, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members, and especially the trust in the fact that others are internally motivated to cooperate.
+This reduced trust in others drops cooperation levels if incentives are removed [@Irwin2014; @Mulder2006].
 
@@
 Moreover, communication's effect is stronger in large groups: when many people are present cooperation rates are lower, so communication between members can buffer this negative effect [@Balliet2010].
-Finally, if communicate with others requires a personal cost, the effect is weaker than if communication is free [@Janssen2014].
+Finally, if communicating with others requires a personal cost, the effect is weaker than if communication is free [@Janssen2014].
 
 The content of the messages is also essential.
-@Koessler2021 identified four steps that need to be present when participants in a social dilemma situation communicate: problem awareness, identification of strategies, agreement and ratification.
+@Koessler2021 identified four steps necessary for an effective communication in social dilemmas: problem awareness, identification of strategies, agreement and ratification.
 In another study, groups who used communication to foster a common social identity, promote cooperative social norms and ensure that all the players publicly committed displayed higher rates of cooperation than other groups [@Adams2022].
@@
 
-Another factor that influences the effect that communication has on cooperation is whether individuals exchange messages before, during or after the cooperative interaction phase.
+Another factor that influences the effect of communication on cooperation is whether individuals exchange messages before, during or after the cooperative phase.
 Concerning the post-game communication, @Kumakawa2013 found that receiving a feedback about the cooperation choice made previously can increase cooperation in the following interactions, especially if the feedback is negative.
@@
 Finally, several studies investigated the effect of gossip as a form of communication that can increase cooperation.
-Gossip is defined as a spread of reputational information about another person [@Feinberg2014], and it increases cooperation in two ways: first, if people know that gossip is possible, they tend to cooperate more to avoid the risk of being the target of such gossip and therefore of being excluded from following interactions.
-Secondly, having information about the past behaviour of potential cooperation partners can help to select the most cooperative people in an interaction situation [@Feinberg2014].
+Gossip is defined as a spread of reputational information about another person [@Feinberg2014], and it increases cooperation in two ways.
+First, if people know that gossip is possible, they tend to cooperate more to avoid the risk of being the target of such gossip and therefore of being excluded from following interactions.
+Secondly, having information about the past behaviour of potential partners can help to select the most cooperative individuals in an interaction situation [@Feinberg2014].
 Moreover, the same authors found that pro-social individuals gossiped more than pro-self.
@@
 Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour [@VonBorgstede2018].
-@Thogersen2008 studied the effect of social norms on daily social dilemma situations such as environmental behaviours, and found that both injunctive (what others approve) and descriptive (what others do) are positively related to behaviours.
+@Thogersen2008 studied the effect of social norms on daily social dilemma situations such as environmental behaviours, and found that both injunctive (what others approve) and descriptive (what others do) norms are positively related to behaviours.
 Moreover, cooperation can be maintained via social norms, because people who do not respect them are susceptible of social sanctions.
@@
 There are several explanations of social norms' effect on cooperation.
-Firstly, according to the appropriateness framework, when taking a decision people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
+First, according to the appropriateness framework, when taking a decision people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
 Therefore they need to define the situation as a cooperative task and to strongly identify with the group [@VanLange2013].
@@
 Testing this assumption, @Arora2012 showed that a greater identification with social group lead to higher levels of cooperation.
-The second explanation concerns conformity: in general people adapt their cooperation to others' behaviour, but this is usually explained by the reciprocity principle (cooperate enhances the probability that others will do the same, and therefore that the final payoff will be higher) [@Bardsley2005a].
+The second explanation concerns conformity: in general people adapt their cooperation to others' behaviour, but this is usually explained by the reciprocity principle (cooperation enhances the probability that others will do the same, and therefore that the final payoff will be higher) [@Bardsley2005a].
 However, these authors demonstrated that people conform to others' behaviour even if this has no impact on their personal payoff.
@@
 In conclusion, social norms have a significant effect on people's cooperation in social dilemma situations.
-Since they are quite easily modified [@Weber2008], shaping cooperative norms can be a powerful instrument to improve cooperation.
+Since they are quite easily modified [e.g.
+@Weber2008], shaping cooperative norms can be a powerful instrument to improve cooperation.
 
@@
 Moreover, this effect is displayed especially in situations when individuals face a cost when cooperating and know that they will not get any personal benefit.
-For instance, @Butz2021 demonstrated that, in a public good game where a part of contributions was donated to a charity association, disclosing identity increased cooperation, but only if the donation was deducted from participants' payoff.
+For instance, @Butz2021 demonstrated that, in a public good game where a part of contributions was donated to a charity association, disclosing identities increased cooperation, but only if the donation was deducted from participants' payoff.
 In the same direction, @VanVugt2010a found that, when actions were public, contributions were higher if the public good was already attained or unattainable, and therefore if participants did not have a personal interest in cooperating.
@@
 A possible way to do this is to reduce group's size.
-In fact, according to @Romano2016, a larger group leads to de-individuation, because it is more difficult to understand who is defecting.
+In fact, according to @Romano2016, larger groups lead to de-individuation, because it is more difficult to understand who is defecting.
 Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable.
@@
 This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good.
-Increasing cooperation through the reduction of anonymity is also possible by giving public feedbacks about people's cooperation [@Przepiorka2020].
 
@@
 In conclusion, reducing anonymity during interactions is essential to improve cooperation, because this can facilitate the implementation of others cooperation-enhancing techniques [@Wang2017].
-Moreover, it exists several low-cost method to make situations non-anonymous.
+Moreover, there are several low-cost method to make situations non-anonymous.
 
@@
 Through a scoping review approach, the current paper identified several factors that could impact cooperation in social dilemmas and in commons.
-Some of this elements can be related to the principles to successfully manage a common resource that Ostrom drew after the observation of several communities [@Ostrom1990].
+Some of these elements can be related to the principles to successfully manage a common resource that @Ostrom1990 drew after the observation of several real-life cases.
 In fact, her first statement says that commons need clearly defined boundaries: therefore, it must be clear who has the right to benefit from the common resource and who does not.
@@
 Even if Ostrom developed this principle on a more organizational level, the secondary effect of creating a social identity for commons' members can also contribute to improve cooperation.
-Moreover, individuals who are part of the group, and who are therefore affected by the commons' rules, must be able to participate in modifying them (principle 3).
-This statement shows the importance of social norms, and especially of injunctive ones, namely what is morally approved in a social group [@Cialdini1990].
-Moreover, in order to modify such norms, people have to communicate [@Bicchieri2002].
-Communication is also essential for principle 6, who posits that members of a commons must have access to low-cost arenas to resolve conflicts.
+Moreover, individuals who are part of the group, and who are therefore affected by the common's rules, must be able to participate in modifying them (principle 3).
+This statement shows the importance of social norms, especially of injunctive ones, namely what is morally approved in a social group [@Cialdini1990].
+Moreover, in order to modify such norms, people must be able to communicate [@Bicchieri2002].
+Communication is also essential for principle 6, who posits that members of a common must have access to low-cost arenas to resolve conflicts.
 In fact, communication helps to reach an agreement to the strategy that needs to be followed [@Hopthrow2005].
 Finally, Ostrom's principles 4 and 5 underline the importance of incentives, more precisely in the form of a monitoring system implemented by members themselves and a graduate sanctions system toward violators of the rules.
-The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they are worried about others' approval [@Nelissen2013; @Rege2004].
+The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they worry about others' approval [@Nelissen2013; @Rege2004].
 On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^3]
@@
 This is understandable when considering her economic approach to the study of the commons.
-However, taking into account the social dynamics and the individuals who interact within the commons is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
+However, taking into account the social dynamics and the individuals who are commoning is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
 For this reason, this paper made a step further and identified some individual characteristics affecting the efficiency of commons.
@@
 First, according to the analyzed papers, trust has a positive effect on cooperation.
-In fact, since cooperation involves the risk that others will defect, trusting others is essential [@Henry2011].
-Moreover, according to the principle of reciprocity, people cooperate more when facing cooperative partners [@Fehr2022; @VanLange1999].
+In fact, since cooperation involves the risk that others will defect, trusting others is essential in this context [@Henry2011].
+Moreover, according to the principle of reciprocity, people cooperate more facing cooperative partners [@Fehr2002; @VanLange1999].
 However, in real-life situation it is not always possible to know exactly others' contributions, and therefore trust (i.e.
 beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012].
-Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can (not) be successful.
+Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can(not) be successful.
 These evidences fit well with the more general result showing that dispositional trust is a predictor of pro-social behaviour [@Wu2020].
-Finally, this link has a biological grounding: being trusted increases the level of oxytocin (a hormone that helps creating attachment between individuals), and this, in turn, improve the cooperative behaviour toward the person who first showed trust [@Campbell2010].
 
 Secondly, Social Value Orientation has also an impact on cooperation: in fact, there are individual differences in motivation when people have to decide how to allocate a resource between themselves and others [@Murphy2011].
-More specifically, pro-social individuals accord more importance to others' and joint outcome than pro-self, and they are therefore more cooperative [@VanLange1999].
+More specifically, pro-social individuals are more cooperative than pro-self because they value more others' and joint outcome [@VanLange1999].
 This is also confirmed experimentally by @Fiedler2013, who showed that pro-social and pro-self processed the situation in a similar way, but accorded different weights to the outcome for themselves and others.
-Finally, since they value more the equality in outcomes, pro-social can behave even less cooperatively than pro-self when reciprocity is violated [@VanLange1999].
+Finally, since they value the equality in outcomes, pro-social can behave even less cooperatively than pro-self when reciprocity is violated [@VanLange1999].
 
-Concerning gender effect on cooperation, the existing literature about gender stereotypes would predict that women cooperate more than men.
-In fact, according to the stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012], and this lead to the perception that women's intentions are more benevolent than those of men [@Ellemers2017].
+Concerning gender effect on cooperation, the existing literature would predict that women cooperate more than men.
+In fact, according to gender stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012], and this lead to the perception that women's intentions are more benevolent than those of men [@Ellemers2018].
 In line with these predictions, @Westermann2005 found that, managing a natural resource, groups where women were present displayed more solidarity and collaboration comparing to all-men groups.
-Despite these evidences, this review found that there is no general gender effect on cooperation and that a lot of moderator are at stake.
+Despite these evidences, this review revealed that there is no general gender effect on cooperation and that a lot of moderator are at stake.
+This shows that this effect is extremely dependent on the situation.
 Moreover, gender is always embedded with social status dynamics [@Sell2009], and it is therefore difficult to separate the two effects.
@@
 This is negatively correlated with concern about others and altruism [@Pratto1994].
-Finally, although the differences between social statuses, people tend to cooperate more with individuals of their same social class than with others, and this effect is manly due to group identification [@Aksoy2019].
-Social status is therefore deeply connected to the last of the identified individual factors, group identification.
+Finally, although there are differences between social statuses, people tend to cooperate more with individuals of their same social class than with others, and this effect is manly due to group identification [@Aksoy2019].
+Social status is therefore deeply connected to the last of the individual factors, group identification.
 
@@
 In fact, in-group identification is the main predictor of collective action in the Social Identity Model of Collective Action [SIMCA, @VanZomeren2008].
-Moreover, @Fritsche2018 apply this social identity approach to environmentalism with the Social Identity Model of Pro-Environmental Action (SIMPEA).
+Moreover, @Fritsche2018 apply this social identity approach to environmentalism with the Social Identity Model of Pro-Environmental Action (SIMPEA), where group identification is once again the main predictor.
 According to its authors, the climate crisis has the structure of common good dilemmas, because environmental goals can be attained only if everybody cooperates.
-Group identification is once again the main predictor of such collective actions.
+These results confirm the strong consensus found about the link between social identification and cooperation.
 
@@
 
-Until now, the identified factors has been discussed separately.
-However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.
-For instance, incentives are more useful to improve cooperation of low-, rather than high-identified, group members [@VanVugt2009]; trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019].
-These connections are also confirmed in the litterature.
+Until now, the identified factors has been discussed separately. However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.
 
--
+For instance, there are gender differences in trust and SVO.
+More specifically, trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019], and a study assessing SVO found that women were significantly more prevalent between pro-social and less between pro-self [@VanLange1999].
+Also, SVO and trust are positively correlated [@Ackermann2019], and @Bogaert2008 even theorized that the expectancy about others' behaviour is actually a part of the construct of SVO.
+Therefore, pro-self individuals show less cooperation in part because they expect others not to cooperate.
+Finally, trust can differ based on social status: high-status people display more generalized trust (i.e.
+general belief on others' benevolence), while low-status more depersonalized trust (i.e.
+more trust in other members of their in-group, just because of their membership) [@Navarro-Carrillo2018].
+This is consistent with the results about social status mentioned previously: since high-status individuals perceive the system as fair [@Caricati2012], it is easier for them to believe that others have benevolent intention.
+On the other hand, low-status individuals see themselves as more similar between each-other than high status [@Lorenzi-Cioldi2002], therefore they trust other members of their group just because of their belonging.
 
-    -   @Janssen2015: confirmation of several factors
+Secondly, communication impacts several other factors.
+For instance, it plays an essential role in shaping social norms [@Hogg2006; @Bicchieri2002] and it can improve cooperation by signalling a person's intentions and trustworthiness [@Janssen2015].
+Moreover, in a study about organizations, communication was a strong predictor of commitment, that is a component of group identification.
+This link was especially present for vertical communication, i.e.
+exchanges about organizational strategies between members at different level of the hierarchy [@Postmes2001].
+Therefore, having the opportunity to communicate about the strategies that need to be implemented improve one's identification with the group.
 
-        -   cheap talk (= communication who does not affect the payoff of the game) can also improve cooperation because it signals intentions and trustworthiness
+Another factor that influences others is group identification.
+First, as a consequence of the Social Identity Theory, people who strongly identify with their group are more willing to comply to the group's norms and to pursuit the group's goals [@Tajfel1974].
+Therefore, high-identified members need less cooperation-enhancing measures.
+For instance, incentives are more useful to improve cooperation of low-, rather than high-identified, group members [@VanVugt2009], because high-identified members are already motivated to cooperate.
+Similarly, given their stronger willingness to act for the group's good, high-identified individuals cooperate even in an anonymous condition, while low-identified acted more for the group goal if their actions were accountable [@Barreto2000].
 
-        -   Behavior motivated by moral obligations and social preferences can be undermined by economic interventions
+As already mentioned in the results section, anonymity underlies several other factors.
+First, when actions are accountable, people are more concerned about others' approval and therefore show more conformity to social norms [@Nelissen2013; @Rege2004].
+Also, in large groups [where, as a consequence of the group size, levels of anonymity are higher, @Romano2016] it is more difficult to evaluate the trustworthiness of other participants than in small ones [@Janssen2015].
 
-        -   Larger groups will make it more difficult to evaluate the trustworthiness of all other participants and make it easier to free ride on actions of others
+Finally, economic incentives can have a negative impact on people's internal motivation to cooperate, because they change the perception of the context from ethical to economic [@Janssen2015; @VanVugt2009].
+Therefore, even if incentives such as punishments or rewards can be useful to improve cooperation, they reduce the impact of the other factors.
+For instance, when incentives are present, people think that others cooperate because of them, and this leads to reduced levels of trust [@Irwin2014].
 
--   group factors: communication linked to social norms and social identity + anonymity underlies all the others + incentives has dark sides
-
-    -   @Ackermann2019: link between SVO and trust + @Bogaert2008
-
-    -   @Navarro-Carillo2018: high status more generalized trust, low status more in-group depersonalized trust (because more social networks) =\> link with gender and trust
-
-    -   @Aksoy2019: see if class or group had a stronger impact =\> could be a reference to say that it is important to create a common social identity that makes weaker the effect of previous belongings **???**
-
-    -   @Hogg2006: communication and social identity
-
-    -   @Chou2013: link between trust and collective efficacy, so that trust could also fit in SIMPEA and SIMCA
-
-    -   de-individualized trust = more trust in people of in-group just because they are in-group
-
-    -   @VanLange1999 =\> women were more prevalent between pro-socials and less between pro-selves (secondary result)
-
-    -
-
-```{=html}
-<!-- -->
-```
--   individual factors: some of them can be manipulated to improve cooperation, some of them must just be taken into account when "planning"
-
--   group factors = strategies that groups can implement to improve cooperation
-
--   =\> talk about the practical implication of this (interventions, ...) + say that a factor will have not only an impact on cooperation, but also on other factors
+In summary, this review has practical implications and can be used as a guide for commons members to design campaigns or activities to improve cooperation.
+In fact, some of the identified factors can be manipulated in order to create better conditions for cooperation to arise.
+Moreover, since the different elements are linked, they can impact cooperation both directly and indirectly, via mediation and moderation effects.
+Based on the consensus of the results and on the quantity of connections with other elements, the factors that seem to have a stronger effect are trust, communication, group identification and accountability of actions.
+Therefore, interventions based on this elements can be very powerful tools to improve cooperation in commons.
+On the other hand, some individual factor cannot be manipulated, but must be taken into account when designing an intervention.
+For instance, commons' composition in terms of gender and social status can have a large influence on the overall cooperation.
 
@@
 
-To conclude, this review's aim was to provide an overview of the factors that affect cooperation in social dilemma situations such as commons.
-While attaining this goal, the current paper has also highlighted a lack of systematic studies about cooperation in commons.
-+ say the first important practical implication that we can already deduce (social identity, ...)
+To conclude, since cooperating is essential for the success of a common, this review's aim was to provide an overview of the factors that affect cooperation in social dilemma situations such as commons.
+While attaining this goal, the current paper also highlighted a lack of systematic studies about cooperation in commons.
+However, several limitations can be identified.
 
-However, it is not without limitations, thus further researches are necessary to reach a deeper understanding of the topic.
-First, most of the studies included had a laboratory social dilemma setting, who are simplier than real-life situations and do not allow to exactly reproduce the dynamics present in a commons [@Henry2011; @Cole2010].
-In fact, some elements such as cultural factors and specific ecological conditions affect the decision making process, and cannot be reproducted in lab experiments [@Janssen2015].
-Therefore, this papers offers a good basis about elements influencing cooperation in commons, but future studies should confirm this results in real-life settings.
+First, most of the included studies had a laboratory social dilemma setting, that is a simplification of real-life situations and do not allow to exactly reproduce the dynamics present in a common [@Henry2011; @Cole2010].
+In fact, some elements such as cultural factors and specific ecological conditions affecting the decision making process cannot be reproduced in lab experiments [@Janssen2015].
+Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings.
 Moreover, this review is not informative about the relative importance of each factor.
@@
 
-Another limitation of the current review is the lack of representation of the global population.
+Another limitation is the lack of representation of the global population.
 In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Global North.
@@
 How the different factors evolve and influence each-others over time?
-That is why longitudinal investigations about the evolution of commons are needed.
+For this reason, longitudinal investigations about the evolution of commons are needed.
+
+In conclusion, a successful commons relies on the cooperation of its members, but this topic has not yet been extensively studied.
+Thus, further researches are needed to address the limitations of the current study and to reach a deeper understanding of this topic.
 
@@
 :::
+
+\newpage
+
+# Figures
+
+```{r}
+library(DiagrammeR)
+library(webshot2)
+DiagrammeR::grViz("digraph {
+graph [layout = neato, rankdir = TB]
+
+node [shape = rectangle, fontsize = 14, fontname = Arial]       
+rec1 [label = 'Papers identified from search engines
+n = 5210', pos='0,0!', width = 4.5, height = 0.5]
+rec2 [label = 'Duplicates
+n = 624', pos='4,0!', width = 2, height = 0.5]
+rec3 [label = 'Papers screened based on titles and abstracts
+n = 4586', pos='0,-1!', width = 4.5, height = 0.5]
+rec4 [label = 'Not suitable papers
+n = 4333', pos='4,-1!', width = 2, height = 0.5]
+rec5 [label = 'Papers read completely
+n = 253', pos='0,-2!', width = 4.5, height = 0.5]
+rec6 [label = 'Not suitable papers
+n = 164', pos='4,-2!', width = 2, height = 0.5]
+rec7 [label = 'Papers included
+n = 89', pos='0,-3!', width = 4.5, height = 0.5]
+
+# edge definitions with the node IDs
+rec1 -> rec2
+rec3 -> rec4
+rec5 -> rec6
+rec1 -> rec3 -> rec5 -> rec7
+}",
+height = 500)
+```
+
+Figure 1. Flow diagram of the scoping review selection process.

### 2023-11-03 scoping_review_short.Rmd
03.11

--- 2023-11-03 paper1_markdown.Rmd
@@
   The goal of the current scoping review is to identify the factors that impact cooperation in social dilemma situations, to gain a better understanding of what could shape cooperation in commons.
-A key-word search and a subsequent selection lead to the inclusion of 89 papers, who are used to identify 9 factors that influence cooperation both at the individual and group level.
+A key-word search and a subsequent selection lead to the inclusion of 89 papers, who are used to identify 9 factors that can influence cooperation both at the individual and group level: *gender, social status, group identification, values and personality traits, trust, incentives, communication, social norms and anonymity*.
 These factors are discussed within the existing literature on commons and cooperation.
-Finally, the practical implication of this work for commons' organization, as well as the review's limitations, are highlighted.
+*More specifically, the influences that these elements can have on each-other are highlighted, showing that the totality of factors should be taken into account when investigating cooperation in commons.* Finally, the practical implication of this work for commons' organization, as well as the review's limitations, are pointed out.
 
@@
 
-During last years, the interest in alternative ways of social organization increased drastically because of the social and ecological crises we are facing [@Euler2018].
-Commons are a possible solution, since they represent an alternative way of organizing resources not involving the classic private and public model [@Ostrom1990].
-In her seminal work, Ostrom refers to commons as a resource system equally shared between a self-managed community of users, also because of the difficulty of excluding somebody from benefiting from its use [@Ostrom1990].
-Commons can also be understood "as collaborative arrangements for value production processes that are based on participatory principles" [@Seravalli2018a, p.
-1].
-Therefore, beyond the material aspect of the commons, the notion of social practices (referred as commoning) is also essential [@Euler2018].
-Commoning is the process through which people manage to find solutions for their needs by self-organizing independently from the state or the market.
-The community is therefore engaged in defining rules to successfully manage a shared resource [@Meroni2022], and that is why taking into account the specific community who is commoning is crucial to fully understand a common [@Dove2019].
-@Bollier2019 are even more radical: for them, the term "commons" should not be defined as a resource at all, but as "living social systems" who allow people to self-organize to address shared problems.
-These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look to the people who form these communities and to their organization.
+**TO DO LIST:**
 
-Commons are currently receiving more and more attention because they function outside of the capitalist system, they respect the planet by giving mutual benefits to their members, and they could be the needed change toward more sustainable and fair economy and society [@Meroni2022; @Seravalli2018a].
-In fact, having small groups with a high perception of risk and a minimal uncertainty in collective goal, possibly focused on regional issues, could significantly improve the probability of success in attaining common goals related to sustainability [@Pacheco2014].
-Moreover, it is easier to coordinate on a local, rather than global, level [@Carpenter2011].
-Broadly, commons represent a possible solution simply by showing that alternatives to the classic model are possible [@Baibarac-Duignan2023].
+-   **try to shorten as much as possible the result section by putting detailed results on the table**
 
-In order for a common to be successful, its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998].
-However, this cooperation can be difficult to achieve.
-This is explained by two characteristics of the commons' social dynamics.
-First, there is a strong asymmetry between individual and collective, with collectivity having a strong impact on the individuals and personal decisions having a smaller effect on the group [@Kramer1984].
-Therefore, if people are uncertain about others' intentions, the best solution is pursuing their personal self-interest.
-Secondly, in a common, every member faces a conflict between individual, short-term interests and collective, long-term ones [@Hardin1968].
-For instance, a fisher could be tempted to fish in large quantity from a common basin, but if every other fisher did the same there would not be enough fish for the following seasons.
-According to @Hardin1968 and his "Tragedy of the Commons", individuals' greed to maximize their personal payoff will inevitably lead to the destruction of the common resource.
-For these reasons, it is essential to understand why people do (not) cooperate in commons, and which factors can impact cooperation.
+-   **put the references in the table (ex: gender, 11 papers --\> put the 11 references in the case)**
 
-## The study of cooperation
-
-There are different approaches to the study of cooperation.
-For instance, classical economic theories consider individuals as completely rational and always maximizing (expected) utility [@Edwards1954].
-Thus, according to these theories, individuals are not supposed to behave altruistically, namely to incur a personal cost while benefiting others [@Wittek2015].
-Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage.
-For example, the theory of competitive altruism posits that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation [@Roberts1998].
-Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
-
-Cooperation has also extensively been studied through social dilemma.
-In such situations, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
-However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
-This approach is very useful to gain insights into how cooperation works because it provides a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
-While according to economic and evolutionary theories individuals are always pursuing their self-interest (either by defecting to maximize their personal payoff, either by cooperating to increase their social status and reputation), social dilemma experiments' results show that it is not always the case.
-First, it is observed that a significant amount of people are "strong reciprocators": they are willing to use their personal resources to reward cooperators and punish defectors, even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009].
-Moreover, social dilemma experiments provided evidences suggesting that people do not always thoroughly analyze the context to take a rational decision.
-In fact, cooperation seems to be the intuitive option, while defection needs more thinking [@Kieslich2014].
-Additionally, people can also cooperate in part because they are confused about the situation [@Andreoni1995].
-In fact, @Fosgaard2017 showed that, in some experiments, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff, and these misconceptions can vary depending on how the game is presented.
-Moreover, there are individual differences in the level of rationality, i.e.
-the ability to think analytically at the situation [@Lang2018]: individuals scoring low in rationality cooperate more than individuals with an high score.
-These evidences suggest that people are not always rational in the economic, individualistic way [@Kollock1998], and that there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].
-
-## Current review
-
-Like social dilemma experiments challenge economic and evolutionary assumptions about cooperation, so do observations of real-life commons with Hardin's "Tragedy of the Commons": there are many examples of successful commons [e.g.
-@Ostrom1990; @Franzen2019].
-A possible explanation is the Greed Efficiency Fairness hypothesis: people's greed to pursuit their personal interest is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
-Thus, cooperation is not always driven by personal interest, and people care about others and environment [@Torsvik2011; @VanVugt2009].
-
-However, cooperation in commons has not been systematically studied like it has been in social dilemmas, and there is therefore a lack of knowledge about the factors that could enhance cooperation in this context.
-A way to start to fill this gap is to apply results of social dilemma to the commons.
-Linking these two topics is pertinent for at least three reasons.
-First, social dilemmas and commons share the same basic conflict between personal and collective interests [@Hardin1968; @Dawes1980].
-For this reason, commons can be considered as a particular case of social dilemma (for example, @Sussman2016 used the term of "commons dilemma").
-Secondly, cooperation and defection in social dilemma laboratory experiments can predict people's behaviour in a commons situation [e.g.
-@Reindl2019; @Ros-Galvez2015].
-Finally, others studies already used a social dilemma framework to study real-life commons [e.g.
-@Hartl2022].
-
-Based on these evidences, the aim of the present review is to use social dilemma literature to gain insights into cooperation in commons by (a) identifying individual factors that can shape it and (b) understanding which strategies groups can implement to encourage their members to cooperate.
-It is important to note that the point (b) will focus exclusively on bottom-up strategies that groups can adopt, and not on top-down solutions like privatization or centralized control of the resource.
-In fact, it is well demonstrated that members of a common can efficiently manage it without the intervention of an external institution [@Larsson2016].
-Moreover, bottom-up solutions are often more efficient than the two others [@Ostrom1990].
-
-# Methods
-
-Given the exploratory nature of this paper, a scoping review approach is used [@Munn2018].
-To conduct it, different scientific publications were analyzed in response to the research questions.
-To gather the papers, a Boolean search methodology was used in several scientific search engines such as Scopus, Web of Science and ScienceDirect.
-The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust", and they were paired with "AND" and "OR" Boolean operators.
-The research was made during the month of August, 2023.
-According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included, to have an idea as complete as possible about the existing literature on the topic.
-Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision.
-There were however some selection criteria concerning the papers' methodology and content.
-First, as mentioned in the introduction, papers investigating how an external entity/institution shapes cooperation were not included.
-Secondly, human participants were needed, so papers who studied social dilemmas with an agent-based model were also excluded.
-Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.
-
-Initially, 5210 papers emerged from the key phrases search.
-After deleting the duplicates, the count was of 4586.
-Based on titles and abstracts, 4333 articles were eliminated, leaving 253 texts to examine.
-After a full-text evaluation of the remaining papers, 89 were selected for the present review.
-Figure 1 resumes this selection process.
-
-## Papers' description
-
-The 89 included papers were published between 1984 and 2023, with a median of 2015.
-Almost all of the selected texts were journal articles, with the only exception being a book chapter.
-Most of them were experimental studies (*N*=60), followed by literature review and meta-analysis (*N*=14) and correlational studies[^1] (*N*=14).
-The remaining paper was a qualitative study.
-
-[^1]: Studies where at least a variable is manipulated by researchers are part of the category "experimental studies", while "correlational studies" refers to papers using quantitative analysis, but without manipulations.
-
-The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=75) refers to high controlled laboratory experiments where participants had to take cooperative decision.
-Usually some variables were manipulated to investigate the influence of a specific factor on cooperation [e.g.
-@Zhang2019].
-The type of paradigm could be a public good game (where participants could decide how much to contribute to a public good, e.g.
-@Torsvik2011) or a common resource game (where participants could decide how much to take from a common resource, e.g.
-@Nockur2020).
-Moreover, the type of game could vary during the experiment [e.g.
-@Fosgaard2019].
-The second category is "real-life social dilemma situation" (*N*=7), and investigated cooperation in different real-life situations with a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
-Thirdly, "real-life commons" (*N*=4) refers to papers who studied cooperation with participants that were members of a common in their everyday life.
-Finally, papers in the category "commons modeled by a social dilemma experiment" (*N*=3) used a laboratory social dilemma paradigm, but with clear references to a concrete common.
-For instance, in @Mosler1993, participants had to imagine to be fishermen who shared a common basin.
-
-Most of the papers concerned psychology and economy.
-In fact, thirty-four papers were published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin*, and fourteen in economic journals (e.g.
-*Experimental Economics*).
-Additionally, some papers (*N*=8) were published in interdisciplinary journals such as *Journal of Economic Psychology.*
-
-Finally, most of the studies were conducted in Europe (*N*=38) (especially in Germany (*N*=12) and in the Netherlands (*N*=8)), followed by North America (*N*=20, *N*=19 of which in the USA) and Asia (*N*=9, *N*=6 of which in China).
-Moreover, *N*=6 studies were set in more than one country, and *N*=14 were meta-analysis or literature reviews.
-The two remaining studies took place in Australia and in Colombia, respectively.
+-   **look for journals and their requirements to know how much shorten and how to frame the introduction + discussion (ask Vincent which journal he chose?)**
 
@@
 
-## Social status
-
-Few studies have investigated how social status impact cooperation, and their results do not allow to draw a clear conclusion about this effect.
-For instance, advantaged members (i.e.
-high-status class) tend to cooperate less than disadvantaged ones [@Aksoy2019].
-In fact, when participants did not receive the same endowment at the beginning of the experiment, contributions of "rich" and "poor" members converged [@Kingsley2016].
-In other words, proportionally to their resources, low-status participants cooperated more.
-However, in their review, @VanLange2013 identified some studies that observed the opposite effect, namely that wealthier people (or those who benefited more from a common resource) contributed more to the common good than the other.
-
-Social status can also create inter-class conflicts.
-In fact, people cooperated more with the members of the same social class than with other classes' members [@Aksoy2019].
-Moreover, a form of solidarity is observed between low-status members: in a study where participants had the opportunity to punish others for a non-cooperative behaviour, low-status members punished significantly less other low-status participants [@Chen2022].
-Also, in another experiment, participants were randomly advantaged during the interaction: subjects who received a lot of advantages were discriminated by others, and especially by the ones who were rarely advantaged [@Camera2020].
-
-Regarding the overall group composition, results are not consensual.
-On one hand, @Aksoy2019 found that groups with an inequality of status between members displayed lower levels of cooperation than homogeneous groups.
-On the other hand, economic and socio-cultural heterogeneity, although being negatively correlated with in-group trust, does not have a direct effect on a common-pool resource well-being [@VanKlingeren2021].
-
-In conclusion, social status impacts cooperation, but it seems to have multiple effects.
-Moreover, similarly to what @Sell2009 affirmed about the effects of gender and social status, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
-This shows that social identity and social status are deeply connected, and that it is difficult to separate their effects on cooperation.
-
-## Group identification
-
-Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group [e.g.
-@Arora2016; @Noonan2016; @Gomez-Ruiz2020].
-For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions.
-This is explained by the fact that, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016].
-A strong social identity also maintains a high level of cooperation over time [@Zhang2019].
-Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect.
-Group identification can also be easily implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992].
-Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].
-
-However, the fact that not all members identify with their group to the same extent can lead to inequalities on cooperation.
-For example, @VanVugt2009 mentioned that high-identified individual can even compensate, by cooperating more, for other in-group members' defection.
-The same result was also found by @Arora2016: high-identified individuals cooperated more than low-identified ones when faced to an in-group participant who defected (and this difference was not found when the defector was not a group member).
-However, this compensation came with a cost, since participants who compensated for an in-group defector reported lower trust toward this person.
-
-Another well replicated result is the positive effect of intergroup competition on intragroup cooperation.
-In fact, in-group identification can be enhanced via a competition between different groups, because in such a context individual's and group's interests are aligned [@Puurtinen2009].
-In fact, these authors demonstrated that cooperation was higher in an intergroup-competition condition than in a non-competitive condition.
-Moreover, when participants had to compete against other groups, they reported higher levels of anger toward in-group free-riders and they felt more guilty after a defection decision.
-In another experiment using a public resource game, intergroup competition reduced resources consumption, while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
-This shows that the increase of cooperation via competition is due to group membership factors, and not to competition in itself.
-
-However, despite the observed beneficial effects of inducing an intergroup competition, this could be harmful in real-life situations.
-This is especially true in case of resources that are shared between several groups, which are at greater risk of over-exploitation in case of intergroup competition [@VanVugt2009].
-A possible solution to maintain the positive effects of group identification, while eliminating the risk of over-exploitation caused by the competitive context, is to prime a superordinate identity [@VanVugt2009].
-In fact, intergroup cooperation can be enhanced by making salient the common characteristics of the different groups, instead of their differences [@Kramer1984].
-Another effective way to create a superordinate identity is to induce the feeling of a common fate, for example through a collective risk.
-In fact, a common fate allows a group to become real [@Zhang2019], and can therefore erase intergroup competition.
-
-Finally, social identity does not only have a main effect on people's cooperation, but can also moderate other factors' impact.
-For example, monetary incentive are more effective at enhancing cooperation of low-identified individual than of high-identified ones [@VanVugt2009].
-Moreover, a previous group failure can decrease cooperation between low-identified member, but this effect is not observed in people who have a strong identification with their group [@Jackson2011; @Jackson2012].
-
-In general, social identity seems to have a positive and largely observed effect on individuals' cooperation.
-This is due to the fact that humans have a very developed sense of belonging to social groups, and that this has an impact on their willingness to help other members of their group [@VanVugt2009].
-Since priming a common social identity is quite simple (e.g.
-@Kramer1984; @Zhang2019), this could be a very powerful technique to enhance cooperation in an easy and cheap way.
-
-## Values and personality traits
-
-Personal values and personality traits can play an important role in predicting cooperative behaviour [@Hilbig2018].
-One of the most studied is the Social Value Orientation (SVO), that divides people in pro-social and pro-self based on how much they value their own and others' outcomes in situations of interdependence [@Balliet2009].
-The effect of SVO on cooperation is very consensual: in a meta-analysis, 81 out of the 82 papers examined reported that pro-social cooperated significantly more than pro-self [@Balliet2009].
-
-However, this general effect is subjected to several moderators.
-For example, pro-self individuals cooperated more in a game where economic incentives to cooperation were present than in a game without such incentives, while pro-social did not display this difference and showed high levels of cooperation in both contexts [@Emonds2011].
-A similar effect is also described by @Balliet2009, who found a stronger effect of SVO in unpaid games than in paid ones, because, when monetary rewards were present, pro-self increased their cooperation.
-Therefore, pro-self individuals also cooperate, but only when cooperation serves their personal interest.
-In fact, in a study about commuting habits, the extent to which the cooperative behaviour (i.e.
-choosing to commute by public transportation or carpooling) was perceived as efficient impacted pro-self individual's decision more than pro-social's [@VanLange1998].
-
-Moreover, SVO has a stronger effect if there is an uncertainty about the number of individuals having access to a common resource: when the number of other participants was not known, pro-social, but not pro-self, reduced their harvesting comparing to a group-size certainty condition [@DeKwaadsteniet2008].
-The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self mainly think at their own personal interest.
-Also, SVO effect is partly explained by trust, i.e.
-the extent to which people think that their interaction partners will also cooperate.
-In fact, in @VanLange1998, pro-social individuals with a low level of trust did not make different decisions than pro-self individuals, while the most cooperative were pro-social with an high level of trust.
-Finally, the intuitive choice is to cooperate for pro-social individuals, while it is to defect for pro-self [@Lu2019].
-However, pro-self can cooperate more if they have the possibility to deliberate about the situation, because they realize that the best strategy to maximize the joint (and thus personal) outcome is cooperation.
-
-Other studies also focused on how much people are self- or social-oriented by using other constructs.
-For example, @Liu2009a demonstrated that priming a common fate to induce a context of interdependence significantly increased the cooperation level of participants with an independent self, but had no effect on participants with an interdependent self (who already displayed high levels of cooperation).
-Moreover, in a social dilemma experiment, competitive, individualistic people were motivated just by personal gain, while people who saw themselves as a part of a group were more interested on maximizing the income of each member, even at the cost to have a smaller personal payoff [@Probst1999].
-Also, high allocentric (i.e collectivist) individuals cooperated more than low allocentric ones when the perceived social norms are cooperative: this means that they are more sensitive to social cues and therefore they adapt their behaviour to social norms [@Chen2007].
-
-Finally, there are other personal values and traits that can affect cooperation.
-For example, pro-environmental values are negatively correlated with harvesting from a common resource, but only when the resource is scarce; therefore these values are more likely to motivate difficult, rather than easy, ecological behaviours [@Sussman2016].
-Levels of harvesting from a common resource are also lower between left-wingers than right-wingers [@Fosgaard2019].
-Moreover, humility and honesty are significant predictors of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018].
-Self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017].
-Lastly, people with an higher justice sensitivity make bigger contributions to a public good [@Schlosser2018].
-
-In conclusion, values and personality traits have a large impact on human cooperation, and it is thus very important to take them into account when investigating this phenomenon.
-Interestingly, some social psychological techniques (e.g.
-elaboration) allow to modify an individual's values [@Sussman2016].
-Such techniques could therefore be used to improve cooperation.
-
-## Trust and beliefs about others' contribution
-
-Trust can be defined as the "expectations of others' benevolent motives in situations that involve a conflict between self and collective interests" [@Balliet2013, p.1].
-Trust can be dispositional or a state; the former is an individual's general trait, and is usually measured with personality scales, the latter is linked to the context, and can be operazionalized by expectations about a partner's behaviour in a specific situation [@Balliet2013].
-The two are positively correlated [@Lubke2021], and both have a positive general effect on cooperation [@VanLange2013; @Balliet2013].
-In fact, high levels of trust are associated with more contributions to a public good [@Kocher2015], and a participant's contribution in a public good game can be predicted by her beliefs about others' contributions [@Smith2013].
-
-Several studied confirmed this relationship.
-For instance, @Chaudhuri2002 demonstrated that people who cooperated more in a first public good game trusted more their partner in a following interaction than people whose main strategy was defecting.
-Moreover, people that were pessimistic about others' contribution cooperated significantly less than the optimistic [@Oyediran2018], and those who free-rode in a public good game, compared to cooperators, believed that others contributed less [@Kocher2015].
-Also, people were more willing to purchase actions for a CO2 mitigation initiative when they believed that the majority of others had also bought them [@Sturm2019].
-Finally, in a study about self-administered outlets in Swiss farms (i.e.
-outlets where nobody monitors if people pay or not their purchases), @Franzen2019 found that a farmer's general trust in other people is a significant predictor of the probability of having such an outlet.
-Concerning the moderators, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
-
-People can also display different levels of trust in the "reliability, effectiveness and legitimacy of public institutions" [@Rompf2017, p.
-2].
-These authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to comply to norms.
-Moreover, the effects of perceived costs and benefits of the action are less predictive in people with high institutional trust.
-
-Finally, trusting others (and the institutions) is essential to display higher level of cooperation.
-However, general beliefs about others' cooperation are quite low compared to the actual behaviours, and this trust gap can undermine cooperation, since people's actions are significantly predicted by their beliefs [@Lubke2021].
-In order to increase trust and, consequently, cooperation, it is therefore essential to provide people with reliable information about others' behaviour.
-
-# Organizational factors
-
-## Incentives
-
-Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^2].
-In the literature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
-In general, when there is the possibility for participants to punish others members based on their contributions, cooperation is higher than when this is not possible [e.g.
-@Pfattheicher2018; @Balliet2011a].
-Moreover, the presence of a punishment system increases the perception of fairness [@Nockur2021].
-
-[^2]: Since the interest of the present review is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
-Incentives given by third party have also an effect on cooperation, but they are not included in this review.
-
-However, this main results is subjected to several moderators.
-First, the punishment have a bigger impact on cooperation if its implementation is costly for the punishers than if it is free [@Balliet2011a], but at the same time the cost should not be too high [@Egas2008].
-Moreover, punishments are more effective if the interaction is among friends than among strangers, and if people know that they will have to interact repeatedly with each other [@Balliet2011a].
-In fact, in short interactions, if punishment is costly, individuals who punish others are the ones with the lowest personal income [@Milinski2012], and this could discourage the application of the fine.
-Also, an experiment showed that a punishment system increased cooperation in groups where all members had the same amount of resources, but not in groups where income was heterogeneous [@Kingsley2016].
-In fact, @Chen2022 found that, in groups where the initial endowment was heterogeneous, participants that received less didn't punish the others "low-status" members.
-This solidarity could therefore encourage free-riding.
-Moreover, the effect of punishment is stronger when only cooperators have the power to punish defectors, than when everybody can punish [@Xiao2016].
-Finally, a plain situation is also needed to have a stronger effect of punishment: the link between behaviour and outcome must be clear, without random factors affecting the final outcome [@Xiao2016], and the punishment must be highly effective [@Egas2008].
-
-However, punishment must be applied with carefulness: @Rockenbach2019 compared the strategies of different groups, and found that the most successful ones (whose members had the highest payoff at the end of the experiment) punished with caution and not in early stages of the game.
-In these groups, a norm of when and how punishment should be applied seems to exist.
-Moreover, punishment has also two main negative sides.
-First, it could entails a second-order social dilemma [@Milinski2012], since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators.
-Secondly, anti-social punishment can arise.
-This term refer to the punishment of cooperators by non-cooperators, and it is present when all participants can punish independently of their contributions [@Xiao2016].
-In this context, defectors can see cooperators as rule breakers, and anti-social punishment is a sort of retaliation [@VanDijk2015].
-
-A possible solution could be to implement a system of democratic punishment, where a fine is given only if a majority of participants agree.
-In fact, compared to a peer punishment system where participants decide individually if and who punish, in a democratic system anti-social punishment is less present, general punishment level is lower, and final payoff and cooperation rates are higher [@Pfattheicher2018].
-
-Rewarding systems, on the other side, are less investigated.
-Globally, they have a positive effect on cooperation [@Balliet2011a].
-However, some studies found that they were more efficient than punishment [e.g.
-@Chen2022], while others came to the opposite conclusion [e.g.
-@Milinski2012] or found no difference between the two systems [e.g.
-@Balliet2011a].
-In a meta-analysis, @Balliet2011a found that rewards had a stronger effect on cooperation if their implementation was costly rather than free, and in iterated, rather than single, interactions.
-Moreover, rewarding was more effective in situations where participants had to decide how much take from a common resource, compared to when they had to decide how much contribute to a common good.
-
-In general, incentives seem to be a powerful tool to enhance cooperation, but they have a dark side.
-First, they reduce participants' intrinsic motivation [@VanDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
-In fact, @Schlosser2018 demonstrated that people's level of justice sensitivity could predict their contributions to a public good game, but this link disappeared when a punishment system was introduced.
-Secondly, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members, and especially the trust in the fact that others are internally motivated to cooperate.
-This reduced trust in others drops cooperation levels if incentives are removed [@Irwin2014; @Mulder2006].
-
-Finally, incentives are often studied in economic formats, but they can also be social.
-For example, the expectation of honour or shame (after cooperating or defecting, respectively) is enough to enhance cooperation [@Jacquet2011].
-Moreover, expressing disapproval toward defectors can boost cooperation by inducing more compliance to the cooperative social norm [@Nelissen2013].
-Even an ostracism system where participants can vote to exclude other members from the game is very effective in increasing cooperation [@Maier-Rigaud2010].
-In general, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
-
-To conclude, economic incentives can have a positive effect on cooperation, but their efficient implementation must be insured all along the interaction, otherwise cooperation rates would drop.
-On the other hand, social incentives seem to have the same positive effect, and their removal do not cause a reduction of cooperation.
-However, there is a lack of studies focusing on this kind of sanctions.
-
-## Communication
-
-Communication has a global positive effect on cooperation [e.g.
-@Balliet2010; @Bicchieri2002], but this effect is subjected to several moderators.
-First, talking is more powerful than sending written messages, because it allows non-verbal communication and facilitates the social norms formation process.
-Moreover, communication's effect is stronger in large groups: when many people are present cooperation rates are lower, so communication between members can buffer this negative effect [@Balliet2010].
-Finally, if communicating with others requires a personal cost, the effect is weaker than if communication is free [@Janssen2014].
-
-The content of the messages is also essential.
-@Koessler2021 identified four steps necessary for an effective communication in social dilemmas: problem awareness, identification of strategies, agreement and ratification.
-In another study, groups who used communication to foster a common social identity, promote cooperative social norms and ensure that all the players publicly committed displayed higher rates of cooperation than other groups [@Adams2022].
-However, casual chit-chat also plays a very important role in increasing cooperation [@Koessler2021].
-Also, the increase of cooperation through communication can be explained by the normative content that people are shaping while exchanging messages [@Janssen2014], and by the fact that it allows participant to reach a consensus about the best strategy [@Hopthrow2005].
-Moreover, even if communication also helps to create a social identity, the effect of social norms is a stronger mediator of the link between communication and cooperation [@Bicchieri2002].
-
-Another factor that influences the effect of communication on cooperation is whether individuals exchange messages before, during or after the cooperative phase.
-Concerning the post-game communication, @Kumakawa2013 found that receiving a feedback about the cooperation choice made previously can increase cooperation in the following interactions, especially if the feedback is negative.
-However, just the fact of knowing that a discussion will follow is not enough to enhance cooperation, and can even have a counterproductive effect, because forcing people to think about a future discussion make them reflect more on the situation and thus act more rationally [@Torsvik2011].
-On the other hand, communication before or during the interaction have both a positive impact on cooperation, and the difference between their effect is not significant [@Balliet2010].
-
-Finally, several studies investigated the effect of gossip as a form of communication that can increase cooperation.
-Gossip is defined as a spread of reputational information about another person [@Feinberg2014], and it increases cooperation in two ways.
-First, if people know that gossip is possible, they tend to cooperate more to avoid the risk of being the target of such gossip and therefore of being excluded from following interactions.
-Secondly, having information about the past behaviour of potential partners can help to select the most cooperative individuals in an interaction situation [@Feinberg2014].
-Moreover, the same authors found that pro-social individuals gossiped more than pro-self.
-This shows that gossip can have the pro-social function of protecting others from a potential exploitation [@Feinberg2012].
-However, gossip has also some self-interest effects: for instance, observing another subject being exploited and having the opportunity to gossip about the exploiter significantly reduced negative affects in @Feinberg2012 's participants.
-Moreover, providing correct information while gossiping helps to build a positive reputation [@Giardini2021].
-
-In conclusion, when people have the possibility to communicate before, during or after a cooperative interaction, the cooperation level increases.
-Even if the strength of this effect can vary depending on the situation, communication never seems to have a negative impact on cooperation.
-
-## Social Norms
-
-Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour [@VonBorgstede2018].
-@Thogersen2008 studied the effect of social norms on daily social dilemma situations such as environmental behaviours, and found that both injunctive (what others approve) and descriptive (what others do) norms are positively related to behaviours.
-Moreover, cooperation can be maintained via social norms, because people who do not respect them are susceptible of social sanctions.
-In fact, if social approval is possible, people cooperate more [@Rege2004].
-
-There are several explanations of social norms' effect on cooperation.
-First, according to the appropriateness framework, when taking a decision people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
-Therefore they need to define the situation as a cooperative task and to strongly identify with the group [@VanLange2013].
-This leads to a greater accessibility of group's norms and consequently (if the norms are cooperative) to more cooperation.
-Testing this assumption, @Arora2012 showed that a greater identification with social group lead to higher levels of cooperation.
-The second explanation concerns conformity: in general people adapt their cooperation to others' behaviour, but this is usually explained by the reciprocity principle (cooperation enhances the probability that others will do the same, and therefore that the final payoff will be higher) [@Bardsley2005a].
-However, these authors demonstrated that people conform to others' behaviour even if this has no impact on their personal payoff.
-Therefore, people have a general tendency to imitate others to follow social norms.
-
-Finally, social norms can be modified by participants.
-For instance, @Weber2008 demonstrated that in several social dilemma experiment there are consistent cooperators, i.e.
-people who always cooperate.
-The presence of these people can increase other members' cooperation, and this effect is mediated by the perception of the social norms.
-Moreover, social norms can also be shaped via communication [@Bicchieri2002].
-
-In conclusion, social norms have a significant effect on people's cooperation in social dilemma situations.
-Since they are quite easily modified [e.g.
-@Weber2008], shaping cooperative norms can be a powerful instrument to improve cooperation.
-
-## Anonymity
-
-There are not many studies on the influence of anonymity on cooperation, but, according to @Wang2017, most of the factors that can increase cooperation rely on a reduction of anonymity.
-For instance, it is not possible to punish defectors without knowing who they are.
-Therefore, in general it seems that non-anonymous situations can significantly increase cooperation and reduce defection [@Wang2017].
-This can be explained by the fact that, when their actions are visible, people worry about others' approval [@Rege2004] and that, in non-anonymous situations, contributions can be a self-presentation strategy, because being perceived as pro-social can increase one's social status [@VanVugt2010a].
-There are therefore more social incentives to cooperate in non-anonymous, rather than anonymous, situations.
-
-Moreover, this effect is displayed especially in situations when individuals face a cost when cooperating and know that they will not get any personal benefit.
-For instance, @Butz2021 demonstrated that, in a public good game where a part of contributions was donated to a charity association, disclosing identities increased cooperation, but only if the donation was deducted from participants' payoff.
-In the same direction, @VanVugt2010a found that, when actions were public, contributions were higher if the public good was already attained or unattainable, and therefore if participants did not have a personal interest in cooperating.
-
-Reducing anonymity in cooperative interactions can be very effective to encourage people to contribute more.
-A possible way to do this is to reduce group's size.
-In fact, according to @Romano2016, larger groups lead to de-individuation, because it is more difficult to understand who is defecting.
-Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable.
-Moreover, communication is easier in smaller groups [@VonBorgstede2018].
-This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good.
-
-Another effective method to reduce anonymity is to make people publicly promise to cooperate before the cooperative interaction.
-For instance, in a laboratory experiment modeling a common pool resource, people who publicly committed exploited significantly less the resource than people who committed in private, even if after committing they were not restricted in their harvesting possibilities [@Mosler1993].
-This results was also confirmed by @Przepiorka2020, who showed that non-binding promises increased cooperation.
-Moreover, even a compulsory commitment has a beneficial effect on cooperation, even if the most efficient groups are those where all participants signed voluntary the pledge [@Koessler2021a].
-
-In conclusion, reducing anonymity during interactions is essential to improve cooperation, because this can facilitate the implementation of others cooperation-enhancing techniques [@Wang2017].
-Moreover, there are several low-cost method to make situations non-anonymous.
-
 # Discussion
-
-Through a scoping review approach, the current paper identified several factors that could impact cooperation in social dilemmas and in commons.
-Some of these elements can be related to the principles to successfully manage a common resource that @Ostrom1990 drew after the observation of several real-life cases.
-In fact, her first statement says that commons need clearly defined boundaries: therefore, it must be clear who has the right to benefit from the common resource and who does not.
-This could be linked to the social identity construct, since only when an in- and an out-group exist social identity is salient and therefore an identification is possible [@Tajfel1974].
-Even if Ostrom developed this principle on a more organizational level, the secondary effect of creating a social identity for commons' members can also contribute to improve cooperation.
-Moreover, individuals who are part of the group, and who are therefore affected by the common's rules, must be able to participate in modifying them (principle 3).
-This statement shows the importance of social norms, especially of injunctive ones, namely what is morally approved in a social group [@Cialdini1990].
-Moreover, in order to modify such norms, people must be able to communicate [@Bicchieri2002].
-Communication is also essential for principle 6, who posits that members of a common must have access to low-cost arenas to resolve conflicts.
-In fact, communication helps to reach an agreement to the strategy that needs to be followed [@Hopthrow2005].
-Finally, Ostrom's principles 4 and 5 underline the importance of incentives, more precisely in the form of a monitoring system implemented by members themselves and a graduate sanctions system toward violators of the rules.
-The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they worry about others' approval [@Nelissen2013; @Rege2004].
-On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^3]
-
-[^3]: Principles 2, 7 and 8 refer to elements that are not pertinent to the current review, and therefore do not match any of the factors identified.
-
-Ostrom's principles are therefore in line with the results of this review, especially concerning factors at the organizational level.
-This is understandable when considering her economic approach to the study of the commons.
-However, taking into account the social dynamics and the individuals who are commoning is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
-For this reason, this paper made a step further and identified some individual characteristics affecting the efficiency of commons.
-The effects of these factors seem to be coherent with the existing literature.
-
-First, according to the analyzed papers, trust has a positive effect on cooperation.
-In fact, since cooperation involves the risk that others will defect, trusting others is essential in this context [@Henry2011].
-Moreover, according to the principle of reciprocity, people cooperate more facing cooperative partners [@Fehr2002; @VanLange1999].
-However, in real-life situation it is not always possible to know exactly others' contributions, and therefore trust (i.e.
-beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012].
-Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can(not) be successful.
-These evidences fit well with the more general result showing that dispositional trust is a predictor of pro-social behaviour [@Wu2020].
-
-Secondly, Social Value Orientation has also an impact on cooperation: in fact, there are individual differences in motivation when people have to decide how to allocate a resource between themselves and others [@Murphy2011].
-More specifically, pro-social individuals are more cooperative than pro-self because they value more others' and joint outcome [@VanLange1999].
-This is also confirmed experimentally by @Fiedler2013, who showed that pro-social and pro-self processed the situation in a similar way, but accorded different weights to the outcome for themselves and others.
-Finally, since they value the equality in outcomes, pro-social can behave even less cooperatively than pro-self when reciprocity is violated [@VanLange1999].
-
-Concerning gender effect on cooperation, the existing literature would predict that women cooperate more than men.
-In fact, according to gender stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012], and this lead to the perception that women's intentions are more benevolent than those of men [@Ellemers2018].
-In line with these predictions, @Westermann2005 found that, managing a natural resource, groups where women were present displayed more solidarity and collaboration comparing to all-men groups.
-Despite these evidences, this review revealed that there is no general gender effect on cooperation and that a lot of moderator are at stake.
-This shows that this effect is extremely dependent on the situation.
-Moreover, gender is always embedded with social status dynamics [@Sell2009], and it is therefore difficult to separate the two effects.
-The analyzed studies about social status and cooperation showed that usually members of low-status groups cooperated more and showed more solidarity with others low-status members than high-status.
-Although the effect of social status on cooperation has not been extensively studied, these results seem to be consistent with the existing literature on social status.
-For instance, members of high-status groups are more individualistic, because their group belonging does not reduce individual characteristics as it does with low-status [@Lorenzi-Cioldi2002].
-Moreover, high-status individuals display more system justification than low status [@Caricati2012], and higher levels of Social Dominance Orientation [@Vargas-Salfate2018].
-Therefore, they see the social system as fair and secure and they have a preference for inequality between social groups.
-This is negatively correlated with concern about others and altruism [@Pratto1994].
-Finally, although there are differences between social statuses, people tend to cooperate more with individuals of their same social class than with others, and this effect is manly due to group identification [@Aksoy2019].
-Social status is therefore deeply connected to the last of the individual factors, group identification.
-
-The reviewed results showed that the more individuals identify with their group, the more they are likely to act for the group's good.
-In fact, people's identity is also composed by their group affiliations, and the stronger they identify with a social group, the more important this group becomes for their identity and the more their personal interests aligns with group's ones [@Tajfel1974].
-Also, within a social group, individuals perceive themselves as more similar to other members [@Turner1984], and therefore they are more susceptible to adopt collective goals and behaviours [@Fritsche2018].
-Moreover, strongly identified people are less likely to leave a social group in case of failure or difficulties [@Ellemers1997].
-Thus, in order for a social group to be successful, its members must strongly identify with it.
-In fact, in-group identification is the main predictor of collective action in the Social Identity Model of Collective Action [SIMCA, @VanZomeren2008].
-Moreover, @Fritsche2018 apply this social identity approach to environmentalism with the Social Identity Model of Pro-Environmental Action (SIMPEA), where group identification is once again the main predictor.
-According to its authors, the climate crisis has the structure of common good dilemmas, because environmental goals can be attained only if everybody cooperates.
-These results confirm the strong consensus found about the link between social identification and cooperation.
-
-## Factors' interactions
-
-Until now, the identified factors has been discussed separately. However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.
-
-For instance, there are gender differences in trust and SVO.
-More specifically, trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019], and a study assessing SVO found that women were significantly more prevalent between pro-social and less between pro-self [@VanLange1999].
-Also, SVO and trust are positively correlated [@Ackermann2019], and @Bogaert2008 even theorized that the expectancy about others' behaviour is actually a part of the construct of SVO.
-Therefore, pro-self individuals show less cooperation in part because they expect others not to cooperate.
-Finally, trust can differ based on social status: high-status people display more generalized trust (i.e.
-general belief on others' benevolence), while low-status more depersonalized trust (i.e.
-more trust in other members of their in-group, just because of their membership) [@Navarro-Carrillo2018].
-This is consistent with the results about social status mentioned previously: since high-status individuals perceive the system as fair [@Caricati2012], it is easier for them to believe that others have benevolent intention.
-On the other hand, low-status individuals see themselves as more similar between each-other than high status [@Lorenzi-Cioldi2002], therefore they trust other members of their group just because of their belonging.
-
-Secondly, communication impacts several other factors.
-For instance, it plays an essential role in shaping social norms [@Hogg2006; @Bicchieri2002] and it can improve cooperation by signalling a person's intentions and trustworthiness [@Janssen2015].
-Moreover, in a study about organizations, communication was a strong predictor of commitment, that is a component of group identification.
-This link was especially present for vertical communication, i.e.
-exchanges about organizational strategies between members at different level of the hierarchy [@Postmes2001].
-Therefore, having the opportunity to communicate about the strategies that need to be implemented improve one's identification with the group.
-
-Another factor that influences others is group identification.
-First, as a consequence of the Social Identity Theory, people who strongly identify with their group are more willing to comply to the group's norms and to pursuit the group's goals [@Tajfel1974].
-Therefore, high-identified members need less cooperation-enhancing measures.
-For instance, incentives are more useful to improve cooperation of low-, rather than high-identified, group members [@VanVugt2009], because high-identified members are already motivated to cooperate.
-Similarly, given their stronger willingness to act for the group's good, high-identified individuals cooperate even in an anonymous condition, while low-identified acted more for the group goal if their actions were accountable [@Barreto2000].
-
-As already mentioned in the results section, anonymity underlies several other factors.
-First, when actions are accountable, people are more concerned about others' approval and therefore show more conformity to social norms [@Nelissen2013; @Rege2004].
-Also, in large groups [where, as a consequence of the group size, levels of anonymity are higher, @Romano2016] it is more difficult to evaluate the trustworthiness of other participants than in small ones [@Janssen2015].
-
-Finally, economic incentives can have a negative impact on people's internal motivation to cooperate, because they change the perception of the context from ethical to economic [@Janssen2015; @VanVugt2009].
-Therefore, even if incentives such as punishments or rewards can be useful to improve cooperation, they reduce the impact of the other factors.
-For instance, when incentives are present, people think that others cooperate because of them, and this leads to reduced levels of trust [@Irwin2014].
-
-In summary, this review has practical implications and can be used as a guide for commons members to design campaigns or activities to improve cooperation.
-In fact, some of the identified factors can be manipulated in order to create better conditions for cooperation to arise.
-Moreover, since the different elements are linked, they can impact cooperation both directly and indirectly, via mediation and moderation effects.
-Based on the consensus of the results and on the quantity of connections with other elements, the factors that seem to have a stronger effect are trust, communication, group identification and accountability of actions.
-Therefore, interventions based on this elements can be very powerful tools to improve cooperation in commons.
-On the other hand, some individual factor cannot be manipulated, but must be taken into account when designing an intervention.
-For instance, commons' composition in terms of gender and social status can have a large influence on the overall cooperation.
-
-# Limitations, future perspectives and conclusion
-
-To conclude, since cooperating is essential for the success of a common, this review's aim was to provide an overview of the factors that affect cooperation in social dilemma situations such as commons.
-While attaining this goal, the current paper also highlighted a lack of systematic studies about cooperation in commons.
-However, several limitations can be identified.
-
-First, most of the included studies had a laboratory social dilemma setting, that is a simplification of real-life situations and do not allow to exactly reproduce the dynamics present in a common [@Henry2011; @Cole2010].
-In fact, some elements such as cultural factors and specific ecological conditions affecting the decision making process cannot be reproduced in lab experiments [@Janssen2015].
-Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings.
-Moreover, this review is not informative about the relative importance of each factor.
-To shed light on this topic, quantitative studies are needed.
-
-Another limitation is the lack of representation of the global population.
-In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Global North.
-The current results apply therefore to Western societies and should not be generalized to Global South.
-In fact, there are cultural differences in the levels of individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989].
-These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g.
-@Kuwabara2014].
-For this reason, it is likely that underlying mechanism of cooperation are different for Global South and North: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.
-
-Finally, the papers included in this review did not provide a longitudinal perspective on the study of cooperation, leaving therefore some open questions: which factors are more important in the early or in the late stages of cooperation?
-How the different factors evolve and influence each-others over time?
-For this reason, longitudinal investigations about the evolution of commons are needed.
-
-In conclusion, a successful commons relies on the cooperation of its members, but this topic has not yet been extensively studied.
-Thus, further researches are needed to address the limitations of the current study and to reach a deeper understanding of this topic.
 
@@
 :::
-
-\newpage
-
-# Figures
-
-```{r}
-library(DiagrammeR)
-library(webshot2)
-DiagrammeR::grViz("digraph {
-graph [layout = neato, rankdir = TB]
-
-node [shape = rectangle, fontsize = 14, fontname = Arial]       
-rec1 [label = 'Papers identified from search engines
-n = 5210', pos='0,0!', width = 4.5, height = 0.5]
-rec2 [label = 'Duplicates
-n = 624', pos='4,0!', width = 2, height = 0.5]
-rec3 [label = 'Papers screened based on titles and abstracts
-n = 4586', pos='0,-1!', width = 4.5, height = 0.5]
-rec4 [label = 'Not suitable papers
-n = 4333', pos='4,-1!', width = 2, height = 0.5]
-rec5 [label = 'Papers read completely
-n = 253', pos='0,-2!', width = 4.5, height = 0.5]
-rec6 [label = 'Not suitable papers
-n = 164', pos='4,-2!', width = 2, height = 0.5]
-rec7 [label = 'Papers included
-n = 89', pos='0,-3!', width = 4.5, height = 0.5]
-
-# edge definitions with the node IDs
-rec1 -> rec2
-rec3 -> rec4
-rec5 -> rec6
-rec1 -> rec3 -> rec5 -> rec7
-}",
-height = 500)
-```
-
-Figure 1. Flow diagram of the scoping review selection process.

### 2023-11-03 scoping_review_short.Rmd
Add files via upload

@@
 
+## Social status
+
+Few studies have investigated how social status impact cooperation, and their results do not allow to draw a clear conclusion about this effect.
+For instance, advantaged members (i.e.
+high-status class) tend to cooperate less than disadvantaged ones [@Aksoy2019].
+In fact, when participants did not receive the same endowment at the beginning of the experiment, contributions of "rich" and "poor" members converged [@Kingsley2016].
+In other words, proportionally to their resources, low-status participants cooperated more.
+However, in their review, @VanLange2013 identified some studies that observed the opposite effect, namely that wealthier people (or those who benefited more from a common resource) contributed more to the common good than the other.
+
+Social status can also create inter-class conflicts.
+In fact, people cooperated more with the members of the same social class than with other classes' members [@Aksoy2019].
+Moreover, a form of solidarity is observed between low-status members: in a study where participants had the opportunity to punish others for a non-cooperative behaviour, low-status members punished significantly less other low-status participants [@Chen2022].
+Also, in another experiment, participants were randomly advantaged during the interaction: subjects who received a lot of advantages were discriminated by others, and especially by the ones who were rarely advantaged [@Camera2020].
+
+Regarding the overall group composition, results are not consensual.
+On one hand, @Aksoy2019 found that groups with an inequality of status between members displayed lower levels of cooperation than homogeneous groups.
+On the other hand, economic and socio-cultural heterogeneity, although being negatively correlated with in-group trust, does not have a direct effect on a common-pool resource well-being [@VanKlingeren2021].
+
+In conclusion, social status impacts cooperation, but it seems to have multiple effects.
+Moreover, similarly to what @Sell2009 affirmed about the effects of gender and social status, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
+This shows that social identity and social status are deeply connected, and that it is difficult to separate their effects on cooperation.
+
+## Group identification
+
+Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group [e.g.
+@Arora2016; @Noonan2016; @Gomez-Ruiz2020].
+For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions.
+This is explained by the fact that, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016].
+A strong social identity also maintains a high level of cooperation over time [@Zhang2019].
+Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect.
+Group identification can also be easily implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992].
+Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].
+
+However, the fact that not all members identify with their group to the same extent can lead to inequalities on cooperation.
+For example, @VanVugt2009 mentioned that high-identified individual can even compensate, by cooperating more, for other in-group members' defection.
+The same result was also found by @Arora2016: high-identified individuals cooperated more than low-identified ones when faced to an in-group participant who defected (and this difference was not found when the defector was not a group member).
+However, this compensation came with a cost, since participants who compensated for an in-group defector reported lower trust toward this person.
+
+Another well replicated result is the positive effect of intergroup competition on intragroup cooperation.
+In fact, in-group identification can be enhanced via a competition between different groups, because in such a context individual's and group's interests are aligned [@Puurtinen2009].
+In fact, these authors demonstrated that cooperation was higher in an intergroup-competition condition than in a non-competitive condition.
+Moreover, when participants had to compete against other groups, they reported higher levels of anger toward in-group free-riders and they felt more guilty after a defection decision.
+In another experiment using a public resource game, intergroup competition reduced resources consumption, while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
+This shows that the increase of cooperation via competition is due to group membership factors, and not to competition in itself.
+
+However, despite the observed beneficial effects of inducing an intergroup competition, this could be harmful in real-life situations.
+This is especially true in case of resources that are shared between several groups, which are at greater risk of over-exploitation in case of intergroup competition [@VanVugt2009].
+A possible solution to maintain the positive effects of group identification, while eliminating the risk of over-exploitation caused by the competitive context, is to prime a superordinate identity [@VanVugt2009].
+In fact, intergroup cooperation can be enhanced by making salient the common characteristics of the different groups, instead of their differences [@Kramer1984].
+Another effective way to create a superordinate identity is to induce the feeling of a common fate, for example through a collective risk.
+In fact, a common fate allows a group to become real [@Zhang2019], and can therefore erase intergroup competition.
+
+Finally, social identity does not only have a main effect on people's cooperation, but can also moderate other factors' impact.
+For example, monetary incentive are more effective at enhancing cooperation of low-identified individual than of high-identified ones [@VanVugt2009].
+Moreover, a previous group failure can decrease cooperation between low-identified member, but this effect is not observed in people who have a strong identification with their group [@Jackson2011; @Jackson2012].
+
+In general, social identity seems to have a positive and largely observed effect on individuals' cooperation.
+This is due to the fact that humans have a very developed sense of belonging to social groups, and that this has an impact on their willingness to help other members of their group [@VanVugt2009].
+Since priming a common social identity is quite simple (e.g.
+@Kramer1984; @Zhang2019), this could be a very powerful technique to enhance cooperation in an easy and cheap way.
+
+## Values and personality traits
+
+Personal values and personality traits can play an important role in predicting cooperative behaviour [@Hilbig2018].
+One of the most studied is the Social Value Orientation (SVO), that divides people in pro-social and pro-self based on how much they value their own and others' outcomes in situations of interdependence [@Balliet2009].
+The effect of SVO on cooperation is very consensual: in a meta-analysis, 81 out of the 82 papers examined reported that pro-social cooperated significantly more than pro-self [@Balliet2009].
+
+However, this general effect is subjected to several moderators.
+For example, pro-self individuals cooperated more in a game where economic incentives to cooperation were present than in a game without such incentives, while pro-social did not display this difference and showed high levels of cooperation in both contexts [@Emonds2011].
+A similar effect is also described by @Balliet2009, who found a stronger effect of SVO in unpaid games than in paid ones, because, when monetary rewards were present, pro-self increased their cooperation.
+Therefore, pro-self individuals also cooperate, but only when cooperation serves their personal interest.
+In fact, in a study about commuting habits, the extent to which the cooperative behaviour (i.e.
+choosing to commute by public transportation or carpooling) was perceived as efficient impacted pro-self individual's decision more than pro-social's [@VanLange1998].
+
+Moreover, SVO has a stronger effect if there is an uncertainty about the number of individuals having access to a common resource: when the number of other participants was not known, pro-social, but not pro-self, reduced their harvesting comparing to a group-size certainty condition [@DeKwaadsteniet2008].
+The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self mainly think at their own personal interest.
+Also, SVO effect is partly explained by trust, i.e.
+the extent to which people think that their interaction partners will also cooperate.
+In fact, in @VanLange1998, pro-social individuals with a low level of trust did not make different decisions than pro-self individuals, while the most cooperative were pro-social with an high level of trust.
+Finally, the intuitive choice is to cooperate for pro-social individuals, while it is to defect for pro-self [@Lu2019].
+However, pro-self can cooperate more if they have the possibility to deliberate about the situation, because they realize that the best strategy to maximize the joint (and thus personal) outcome is cooperation.
+
+Other studies also focused on how much people are self- or social-oriented by using other constructs.
+For example, @Liu2009a demonstrated that priming a common fate to induce a context of interdependence significantly increased the cooperation level of participants with an independent self, but had no effect on participants with an interdependent self (who already displayed high levels of cooperation).
+Moreover, in a social dilemma experiment, competitive, individualistic people were motivated just by personal gain, while people who saw themselves as a part of a group were more interested on maximizing the income of each member, even at the cost to have a smaller personal payoff [@Probst1999].
+Also, high allocentric (i.e collectivist) individuals cooperated more than low allocentric ones when the perceived social norms are cooperative: this means that they are more sensitive to social cues and therefore they adapt their behaviour to social norms [@Chen2007].
+
+Finally, there are other personal values and traits that can affect cooperation.
+For example, pro-environmental values are negatively correlated with harvesting from a common resource, but only when the resource is scarce; therefore these values are more likely to motivate difficult, rather than easy, ecological behaviours [@Sussman2016].
+Levels of harvesting from a common resource are also lower between left-wingers than right-wingers [@Fosgaard2019].
+Moreover, humility and honesty are significant predictors of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018].
+Self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017].
+Lastly, people with an higher justice sensitivity make bigger contributions to a public good [@Schlosser2018].
+
+In conclusion, values and personality traits have a large impact on human cooperation, and it is thus very important to take them into account when investigating this phenomenon.
+Interestingly, some social psychological techniques (e.g.
+elaboration) allow to modify an individual's values [@Sussman2016].
+Such techniques could therefore be used to improve cooperation.
+
+## Trust and beliefs about others' contribution
+
+Trust can be defined as the "expectations of others' benevolent motives in situations that involve a conflict between self and collective interests" [@Balliet2013, p.1].
+Trust can be dispositional or a state; the former is an individual's general trait, and is usually measured with personality scales, the latter is linked to the context, and can be operazionalized by expectations about a partner's behaviour in a specific situation [@Balliet2013].
+The two are positively correlated [@Lubke2021], and both have a positive general effect on cooperation [@VanLange2013; @Balliet2013].
+In fact, high levels of trust are associated with more contributions to a public good [@Kocher2015], and a participant's contribution in a public good game can be predicted by her beliefs about others' contributions [@Smith2013].
+
+Several studied confirmed this relationship.
+For instance, @Chaudhuri2002 demonstrated that people who cooperated more in a first public good game trusted more their partner in a following interaction than people whose main strategy was defecting.
+Moreover, people that were pessimistic about others' contribution cooperated significantly less than the optimistic [@Oyediran2018], and those who free-rode in a public good game, compared to cooperators, believed that others contributed less [@Kocher2015].
+Also, people were more willing to purchase actions for a CO2 mitigation initiative when they believed that the majority of others had also bought them [@Sturm2019].
+Finally, in a study about self-administered outlets in Swiss farms (i.e.
+outlets where nobody monitors if people pay or not their purchases), @Franzen2019 found that a farmer's general trust in other people is a significant predictor of the probability of having such an outlet.
+Concerning the moderators, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
+
+People can also display different levels of trust in the "reliability, effectiveness and legitimacy of public institutions" [@Rompf2017, p.
+2].
+These authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to comply to norms.
+Moreover, the effects of perceived costs and benefits of the action are less predictive in people with high institutional trust.
+
+Finally, trusting others (and the institutions) is essential to display higher level of cooperation.
+However, general beliefs about others' cooperation are quite low compared to the actual behaviours, and this trust gap can undermine cooperation, since people's actions are significantly predicted by their beliefs [@Lubke2021].
+In order to increase trust and, consequently, cooperation, it is therefore essential to provide people with reliable information about others' behaviour.
+
+# Organizational factors
+
+## Incentives
+
+Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^1].
+In the literature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
+In general, when there is the possibility for participants to punish others members based on their contributions, cooperation is higher than when this is not possible [e.g.
+@Pfattheicher2018; @Balliet2011a].
+Moreover, the presence of a punishment system increases the perception of fairness [@Nockur2021].
+
+[^1]: Since the interest of the present review is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
+Incentives given by third party have also an effect on cooperation, but they are not included in this review.
+
+However, this main results is subjected to several moderators.
+First, the punishment has a bigger impact on cooperation if its implementation is costly for the punishers than if it is free [@Balliet2011a], but at the same time the cost should not be too high [@Egas2008].
+Moreover, punishments are more effective if the interaction is among friends than among strangers, and if people know that they will have to interact repeatedly with each other [@Balliet2011a].
+In fact, in short interactions, if punishment is costly, individuals who punish others are the ones with the lowest personal income [@Milinski2012], and this could discourage the application of the fine.
+Also, an experiment showed that a punishment system increased cooperation in groups where all members had the same amount of resources, but not in groups where income was heterogeneous [@Kingsley2016].
+In fact, @Chen2022 found that, in groups where the initial endowment was heterogeneous, participants that received less didn't punish the others "low-status" members.
+This solidarity could therefore encourage free-riding.
+Moreover, the effect of punishment is stronger when only cooperators have the power to punish defectors, than when everybody can punish [@Xiao2016].
+Finally, a plain situation is also needed to have a stronger effect of punishment: the link between behaviour and outcome must be clear, without random factors affecting the final outcome [@Xiao2016], and the punishment must be highly effective [@Egas2008].
+
+However, punishment must be applied with carefulness: @Rockenbach2019 compared the strategies of different groups, and found that the most successful ones (whose members had the highest payoff at the end of the experiment) punished with caution and not in early stages of the game.
+In these groups, a norm of when and how punishment should be applied seems to exist.
+Moreover, punishment has also two main negative sides.
+First, it could entails a second-order social dilemma [@Milinski2012], since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators.
+Secondly, anti-social punishment can arise.
+This term refer to the punishment of cooperators by non-cooperators, and it is present when all participants can punish independently of their contributions [@Xiao2016].
+In this context, defectors can see cooperators as rule breakers, and anti-social punishment is a sort of retaliation [@VanDijk2015].
+
+A possible solution could be to implement a system of democratic punishment, where a fine is given only if a majority of participants agree.
+In fact, compared to a peer punishment system where participants decide individually if and who punish, in a democratic system anti-social punishment is less present, general punishment level is lower, and final payoff and cooperation rates are higher [@Pfattheicher2018].
+
+Rewarding systems, on the other side, are less investigated.
+Globally, they have a positive effect on cooperation [@Balliet2011a].
+However, some studies found that they were more efficient than punishment [e.g.
+@Chen2022], while others came to the opposite conclusion [e.g.
+@Milinski2012] or found no difference between the two systems [e.g.
+@Balliet2011a].
+In a meta-analysis, @Balliet2011a found that rewards had a stronger effect on cooperation if their implementation was costly rather than free, and in iterated, rather than single, interactions.
+Moreover, rewarding was more effective in situations where participants had to decide how much take from a common resource, compared to when they had to decide how much contribute to a common good.
+
+In general, incentives seem to be a powerful tool to enhance cooperation, but they have a dark side.
+First, they reduce participants' intrinsic motivation [@VanDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+In fact, @Schlosser2018 demonstrated that people's level of justice sensitivity could predict their contributions to a public good game, but this link disappeared when a punishment system was introduced.
+Secondly, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members, and especially the trust in the fact that others are internally motivated to cooperate.
+This reduced trust in others drops cooperation levels if incentives are removed [@Irwin2014; @Mulder2006].
+
+Finally, incentives are often studied in economic formats, but they can also be social.
+For example, the expectation of honour or shame (after cooperating or defecting, respectively) is enough to enhance cooperation [@Jacquet2011].
+Moreover, expressing disapproval toward defectors can boost cooperation by inducing more compliance to the cooperative social norm [@Nelissen2013].
+Even an ostracism system where participants can vote to exclude other members from the game is very effective in increasing cooperation [@Maier-Rigaud2010].
+In general, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
+
+To conclude, economic incentives can have a positive effect on cooperation, but their efficient implementation must be insured all along the interaction, otherwise cooperation rates would drop.
+On the other hand, social incentives seem to have the same positive effect, and their removal do not cause a reduction of cooperation.
+However, there is a lack of studies focusing on this kind of sanctions.
+
+## Communication
+
+Communication has a global positive effect on cooperation [e.g.
+@Balliet2010; @Bicchieri2002], but this effect is subjected to several moderators.
+First, talking is more powerful than sending written messages, because it allows non-verbal communication and facilitates the social norms formation process.
+Moreover, communication's effect is stronger in large groups: when many people are present cooperation rates are lower, so communication between members can buffer this negative effect [@Balliet2010].
+Finally, if communicating with others requires a personal cost, the effect is weaker than if communication is free [@Janssen2014].
+
+The content of the messages is also essential.
+@Koessler2021 identified four steps necessary for an effective communication in social dilemmas: problem awareness, identification of strategies, agreement and ratification.
+In another study, groups who used communication to foster a common social identity, promote cooperative social norms and ensure that all the players publicly committed displayed higher rates of cooperation than other groups [@Adams2022].
+However, casual chit-chat also plays a very important role in increasing cooperation [@Koessler2021].
+Also, the increase of cooperation through communication can be explained by the normative content that people are shaping while exchanging messages [@Janssen2014], and by the fact that it allows participant to reach a consensus about the best strategy [@Hopthrow2005].
+Moreover, even if communication also helps to create a social identity, the effect of social norms is a stronger mediator of the link between communication and cooperation [@Bicchieri2002].
+
+Another factor that influences the effect of communication on cooperation is whether individuals exchange messages before, during or after the cooperative phase.
+Concerning the post-game communication, @Kumakawa2013 found that receiving a feedback about the cooperation choice made previously can increase cooperation in the following interactions, especially if the feedback is negative.
+However, just the fact of knowing that a discussion will follow is not enough to enhance cooperation, and can even have a counterproductive effect, because forcing people to think about a future discussion make them reflect more on the situation and thus act more rationally [@Torsvik2011].
+On the other hand, communication before or during the interaction have both a positive impact on cooperation, and the difference between their effect is not significant [@Balliet2010].
+
+Finally, several studies investigated the effect of gossip as a form of communication that can increase cooperation.
+Gossip is defined as a spread of reputational information about another person [@Feinberg2014], and it increases cooperation in two ways.
+First, if people know that gossip is possible, they tend to cooperate more to avoid the risk of being the target of such gossip and therefore of being excluded from following interactions.
+Secondly, having information about the past behaviour of potential partners can help to select the most cooperative individuals in an interaction situation [@Feinberg2014].
+Moreover, the same authors found that pro-social individuals gossiped more than pro-self.
+This shows that gossip can have the pro-social function of protecting others from a potential exploitation [@Feinberg2012].
+However, gossip has also some self-interest effects: for instance, observing another subject being exploited and having the opportunity to gossip about the exploiter significantly reduced negative affects in @Feinberg2012 's participants.
+Moreover, providing correct information while gossiping helps to build a positive reputation [@Giardini2021].
+
+In conclusion, when people have the possibility to communicate before, during or after a cooperative interaction, the cooperation level increases.
+Even if the strength of this effect can vary depending on the situation, communication never seems to have a negative impact on cooperation.
+
+## Social Norms
+
+Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour [@VonBorgstede2018].
+@Thogersen2008 studied the effect of social norms on daily social dilemma situations such as environmental behaviours, and found that both injunctive (what others approve) and descriptive (what others do) norms are positively related to behaviours.
+Moreover, cooperation can be maintained via social norms, because people who do not respect them are susceptible of social sanctions.
+In fact, if social approval is possible, people cooperate more [@Rege2004].
+
+There are several explanations of social norms' effect on cooperation.
+First, according to the appropriateness framework, when taking a decision people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
+Therefore they need to define the situation as a cooperative task and to strongly identify with the group [@VanLange2013].
+This leads to a greater accessibility of group's norms and consequently (if the norms are cooperative) to more cooperation.
+Testing this assumption, @Arora2012 showed that a greater identification with social group lead to higher levels of cooperation.
+The second explanation concerns conformity: in general people adapt their cooperation to others' behaviour, but this is usually explained by the reciprocity principle (cooperation enhances the probability that others will do the same, and therefore that the final payoff will be higher) [@Bardsley2005a].
+However, these authors demonstrated that people conform to others' behaviour even if this has no impact on their personal payoff.
+Therefore, people have a general tendency to imitate others to follow social norms.
+
+Finally, social norms can be modified by participants.
+For instance, @Weber2008 demonstrated that in several social dilemma experiment there are consistent cooperators, i.e.
+people who always cooperate.
+The presence of these people can increase other members' cooperation, and this effect is mediated by the perception of the social norms.
+Moreover, social norms can also be shaped via communication [@Bicchieri2002].
+
+In conclusion, social norms have a significant effect on people's cooperation in social dilemma situations.
+Since they are quite easily modified [e.g.
+@Weber2008], shaping cooperative norms can be a powerful instrument to improve cooperation.
+
+## Anonymity
+
+There are not many studies on the influence of anonymity on cooperation, but, according to @Wang2017, most of the factors that can increase cooperation rely on a reduction of anonymity.
+For instance, it is not possible to punish defectors without knowing who they are.
+Therefore, in general it seems that non-anonymous situations can significantly increase cooperation and reduce defection [@Wang2017].
+This can be explained by the fact that, when their actions are visible, people worry about others' approval [@Rege2004] and that, in non-anonymous situations, contributions can be a self-presentation strategy, because being perceived as pro-social can increase one's social status [@VanVugt2010a].
+There are therefore more social incentives to cooperate in non-anonymous, rather than anonymous, situations.
+
+Moreover, this effect is displayed especially in situations when individuals face a cost when cooperating and know that they will not get any personal benefit.
+For instance, @Butz2021 demonstrated that, in a public good game where a part of contributions was donated to a charity association, disclosing identities increased cooperation, but only if the donation was deducted from participants' payoff.
+In the same direction, @VanVugt2010a found that, when actions were public, contributions were higher if the public good was already attained or unattainable, and therefore if participants did not have a personal interest in cooperating.
+
+Reducing anonymity in cooperative interactions can be very effective to encourage people to contribute more.
+A possible way to do this is to reduce group's size.
+In fact, according to @Romano2016, larger groups lead to de-individuation, because it is more difficult to understand who is defecting.
+Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable.
+Moreover, communication is easier in smaller groups [@VonBorgstede2018].
+This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good.
+
+Another effective method to reduce anonymity is to make people publicly promise to cooperate before the cooperative interaction.
+For instance, in a laboratory experiment modeling a common pool resource, people who publicly committed exploited significantly less the resource than people who committed in private, even if after committing they were not restricted in their harvesting possibilities [@Mosler1993].
+This results was also confirmed by @Przepiorka2020, who showed that non-binding promises increased cooperation.
+Moreover, even a compulsory commitment has a beneficial effect on cooperation, even if the most efficient groups are those where all participants signed voluntary the pledge [@Koessler2021a].
+
+In conclusion, reducing anonymity during interactions is essential to improve cooperation, because this can facilitate the implementation of others cooperation-enhancing techniques [@Wang2017].
+Moreover, there are several low-cost method to make situations non-anonymous.
+
+#
+
 # Discussion

### 2023-11-03 scoping_review_short.Rmd
short version of gender, social status, SVO and trust

@@
 
+Five individuals factors that can impact cooperation emerged from the litterature review: gender, social status, group identification, values and personality traits, and trust.
+In the following sections, the principal effects of these factors on cooperation are described.
+Moreover, an overview of the moderators of each effect is provided.
+More details about moderators are included in the Annexe A.
+
 ## Gender
@@
 The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results.
-Sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], but, in general, meta-analysis found a non significant effect size [e.g.
-@Balliet2011; @Spadaro2023].
-This indicates that gender differences in cooperation are very flexible and can vary depending on the context [@Spadaro2023].
-Therefore, when a significant effect is observed, it means that gender has somewhat been made salient by the situation [@Sell2009].
+Sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], but two meta-analysis found a non significant effect size [@Balliet2011; @Spadaro2023].
+This indicates that gender differences in cooperation are very flexible and depend on the context [@Spadaro2023].
+More specifically, @Sell2009 explained this contradictory results "by structural differences [of the experimental settings] and identities triggered by those differences" (p.
+322).
 
-Interaction partners can moderate this effect.
-In fact, in a social dilemma experiment, women were more cooperative toward strangers than men, while men cooperated more in a group of friends.
-Moreover, after a socialization phase where strangers could interact, men cooperated more than women [@Peshkovskaya2017].
-These results seem to indicate that men accord more importance at the relationship with other members than women.
-In fact, the creation of a team identity enhances men's, but not women's, cooperation [@Gomez-Ruiz2020].
-Moreover, in a social dilemma with many iterations, men, but not women, tended to increase their cooperation over time [@Balliet2011].
+The effect of gender on cooperation is therefore subjected to several moderators, since the situation in which women and men interact is essential to determine which gender will cooperate more.
+For instance, men are more cooperative when they know the other participants [@Peshkovskaya2017], when they feel part of a team [@Gomez-Ruiz2020] or when they interact repeatedly with the same group [@Balliet2011].
+The partners' gender is also an important moderator.
+Men-only groups are more cooperative than women-only [@Colman2018; @Peshkovskaya2019], while women cooperate more in mixed groups [@Balliet2011; @Peshkovskaya2019].
+In general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023], even if this effect of group composition can be moderated by other factos [e.g.
+@Barrero-Amortegui2021].
+Moreover, men are more sensitive to greed incentives than women , and thus they cooperate less in situations with strong temptations to free-ride are present [@Simpson2003].
+On the other hand, women's principal motive in cooperative interaction is avoiding to be exploited, and that is why the cooperate less if they don't trust other participants or if they believe than others provide small contributions [@Irwin2015; @Dorrough2019].
 
-The partners' gender also have an impact on women's and men's cooperation.
-In general, groups composed by men only are more cooperative than only-women groups.
-This is explained by the fact that women, compared to men, are generally less concerned by the maximization of their personal payoff and more about relative payoff.
-Thus, the defection strategy allows them to avoid earning less than the other players [@Colman2018].
-Moreover, men display higher levels of gratitude and trust in same-sex groups than women [@Peshkovskaya2019].
-On the other side, women cooperate more in mixed group.
-In fact, when both men and women are present, gender stereotypes are activated and people tend to adapt their behaviour to them.
-This leads women to behave in a more pro-social, altruistic way and men to be more self-oriented and competitive [@Balliet2011].
-The same result is also found by @Peshkovskaya2019, who additionally demonstrated that women reported a stronger social connection with their partners in mixed than in same-sex groups.
-The overall group composition also have an impact on cooperation: in general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023].
-However, @Barrero-Amortegui2021 showed that groups with a majority of women were more cooperative only after the signature of an agreement against excessive harvesting of a common resource.
-Therefore, even the effect of group composition seems to be subjected to moderator variables.
-
-Another reason why gender differences in cooperation are often very small is that fear and greed motives are confused in a classical social dilemma situation [@Simpson2003].
-In this contexts, a feeling of fear arises when one's cooperation could be exploited by others' free-riding, while greed is the feeling associated with the temptation to free-ride on others' cooperation.
-According to social psychology and evolutionary theories, the author expected women to defect more when fear incentives were present, and men to defect more with greed incentives.
-Although only the second hypothesis was corroborated, his intuition about women being more sensitive to the fear of being exploited is confirmed by other studies.
-For example, women level of cooperation is predicted by their trust in their interaction partner, while men's trust and cooperation are not linked [@Irwin2015].
-Moreover, women's lower cooperation is explained by the fact that they expected their partner to contribute less to the common good [@Dorrough2019].
-
-Finally, some of the analyzed papers presented interesting secondary results.
-First, against their authors' expectations, some intercultural studies showed that the gender difference in cooperation is not explained by the level of gender equality of the country [@Dorrough2019; @Spadaro2023].
-Secondly, in an experiment not involving a social dilemma, women were significantly more altruistic than men [@Dorrough2019].
-According to the authors, this underlines the importance of distinguishing between prosociality and strategic interactions that characterize social dilemmas.
-Therefore, in a situation where classical attributes of social dilemmas are not explicit, gender difference in cooperation could not be subjected to the same moderator effects described above.
-Lastly, according to @Sell2009, it is not possible to think about gender without relying it to social status, with men representing the high-status group.
-Therefore, gender differences in cooperation could also be caused by social status: to have a better understanding of this hypothesis, it would be interesting to investigate the difference in cooperation between two other social groups with a different status (e.g.
-high and low socioeconomic status).
-
-In conclusion, "at times women are more cooperative than men, less cooperative than men, or equally as cooperative as men.
-These variations are explained, in large part, by structural differences and identities triggered by those differences" [@Sell2009, p.
-322].
-The context in which men and women interact is therefore essential to predict if a gender will cooperate more than the other, and which one.
+Lastly, gender differences are also linked to social status, with women representing the low-status group.
+Therefore, gender differences in cooperation could also be partly explained by social status: to have a better understanding of this hypothesis, it is important to understand how social status impact cooperation.
 
@@
 
-Few studies have investigated how social status impact cooperation, and their results do not allow to draw a clear conclusion about this effect.
-For instance, advantaged members (i.e.
-high-status class) tend to cooperate less than disadvantaged ones [@Aksoy2019].
-In fact, when participants did not receive the same endowment at the beginning of the experiment, contributions of "rich" and "poor" members converged [@Kingsley2016].
-In other words, proportionally to their resources, low-status participants cooperated more.
-However, in their review, @VanLange2013 identified some studies that observed the opposite effect, namely that wealthier people (or those who benefited more from a common resource) contributed more to the common good than the other.
+The results of studies investigating the impact of social status on cooperation do not allow to draw a clear conclusion about this effect.
+For instance, some findings suggest that low-status participants cooperate more than high-status ones by contributing a higher proportion of their endowments [@Kingsley2016].
+However, @VanLange2013 identified some studies where wealthier people cooperated more.
 
-Social status can also create inter-class conflicts.
-In fact, people cooperated more with the members of the same social class than with other classes' members [@Aksoy2019].
-Moreover, a form of solidarity is observed between low-status members: in a study where participants had the opportunity to punish others for a non-cooperative behaviour, low-status members punished significantly less other low-status participants [@Chen2022].
-Also, in another experiment, participants were randomly advantaged during the interaction: subjects who received a lot of advantages were discriminated by others, and especially by the ones who were rarely advantaged [@Camera2020].
+Social status can also create inter-class conflicts, because people tend to cooperate more with the members of the same social class than with other classes' members [@Aksoy2019].
+This is especially true for low-status groups, where solidarity can arise either in the form of discrimination toward high-status members [@Camera2020], or of less punishments for other low-status [@Chen2022].
 
@@
 
-In conclusion, social status impacts cooperation, but it seems to have multiple effects.
-Moreover, similarly to what @Sell2009 affirmed about the effects of gender and social status, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
+Lastly, similarly to what @Sell2009 affirmed about the effects of gender and social status, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
 This shows that social identity and social status are deeply connected, and that it is difficult to separate their effects on cooperation.
@@
 
-Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group [e.g.
+Social identity have a widely demonstrated positive effect on cooperation: the more individuals identify with a group, the more they cooperate with other members of the group [e.g.
 @Arora2016; @Noonan2016; @Gomez-Ruiz2020].
-For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions.
-This is explained by the fact that, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016].
+In fact, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goals [@Arora2016].
 A strong social identity also maintains a high level of cooperation over time [@Zhang2019].
+The strength of this effect is further confirmed by the fact that it is the same for individualist and collectivist individuals [@Chen2007], and that it works even when groups are created in a laboratory experiment [@Wit1992].
+
 Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect.
@@
 
-Personal values and personality traits can play an important role in predicting cooperative behaviour [@Hilbig2018].
+Personal values and personality traits play an important role in predicting cooperative behaviour [@Hilbig2018].
 One of the most studied is the Social Value Orientation (SVO), that divides people in pro-social and pro-self based on how much they value their own and others' outcomes in situations of interdependence [@Balliet2009].
-The effect of SVO on cooperation is very consensual: in a meta-analysis, 81 out of the 82 papers examined reported that pro-social cooperated significantly more than pro-self [@Balliet2009].
+The effect of SVO on cooperation has been widely demonstrated: in a meta-analysis, 81 out of the 82 papers examined reported that pro-social cooperated significantly more than pro-self [@Balliet2009].
 
-However, this general effect is subjected to several moderators.
-For example, pro-self individuals cooperated more in a game where economic incentives to cooperation were present than in a game without such incentives, while pro-social did not display this difference and showed high levels of cooperation in both contexts [@Emonds2011].
-A similar effect is also described by @Balliet2009, who found a stronger effect of SVO in unpaid games than in paid ones, because, when monetary rewards were present, pro-self increased their cooperation.
-Therefore, pro-self individuals also cooperate, but only when cooperation serves their personal interest.
-In fact, in a study about commuting habits, the extent to which the cooperative behaviour (i.e.
+There are several moderators to this main effect.
+For instance, when economic incentives to cooperation are present, pro-self individuals attain a level of cooperation similar to pro-social's one [@Emonds2011; @Balliet2009].
+Similarly, in a study about commuting habits, the extent to which the cooperative behaviour (i.e.
 choosing to commute by public transportation or carpooling) was perceived as efficient impacted pro-self individual's decision more than pro-social's [@VanLange1998].
+Another moderator is the uncertainity about how many individuals compose the group: if the uncerainty is high pro-social, but not pro-self, increse their level of cooperation [@DeKwaadsteniet2008].
+Finally, pro-self increase their cooperation if they have the possibility to deliberate about the situation [@Lu2019].
 
-Moreover, SVO has a stronger effect if there is an uncertainty about the number of individuals having access to a common resource: when the number of other participants was not known, pro-social, but not pro-self, reduced their harvesting comparing to a group-size certainty condition [@DeKwaadsteniet2008].
-The same authors demonstrated that this result is explained by the fact that pro-social individuals want to maximize the joint outcome, while pro-self mainly think at their own personal interest.
-Also, SVO effect is partly explained by trust, i.e.
-the extent to which people think that their interaction partners will also cooperate.
-In fact, in @VanLange1998, pro-social individuals with a low level of trust did not make different decisions than pro-self individuals, while the most cooperative were pro-social with an high level of trust.
-Finally, the intuitive choice is to cooperate for pro-social individuals, while it is to defect for pro-self [@Lu2019].
-However, pro-self can cooperate more if they have the possibility to deliberate about the situation, because they realize that the best strategy to maximize the joint (and thus personal) outcome is cooperation.
-
-Other studies also focused on how much people are self- or social-oriented by using other constructs.
-For example, @Liu2009a demonstrated that priming a common fate to induce a context of interdependence significantly increased the cooperation level of participants with an independent self, but had no effect on participants with an interdependent self (who already displayed high levels of cooperation).
-Moreover, in a social dilemma experiment, competitive, individualistic people were motivated just by personal gain, while people who saw themselves as a part of a group were more interested on maximizing the income of each member, even at the cost to have a smaller personal payoff [@Probst1999].
-Also, high allocentric (i.e collectivist) individuals cooperated more than low allocentric ones when the perceived social norms are cooperative: this means that they are more sensitive to social cues and therefore they adapt their behaviour to social norms [@Chen2007].
-
-Finally, there are other personal values and traits that can affect cooperation.
-For example, pro-environmental values are negatively correlated with harvesting from a common resource, but only when the resource is scarce; therefore these values are more likely to motivate difficult, rather than easy, ecological behaviours [@Sussman2016].
-Levels of harvesting from a common resource are also lower between left-wingers than right-wingers [@Fosgaard2019].
-Moreover, humility and honesty are significant predictors of cooperation [@Kieslich2014], and this is due to the fact that people with such characteristics manage to resist to the temptation to exploit others' contributions [@Hilbig2018].
-Self-control also plays a role, in the sense that more self-control leads to a greater cooperation [@Kocher2017].
-Lastly, people with an higher justice sensitivity make bigger contributions to a public good [@Schlosser2018].
-
-In conclusion, values and personality traits have a large impact on human cooperation, and it is thus very important to take them into account when investigating this phenomenon.
-Interestingly, some social psychological techniques (e.g.
-elaboration) allow to modify an individual's values [@Sussman2016].
-Such techniques could therefore be used to improve cooperation.
+Other studies also focused on how much people are self- or social-orientation impact cooperation by using other constructs.
+More cooperative individuals have an interdependent definition of the self [@Liu2009a] and see themselves as part of the group [@Probst1999].
+Moreover, allocentric (i.e.
+collectivist) people are more sensitive to cooperative social norms [@Chen2007].
+Finally, other personal values and traits that affect cooperation include pro-environmental values [@Sussman2016], political orientation [@Fosgaard2019], humility and honesty [@Kieslich2014; Hilbig2018], self-control [@Kocher], and justice sensitivity [@Schlosser2018].
 
@@
 Trust can be defined as the "expectations of others' benevolent motives in situations that involve a conflict between self and collective interests" [@Balliet2013, p.1].
-Trust can be dispositional or a state; the former is an individual's general trait, and is usually measured with personality scales, the latter is linked to the context, and can be operazionalized by expectations about a partner's behaviour in a specific situation [@Balliet2013].
+There are two category of trust: first, dispositional trust is an individual general trait that can be assessed with personality scale.
+Secondly, state trust is linked to the context and represent the expectations about a pertner's behaviour in a specific situation [@Balliet2013].
 The two are positively correlated [@Lubke2021], and both have a positive general effect on cooperation [@VanLange2013; @Balliet2013].
-In fact, high levels of trust are associated with more contributions to a public good [@Kocher2015], and a participant's contribution in a public good game can be predicted by her beliefs about others' contributions [@Smith2013].
 
-Several studied confirmed this relationship.
-For instance, @Chaudhuri2002 demonstrated that people who cooperated more in a first public good game trusted more their partner in a following interaction than people whose main strategy was defecting.
-Moreover, people that were pessimistic about others' contribution cooperated significantly less than the optimistic [@Oyediran2018], and those who free-rode in a public good game, compared to cooperators, believed that others contributed less [@Kocher2015].
-Also, people were more willing to purchase actions for a CO2 mitigation initiative when they believed that the majority of others had also bought them [@Sturm2019].
-Finally, in a study about self-administered outlets in Swiss farms (i.e.
-outlets where nobody monitors if people pay or not their purchases), @Franzen2019 found that a farmer's general trust in other people is a significant predictor of the probability of having such an outlet.
-Concerning the moderators, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
+Several studied confirmed this relationship: high levels of trust are associated with more contributions to a public good [@Kocher2015], individuals' cooperation can be predicted by their beliefs about others' contributions [@Smith2013], people who are pessimistic about others' contribution cooperate significantly less than optimistic [@Oyediran2018], and individuals who cooperate more display higher levels of trust in following interactions [@Chaudhuri2002].
+The effect of trust on cooperation has also been demostrated in real-life studies [e.g.
+@Sturm2019; @Franzen2019].
+Finally, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
 
@@
 2].
-These authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to comply to norms.
+Institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to comply to norms.
 Moreover, the effects of perceived costs and benefits of the action are less predictive in people with high institutional trust.
-
-Finally, trusting others (and the institutions) is essential to display higher level of cooperation.
-However, general beliefs about others' cooperation are quite low compared to the actual behaviours, and this trust gap can undermine cooperation, since people's actions are significantly predicted by their beliefs [@Lubke2021].
-In order to increase trust and, consequently, cooperation, it is therefore essential to provide people with reliable information about others' behaviour.
 

### 2023-11-06 scoping_review_short.Rmd
short version individual factors

@@
 
-Five individuals factors that can impact cooperation emerged from the litterature review: gender, social status, group identification, values and personality traits, and trust.
+Five individual factors that can impact cooperation emerged from the litterature review: gender, social status, group identification, values and personality traits, and trust.
 In the following sections, the principal effects of these factors on cooperation are described.
@@
 The effect of gender on cooperation is therefore subjected to several moderators, since the situation in which women and men interact is essential to determine which gender will cooperate more.
-For instance, men are more cooperative when they know the other participants [@Peshkovskaya2017], when they feel part of a team [@Gomez-Ruiz2020] or when they interact repeatedly with the same group [@Balliet2011].
+For instance, men are more cooperative when they know other participants [@Peshkovskaya2017], when they feel part of a team [@Gomez-Ruiz2020] or when they interact repeatedly with the same group [@Balliet2011].
 The partners' gender is also an important moderator.
 Men-only groups are more cooperative than women-only [@Colman2018; @Peshkovskaya2019], while women cooperate more in mixed groups [@Balliet2011; @Peshkovskaya2019].
-In general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023], even if this effect of group composition can be moderated by other factos [e.g.
+In general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023], even if this effect of group composition can be moderated by other factors [e.g.
 @Barrero-Amortegui2021].
 Moreover, men are more sensitive to greed incentives than women , and thus they cooperate less in situations with strong temptations to free-ride are present [@Simpson2003].
-On the other hand, women's principal motive in cooperative interaction is avoiding to be exploited, and that is why the cooperate less if they don't trust other participants or if they believe than others provide small contributions [@Irwin2015; @Dorrough2019].
+On the other hand, women's principal motive in cooperative interaction is avoiding to be exploited, and that is why they cooperate less if they don't trust other participants or if they believe than others provide small contributions [@Irwin2015; @Dorrough2019].
 
-Lastly, gender differences are also linked to social status, with women representing the low-status group.
-Therefore, gender differences in cooperation could also be partly explained by social status: to have a better understanding of this hypothesis, it is important to understand how social status impact cooperation.
+Lastly, gender differences are also linked to social status, with women representing the low-status group [@Sell2009].
+Therefore, gender differences in cooperation could also be partly explained by social status: to have a better understanding of this hypothesis, it is important to gain insights on how social status impact cooperation.
 
@@
 
-Social identity have a widely demonstrated positive effect on cooperation: the more individuals identify with a group, the more they cooperate with other members of the group [e.g.
-@Arora2016; @Noonan2016; @Gomez-Ruiz2020].
-In fact, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goals [@Arora2016].
-A strong social identity also maintains a high level of cooperation over time [@Zhang2019].
-The strength of this effect is further confirmed by the fact that it is the same for individualist and collectivist individuals [@Chen2007], and that it works even when groups are created in a laboratory experiment [@Wit1992].
+Social identity has a strong, positive effect on cooperation: the more individuals identify with a group, the more they cooperate with other members of the group [@VanVugt2009], for instance by providing more voluntary activities for the collective good [@Noonan2016].
+In fact, humans have a very developed sense of belonging to social groups, and when they strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016].
+A strong identification also maintains high levels of cooperation over time [@Zhang2019].
+Finally, further confirmations of the strength of this effect are the fact that it is the same for individualist and collectivist people [@Chen2007] and that group identification can be easily implemented in a laboratory experiment and still have a strong effect on cooperation [@Wit1992].
 
-Moreover, the link between group identification and cooperation is the same for individualist and collectivist people [@Chen2007], which is a further confirmation of the strength of this effect.
-Group identification can also be easily implemented in a laboratory experiment, and it has still a strong positive effect on cooperation [@Wit1992].
-Finally, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].
+In general, people cooperate more with other in-group members than with out-group [@Dorrough2015; @Aksoy2019], but the individual differences in the strength of identification can lead to inequalities on cooperation.
+High-identified individuals can even compensate, by cooperating more, for other in-group members' defection [@VanVugt2009; @Arora2016].
 
-However, the fact that not all members identify with their group to the same extent can lead to inequalities on cooperation.
-For example, @VanVugt2009 mentioned that high-identified individual can even compensate, by cooperating more, for other in-group members' defection.
-The same result was also found by @Arora2016: high-identified individuals cooperated more than low-identified ones when faced to an in-group participant who defected (and this difference was not found when the defector was not a group member).
-However, this compensation came with a cost, since participants who compensated for an in-group defector reported lower trust toward this person.
+Intragroup cooperation can be enhanced via a competition between different groups, because in such a context individual's and group's interests are aligned [@Puurtinen2009].
+Moreover, a study showed that intergroup competition increased cooperation, while individual, dispositional competitiveness had the opposite effect [@Nockur2020].
+This demonstrated that the increase of cooperation via competition is due to group membership factors, and not to competition in itself.
 
-Another well replicated result is the positive effect of intergroup competition on intragroup cooperation.
-In fact, in-group identification can be enhanced via a competition between different groups, because in such a context individual's and group's interests are aligned [@Puurtinen2009].
-In fact, these authors demonstrated that cooperation was higher in an intergroup-competition condition than in a non-competitive condition.
-Moreover, when participants had to compete against other groups, they reported higher levels of anger toward in-group free-riders and they felt more guilty after a defection decision.
-In another experiment using a public resource game, intergroup competition reduced resources consumption, while individual, dispositional competitiveness predicted an higher level of harvesting [@Nockur2020].
-This shows that the increase of cooperation via competition is due to group membership factors, and not to competition in itself.
+Despite the beneficial effects of inducing an intergroup competition, this could be harmful in real-life situations, like for instance in case of resources shared between several groups.
+In fact, there is a greater risk of over-exploitation if an intergroup competition is present [@VanVugt2009].
+To maintain the positive effect of group identification while eliminating the risks associated to the competition, it is useful to prime a superordinate identity [@VanVugt2009].
+This can be done by making salient the common characteristics of the different groups instead of their differences [@Kramer1984] or by inducing the feeling of a common fate [e.g.
+a collective risk, @Zhang2019].
 
-However, despite the observed beneficial effects of inducing an intergroup competition, this could be harmful in real-life situations.
-This is especially true in case of resources that are shared between several groups, which are at greater risk of over-exploitation in case of intergroup competition [@VanVugt2009].
-A possible solution to maintain the positive effects of group identification, while eliminating the risk of over-exploitation caused by the competitive context, is to prime a superordinate identity [@VanVugt2009].
-In fact, intergroup cooperation can be enhanced by making salient the common characteristics of the different groups, instead of their differences [@Kramer1984].
-Another effective way to create a superordinate identity is to induce the feeling of a common fate, for example through a collective risk.
-In fact, a common fate allows a group to become real [@Zhang2019], and can therefore erase intergroup competition.
-
-Finally, social identity does not only have a main effect on people's cooperation, but can also moderate other factors' impact.
-For example, monetary incentive are more effective at enhancing cooperation of low-identified individual than of high-identified ones [@VanVugt2009].
-Moreover, a previous group failure can decrease cooperation between low-identified member, but this effect is not observed in people who have a strong identification with their group [@Jackson2011; @Jackson2012].
-
-In general, social identity seems to have a positive and largely observed effect on individuals' cooperation.
-This is due to the fact that humans have a very developed sense of belonging to social groups, and that this has an impact on their willingness to help other members of their group [@VanVugt2009].
-Since priming a common social identity is quite simple (e.g.
-@Kramer1984; @Zhang2019), this could be a very powerful technique to enhance cooperation in an easy and cheap way.
+Finally, social identification can also moderate other factors' impact on the willingness to cooperate, such as monetary incentives [@VanVugt2009] or a previous group failure [@Jackson2011; @Jackson2012].
 
@@
 choosing to commute by public transportation or carpooling) was perceived as efficient impacted pro-self individual's decision more than pro-social's [@VanLange1998].
-Another moderator is the uncertainity about how many individuals compose the group: if the uncerainty is high pro-social, but not pro-self, increse their level of cooperation [@DeKwaadsteniet2008].
+Another moderator is the uncertainity about the group's size: if the uncerainty is high pro-social, but not pro-self, increse their level of cooperation [@DeKwaadsteniet2008].
 Finally, pro-self increase their cooperation if they have the possibility to deliberate about the situation [@Lu2019].
@@
 Other studies also focused on how much people are self- or social-orientation impact cooperation by using other constructs.
-More cooperative individuals have an interdependent definition of the self [@Liu2009a] and see themselves as part of the group [@Probst1999].
+More cooperative individuals have an interdependent definition of the self [@Liu2009a] and see themselves as part of the group [ @Probst1999].
 Moreover, allocentric (i.e.
 collectivist) people are more sensitive to cooperative social norms [@Chen2007].
-Finally, other personal values and traits that affect cooperation include pro-environmental values [@Sussman2016], political orientation [@Fosgaard2019], humility and honesty [@Kieslich2014; Hilbig2018], self-control [@Kocher], and justice sensitivity [@Schlosser2018].
+Finally, other personal values and traits that affect cooperation include pro-environmental values [@Sussman2016], political orientation [@Fosgaard2019], humility and honesty [@Kieslich2014; @Hilbig2018], self-control [@Kocher2017], and justice sensitivity [@Schlosser2018].
 
@@
 There are two category of trust: first, dispositional trust is an individual general trait that can be assessed with personality scale.
-Secondly, state trust is linked to the context and represent the expectations about a pertner's behaviour in a specific situation [@Balliet2013].
+Secondly, state trust is linked to the context and represent the expectations about a partner's behaviour in a specific situation [@Balliet2013].
 The two are positively correlated [@Lubke2021], and both have a positive general effect on cooperation [@VanLange2013; @Balliet2013].
 
-Several studied confirmed this relationship: high levels of trust are associated with more contributions to a public good [@Kocher2015], individuals' cooperation can be predicted by their beliefs about others' contributions [@Smith2013], people who are pessimistic about others' contribution cooperate significantly less than optimistic [@Oyediran2018], and individuals who cooperate more display higher levels of trust in following interactions [@Chaudhuri2002].
+Several studied confirmed this relationship.
+For instance, high levels of trust are associated with more contributions to a public good [@Kocher2015], individuals' cooperation can be predicted by their beliefs about others' contributions [@Smith2013], people who are pessimistic about others' contribution cooperate significantly less than optimistic [@Oyediran2018], and individuals who cooperate more display higher levels of trust in following interactions [@Chaudhuri2002].
 The effect of trust on cooperation has also been demostrated in real-life studies [e.g.

### 2023-11-06 scoping_review_short.Rmd
short version of all the factors

@@
 
--   **try to shorten as much as possible the result section by putting detailed results on the table**
-
--   **put the references in the table (ex: gender, 11 papers --\> put the 11 references in the case)**
+-   **Shorten OK, see how organize the table (putting all the details of the original paper?)**
 
@@
 Moreover, an overview of the moderators of each effect is provided.
-More details about moderators are included in the Annexe A.
+More details about moderators are included in the Appendix A.
 
@@
 Social identity has a strong, positive effect on cooperation: the more individuals identify with a group, the more they cooperate with other members of the group [@VanVugt2009], for instance by providing more voluntary activities for the collective good [@Noonan2016].
-In fact, humans have a very developed sense of belonging to social groups, and when they strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016].
+In fact, humans have a very developed sense of belonging to social groups, and when they strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they value more group-related goal [@Arora2016].
 A strong identification also maintains high levels of cooperation over time [@Zhang2019].
@@
 
-Intragroup cooperation can be enhanced via a competition between different groups, because in such a context individual's and group's interests are aligned [@Puurtinen2009].
+Intragroup cooperation can be enhanced via a competition between different groups, because in such a context individuals' and groups' interests are aligned [@Puurtinen2009].
 Moreover, a study showed that intergroup competition increased cooperation, while individual, dispositional competitiveness had the opposite effect [@Nockur2020].
@@
 To maintain the positive effect of group identification while eliminating the risks associated to the competition, it is useful to prime a superordinate identity [@VanVugt2009].
-This can be done by making salient the common characteristics of the different groups instead of their differences [@Kramer1984] or by inducing the feeling of a common fate [e.g.
+This can be done by making salient the common characteristics of the different groups rather than their differences [@Kramer1984] or by inducing the feeling of a common fate [e.g.
 a collective risk, @Zhang2019].
@@
 
+On the organizational level, four factors have emerged from the literature review: incentives, communication, social norms and anonymity.
+As for the individual factors, the main effects of each factor are detailed in the next sections, as well as an overview of possible moderators.
+More details can be found in Appendix A.
+
 ## Incentives
 
-Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^1].
-In the literature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
-In general, when there is the possibility for participants to punish others members based on their contributions, cooperation is higher than when this is not possible [e.g.
-@Pfattheicher2018; @Balliet2011a].
+Cooperation can be modified by introducing incentives, who can be either punishments or rewards[^1].
+In the literature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation has been widely demonstrated.
+In fact, when participants can punish other members for not contributing equally cooperation s higher than when this is not possible [e.g.
+@Balliet2011a; @Pfattheicher2018].
 Moreover, the presence of a punishment system increases the perception of fairness [@Nockur2021].
@@
 
-However, this main results is subjected to several moderators.
-First, the punishment has a bigger impact on cooperation if its implementation is costly for the punishers than if it is free [@Balliet2011a], but at the same time the cost should not be too high [@Egas2008].
-Moreover, punishments are more effective if the interaction is among friends than among strangers, and if people know that they will have to interact repeatedly with each other [@Balliet2011a].
-In fact, in short interactions, if punishment is costly, individuals who punish others are the ones with the lowest personal income [@Milinski2012], and this could discourage the application of the fine.
-Also, an experiment showed that a punishment system increased cooperation in groups where all members had the same amount of resources, but not in groups where income was heterogeneous [@Kingsley2016].
-In fact, @Chen2022 found that, in groups where the initial endowment was heterogeneous, participants that received less didn't punish the others "low-status" members.
-This solidarity could therefore encourage free-riding.
-Moreover, the effect of punishment is stronger when only cooperators have the power to punish defectors, than when everybody can punish [@Xiao2016].
-Finally, a plain situation is also needed to have a stronger effect of punishment: the link between behaviour and outcome must be clear, without random factors affecting the final outcome [@Xiao2016], and the punishment must be highly effective [@Egas2008].
+Several factors moderate this main effect.
+Punishments are more effective if their implementation is (moderately) costly rather than free [@Balliet2011a; @Egas2008], if the members are friends rather than strangers, if they know that they will interact repeatedly [@Balliet2011a], and if only cooperators have the power to punish defectors [@Xiao2016].
+Also, a punishment system increase cooperation mostly in groups where all members have the same income [@Kingsley2016], because in heterogeneous groups a form of solidarity between low-status members arises and encourages free-riding [@Chen2022].
+Finally, a plain situation is needed to have a stronger effect of punishment: the link between behaviour and outcome must be clear, without random factors affecting the final outcome [@Xiao2016], and the punishment must be highly effective [@Egas2008].
 
-However, punishment must be applied with carefulness: @Rockenbach2019 compared the strategies of different groups, and found that the most successful ones (whose members had the highest payoff at the end of the experiment) punished with caution and not in early stages of the game.
-In these groups, a norm of when and how punishment should be applied seems to exist.
-Moreover, punishment has also two main negative sides.
-First, it could entails a second-order social dilemma [@Milinski2012], since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators.
-Secondly, anti-social punishment can arise.
-This term refer to the punishment of cooperators by non-cooperators, and it is present when all participants can punish independently of their contributions [@Xiao2016].
-In this context, defectors can see cooperators as rule breakers, and anti-social punishment is a sort of retaliation [@VanDijk2015].
+At the same time, punishment must be applied with carefulness.
+For instance, the most successful groups are those who punish with caution and not in early stages of the interaction, and who have a norm of when and how punishment should be applied [@Rockenbach2019].
+Moreover, punishment has also two negative sides.
+First, it could entails a second-order social dilemma, since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators [@Milinski2012].
+Secondly, when all participants can punish independently of their contributions, anti-social punishment (i.e.
+the punishment of cooperators by non-cooperators) can arise [@Xiao2016].
+A solution could be to implement a system of democratic punishment, where a fine is given only if a majority of participants agree.
+In fact, with this kind of system the punishment level is lower, while final payoff and cooperation rates are higher [@Pfattheicher2018].
 
-A possible solution could be to implement a system of democratic punishment, where a fine is given only if a majority of participants agree.
-In fact, compared to a peer punishment system where participants decide individually if and who punish, in a democratic system anti-social punishment is less present, general punishment level is lower, and final payoff and cooperation rates are higher [@Pfattheicher2018].
+On the other side, rewarding systems are less investigated.
+Generally, they have a positive effect on cooperation [@Balliet2011a], but it is not clear whether they are more efficient than punishment [as found by @Chen2022], less efficient [see @Milinski2012] or equivalent [see @Balliet2011a].
+Similarly to punishments, rewards have a stronger effect if their implementation is costly and during iterated, rather than single, interactions [@Balliet2011a].
 
-Rewarding systems, on the other side, are less investigated.
-Globally, they have a positive effect on cooperation [@Balliet2011a].
-However, some studies found that they were more efficient than punishment [e.g.
-@Chen2022], while others came to the opposite conclusion [e.g.
-@Milinski2012] or found no difference between the two systems [e.g.
-@Balliet2011a].
-In a meta-analysis, @Balliet2011a found that rewards had a stronger effect on cooperation if their implementation was costly rather than free, and in iterated, rather than single, interactions.
-Moreover, rewarding was more effective in situations where participants had to decide how much take from a common resource, compared to when they had to decide how much contribute to a common good.
-
-In general, incentives seem to be a powerful tool to enhance cooperation, but they have a dark side.
-First, they reduce participants' intrinsic motivation [@VanDijk2015], by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
-In fact, @Schlosser2018 demonstrated that people's level of justice sensitivity could predict their contributions to a public good game, but this link disappeared when a punishment system was introduced.
-Secondly, when incentives are present people think that others cooperate just because of them, and this undermines their trust in other members, and especially the trust in the fact that others are internally motivated to cooperate.
-This reduced trust in others drops cooperation levels if incentives are removed [@Irwin2014; @Mulder2006].
+To conclude, incentives can enhance cooperation, but they have some negative sides.
+First, they reduce participants' intrinsic motivation to cooperate [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+Secondly, incentives undermine participants' trust in other members' internal motivation to cooperate.
+Therefore, if they are removed, cooperation drops [@Irwin2014; @Mulder2006].
 
 Finally, incentives are often studied in economic formats, but they can also be social.
-For example, the expectation of honour or shame (after cooperating or defecting, respectively) is enough to enhance cooperation [@Jacquet2011].
-Moreover, expressing disapproval toward defectors can boost cooperation by inducing more compliance to the cooperative social norm [@Nelissen2013].
-Even an ostracism system where participants can vote to exclude other members from the game is very effective in increasing cooperation [@Maier-Rigaud2010].
-In general, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
-
-To conclude, economic incentives can have a positive effect on cooperation, but their efficient implementation must be insured all along the interaction, otherwise cooperation rates would drop.
-On the other hand, social incentives seem to have the same positive effect, and their removal do not cause a reduction of cooperation.
-However, there is a lack of studies focusing on this kind of sanctions.
+In fact, expecting honour or shame (after cooperating or defecting, respectively), or expressing disapproval toward defectors can enhance cooperation [@Jacquet2011; @Nelissen2013].
+Even an ostracism system where participants can vote to exclude other members is very effective [@Maier-Rigaud2010].
+In conclusion, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
 
@@
 
-Communication has a global positive effect on cooperation [e.g.
-@Balliet2010; @Bicchieri2002], but this effect is subjected to several moderators.
-First, talking is more powerful than sending written messages, because it allows non-verbal communication and facilitates the social norms formation process.
-Moreover, communication's effect is stronger in large groups: when many people are present cooperation rates are lower, so communication between members can buffer this negative effect [@Balliet2010].
-Finally, if communicating with others requires a personal cost, the effect is weaker than if communication is free [@Janssen2014].
+Communication between members has a global positive effect on cooperation [e.g.
+@Balliet2010], because it allows to shape a normative content [@Janssen2014; @Bicchieri2002] and to reach a consensus about the best strategy [@Hopthrow2005].
+In fact, when communication is used to foster a common social identity, promote cooperative social norms and ensure that every member publicly commits, communication is higher [@Adams2022].
 
-The content of the messages is also essential.
-@Koessler2021 identified four steps necessary for an effective communication in social dilemmas: problem awareness, identification of strategies, agreement and ratification.
-In another study, groups who used communication to foster a common social identity, promote cooperative social norms and ensure that all the players publicly committed displayed higher rates of cooperation than other groups [@Adams2022].
+Concerning the moderation effects, oral communication is more powerful than written messages, and communication has a stronger impact in large, rather than small, groups [@Balliet2010].
+Moreover, if communicating requires a personal cost, its effect is weaker than if communication is free [@Janssen2014].
+The content of the message is also essential: to be effective, communication must allow participants to become aware of the problem, identify different strategies and agree on the one to use.
 However, casual chit-chat also plays a very important role in increasing cooperation [@Koessler2021].
-Also, the increase of cooperation through communication can be explained by the normative content that people are shaping while exchanging messages [@Janssen2014], and by the fact that it allows participant to reach a consensus about the best strategy [@Hopthrow2005].
-Moreover, even if communication also helps to create a social identity, the effect of social norms is a stronger mediator of the link between communication and cooperation [@Bicchieri2002].
+Finally, communication before or during the cooperative interaction have both a positive impact on cooperation [@Balliet2010], while knowing that it will be possible to communicate after the interaction does not enhance cooperation [@Kumakawa2013], and can even have a negative effect [@Torsvik2011].
 
-Another factor that influences the effect of communication on cooperation is whether individuals exchange messages before, during or after the cooperative phase.
-Concerning the post-game communication, @Kumakawa2013 found that receiving a feedback about the cooperation choice made previously can increase cooperation in the following interactions, especially if the feedback is negative.
-However, just the fact of knowing that a discussion will follow is not enough to enhance cooperation, and can even have a counterproductive effect, because forcing people to think about a future discussion make them reflect more on the situation and thus act more rationally [@Torsvik2011].
-On the other hand, communication before or during the interaction have both a positive impact on cooperation, and the difference between their effect is not significant [@Balliet2010].
-
-Finally, several studies investigated the effect of gossip as a form of communication that can increase cooperation.
-Gossip is defined as a spread of reputational information about another person [@Feinberg2014], and it increases cooperation in two ways.
-First, if people know that gossip is possible, they tend to cooperate more to avoid the risk of being the target of such gossip and therefore of being excluded from following interactions.
-Secondly, having information about the past behaviour of potential partners can help to select the most cooperative individuals in an interaction situation [@Feinberg2014].
-Moreover, the same authors found that pro-social individuals gossiped more than pro-self.
-This shows that gossip can have the pro-social function of protecting others from a potential exploitation [@Feinberg2012].
-However, gossip has also some self-interest effects: for instance, observing another subject being exploited and having the opportunity to gossip about the exploiter significantly reduced negative affects in @Feinberg2012 's participants.
-Moreover, providing correct information while gossiping helps to build a positive reputation [@Giardini2021].
-
-In conclusion, when people have the possibility to communicate before, during or after a cooperative interaction, the cooperation level increases.
-Even if the strength of this effect can vary depending on the situation, communication never seems to have a negative impact on cooperation.
+A particular form of communication is gossip, i.e.
+the spread of reputational information about another person [@Feinberg2014].
+Gossip increases cooperation by providing information about the past behaviour of potential partners, which helps to select the most cooperative members in a following interaction.
+Moreover, knowing that gossip is possible motivates people to cooperate more to avoid being the target of such gossip [@Feinberg2014].
+Gossip can also have the pro-social function of protecting others from a potential exploitation [@Feinberg2012], and providing correct information while gossiping helps to build a positive reputation [@Giardini2021].
 
@@
 
-Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour [@VonBorgstede2018].
-@Thogersen2008 studied the effect of social norms on daily social dilemma situations such as environmental behaviours, and found that both injunctive (what others approve) and descriptive (what others do) norms are positively related to behaviours.
-Moreover, cooperation can be maintained via social norms, because people who do not respect them are susceptible of social sanctions.
-In fact, if social approval is possible, people cooperate more [@Rege2004].
+Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour like in cooperative situations [@VonBorgstede2018].
+Both injunctive (what others approve) and descriptive (what others do) norms are positively related to cooperative behaviours [@Thogersen2008].
+Moreover, social norms help to maintain cooperation, because individuals who do not respect them are susceptible of social sanction [@Rege2004].
 
-There are several explanations of social norms' effect on cooperation.
-First, according to the appropriateness framework, when taking a decision people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
-Therefore they need to define the situation as a cooperative task and to strongly identify with the group [@VanLange2013].
-This leads to a greater accessibility of group's norms and consequently (if the norms are cooperative) to more cooperation.
-Testing this assumption, @Arora2012 showed that a greater identification with social group lead to higher levels of cooperation.
-The second explanation concerns conformity: in general people adapt their cooperation to others' behaviour, but this is usually explained by the reciprocity principle (cooperation enhances the probability that others will do the same, and therefore that the final payoff will be higher) [@Bardsley2005a].
-However, these authors demonstrated that people conform to others' behaviour even if this has no impact on their personal payoff.
-Therefore, people have a general tendency to imitate others to follow social norms.
+Social norms shape cooperation because, according to the appropriateness framework, when taking a decision people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
+If they define the situation as a cooperative task and strongly identify with the group, group's norms will be more accessible and they will have a stronger impact on behaviour [@VanLange2013].
+Moreover, people have a general tendency to imitate what others do, even if others' actions do not have an impact on their personal gains [@Bardsley2005a].
 
-Finally, social norms can be modified by participants.
-For instance, @Weber2008 demonstrated that in several social dilemma experiment there are consistent cooperators, i.e.
-people who always cooperate.
-The presence of these people can increase other members' cooperation, and this effect is mediated by the perception of the social norms.
-Moreover, social norms can also be shaped via communication [@Bicchieri2002].
-
-In conclusion, social norms have a significant effect on people's cooperation in social dilemma situations.
-Since they are quite easily modified [e.g.
-@Weber2008], shaping cooperative norms can be a powerful instrument to improve cooperation.
+Finally, social norms can be modified by participants' behaviour.
+For instance, the presence of consistent cooperators (i.e.
+people who always cooperate, independently from others' actions) creates a more cooperative social norm and thus increases cooperation [@Weber2008].
+Moreover, participants can also shape social norms via communication [@Bicchieri2002].
 
@@
 
-There are not many studies on the influence of anonymity on cooperation, but, according to @Wang2017, most of the factors that can increase cooperation rely on a reduction of anonymity.
-For instance, it is not possible to punish defectors without knowing who they are.
-Therefore, in general it seems that non-anonymous situations can significantly increase cooperation and reduce defection [@Wang2017].
-This can be explained by the fact that, when their actions are visible, people worry about others' approval [@Rege2004] and that, in non-anonymous situations, contributions can be a self-presentation strategy, because being perceived as pro-social can increase one's social status [@VanVugt2010a].
-There are therefore more social incentives to cooperate in non-anonymous, rather than anonymous, situations.
+In general, in non-anonymous situations cooperation is significantly higher than in anonymous ones [@Wang2017].
+In fact, in such situations there are more social incentives to cooperate, because people worry about others' approval [@Rege2004].
+Moreover, several factors that can increase cooperation rely on a reduction of anonymity [@Wang2017]: for instance, punish defectors is impossible without knowing who they are.
+When behaviours are visible, cooperation can also be a self-presentation strategy to be perceived as pro-social and therefore to increase one's social status.
+In fact, the positive effect of non-anonymity is stronger in situations where cooperation bears a cost without offering a personal gain [@Butz2021; @VanVugt2010a].
 
-Moreover, this effect is displayed especially in situations when individuals face a cost when cooperating and know that they will not get any personal benefit.
-For instance, @Butz2021 demonstrated that, in a public good game where a part of contributions was donated to a charity association, disclosing identities increased cooperation, but only if the donation was deducted from participants' payoff.
-In the same direction, @VanVugt2010a found that, when actions were public, contributions were higher if the public good was already attained or unattainable, and therefore if participants did not have a personal interest in cooperating.
-
-Reducing anonymity in cooperative interactions can be very effective to encourage people to contribute more.
-A possible way to do this is to reduce group's size.
-In fact, according to @Romano2016, larger groups lead to de-individuation, because it is more difficult to understand who is defecting.
-Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable.
-Moreover, communication is easier in smaller groups [@VonBorgstede2018].
-This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good.
-
-Another effective method to reduce anonymity is to make people publicly promise to cooperate before the cooperative interaction.
-For instance, in a laboratory experiment modeling a common pool resource, people who publicly committed exploited significantly less the resource than people who committed in private, even if after committing they were not restricted in their harvesting possibilities [@Mosler1993].
-This results was also confirmed by @Przepiorka2020, who showed that non-binding promises increased cooperation.
-Moreover, even a compulsory commitment has a beneficial effect on cooperation, even if the most efficient groups are those where all participants signed voluntary the pledge [@Koessler2021a].
-
-In conclusion, reducing anonymity during interactions is essential to improve cooperation, because this can facilitate the implementation of others cooperation-enhancing techniques [@Wang2017].
-Moreover, there are several low-cost method to make situations non-anonymous.
-
-#
+Therefore, reducing anonymity in cooperative interaction could significantly improve cooperation.
+A possible way to do this is to reduce group's size, because larger groups lead to de-individuation and it is thus more difficult to identify defectors [@Romano2016].
+In fact, cooperation levels are higher in small, rather than large, groups [@Jiang2021].
+Anonymity can also be reduced by making people publicly promise to cooperate.
+Such a commitment increases significantly cooperation rates, even if after committing people are not forced to cooperate [@Mosler1993; @Przepiorka2020].
+Moreover, even a compulsory commitment has a beneficial effect on cooperation [@Koessler2021a].
 

### 2023-11-09 paper1_markdown.Rmd
09.11

@@
 Commons are currently receiving more and more attention because they function outside of the capitalist system, they respect the planet by giving mutual benefits to their members, and they could be the needed change toward more sustainable and fair economy and society [@Meroni2022; @Seravalli2018a].
-In fact, having small groups with a high perception of risk and a minimal uncertainty in collective goal, possibly focused on regional issues, could significantly improve the probability of success in attaining common goals related to sustainability [@Pacheco2014].
+In fact, having small groups with a high perception of risk and a minimal uncertainty in collective goal, possibly focused on regional issues, could significantly improve the probability of success in attaining common goals related to sustainability [@Pacheco2014 =\> mention that is a mathematical model + combine with @VanVugt1998 ?].
 Moreover, it is easier to coordinate on a local, rather than global, level [@Carpenter2011].
 Broadly, commons represent a possible solution simply by showing that alternatives to the classic model are possible [@Baibarac-Duignan2023].
++ @VanVugt1998: people generally feel more committed to solving problems occurring in their direct environment
 
@@
 There are different approaches to the study of cooperation.
-For instance, classical economic theories consider individuals as completely rational and always maximizing (expected) utility [@Edwards1954].
+For instance, classical economic theories consider individuals as completely rational and always maximizing (expected) utility [@Edwards1954] (see @DeCaro2021 for a more recent reference).
 Thus, according to these theories, individuals are not supposed to behave altruistically, namely to incur a personal cost while benefiting others [@Wittek2015].
-Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage.
-For example, the theory of competitive altruism posits that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation [@Roberts1998].
+Another theoretical approach toward cooperation is the evolutionary perspective, which suggests that individuals can show cooperation, but only when doing so bring them a personal advantage.
+For example, the theory of competitive altruism posits that acting for others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation [@Roberts1998].
 Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
 
-Cooperation has also extensively been studied through social dilemma.
+Cooperation has also extensively been studied through researches on social dilemmas.
 In such situations, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
@@
 This approach is very useful to gain insights into how cooperation works because it provides a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
-While according to economic and evolutionary theories individuals are always pursuing their self-interest (either by defecting to maximize their personal payoff, either by cooperating to increase their social status and reputation), social dilemma experiments' results show that it is not always the case.
+While according to economic and evolutionary theories individuals are always pursuing their self-interest (either by defecting to maximize their personal payoff, or by cooperating to increase their social status and reputation), social dilemma experiments' results show that it is not always the case.
 First, it is observed that a significant amount of people are "strong reciprocators": they are willing to use their personal resources to reward cooperators and punish defectors, even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009].
-Moreover, social dilemma experiments provided evidences suggesting that people do not always thoroughly analyze the context to take a rational decision.
+Moreover, social dilemma experiments provided evidences suggesting that people do not always thoroughly analyze the context to make a rational decision.
 In fact, cooperation seems to be the intuitive option, while defection needs more thinking [@Kieslich2014].
 Additionally, people can also cooperate in part because they are confused about the situation [@Andreoni1995].
-In fact, @Fosgaard2017 showed that, in some experiments, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff, and these misconceptions can vary depending on how the game is presented.
+In fact, @Fosgaard2017 showed that, in some experiments, there is a considerable number of participants who do not correctly understand the strategies to maximize the personal or the collective payoff, and these misconceptions can vary depending on how the game is presented.
 Moreover, there are individual differences in the level of rationality, i.e.
-the ability to think analytically at the situation [@Lang2018]: individuals scoring low in rationality cooperate more than individuals with an high score.
+the ability to think analytically about the situation [@Lang2018]: individuals scoring low in rationality cooperate more than individuals with a high score.
 These evidences suggest that people are not always rational in the economic, individualistic way [@Kollock1998], and that there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].
@@
 @Ostrom1990; @Franzen2019].
-A possible explanation is the Greed Efficiency Fairness hypothesis: people's greed to pursuit their personal interest is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
-Thus, cooperation is not always driven by personal interest, and people care about others and environment [@Torsvik2011; @VanVugt2009].
+A possible explanation is the Greed Efficiency Fairness hypothesis: people's greed to pursue their personal interests is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
+Thus, cooperation is not always driven by personal interest, and people care about others and the environment [@Torsvik2011; @VanVugt2009].
 
 However, cooperation in commons has not been systematically studied like it has been in social dilemmas, and there is therefore a lack of knowledge about the factors that could enhance cooperation in this context.
-A way to start to fill this gap is to apply results of social dilemma to the commons.
+A way to start to fill this gap is to apply the results of social dilemmas to the commons.
 Linking these two topics is pertinent for at least three reasons.
 First, social dilemmas and commons share the same basic conflict between personal and collective interests [@Hardin1968; @Dawes1980].
-For this reason, commons can be considered as a particular case of social dilemma (for example, @Sussman2016 used the term of "commons dilemma").
+For this reason, commons can be considered as a particular case of social dilemma (for example, @Sussman2016 used the term of "commons dilemma" + @Kopelman2022, at the beginning also use the term of "commons dilemma" and she explains better).
 Secondly, cooperation and defection in social dilemma laboratory experiments can predict people's behaviour in a commons situation [e.g.
 @Reindl2019; @Ros-Galvez2015].
-Finally, others studies already used a social dilemma framework to study real-life commons [e.g.
+Finally, other studies already used a social dilemma framework to study real-life commons [e.g.
 @Hartl2022].
 
-Based on these evidences, the aim of the present review is to use social dilemma literature to gain insights into cooperation in commons by (a) identifying individual factors that can shape it and (b) understanding which strategies groups can implement to encourage their members to cooperate.
+Based on these evidences, the aim of the present review is to apply social dilemma literature to gain insights into cooperation in commons by (a) identifying individual factors that can shape it and (b) understanding which strategies groups can implement to encourage their members to cooperate.
 It is important to note that the point (b) will focus exclusively on bottom-up strategies that groups can adopt, and not on top-down solutions like privatization or centralized control of the resource.
@@
 The research was made during the month of August, 2023.
-According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included, to have an idea as complete as possible about the existing literature on the topic.
+According to @Munn2022, the type of source was not a selection criterion, therefore journal articles, conference papers and book chapters could be included, to have an idea as complete as possible about the existing literature on the topic.
 Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision.
@@
 First, as mentioned in the introduction, papers investigating how an external entity/institution shapes cooperation were not included.
-Secondly, human participants were needed, so papers who studied social dilemmas with an agent-based model were also excluded.
+Secondly, human participants were needed, so papers that studied social dilemmas with an agent-based model were also excluded.
 Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.
@@
 Cooperation rates can be modified by introducing incentives, who can be either punishments or rewards[^2].
-In the literature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
+In the literature, punishment has received a greater attention than reward [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation is very consensual.
 In general, when there is the possibility for participants to punish others members based on their contributions, cooperation is higher than when this is not possible [e.g.
@@
 However, this main results is subjected to several moderators.
-First, the punishment have a bigger impact on cooperation if its implementation is costly for the punishers than if it is free [@Balliet2011a], but at the same time the cost should not be too high [@Egas2008].
+First, the punishment has a bigger impact on cooperation if its implementation is costly for the punishers than if it is free [@Balliet2011a], but at the same time the cost should not be too high [@Egas2008].
 Moreover, punishments are more effective if the interaction is among friends than among strangers, and if people know that they will have to interact repeatedly with each other [@Balliet2011a].
@@
 
+@Kopelman2002: some of the factors are the same =\> see the structure that they used (individual vs situational, with situational further divided into "task structure-related" and "perception of the task")
+
 First, according to the analyzed papers, trust has a positive effect on cooperation.
@@
 Figure 1. Flow diagram of the scoping review selection process.
+
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Factor                   | Type of factor | N analyzed papers             | General effect on cooperation                                                             | Moderators                                                                                                                                                                                                                                                                                            |
++:=========================+================+===============================+===========================================================================================+=======================================================================================================================================================================================================================================================================================================+
+| Gender                   | Individual     | 11                            | ?
+| Interaction partners: women cooperate more toward strangers, men cooperated more toward friends                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Partners' gender: only-men groups are more cooperative than only-women ones, women cooperate more in mixed groups than men                                                                                                                                                                            |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Group composition: groups with a majority of women cooperate more                                                                                                                                                                                                                                     |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Fear of being exploited: women, but not men, cooperation is predicted by their trust in others                                                                                                                                                                                                        |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Social status            | Individual     | 6                             | ?
+| Solidarity: low-status members punish less others low-status if they don't cooperate and cooperate less with high-status                                                                                                                                                                              |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Group identification     | Individual     | 14                            | Strongly identified individuals cooperate more with the in-group than low-identified ones | Inter-group competition: if different groups have to compete, intragroup competition increases                                                                                                                                                                                                        |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Superordinate identity: maintains the positive effects of group identification and eliminates the risk linked to intergroup competition                                                                                                                                                               |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Social Value Orientation | Individual     | 8 (SVO)                       | Pro-social individuals cooperate more than pro-self                                       | Economic incentives: pro-self improve their cooperation if incentives are present                                                                                                                                                                                                                     |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                | 6 (other personality factors) |                                                                                           | Uncertainty about number of members: pro-social, but not pro-self, improve their cooperation if the number of members is not known                                                                                                                                                                    |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Deliberation: pro-self improve their cooperation if they have the possibility to deliberate about the situation                                                                                                                                                                                       |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Trust                    | Individual     | 10                            | People with high levels of trust cooperate more than people with low levels               | Conflict between personal and collective interests: trust has a stronger effect in situations with a large, rather than small, conflict                                                                                                                                                               |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Uncertainty about others' intentions: trust has a stronger effect if the uncertainty is high than low                                                                                                                                                                                                 |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Incentives               | Organizational | 17                            | Punishment and reward systems have a positive effect on cooperation                       | Cost of implementation: incentives are more effective if they are costly than if they are free                                                                                                                                                                                                        |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Repeated interactions: incentives' effect is stronger in iterated, rather than single, interactions                                                                                                                                                                                                   |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Group homogeneity: punishments increase cooperation in homogeneous groups, but not in heterogeneous                                                                                                                                                                                                   |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Organization: punishments are more effective when only cooperator can punish defectors, rather than when everybody can punish.
+A democratic punishment system (where a fine is given only if a majority agrees) is more effective than a system where everybody can decide individually who punishing |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Type of incentives: cooperation drops after economic incentives are removed, but not after the removal of social ones                                                                                                                                                                                 |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Communication            | Organizational | 11                            | Having the possibility to communicate with other members increases cooperation            | Form: oral communication has a stronger effect on cooperation than written messages                                                                                                                                                                                                                   |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Group size: the effect of communication on cooperation is stronger in large, rather than small groups                                                                                                                                                                                                 |
+|                          |                |                               |                                                                                           |                                                                                                                                                                                                                                                                                                       |
+|                          |                |                               |                                                                                           | Content: groups that use communication to foster a social identity and to promote cooperative social norms cooperate more than other groups                                                                                                                                                           |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Social norms             | Organizational | 8                             | Cooperative social norms increase cooperation                                             | Anonymity: if behaviours are observable, people comply more to social norms                                                                                                                                                                                                                           |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
+| Anonymity                | Organizational | 10                            | People cooperate more in non-anonymous situations than in anonymous ones                  | Personal interest: if there is no personal interest in cooperating, the improvement on cooperation in non-anonymous situations is stronger                                                                                                                                                            |
++--------------------------+----------------+-------------------------------+-------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

### 2023-11-09 scoping_review_short.Rmd
09.11

@@
 
-**TO DO LIST:**
-
--   **Shorten OK, see how organize the table (putting all the details of the original paper?)**
-
--   **look for journals and their requirements to know how much shorten and how to frame the introduction + discussion (ask Vincent which journal he chose?)**
-
 # Individual factors
@@
 Social identity has a strong, positive effect on cooperation: the more individuals identify with a group, the more they cooperate with other members of the group [@VanVugt2009], for instance by providing more voluntary activities for the collective good [@Noonan2016].
-In fact, humans have a very developed sense of belonging to social groups, and when they strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they value more group-related goal [@Arora2016].
+In fact, humans have a very developed sense of belonging, and when they strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they value more group-related goal [@Arora2016].
 A strong identification also maintains high levels of cooperation over time [@Zhang2019].
@@
 
-Despite the beneficial effects of inducing an intergroup competition, this could be harmful in real-life situations, like for instance in case of resources shared between several groups.
+Despite the beneficial effects of inducing an intergroup competition, this could be harmful in real-life situations, like resources shared between several groups.
 In fact, there is a greater risk of over-exploitation if an intergroup competition is present [@VanVugt2009].
-To maintain the positive effect of group identification while eliminating the risks associated to the competition, it is useful to prime a superordinate identity [@VanVugt2009].
-This can be done by making salient the common characteristics of the different groups rather than their differences [@Kramer1984] or by inducing the feeling of a common fate [e.g.
-a collective risk, @Zhang2019].
+To maintain the positive effect of group identification while eliminating the risks associated to the competition, it is useful to prime a super-ordinate identity [@VanVugt2009].
+This can be done by making salient the common characteristics of the different groups rather than their differences [@Kramer1984] or by inducing the feeling of a common fate [@Zhang2019].
 
@@
 Other studies also focused on how much people are self- or social-orientation impact cooperation by using other constructs.
-More cooperative individuals have an interdependent definition of the self [@Liu2009a] and see themselves as part of the group [ @Probst1999].
+More cooperative individuals have an interdependent definition of the self [@Liu2009a] and see themselves as part of the group [@Probst1999].
 Moreover, allocentric (i.e.
@@
 For instance, high levels of trust are associated with more contributions to a public good [@Kocher2015], individuals' cooperation can be predicted by their beliefs about others' contributions [@Smith2013], people who are pessimistic about others' contribution cooperate significantly less than optimistic [@Oyediran2018], and individuals who cooperate more display higher levels of trust in following interactions [@Chaudhuri2002].
-The effect of trust on cooperation has also been demostrated in real-life studies [e.g.
+The effect of trust on cooperation has also been demonstrated in real-life studies [e.g.
 @Sturm2019; @Franzen2019].
@@
 2].
-Institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to comply to norms.
-Moreover, the effects of perceived costs and benefits of the action are less predictive in people with high institutional trust.
+Institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied motivate people to comply to norms.
 
@@
 Cooperation can be modified by introducing incentives, who can be either punishments or rewards[^1].
-In the literature, punishment has received a greater attention than rewards [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation has been widely demonstrated.
-In fact, when participants can punish other members for not contributing equally cooperation s higher than when this is not possible [e.g.
+In the literature, punishment has received a greater attention than reward [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation has been widely demonstrated.
+In fact, when participants can punish other members for not contributing equally cooperation is higher than when this is not possible [e.g.
 @Balliet2011a; @Pfattheicher2018].
@@
 Also, a punishment system increase cooperation mostly in groups where all members have the same income [@Kingsley2016], because in heterogeneous groups a form of solidarity between low-status members arises and encourages free-riding [@Chen2022].
-Finally, a plain situation is needed to have a stronger effect of punishment: the link between behaviour and outcome must be clear, without random factors affecting the final outcome [@Xiao2016], and the punishment must be highly effective [@Egas2008].
+Finally, to have a stronger effect of punishment, the link between behaviour and outcome must be clear [@Xiao2016], and the punishment must be highly effective [@Egas2008].
 
@@
 Moreover, knowing that gossip is possible motivates people to cooperate more to avoid being the target of such gossip [@Feinberg2014].
-Gossip can also have the pro-social function of protecting others from a potential exploitation [@Feinberg2012], and providing correct information while gossiping helps to build a positive reputation [@Giardini2021].
+Gossip can also have the pro-social function of protecting others from a potential exploitation [@Feinberg2012].
+Finally, providing correct information while gossiping helps to build a positive reputation [@Giardini2021] and reduces negative affects on the gossip actor [@Feinberg2012].
 
@@
 
-Social norms shape cooperation because, according to the appropriateness framework, when taking a decision people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
+Social norms shape cooperation because, when taking a decision, people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
 If they define the situation as a cooperative task and strongly identify with the group, group's norms will be more accessible and they will have a stronger impact on behaviour [@VanLange2013].

### 2023-11-15 scoping_review_short.Rmd
15.11

@@
 
+During last years, the interest in alternative ways of social organization increased drastically because of the social and ecological crises we are facing [@Euler2018].
+Commons are one of these alternatives, since they are a way of organizing resources not involving the classic private and public model [@Ostrom1990], and, therefore, they represent an option to the capitalistic system [@Euler2019].
+For this reason, commons could be the needed change to attain a more sustainable and fair social organization [@Seravalli2018].
+
+Commons have been defined in different ways, starting by Elinor Ostrom who, in her seminal work, refers to them as a resource system shared between a self-managed community of users [@Ostrom1990].
+This community has a set of social practices, values and norms.
+Therefore, it is important to consider the commons not only as a resource, but as the integration of the resource, the community and its social protocols [@Bollier2014].
+For this reason, beyond the material aspect, the notion of social practices (i.e.
+commoning) is essential [@Euler2018].
+"Commoning" refers to the process through which people (i.e.
+the commoners) find solutions for their needs by self-organizing independently from the state or the market, and by creating autonomously managed institutions to govern the shared resource [@Euler2018; @Schmelzer2022].
+The community is therefore engaged in defining rules to successfully manage the commons [@Meroni2022].
+In conclusion, commons can be understood as "living social systems" who allow commoners to self-organize to address shared problems [@Bollier2019].
+
+These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look to the people who form it.
+More specifically, in order for a commons[^1] to be successful, its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998].
+Although its importance, cooperation can be difficult to achieve due to two characteristics of the commons' social dynamic.
+First, people can believe that their individual contribution will not have a big impact, and this feeling of personal inefficacy discourages cooperation [@VanVugt1998].
+Secondly, in a commons, every member faces a conflict between individual, short-term interests and collective, long-term ones [@Hardin1968].
+Act for the common good requires a personal sacrifice, and therefore the temptation to pursue the individual interest is constantly present.
+For these reasons, it is essential to understand how cooperation in commons can be improved, and which factors impact it.
+
+[^1]: The term "commons" is both singular and plural [@Bollier2014]. For the difference between the singular forms "common" and "commons", see @Feinberg2021.
+
+## Cooperating in commons
+
+In the existing literature, there are several explications of why people adopt or not cooperative behaviours in commons.
+For instance, the Rational Choice Theory predicts that people are too self-interested to cooperate in such contexts.
+As a consequence, they will inevitably destroy the shared resource, unless an external institution forces them to cooperate [@DeCaro2021; @Hardin1968].
+However, there are some less pessimistic theories that predict that people can transcend their personal interest and successfully cooperate in commons.
+An example is the Greed Efficiency Fairness hypothesis, which posits that the individuals' greed to pursue their narrow interests is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
+Similarly, according to the Humanistic Rational Choice Theory, the desire to maintain basic social-psychological needs motivates people to cooperate [@DeCaro2021].
+Finally, cooperating in commons can also be a self-presentation strategy [@VanVugt2010a], since showing altruistic behaviours has a positive effect on reputation [@Roberts1998].
+
+On a more practical level, @Ostrom1990 reported several cases of successful commons, where individuals managed to create a system to ensure cooperation.
+Based on her observations, she established eight design principles that distinguish successful from unsuccessful commons.
+First, commons need clearly defined boundaries to determine who has access to the shared resource, and the governing rules must take into account the local conditions.
+Moreover, people affected by these rules must be able to participate in modifying them.
+A monitoring and a graduated sanctions system must also be implemented, as well as low-cost conflict resolution arena.
+Finally, external authorities must not challenge the commons' members' right to self-organize[^2] [@Ostrom1990].
+
+[^2]: The last principle is valid only for commons that are part of a larger system, and is about nested enterprises: all the governance activities should be organized in multiple layers of nested enterprises.
+
+There are therefore several studies that focused on commons and on how they can be successful, but social psychological and quantitative perspectives are missing from this literature.
+In fact, to the authors' knowledge, there are few or no studies that investigated the causal effect of individual and group factors on people's willingness to cooperate in a real-life commons.
+
+At the same time, this approach is very popular in the laboratory study of social dilemmas, which allowed to identify several factors that shape cooperation [e.g.
+@VanLange2013].
+In this experiments, people face a conflict between personal and collective interest: each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
+At the same time, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
+Since many of the current global problems have a social dilemma structure, this topic has been extensively studied in different fields such as psychology, economy, biology, or mathematics [@VanLange2013].
+Thanks to their easy implementation in a laboratory, social dilemmas are very useful to gain insights into how cooperation works, because they provide a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
+
+## Current review
+
+Commons and social dilemmas are deeply linked.
+First, they share the same basic conflict between personal and collective interests [@Hardin1968; @Dawes1980].
+For this reason, commons can be considered as a particular case of social dilemma.
+In fact, @Kopelman2002 used the term of "commons dilemma" to define situations where a non cooperative behaviour can seriously endanger the future of the shared resource.
+Moreover, commons have been classified by @Cumming2018 as "take-some dilemmas", a specific kind of social dilemma where people are tempted to increase their personal benefit by taking more than their fair share from a shared resource.
+Moreover, cooperation and defection in social dilemma laboratory experiments can predict people's behaviour in a real-life commons [e.g.
+@Reindl2019].
+
+The aim of the current paper is to synthesize the existing researches about cooperation in social dilemmas, to provide a set of factors that could impact cooperative behaviours in commons.
+This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation in this context.
+Other studies already used a social dilemma framework to study real-life commons [e.g.
+@Hartl2022].
+While these studies usually focused on just one particular case, the current review is seeking to extend this approach by using social dilemma literature to gain a global understanding of cooperation in commons.
+
+This scoping review has two main goals.
+The first is to identify individual factors that can shape cooperation in commons.
+In fact, taking into account the specific community and commoners is essential to fully understand a commons' functioning [@Dove2019].
+Moreover, since it has been widely demonstrated that commoners can successfully self-organize to govern a commons [@Ostrom1990; @Larsson2016], the second goal is to understand which strategies groups can implement to encourage their members to cooperate.
+
+# Methods
+
+To conduct this scoping review, different scientific publications were analyzed in response to the research questions.
+To gather the papers, we performed a Boolean search methodology in Scopus, Web of Science and ScienceDirect.
+The main key phrases were "social dilemma", "public good", "common resource", and "commons", and each of them was paired with each one of the following: "cooperation", "conflicts", "reciprocity", and "trust".
+The research was made during the month of August, 2023.
+According to @Munn2022, the type of source was not a selection criterion, therefore journal articles, conference papers and book chapters could be included, to have an idea as complete as possible about the existing literature on the topic.
+Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision.
+There were however some selection criteria concerning the papers' methodology.
+First, only papers written in English were selected.
+Moreover, human participants were needed, so studies of social dilemmas through an agent-based model were excluded.
+Secondly, among experimental or correlative studies, only cases with adult participants were selected.
+
+Initially, 5210 papers emerged from the key phrases search.
+Deleting the duplicates reduced them to 4586.
+Based on titles and abstracts, 4333 articles were eliminated, leaving 253 texts to examine.
+After a full-text evaluation of the remaining papers, 89 were selected for the present review.
+Figure 1 resumes this selection process.
+
+## Papers' description
+
+The 89 included papers were published between 1984 and 2023, with a median of 2015.
+Almost all of the selected texts were journal articles, with the only exception being a book chapter.
+Most of them were experimental studies (*N*=60), followed by literature review and meta-analysis (*N*=14) and correlative studies[^3] (*N*=14).
+The remaining paper was a qualitative study.
+
+[^3]: Studies where at least one variable is manipulated by researchers are part of the category "experimental studies", while "correlative studies" refers to papers using quantitative analysis, but without manipulations.
+
+### Topic
+
+The papers' topic were in four categories: first, "lab-based social dilemma" (*N*=75) refers to highly controlled laboratory experiments where participants had to take cooperative decision.
+The second category is "real-life social dilemma" (*N*=7), and investigated cooperation in different real-life situations with a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
+Thirdly, papers in the category "lab-based commons" (*N*=3) used a laboratory social dilemma paradigm, but with clear references to a concrete common.
+For instance, in @Mosler1993, participants had to imagine to be fishermen who shared a common basin.
+Finally, "real-life commons" (*N*=4) refers to papers who studied cooperation with participants that were members of a commons in their everyday life.
+
+### Journal
+
+Most of the papers concerned psychology and economy.
+In fact, more than a half was published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin* (*N*=34), in economic journals like *Experimental Economics* (*N*=14), or in interdisciplinary ones such as *Journal of Economic Psychology* (*N*=8).
+
+### Country
+
+Finally, most of the studies were conducted in Europe (*N*=40) (especially in Germany (*N*=12) and in the Netherlands (*N*=8)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=7, of which *N*=6 in China).
+Moreover, six studies were set in more than one country, and fourteen were meta-analysis or literature reviews.
+The two remaining studies took place in Australia and in Colombia, respectively.
+
+A resume of the papers' description is provided in Table 1.
+
 # Individual factors
 
-Five individual factors that can impact cooperation emerged from the litterature review: gender, social status, group identification, values and personality traits, and trust.
-In the following sections, the principal effects of these factors on cooperation are described.
+Five individual factors that can impact cooperation emerged from the literature review: gender, social status, group identification, values and personality traits, and trust.
+In the following sections, their principal effects on cooperation are described.
 Moreover, an overview of the moderators of each effect is provided.
@@
 
-Lastly, gender differences are also linked to social status, with women representing the low-status group [@Sell2009].
-Therefore, gender differences in cooperation could also be partly explained by social status: to have a better understanding of this hypothesis, it is important to gain insights on how social status impact cooperation.
+Lastly, gender is also linked to social status, with women representing the low-status group [@Sell2009].
+Therefore, gender differences in cooperation could also be partly explained by social status: to have a better understanding of this hypothesis, it is important to gain insights on how social status impacts cooperation.
 
@@
 
-Cooperation can be modified by introducing incentives, who can be either punishments or rewards[^1].
-In the literature, punishment has received a greater attention than reward [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation has been widely demonstrated.
-In fact, when participants can punish other members for not contributing equally cooperation is higher than when this is not possible [e.g.
-@Balliet2011a; @Pfattheicher2018].
-Moreover, the presence of a punishment system increases the perception of fairness [@Nockur2021].
-
-[^1]: Since the interest of the present review is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included.
-Incentives given by third party have also an effect on cooperation, but they are not included in this review.
+Cooperation can be modified by introducing incentive systems, that can be either punishments or rewards.
+In the literature, punishment has received a greater attention [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation has been widely demonstrated.
+In fact, when participants can punish other members for not contributing equally, cooperation and the perceived fairness are higher [@Pfattheicher2018; @Nockur2021].
 
@@
 At the same time, punishment must be applied with carefulness.
-For instance, the most successful groups are those who punish with caution and not in early stages of the interaction, and who have a norm of when and how punishment should be applied [@Rockenbach2019].
-Moreover, punishment has also two negative sides.
-First, it could entails a second-order social dilemma, since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators [@Milinski2012].
-Secondly, when all participants can punish independently of their contributions, anti-social punishment (i.e.
-the punishment of cooperators by non-cooperators) can arise [@Xiao2016].
-A solution could be to implement a system of democratic punishment, where a fine is given only if a majority of participants agree.
-In fact, with this kind of system the punishment level is lower, while final payoff and cooperation rates are higher [@Pfattheicher2018].
+Ideally, groups should not punish in early stages of the interaction, and have a norm of when and how punishment must be applied [@Rockenbach2019].
+Moreover, punishment could entails a second-order social dilemma, since cooperators are better-off by non punishing, if all others do [@Milinski2012].
+Also, if there are no rules on who can punish, non-cooperators can punish cooperators as a form of retaliation [@Xiao2016; @VanDijk2015].
+A democratic punishment system, where a fine is given only if a majority agree, could solve these problems [@Pfattheicher2018].
 
 On the other side, rewarding systems are less investigated.
-Generally, they have a positive effect on cooperation [@Balliet2011a], but it is not clear whether they are more efficient than punishment [as found by @Chen2022], less efficient [see @Milinski2012] or equivalent [see @Balliet2011a].
-Similarly to punishments, rewards have a stronger effect if their implementation is costly and during iterated, rather than single, interactions [@Balliet2011a].
+Generally, they have a positive effect on cooperation [@Balliet2011a], but it is not clear whether they are more efficient than punishment [see @Chen2022], less efficient [see @Milinski2012] or equivalent [see @Balliet2011a].
+Rewards have a stronger effect if their implementation is costly and during iterated, rather than single, interactions [@Balliet2011a].
 
-To conclude, incentives can enhance cooperation, but they have some negative sides.
-First, they reduce participants' intrinsic motivation to cooperate [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
-Secondly, incentives undermine participants' trust in other members' internal motivation to cooperate.
+In general, even if they enhance cooperation, incentives have negative sides: they reduce participants' intrinsic motivation to cooperate [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+They also undermine participants' trust in other members' internal motivation to cooperate.
 Therefore, if they are removed, cooperation drops [@Irwin2014; @Mulder2006].
@@
 
+The aim of the present paper was to synthesize the existing literature about cooperation in social dilemmas, to identify factors that could impact cooperative behaviours in commons.
+Through a scoping review approach, we identified nine factors, both at the individual and group level.
+Our results seem to be in line with others findings about cooperation in commons.
+For instance, factors such as gender, social status, SVO, incentives, and communication were also found by @Kopelman2002 in their review about lab-based commons, and their effects were the same as the ones reported in the current paper.
+
+Moreover, some of the factors can be related to Ostrom's principles to successfully manage a common resource [@Ostrom1990].
+For instance, the clearly defined boundaries can strengthen commoners' social identification, since only when an in- and an out-group exist social identity is salient and therefore an identification is possible [@Tajfel1974].
+Even if Ostrom developed this principle on a more organizational level, its secondary effect of creating a social identity can also contribute to improve cooperation.
+Secondly, communication is essential for the commoners to shape social norms [@Bicchieri2002] and to resolve conflicts.
+Finally, the principles about the monitoring and the graduated sanction systems underline the importance of incentives.
+The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they worry about others' approval [@Nelissen2013; @Rege2004].
+On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^4]
+
+[^4]: Principles 2, 7 and 8 refer to elements that are not pertinent to the current review, and therefore do not match any of the factors identified.
+
+Ostrom's principles are especially related to factors at the organizational level.
+This is understandable when considering her economic approach to the study of the commons.
+However, taking into account the social dynamics and the characteristics of the commoners is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
+For this reason, this paper made a step further and identified some individual characteristics affecting the efficiency of commons.
+Although less studied in commons literature, these individual factors are consistent with existing theories.
+
+First, the reported positive effects of trust on cooperation can be explained through the principle of reciprocity, that posits that individuals cooperate more facing cooperative partners [@Fehr2002; @VanLange1999].
+Since in real-life situations it is not always possible to know exactly others' contributions, trust (i.e.
+beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012].
+Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can be successful.
+
+Secondly, the influence of SVO on cooperation is explained by the difference between pro-social and pro-self in the importance accorded to the relative benefits.
+More specifically, pro-social value more others' outcome and equality in outcomes than pro-self [@VanLange1999].
+Moreover, the difference in weights accorded to the personal and others' outcome seem to be the only dissimilarity between pro-social and pro-self, because they process the cooperative interaction in the same way [@Fiedler2013].
+
+The reviewed results did not provide a clear conclusion about gender effect on cooperation.
+However, existing theories would predict that women cooperate more than men, because, according to gender stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012].
+In fact, while managing a natural resource, groups partly composed by women display more solidarity and collaboration than all-men groups [@Westermann2005].
+However, every experimental paradigm can trigger the participants' gender identity differently [@Sell2009], and for this reason this effect is subjected to several moderators.
+
+Concerning social status, the analyzed studies showed that usually members of low-status groups cooperated more and showed more solidarity with others low-status members than high-status.
+Although this effect has not been extensively studied, these results seem to be consistent with the existing literature on social status.
+First, there are structural differences between high- and low-status group's dynamic, and this makes high-status members more individualistic than low-status [@Lorenzi-Cioldi2002].
+High-status individuals also display more system justification and more Social Dominance Orientation than low-status [@Caricati2012; @Vargas-Salfate2018]: they see the social system as fair and they have a preference for inequality between social groups.
+This is negatively correlated with concern about others and altruism [@Pratto1994].
+
+The last individual factor was group identification, and the reviewed results showed that the more individuals identify with their group, the more they are likely to act for the group's good.
+In fact, according to the Social Identity Theory, people's identity is also composed by their group affiliations, and the stronger they identify with a social group, the more important this group becomes for their identity and the more their personal interests aligns with group's ones [@Tajfel1974].
+Also, within a social group, individuals perceive themselves as more similar to other members, and therefore they are more susceptible to adopt collective goals and behaviours [@Turner1984; @Fritsche2018].
+Moreover, strongly identified people are less likely to leave a group in case of failure or difficulties [@Ellemers1997].
+Thus, a strong identification is essential for a group's success.
+In-group identification is also essential to engage in collective actions [@VanZomeren2008], and it is the main predictor of pro-environmental actions in the Social Identity Model of Pro-Environmental Action [SIMPEA, @Fritsche2018].
+
+## Factors' interactions
+
+Until now, the identified factors has been discussed separately. However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.
+
+For instance, there are gender differences in trust and SVO: trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019], and women are more prevalent between pro-social and less between pro-self [@VanLange1999].
+Moreover, SVO and trust are linked [@Ackermann2019], and the expectancy about others' cooperation can even be seen as a part of the construct of SVO [@Bogaert2008].
+Therefore, pro-self individuals show less cooperation in part because they expect others not to cooperate.
+
+Trust also depends on social status: high-status individuals display more generalized trust (i.e.
+general beliefs on others' benevolence), while low-status more depersonalized trust (i.e.
+more trust in other members of their in-group, just because of their membership) [@Navarro-Carrillo2018].
+Since high-status individuals perceive the system as fair [@Caricati2012], it is easier for them to believe in others' benevolent intentions.
+Conversely, belonging to the group is more important for low-status than for high-status [@Lorenzi-Cioldi2002], therefore they see other group members as more trustworthy, even without knowing them personally.
+
+\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ OK \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
+
+Secondly, communication impacts several other factors.
+For instance, it plays an essential role in shaping social norms [@Hogg2006; @Bicchieri2002] and it can improve cooperation by signalling a person's intentions and trustworthiness [@Janssen2015].
+Moreover, in a study about organizations, communication was a strong predictor of commitment, that is a component of group identification.
+This link was especially present for vertical communication, i.e.
+exchanges about organizational strategies between members at different level of the hierarchy [@Postmes2001].
+Therefore, having the opportunity to communicate about the strategies that need to be implemented improve one's identification with the group.
+
+Another factor that influences others is group identification.
+First, as a consequence of the Social Identity Theory, people who strongly identify with their group are more willing to comply to the group's norms and to pursuit the group's goals [@Tajfel1974].
+Therefore, high-identified members need less cooperation-enhancing measures.
+For instance, incentives are more useful to improve cooperation of low-, rather than high-identified, group members [@VanVugt2009], because high-identified members are already motivated to cooperate.
+Similarly, given their stronger willingness to act for the group's good, high-identified individuals cooperate even in an anonymous condition, while low-identified acted more for the group goal if their actions were accountable [@Barreto2000].
+
+As already mentioned in the results section, anonymity underlies several other factors.
+First, when actions are accountable, people are more concerned about others' approval and therefore show more conformity to social norms [@Nelissen2013; @Rege2004].
+Also, in large groups [where, as a consequence of the group size, levels of anonymity are higher, @Romano2016] it is more difficult to evaluate the trustworthiness of other participants than in small ones [@Janssen2015].
+
+Finally, economic incentives can have a negative impact on people's internal motivation to cooperate, because they change the perception of the context from ethical to economic [@Janssen2015; @VanVugt2009].
+Therefore, even if incentives such as punishments or rewards can be useful to improve cooperation, they reduce the impact of the other factors.
+For instance, when incentives are present, people think that others cooperate because of them, and this leads to reduced levels of trust [@Irwin2014].
+
+incentives =\> social rewards work better when identifying in the group that can dis-/approve the behaviour @Kopelman2002
+
+##
+
+-   theoretical implications?
+
+Moreover, the analyzed papers showed that people often cooperate.
+This contradicts the Rational Choice Theory (RCT), who posits that individuals are too self interested to sacrifice their personal benefit to the greater good, unless if forced to do so.
+Our results are consistent with the existing literature, since RCT has already been refuted by experimental studies, who demonstrated that cooperation was higher than predicted in social dilemmas, and that it was impacted by variables that should not play a role according to RCT [@Ostrom1998].
+
+This review also confirmed the lack of quantitative studies about cooperation in real-life commons: of the 89 analyzed papers, just three had these characteristics, and they all were correlative.
+Therefore, they could not draw a causal link between the investigated factors and cooperative behaviours.
+
+=\> say that this is a confirmation of a gaps in the literature that should be filled with future researches
+
+-   practical implications: This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation in this context =\> rephrase!
+
+-   In summary, this review has practical implications and can be used as a guide for commons members to design campaigns or activities to improve cooperation.
+In fact, some of the identified factors can be manipulated in order to create better conditions for cooperation to arise.
+Moreover, since the different elements are linked, they can impact cooperation both directly and indirectly, via mediation and moderation effects.
+Based on the consensus of the results and on the quantity of connections with other elements, the factors that seem to have a stronger effect are trust, communication, group identification and accountability of actions.
+Therefore, interventions based on this elements can be very powerful tools to improve cooperation in commons.
+On the other hand, some individual factor cannot be manipulated, but must be taken into account when designing an intervention.
+For instance, commons' composition in terms of gender and social status can have a large influence on the overall cooperation.
+
+# Limitations, future perspectives and conclusion
+
+To conclude, this review summarized existing researches about cooperation in social dilemmas, and therefore provided a set of factors that can help better understanding cooperative behaviours in commons.
+Moreover, it also highlighted a lack of quantitative studies of this topic in real-life commons.
+However, this scoping review has also several limitations.
+
+First, there is a lack of representation of the global population.
+In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Global North.
+The current results apply therefore to Western societies and should not be generalized to Global South.
+In fact, there are cultural differences in individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989].
+These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g.
+@Kuwabara2014].
+It is therefore likely that cooperation relies on different mechanisms in Global South and North: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.
+
+Moreover, although the aim was to use results of social dilemma researches to gain a better understanding of commons, most of the included studies had a laboratory setting.
+Such a simplification of real-life situations do not allow to exactly reproduce the dynamics present in a commons [@Henry2011; @Cole2010].
+In fact, some elements such as cultural factors and specific ecological conditions affecting the decision making process cannot be reproduced in lab experiments [@Janssen2015].
+Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings.
+Moreover, this review is not informative about the relative importance of each factor.
+To shed light on this topic, quantitative studies are needed.
+
+Finally, the papers included in this review did not provide a longitudinal perspective on the study of cooperation, leaving therefore some open questions: which factors are more important in the early or in the late stages of cooperation?
+How the different factors evolve and influence each-others over time?
+To answer these questions, longitudinal investigations are needed.
+
+In conclusion, a successful commons relies on the cooperation of its members, but this topic has not yet been extensively studied.
+Thus, further researches are needed to address the limitations of the current study and to reach a deeper understanding of this topic.
+
 \newpage

### 2023-11-16 scoping_review_short.Rmd
2nd version for feedbacks - 16.11

@@
 abstract: |
-  Commons represent an alternative social organization outside the classical capitalist model, therefore they could be the needed change toward more sustainable societies and economy.
-However, in order for a common to be successful, its members must cooperate, i.e.
+  Commons represent an alternative to the classical capitalist model, therefore they could be the needed change toward a more sustainable society and economy.
+However, in order for a commons to be successful, its members must cooperate, i.e.
 incur a personal sacrifice for the collective good.
-Despite the importance of cooperation, there is a lack of studies that investigated this topic in commons context.
+Despite the importance of cooperation, there is a lack of studies that investigated this topic in real-life commons.
 On the other hand, cooperation has been extensively studied in social dilemma experiments, where personal and collective interests are at odds.
 Since the two contexts share some structural characteristics, the results of social dilemma experiments could be used to gain insights on cooperation in commons.
-  The goal of the current scoping review is to identify the factors that impact cooperation in social dilemma situations, to gain a better understanding of what could shape cooperation in commons.
-A key-word search and a subsequent selection lead to the inclusion of 89 papers, who are used to identify 9 factors that can influence cooperation both at the individual and group level: *gender, social status, group identification, values and personality traits, trust, incentives, communication, social norms and anonymity*.
+  The goal of the current scoping review is to identify the factors that impact cooperation in social dilemma situations, in order to better understand what could shape cooperation in commons.
+A key-word search and a subsequent selection lead to the inclusion of 89 papers, who are used to identify 9 factors that can influence cooperation both at the individual and group level: gender, social status, group identification, values and personality traits, trust, incentives, communication, social norms and anonymity.
 These factors are discussed within the existing literature on commons and cooperation.
-*More specifically, the influences that these elements can have on each-other are highlighted, showing that the totality of factors should be taken into account when investigating cooperation in commons.* Finally, the practical implication of this work for commons' organization, as well as the review's limitations, are pointed out.
+More specifically, the influences that these elements can have on each-other are highlighted, showing that the totality of factors should be taken into account when investigating cooperation in commons.
+Finally, the practical implication of this work for commons' organization, as well as the review's limitations, are pointed out.
 
@@
 Cooperation can be modified by introducing incentive systems, that can be either punishments or rewards.
-In the literature, punishment has received a greater attention [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation has been widely demonstrated.
-In fact, when participants can punish other members for not contributing equally, cooperation and the perceived fairness are higher [@Pfattheicher2018; @Nockur2021].
+Both have a positive effect on cooperation [@Balliet2011a; ].
+However, there are contradictory results about which system is more efficient [see @Chen2022; @Milinski2012].
 
 Several factors moderate this main effect.
-Punishments are more effective if their implementation is (moderately) costly rather than free [@Balliet2011a; @Egas2008], if the members are friends rather than strangers, if they know that they will interact repeatedly [@Balliet2011a], and if only cooperators have the power to punish defectors [@Xiao2016].
-Also, a punishment system increase cooperation mostly in groups where all members have the same income [@Kingsley2016], because in heterogeneous groups a form of solidarity between low-status members arises and encourages free-riding [@Chen2022].
-Finally, to have a stronger effect of punishment, the link between behaviour and outcome must be clear [@Xiao2016], and the punishment must be highly effective [@Egas2008].
+A meta-analysis found that both rewards and punishments are more effective if their implementation is costly rather than free, and during iterated, rather than single, interactions [@Balliet2011a].
+Moreover, punishments work better in groups where all members have the same income [@Kingsley2016], because in heterogeneous groups a form of solidarity between low-status members arises and encourages free-riding [@Chen2022].
+Punishments are also more effective if participants are friends [@Balliet2011a] and when only cooperators have the power to punish defectors [@Xiao2016].
+Finally, the link between behaviour and outcome must be clear [@Xiao2016], and the punishment must have a significant consequence [@Egas2008].
 
-At the same time, punishment must be applied with carefulness.
-Ideally, groups should not punish in early stages of the interaction, and have a norm of when and how punishment must be applied [@Rockenbach2019].
+In general, there are more studies about punishments than about rewards [@VanDijk2015].
+When a punishment system is present, participants' perceived fairness is higher [@Nockur2021].
+However, punishments must be applied with carefulness.
+Ideally, groups should not punish in early stages of the interaction, and have a norm of when and how punish [@Rockenbach2019].
 Moreover, punishment could entails a second-order social dilemma, since cooperators are better-off by non punishing, if all others do [@Milinski2012].
@@
 
-On the other side, rewarding systems are less investigated.
-Generally, they have a positive effect on cooperation [@Balliet2011a], but it is not clear whether they are more efficient than punishment [see @Chen2022], less efficient [see @Milinski2012] or equivalent [see @Balliet2011a].
-Rewards have a stronger effect if their implementation is costly and during iterated, rather than single, interactions [@Balliet2011a].
-
-In general, even if they enhance cooperation, incentives have negative sides: they reduce participants' intrinsic motivation to cooperate [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+Even if they enhance cooperation, incentives have negative sides: they reduce participants' intrinsic motivation [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
 They also undermine participants' trust in other members' internal motivation to cooperate.
@@
 
-The aim of the present paper was to synthesize the existing literature about cooperation in social dilemmas, to identify factors that could impact cooperative behaviours in commons.
+The aim of the present paper was to synthesize the existing literature about cooperation in social dilemmas, in order to identify factors that could impact cooperative behaviours in commons.
 Through a scoping review approach, we identified nine factors, both at the individual and group level.
@@
 Even if Ostrom developed this principle on a more organizational level, its secondary effect of creating a social identity can also contribute to improve cooperation.
-Secondly, communication is essential for the commoners to shape social norms [@Bicchieri2002] and to resolve conflicts.
-Finally, the principles about the monitoring and the graduated sanction systems underline the importance of incentives.
+Secondly, communication is essential for the principle about the creation and modification of norms [@Bicchieri2002], and for the one about the arenas to solve conflicts.
+Finally, the principles concerning the monitoring and the graduated sanction systems underline the importance of incentives.
 The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they worry about others' approval [@Nelissen2013; @Rege2004].
@@
 However, taking into account the social dynamics and the characteristics of the commoners is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
-For this reason, this paper made a step further and identified some individual characteristics affecting the efficiency of commons.
+For this reason, this paper went a step further and identified five individual characteristics affecting the efficiency of commons.
 Although less studied in commons literature, these individual factors are consistent with existing theories.
 
-First, the reported positive effects of trust on cooperation can be explained through the principle of reciprocity, that posits that individuals cooperate more facing cooperative partners [@Fehr2002; @VanLange1999].
-Since in real-life situations it is not always possible to know exactly others' contributions, trust (i.e.
+First, the reported positive effects of trust on cooperation is explained through the principle of reciprocity, that posits that individuals cooperate more facing cooperative partners [@Fehr2002; @VanLange1999].
+Since in real-life situations it is not always possible to know exactly others' willingness to contribute, trust (i.e.
 beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012].
@@
 
-Secondly, the influence of SVO on cooperation is explained by the difference between pro-social and pro-self in the importance accorded to the relative benefits.
+Secondly, the influence of SVO on cooperation is due to the difference between pro-social and pro-self in the importance accorded to the relative benefits.
 More specifically, pro-social value more others' outcome and equality in outcomes than pro-self [@VanLange1999].
@@
 However, existing theories would predict that women cooperate more than men, because, according to gender stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012].
-In fact, while managing a natural resource, groups partly composed by women display more solidarity and collaboration than all-men groups [@Westermann2005].
+In fact, groups partly composed by women display more solidarity and collaboration than all-men groups [@Westermann2005].
 However, every experimental paradigm can trigger the participants' gender identity differently [@Sell2009], and for this reason this effect is subjected to several moderators.
@@
 Although this effect has not been extensively studied, these results seem to be consistent with the existing literature on social status.
-First, there are structural differences between high- and low-status group's dynamic, and this makes high-status members more individualistic than low-status [@Lorenzi-Cioldi2002].
+First, there are structural differences between high- and low-status group's dynamic, that make high-status members more individualistic than low-status [@Lorenzi-Cioldi2002].
 High-status individuals also display more system justification and more Social Dominance Orientation than low-status [@Caricati2012; @Vargas-Salfate2018]: they see the social system as fair and they have a preference for inequality between social groups.
@@
 
-Until now, the identified factors has been discussed separately. However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.
-
+Until now, the identified factors has been discussed separately.
+However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.
 For instance, there are gender differences in trust and SVO: trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019], and women are more prevalent between pro-social and less between pro-self [@VanLange1999].
@@
 Since high-status individuals perceive the system as fair [@Caricati2012], it is easier for them to believe in others' benevolent intentions.
-Conversely, belonging to the group is more important for low-status than for high-status [@Lorenzi-Cioldi2002], therefore they see other group members as more trustworthy, even without knowing them personally.
-
-\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ OK \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
+Conversely, belonging to the group is more important for low-status than for high-status [@Lorenzi-Cioldi2002], therefore they see other group's members as more trustworthy, even without knowing them personally.
 
 Secondly, communication impacts several other factors.
-For instance, it plays an essential role in shaping social norms [@Hogg2006; @Bicchieri2002] and it can improve cooperation by signalling a person's intentions and trustworthiness [@Janssen2015].
-Moreover, in a study about organizations, communication was a strong predictor of commitment, that is a component of group identification.
-This link was especially present for vertical communication, i.e.
-exchanges about organizational strategies between members at different level of the hierarchy [@Postmes2001].
-Therefore, having the opportunity to communicate about the strategies that need to be implemented improve one's identification with the group.
+For instance, it plays an essential role in shaping social norms [@Bicchieri2002] and it can improve cooperation by signalling a person's intentions and trustworthiness [@Janssen2015].
+Moreover, the opportunity to exchange about the strategies that need to be implemented improve people's commitment within a group, that is a component of group identification [@Postmes2001].
+At the same time, group identification also moderates other effects.
+First, as a consequence of the Social Identity Theory, high-identified individuals are more willing to comply to the group's norms and to pursue the group's goal [@Tajfel1974].
+Therefore, they need less cooperation-enhancing measures such as incentives [@VanVugt2009] or non-anonymous conditions [@Barreto2000].
+Moreover, social rewards work better with people who strongly identify with the group that can approve their behaviour [@Kopelman2002].
 
-Another factor that influences others is group identification.
-First, as a consequence of the Social Identity Theory, people who strongly identify with their group are more willing to comply to the group's norms and to pursuit the group's goals [@Tajfel1974].
-Therefore, high-identified members need less cooperation-enhancing measures.
-For instance, incentives are more useful to improve cooperation of low-, rather than high-identified, group members [@VanVugt2009], because high-identified members are already motivated to cooperate.
-Similarly, given their stronger willingness to act for the group's good, high-identified individuals cooperate even in an anonymous condition, while low-identified acted more for the group goal if their actions were accountable [@Barreto2000].
+Finally, as mentioned in the results, anonymity underlies several other factors.
+First, people comply more to social norms when actions are accountable, because their concern about others' approval [@Nelissen2013; @Rege2004].
+Also, in large groups [i.e.
+in more anonymous situations, @Romano2016] it is more difficult to asses the trustworthiness of other participants than in small ones [@Janssen2015].
 
-As already mentioned in the results section, anonymity underlies several other factors.
-First, when actions are accountable, people are more concerned about others' approval and therefore show more conformity to social norms [@Nelissen2013; @Rege2004].
-Also, in large groups [where, as a consequence of the group size, levels of anonymity are higher, @Romano2016] it is more difficult to evaluate the trustworthiness of other participants than in small ones [@Janssen2015].
+## Theoretical implications
 
-Finally, economic incentives can have a negative impact on people's internal motivation to cooperate, because they change the perception of the context from ethical to economic [@Janssen2015; @VanVugt2009].
-Therefore, even if incentives such as punishments or rewards can be useful to improve cooperation, they reduce the impact of the other factors.
-For instance, when incentives are present, people think that others cooperate because of them, and this leads to reduced levels of trust [@Irwin2014].
+The analyzed papers showed that people often cooperate.
+This contradicts the Rational Choice Theory (RCT), who posits that individuals are too self interested to sacrifice their personal benefit to the greater good, unless if forced to do so.
+Our general results are therefore consistent with the existing literature, since RCT has already been refuted by experimental studies, who demonstrated that cooperation was higher than predicted in social dilemmas, and that it was impacted by variables that should not play a role according to this theory [@Ostrom1998].
 
-incentives =\> social rewards work better when identifying in the group that can dis-/approve the behaviour @Kopelman2002
+Moreover, this review also corroborated the lack of quantitative studies about cooperation in real-life commons: of the 89 analyzed papers, just three had these characteristics, and they all were correlative.
+Therefore, they could not draw a causal link between the investigated factors and cooperative behaviours.
+This confirms a gap in the literature, that could be filled by futures experimental studies about cooperation in commons.
+Moreover, this review laid the foundations to implement such experiment in real-life commons, by providing a set of factors that could be tested.
 
-##
+## Practical implications
 
--   theoretical implications?
-
-Moreover, the analyzed papers showed that people often cooperate.
-This contradicts the Rational Choice Theory (RCT), who posits that individuals are too self interested to sacrifice their personal benefit to the greater good, unless if forced to do so.
-Our results are consistent with the existing literature, since RCT has already been refuted by experimental studies, who demonstrated that cooperation was higher than predicted in social dilemmas, and that it was impacted by variables that should not play a role according to RCT [@Ostrom1998].
-
-This review also confirmed the lack of quantitative studies about cooperation in real-life commons: of the 89 analyzed papers, just three had these characteristics, and they all were correlative.
-Therefore, they could not draw a causal link between the investigated factors and cooperative behaviours.
-
-=\> say that this is a confirmation of a gaps in the literature that should be filled with future researches
-
--   practical implications: This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation in this context =\> rephrase!
-
--   In summary, this review has practical implications and can be used as a guide for commons members to design campaigns or activities to improve cooperation.
+This review can be used as a guide for commons members to design campaigns or activities to improve cooperation.
 In fact, some of the identified factors can be manipulated in order to create better conditions for cooperation to arise.
-Moreover, since the different elements are linked, they can impact cooperation both directly and indirectly, via mediation and moderation effects.
-Based on the consensus of the results and on the quantity of connections with other elements, the factors that seem to have a stronger effect are trust, communication, group identification and accountability of actions.
+Moreover, since the different elements are linked, they can impact cooperation both directly and indirectly, via mediation or moderation effects.
+Based on the quantity of connections with other elements, the factors that seem to have a stronger effect are trust, communication, group identification and accountability of actions.
 Therefore, interventions based on this elements can be very powerful tools to improve cooperation in commons.
@@
 
-# Limitations, future perspectives and conclusion
+# Limitations and future perspectives
 
 To conclude, this review summarized existing researches about cooperation in social dilemmas, and therefore provided a set of factors that can help better understanding cooperative behaviours in commons.
-Moreover, it also highlighted a lack of quantitative studies of this topic in real-life commons.
-However, this scoping review has also several limitations.
+It also highlighted a lack of quantitative studies about this topic in real-life commons.
+It is, however, not without limitations.
 
@@
 
-Moreover, although the aim was to use results of social dilemma researches to gain a better understanding of commons, most of the included studies had a laboratory setting.
-Such a simplification of real-life situations do not allow to exactly reproduce the dynamics present in a commons [@Henry2011; @Cole2010].
-In fact, some elements such as cultural factors and specific ecological conditions affecting the decision making process cannot be reproduced in lab experiments [@Janssen2015].
+Moreover, our aim was to use results of social dilemma researches to gain a better understanding of commons, therefore most of the included studies had a laboratory setting.
+In fact, this kind of setting is very useful to study social dilemmas because it provides a standard paradigm [@Balliet2011].
+However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and specific ecological conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015].
 Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings.
@@
 In conclusion, a successful commons relies on the cooperation of its members, but this topic has not yet been extensively studied.
-Thus, further researches are needed to address the limitations of the current study and to reach a deeper understanding of this topic.
+Thus, further researches are needed to address the limitations of the current review and to reach a deeper understanding of this topic.
 

### 2023-12-12 scoping_review_short.Rmd
12.12: integration on Vincent's and Lilla's basic feedbacks

@@
 ---
-title             : "Improving the understanding of cooperation in commons through social dilemmas' literature: A scoping review"
-shorttitle        : "Improving the understanding of cooperation in commons"
+title             : "Understanding cooperation in commons through social dilemmas' literature: a scoping review"
+shorttitle        : "Understanding cooperation in commons"
 
@@
   Commons represent an alternative to the classical capitalist model, therefore they could be the needed change toward a more sustainable society and economy.
-However, in order for a commons to be successful, its members must cooperate, i.e.
+However, for a commons to be successful, its members must cooperate, i.e.
 incur a personal sacrifice for the collective good.
-Despite the importance of cooperation, there is a lack of studies that investigated this topic in real-life commons.
+Despite the importance of cooperation, there is a lack of studies that investigated this topic in the scientific field of the commons.
 On the other hand, cooperation has been extensively studied in social dilemma experiments, where personal and collective interests are at odds.
-Since the two contexts share some structural characteristics, the results of social dilemma experiments could be used to gain insights on cooperation in commons.
+Since social dilemma experiments and commons share some structural characteristics, we could gain insights into cooperation in commons and how to implement it thanks to the social dilemmas literature.
   The goal of the current scoping review is to identify the factors that impact cooperation in social dilemma situations, in order to better understand what could shape cooperation in commons.
-A key-word search and a subsequent selection lead to the inclusion of 89 papers, who are used to identify 9 factors that can influence cooperation both at the individual and group level: gender, social status, group identification, values and personality traits, trust, incentives, communication, social norms and anonymity.
+A key-word search and a subsequent selection led to the inclusion of 89 papers, which were used to identify 9 factors that can influence cooperation both at the individual and group level: gender, social status, group identification, values and personality traits, trust, incentives, communication, social norms and anonymity.
 These factors are discussed within the existing literature on commons and cooperation.
-More specifically, the influences that these elements can have on each-other are highlighted, showing that the totality of factors should be taken into account when investigating cooperation in commons.
+More specifically, the influences that these elements can have on each-other are highlighted, showing that all factors should be taken into account when investigating cooperation in commons.
 Finally, the practical implication of this work for commons' organization, as well as the review's limitations, are pointed out.
@@
 
-During last years, the interest in alternative ways of social organization increased drastically because of the social and ecological crises we are facing [@Euler2018].
-Commons are one of these alternatives, since they are a way of organizing resources not involving the classic private and public model [@Ostrom1990], and, therefore, they represent an option to the capitalistic system [@Euler2019].
-For this reason, commons could be the needed change to attain a more sustainable and fair social organization [@Seravalli2018].
+In recent years, the interest in alternative ways of social organization increased drastically due to the social and ecological crises we are facing [@Euler2018].
+Commons are one of these alternatives, since they are a way of organizing resources beyond the classic private and public model [@Ostrom1990], and, therefore, they represent an option to the capitalistic system [@Euler2019].
+For this reason, commons could be an integral part of the path to attain a more sustainable and fair social organization [@Schmelzer2022].
 
 Commons have been defined in different ways, starting by Elinor Ostrom who, in her seminal work, refers to them as a resource system shared between a self-managed community of users [@Ostrom1990].
-This community has a set of social practices, values and norms.
+This community shares a set of social practices, values and norms.
 Therefore, it is important to consider the commons not only as a resource, but as the integration of the resource, the community and its social protocols [@Bollier2014].
@@
 The community is therefore engaged in defining rules to successfully manage the commons [@Meroni2022].
-In conclusion, commons can be understood as "living social systems" who allow commoners to self-organize to address shared problems [@Bollier2019].
+In conclusion, commons can be understood as "living social systems" that allow commoners to self-organize to address shared problems [@Bollier2019].
 
-These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look to the people who form it.
+These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look at the people who form it.
 More specifically, in order for a commons[^1] to be successful, its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998].
-Although its importance, cooperation can be difficult to achieve due to two characteristics of the commons' social dynamic.
+Although it is essential, cooperation can be difficult to achieve due to two characteristics of the commons' social dynamic.
 First, people can believe that their individual contribution will not have a big impact, and this feeling of personal inefficacy discourages cooperation [@VanVugt1998].
@@
 Act for the common good requires a personal sacrifice, and therefore the temptation to pursue the individual interest is constantly present.
-For these reasons, it is essential to understand how cooperation in commons can be improved, and which factors impact it.
+For these reasons, we need to understand the factors that affect cooperation, and how we can improve it.
 
@@
 There are therefore several studies that focused on commons and on how they can be successful, but social psychological and quantitative perspectives are missing from this literature.
-In fact, to the authors' knowledge, there are few or no studies that investigated the causal effect of individual and group factors on people's willingness to cooperate in a real-life commons.
+In fact, to the authors' knowledge, there are few studies that investigated the causal effect of individual and group factors on people's willingness to cooperate in a real-life commons [e.g.
+@Noonan2016].
 
-At the same time, this approach is very popular in the laboratory study of social dilemmas, which allowed to identify several factors that shape cooperation [e.g.
+At the same time, an experimental approach is very popular in the laboratory study of social dilemmas, which identified several factors that shape cooperation [e.g.
 @VanLange2013].
-In this experiments, people face a conflict between personal and collective interest: each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
+In these experiments, people face a conflict between personal and collective interest: each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
 At the same time, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
 Since many of the current global problems have a social dilemma structure, this topic has been extensively studied in different fields such as psychology, economy, biology, or mathematics [@VanLange2013].
-Thanks to their easy implementation in a laboratory, social dilemmas are very useful to gain insights into how cooperation works, because they provide a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
+Social dilemmas are very useful to gain insights into how cooperation works, because they can easily be implemented in a laboratory setting, and they provide a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
 
@@
 For this reason, commons can be considered as a particular case of social dilemma.
-In fact, @Kopelman2002 used the term of "commons dilemma" to define situations where a non cooperative behaviour can seriously endanger the future of the shared resource.
+In fact, @Kopelman2002 used the term of "commons dilemma" to define situations where a non-cooperative behaviour can seriously endanger the future of the shared resource.
 Moreover, commons have been classified by @Cumming2018 as "take-some dilemmas", a specific kind of social dilemma where people are tempted to increase their personal benefit by taking more than their fair share from a shared resource.
@@
 
-The aim of the current paper is to synthesize the existing researches about cooperation in social dilemmas, to provide a set of factors that could impact cooperative behaviours in commons.
-This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation in this context.
+The current paper synthesizes existing research about cooperation in social dilemmas, to provide a set of factors that impact cooperative behaviours in commons.
+This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation beyond artificial laboratory settings.
 Other studies already used a social dilemma framework to study real-life commons [e.g.
@@
 This scoping review has two main goals.
-The first is to identify individual factors that can shape cooperation in commons.
-In fact, taking into account the specific community and commoners is essential to fully understand a commons' functioning [@Dove2019].
+The first is to identify factors on the individual level that can shape cooperation in commons.
 Moreover, since it has been widely demonstrated that commoners can successfully self-organize to govern a commons [@Ostrom1990; @Larsson2016], the second goal is to understand which strategies groups can implement to encourage their members to cooperate.
@@
 
-To conduct this scoping review, different scientific publications were analyzed in response to the research questions.
-To gather the papers, we performed a Boolean search methodology in Scopus, Web of Science and ScienceDirect.
-The main key phrases were "social dilemma", "public good", "common resource", and "commons", and each of them was paired with each one of the following: "cooperation", "conflicts", "reciprocity", and "trust".
-The research was made during the month of August, 2023.
-According to @Munn2022, the type of source was not a selection criterion, therefore journal articles, conference papers and book chapters could be included, to have an idea as complete as possible about the existing literature on the topic.
-Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision.
-There were however some selection criteria concerning the papers' methodology.
-First, only papers written in English were selected.
-Moreover, human participants were needed, so studies of social dilemmas through an agent-based model were excluded.
-Secondly, among experimental or correlative studies, only cases with adult participants were selected.
+To conduct this scoping review, we analyzed different scientific publications in response to the research questions.
+To gather the papers, we performed a Boolean search in Scopus, Web of Science and ScienceDirect.
+The key phrases were "social dilemma", "public good", "common resource", and "commons", and each of them was paired with each one of the following: "cooperation", "conflicts", "reciprocity", and "trust".
+We carried out the research during the month of August, 2023.
+According to @Munn2022, the type of source was not a selection criterion, therefore journal articles, conference papers and book chapters could be included, to have an overview as complete as possible about the existing literature on the topic.
+Moreover, we did not use any chronological or geographical limitations, once again to provide a broader vision.
+However, we implemented some selection criteria concerning the papers' methodology.
+First, we only selected papers written in English.
+Moreover, we focused on studies with human participants (or theoretical articles), so we excluded researches using an agent-based model.
+Secondly, among experimental or correlative studies, we only selected cases with adult participants.
 
@@
 Deleting the duplicates reduced them to 4586.
-Based on titles and abstracts, 4333 articles were eliminated, leaving 253 texts to examine.
-After a full-text evaluation of the remaining papers, 89 were selected for the present review.
+Based on titles and abstracts, we eliminated 4333 articles, leaving 253 texts to examine.
+After a full-text evaluation of the remaining papers, we selected 89 for the present review.
 Figure 1 resumes this selection process.
+
+![Figure 1. Overview of the selection process.](images/figure1-01.png)
 
@@
 The 89 included papers were published between 1984 and 2023, with a median of 2015.
-Almost all of the selected texts were journal articles, with the only exception being a book chapter.
+Almost all the selected texts were journal articles, with the only exception being a book chapter.
 Most of them were experimental studies (*N*=60), followed by literature review and meta-analysis (*N*=14) and correlative studies[^3] (*N*=14).
@@
 
-The papers' topic were in four categories: first, "lab-based social dilemma" (*N*=75) refers to highly controlled laboratory experiments where participants had to take cooperative decision.
-The second category is "real-life social dilemma" (*N*=7), and investigated cooperation in different real-life situations with a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
-Thirdly, papers in the category "lab-based commons" (*N*=3) used a laboratory social dilemma paradigm, but with clear references to a concrete common.
-For instance, in @Mosler1993, participants had to imagine to be fishermen who shared a common basin.
-Finally, "real-life commons" (*N*=4) refers to papers who studied cooperation with participants that were members of a commons in their everyday life.
+We identified two dimensions in the reviewed papers: setting (lab-based vs real-life) and context (social dilemma vs commons).
+There were papers in all four combinations of these dimentions, with the most represented category being "lab-based social dilemma" (*N*=75), namely highly controlled laboratory experiments where participants had to take cooperative decision.
+This was followed by "real-life social dilemma" (*N*=7), which investigated cooperation in different real-life situations with a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
+Finally, "real-life commons" refers to studies of cooperation where participants were members of a commons in their everyday life, while "lab-based commons" refers to studies with a laboratory social dilemma paradigm, but with clear references to a concrete commons [e.g.
+@Mosler1993].
 
@@
 
-Most of the papers concerned psychology and economy.
-In fact, more than a half was published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin* (*N*=34), in economic journals like *Experimental Economics* (*N*=14), or in interdisciplinary ones such as *Journal of Economic Psychology* (*N*=8).
+More than a half of papers was published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin* (*N*=34), in economic journals like *Experimental Economics* (*N*=14), or in interdisciplinary ones such as *Journal of Economic Psychology* (*N*=8).
+The remaining papers where published in journals concerning different topics, such as biology (*N*=6), mathematics and game theory (*N*=4), sustainability (*N*=3), or commons (*N*=2).
 
@@
 Moreover, six studies were set in more than one country, and fourteen were meta-analysis or literature reviews.
-The two remaining studies took place in Australia and in Colombia, respectively.
+The two remaining studies took place in Australia and Colombia, respectively.
 
@@
 
-Five individual factors that can impact cooperation emerged from the literature review: gender, social status, group identification, values and personality traits, and trust.
-In the following sections, their principal effects on cooperation are described.
-Moreover, an overview of the moderators of each effect is provided.
-More details about moderators are included in the Appendix A.
+Our analysis identified five individuals factors that impact cooperation: gender, social status, group identification, values and personality traits, and trust.
+In the following sections, we describe their principal effects on cooperation, and provide an overview of the moderators of each effect.
+More details about moderators are included in Appendix A.
 
@@
 The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results.
-Sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], but two meta-analysis found a non significant effect size [@Balliet2011; @Spadaro2023].
+Sometimes men cooperated more [@Dorrough2019], while sometimes women did [@Peshkovskaya2017].
+However, two meta-analyses reported a non significant effect size [@Balliet2011; @Spadaro2023].
 This indicates that gender differences in cooperation are very flexible and depend on the context [@Spadaro2023].
-More specifically, @Sell2009 explained this contradictory results "by structural differences [of the experimental settings] and identities triggered by those differences" (p.
+More specifically, @Sell2009 explained these contradictory results "by structural differences [of the experimental settings] and identities triggered by those differences" (p.
 322).
@@
 
-Lastly, gender is also linked to social status, with women representing the low-status group [@Sell2009].
-Therefore, gender differences in cooperation could also be partly explained by social status: to have a better understanding of this hypothesis, it is important to gain insights on how social status impacts cooperation.
+Lastly, gender differences in cooperation could be partly explained by social status, where women represent the low-status group [@Sell2009].
+For this reason, it is important to gain insights into how social status impacts cooperation.
 
@@
 
-The results of studies investigating the impact of social status on cooperation do not allow to draw a clear conclusion about this effect.
+The results of studies investigating the impact of social status on cooperation do not allow us to draw a clear conclusion about this effect.
 For instance, some findings suggest that low-status participants cooperate more than high-status ones by contributing a higher proportion of their endowments [@Kingsley2016].
@@
 
-Social status can also create inter-class conflicts, because people tend to cooperate more with the members of the same social class than with other classes' members [@Aksoy2019].
-This is especially true for low-status groups, where solidarity can arise either in the form of discrimination toward high-status members [@Camera2020], or of less punishments for other low-status [@Chen2022].
+Social status can also create inter-class conflicts, because people tend to cooperate more with the members of the same social class than with members of other classes [@Aksoy2019].
+This is especially true for low-status groups, where solidarity can arise either in the form of discrimination toward high-status members [@Camera2020], or in the form of fewer punishments for other low-status [@Chen2022].
 
-Regarding the overall group composition, results are not consensual.
+Regarding the effect of overall group composition, studies disagree.
 On one hand, @Aksoy2019 found that groups with an inequality of status between members displayed lower levels of cooperation than homogeneous groups.
-On the other hand, economic and socio-cultural heterogeneity, although being negatively correlated with in-group trust, does not have a direct effect on a common-pool resource well-being [@VanKlingeren2021].
+On the other hand, economic and socio-cultural heterogeneity are only negatively correlated with in-group trust, while there is no evidence of their effect on the integrity of a common-pool resource [@VanKlingeren2021].
 
-Lastly, similarly to what @Sell2009 affirmed about the effects of gender and social status, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
+Taken together, these results suggest that the impact of social status on cooperation is complex.
+Moreover, similarly to what @Sell2009 reported about the effects of gender and social status, @Aksoy2019 demonstrated that the lower level of cooperation between members of different social classes is mainly due to actors' identification with their classes.
 This shows that social identity and social status are deeply connected, and that it is difficult to separate their effects on cooperation.
@@
 
-In general, people cooperate more with other in-group members than with out-group [@Dorrough2015; @Aksoy2019], but the individual differences in the strength of identification can lead to inequalities on cooperation.
-High-identified individuals can even compensate, by cooperating more, for other in-group members' defection [@VanVugt2009; @Arora2016].
+In general, people cooperate more with other in-group than with out-group members [@Dorrough2015; @Aksoy2019], but the individual differences in the strength of identification can lead to inequalities in cooperation.
+In fact, individuals who strongly identify with their group can even compensate, by cooperating more, for other in-group members' defection [@VanVugt2009; @Arora2016].
 
 Intragroup cooperation can be enhanced via a competition between different groups, because in such a context individuals' and groups' interests are aligned [@Puurtinen2009].
-Moreover, a study showed that intergroup competition increased cooperation, while individual, dispositional competitiveness had the opposite effect [@Nockur2020].
-This demonstrated that the increase of cooperation via competition is due to group membership factors, and not to competition in itself.
+Moreover, a study showed that intergroup competition increased cooperation within the group, while individual, dispositional competitiveness had the opposite effect [@Nockur2020].
+This demonstrated that the increase of cooperation via competition is due to group membership factors, and not to individuals' competitiveness.
 
-Despite the beneficial effects of inducing an intergroup competition, this could be harmful in real-life situations, like resources shared between several groups.
-In fact, there is a greater risk of over-exploitation if an intergroup competition is present [@VanVugt2009].
-To maintain the positive effect of group identification while eliminating the risks associated to the competition, it is useful to prime a super-ordinate identity [@VanVugt2009].
+Despite the beneficial effects of inducing intergroup competition, this could be harmful in real-life situations, where resources are shared between several groups.
+In fact, there is a greater risk of over-exploitation when an intergroup competition is present [@VanVugt2009].
+To maintain the positive effect of group identification while eliminating the risks associated with competition, it is useful to prime a super-ordinate identity [@VanVugt2009].
 This can be done by making salient the common characteristics of the different groups rather than their differences [@Kramer1984] or by inducing the feeling of a common fate [@Zhang2019].
@@
 Trust can be defined as the "expectations of others' benevolent motives in situations that involve a conflict between self and collective interests" [@Balliet2013, p.1].
-There are two category of trust: first, dispositional trust is an individual general trait that can be assessed with personality scale.
+There are two categories of trust: first, dispositional trust is an individual general trait that can be assessed with a personality scale.
 Secondly, state trust is linked to the context and represent the expectations about a partner's behaviour in a specific situation [@Balliet2013].
-The two are positively correlated [@Lubke2021], and both have a positive general effect on cooperation [@VanLange2013; @Balliet2013].
+The two are positively correlated [@Lubke2021], and both have a positive effect on cooperation [@VanLange2013; @Balliet2013].
 
-Several studied confirmed this relationship.
-For instance, high levels of trust are associated with more contributions to a public good [@Kocher2015], individuals' cooperation can be predicted by their beliefs about others' contributions [@Smith2013], people who are pessimistic about others' contribution cooperate significantly less than optimistic [@Oyediran2018], and individuals who cooperate more display higher levels of trust in following interactions [@Chaudhuri2002].
-The effect of trust on cooperation has also been demonstrated in real-life studies [e.g.
-@Sturm2019; @Franzen2019].
+Several studies have confirmed this relationship.
+For instance, high levels of trust are associated with more contributions to a public good [@Kocher2015], individuals' cooperation can be predicted by their beliefs about others' contributions [@Smith2013], people who are pessimistic about others' contribution cooperate significantly less than optimistic people [@Oyediran2018], and individuals who cooperate more display higher levels of trust in following interactions [@Chaudhuri2002].
+The enhancing effect of trust on cooperation has also been demonstrated in real-life studies [see for example @Sturm2019; @Franzen2019].
 Finally, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
@@
 2].
-Institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied motivate people to comply to norms.
+Institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied motivates people to comply with norms.
 
@@
 
-On the organizational level, four factors have emerged from the literature review: incentives, communication, social norms and anonymity.
-As for the individual factors, the main effects of each factor are detailed in the next sections, as well as an overview of possible moderators.
+On the organizational level, we identified four factors from the reviewed papers: incentives, communication, social norms and anonymity.
+As for the individual factors, in the following sections we detail the main effects of each factor, and we provide an overview of possible moderators.
 More details can be found in Appendix A.
@@
 Cooperation can be modified by introducing incentive systems, that can be either punishments or rewards.
-Both have a positive effect on cooperation [@Balliet2011a; ].
-However, there are contradictory results about which system is more efficient [see @Chen2022; @Milinski2012].
+Both have a positive effect on cooperation [@Balliet2011a].
+However, some studies found that punishments are more efficient than rewards [e.g.
+@Milinski], while others came to the opposite conclusion [e.g.
+@Chen2022].
 
-Several factors moderate this main effect.
+Several factors moderate the main effect of incentives on cooperation.
 A meta-analysis found that both rewards and punishments are more effective if their implementation is costly rather than free, and during iterated, rather than single, interactions [@Balliet2011a].
@@
 
-In general, there are more studies about punishments than about rewards [@VanDijk2015].
-When a punishment system is present, participants' perceived fairness is higher [@Nockur2021].
+In general, there are more studies on punishments than on rewards [@VanDijk2015].
+When a punishment system is present, participants' perceive the situation as more fair [@Nockur2021].
 However, punishments must be applied with carefulness.
-Ideally, groups should not punish in early stages of the interaction, and have a norm of when and how punish [@Rockenbach2019].
-Moreover, punishment could entails a second-order social dilemma, since cooperators are better-off by non punishing, if all others do [@Milinski2012].
-Also, if there are no rules on who can punish, non-cooperators can punish cooperators as a form of retaliation [@Xiao2016; @VanDijk2015].
-A democratic punishment system, where a fine is given only if a majority agree, could solve these problems [@Pfattheicher2018].
+Ideally, groups should not punish in the early stages of the interaction, and have a norm of when and how to punish [@Rockenbach2019].
+Moreover, a punishment system could entail a second-order social dilemma, since cooperators are better-off by not investing resources into punishing, if all others do [@Milinski2012].
+Also, if there are no rules about who can punish, non-cooperators can punish cooperators as a form of retaliation [@Xiao2016; @VanDijk2015].
+A democratic punishment system, where a fine is given only if a majority agree, could solve this problem [@Pfattheicher2018].
 
-Even if they enhance cooperation, incentives have negative sides: they reduce participants' intrinsic motivation [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
+Despite enhancing cooperation, incentives have negative sides: they reduce participants' intrinsic motivation [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009].
 They also undermine participants' trust in other members' internal motivation to cooperate.
@@
 In fact, expecting honour or shame (after cooperating or defecting, respectively), or expressing disapproval toward defectors can enhance cooperation [@Jacquet2011; @Nelissen2013].
-Even an ostracism system where participants can vote to exclude other members is very effective [@Maier-Rigaud2010].
+An ostracism system where participants can vote to exclude other members is also very effective [@Maier-Rigaud2010].
 In conclusion, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
@@
 
-Communication between members has a global positive effect on cooperation [e.g.
-@Balliet2010], because it allows to shape a normative content [@Janssen2014; @Bicchieri2002] and to reach a consensus about the best strategy [@Hopthrow2005].
-In fact, when communication is used to foster a common social identity, promote cooperative social norms and ensure that every member publicly commits, communication is higher [@Adams2022].
+Communication between members has a general positive effect on cooperation [e.g.
+@Balliet2010], because it allows to shape a cooperative social norms [@Janssen2014; @Bicchieri2002] and to reach a consensus about the best strategy for the group [@Hopthrow2005].
+In fact, when communication is used to foster a common social identity, promote cooperative social norms and ensure that every member publicly commits, cooperation is higher [@Adams2022].
 
@@
 Moreover, if communicating requires a personal cost, its effect is weaker than if communication is free [@Janssen2014].
-The content of the message is also essential: to be effective, communication must allow participants to become aware of the problem, identify different strategies and agree on the one to use.
-However, casual chit-chat also plays a very important role in increasing cooperation [@Koessler2021].
+The content of the message is also essential: to be effective, communication must allow participants to become aware of the problem faced by the group, identify different strategies and agree on the one to use.
+In addition, casual chit-chat also plays a very important role in increasing cooperation [@Koessler2021].
 Finally, communication before or during the cooperative interaction have both a positive impact on cooperation [@Balliet2010], while knowing that it will be possible to communicate after the interaction does not enhance cooperation [@Kumakawa2013], and can even have a negative effect [@Torsvik2011].
@@
 the spread of reputational information about another person [@Feinberg2014].
-Gossip increases cooperation by providing information about the past behaviour of potential partners, which helps to select the most cooperative members in a following interaction.
+Gossip increases cooperation by providing information about the past behaviour of potential partners, which helps to select the most cooperative members in the following interaction.
 Moreover, knowing that gossip is possible motivates people to cooperate more to avoid being the target of such gossip [@Feinberg2014].
-Gossip can also have the pro-social function of protecting others from a potential exploitation [@Feinberg2012].
+Gossip can also have the pro-social function of protecting others from potential exploitation [@Feinberg2012].
 Finally, providing correct information while gossiping helps to build a positive reputation [@Giardini2021] and reduces negative affects on the gossip actor [@Feinberg2012].
@@
 Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour like in cooperative situations [@VonBorgstede2018].
-Both injunctive (what others approve) and descriptive (what others do) norms are positively related to cooperative behaviours [@Thogersen2008].
-Moreover, social norms help to maintain cooperation, because individuals who do not respect them are susceptible of social sanction [@Rege2004].
+Both injunctive (what others approve) and descriptive (how others actually behave) norms impact cooperative behaviours [@Thogersen2008].
+Moreover, social norms help to maintain cooperation, because individuals who do not respect them are susceptible to social sanctions [@Rege2004].
 
@@
 In general, in non-anonymous situations cooperation is significantly higher than in anonymous ones [@Wang2017].
-In fact, in such situations there are more social incentives to cooperate, because people worry about others' approval [@Rege2004].
-Moreover, several factors that can increase cooperation rely on a reduction of anonymity [@Wang2017]: for instance, punish defectors is impossible without knowing who they are.
+In such situations there are more social incentives to cooperate, because people worry about others' approval [@Rege2004].
+Moreover, several factors that can increase cooperation rely on a reduction of anonymity [@Wang2017]: for instance, punishing defectors is impossible without knowing who they are.
 When behaviours are visible, cooperation can also be a self-presentation strategy to be perceived as pro-social and therefore to increase one's social status.
-In fact, the positive effect of non-anonymity is stronger in situations where cooperation bears a cost without offering a personal gain [@Butz2021; @VanVugt2010a].
+In fact, the positive effect of non-anonymity is stronger in situations where cooperation bears a cost without offering personal gain [@Butz2021; @VanVugt2010a].
 
 Therefore, reducing anonymity in cooperative interaction could significantly improve cooperation.
-A possible way to do this is to reduce group's size, because larger groups lead to de-individuation and it is thus more difficult to identify defectors [@Romano2016].
-In fact, cooperation levels are higher in small, rather than large, groups [@Jiang2021].
+A possible way to do this is to reduce the group's size, because larger groups lead to de-individuation and it is thus more difficult to identify defectors [@Romano2016].
+In fact, cooperation levels are higher in small, compared to large, groups [@Jiang2021].
 Anonymity can also be reduced by making people publicly promise to cooperate.
-Such a commitment increases significantly cooperation rates, even if after committing people are not forced to cooperate [@Mosler1993; @Przepiorka2020].
-Moreover, even a compulsory commitment has a beneficial effect on cooperation [@Koessler2021a].
+Such a commitment significantly increases cooperation rates, even if after committing people are not forced to cooperate [@Mosler1993; @Przepiorka2020].
+Even a compulsory commitment has a beneficial effect on cooperation [@Koessler2021a].
 
@@
 
-Until now, the identified factors has been discussed separately.
+Until now, the identified factors have been discussed separately.
 However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.

### 2023-12-18 scoping_review_short.Rmd
18.12 (=> inclusion of feedback)

@@
 abstract: |
-  Commons represent an alternative to the classical capitalist model, therefore they could be the needed change toward a more sustainable society and economy.
+  Private ownership and commodification of resources are central aspects of the current capitalistic social organization.
+This has detrimental effects both on social and environmental levels.
+Commons represent an alternative to this system, therefore they could be the needed change toward a more sustainable society and economy.
 However, for a commons to be successful, its members must cooperate, i.e.
@@
 On the other hand, cooperation has been extensively studied in social dilemma experiments, where personal and collective interests are at odds.
-Since social dilemma experiments and commons share some structural characteristics, we could gain insights into cooperation in commons and how to implement it thanks to the social dilemmas literature.
+Since social dilemma experiments and commons share some structural characteristics, we could gain insights into cooperation in commons and how to promote it thanks to the social dilemmas literature.
   The goal of the current scoping review is to identify the factors that impact cooperation in social dilemma situations, in order to better understand what could shape cooperation in commons.
-A key-word search and a subsequent selection led to the inclusion of 89 papers, which were used to identify 9 factors that can influence cooperation both at the individual and group level: gender, social status, group identification, values and personality traits, trust, incentives, communication, social norms and anonymity.
-These factors are discussed within the existing literature on commons and cooperation.
-More specifically, the influences that these elements can have on each-other are highlighted, showing that all factors should be taken into account when investigating cooperation in commons.
-Finally, the practical implication of this work for commons' organization, as well as the review's limitations, are pointed out.
+A key-word search and a subsequent selection led to the inclusion of 89 papers, which were used to identify 9 factors that influence cooperation both at the individual and group level: gender, social status, group identification, values and personality traits, trust, incentives, communication, social norms and anonymity.
+The influences that these elements can have on each-other are highlighted, showing that all factors should be taken into account when investigating cooperation in commons.
+Finally, the theoretical and practical implications of this work for commons' organization, as well as the review's limitations, are pointed out.
 
@@
 mask                    : no
+disambiguate_authors    : no
 
@@
 
+<!-- change of the initial paragraph and of the definition -->
+
 In recent years, the interest in alternative ways of social organization increased drastically due to the social and ecological crises we are facing [@Euler2018].
-Commons are one of these alternatives, since they are a way of organizing resources beyond the classic private and public model [@Ostrom1990], and, therefore, they represent an option to the capitalistic system [@Euler2019].
-For this reason, commons could be an integral part of the path to attain a more sustainable and fair social organization [@Schmelzer2022].
+Commons could be an integral part of the path to attain a more sustainable and fair social organization [@Schmelzer2022].
+In fact, they are a way of organizing resources beyond the classic private and public model [@Ostrom1990] and they are not organized around market competition [@Euler2019].
+Commons express "a broader conception of property, referring to social goods [...] which a community, not the state or any individual, collectively owns, manages, and controls" [@Federici2011, p.
+41].
+Giving their characteristics, commons represent an option to the capitalistic system [@Euler2019] and its detrimental effects on natural resources and human well-being.
 
-Commons have been defined in different ways, starting by Elinor Ostrom who, in her seminal work, refers to them as a resource system shared between a self-managed community of users [@Ostrom1990].
-This community shares a set of social practices, values and norms.
-Therefore, it is important to consider the commons not only as a resource, but as the integration of the resource, the community and its social protocols [@Bollier2014].
-For this reason, beyond the material aspect, the notion of social practices (i.e.
-commoning) is essential [@Euler2018].
-"Commoning" refers to the process through which people (i.e.
-the commoners) find solutions for their needs by self-organizing independently from the state or the market, and by creating autonomously managed institutions to govern the shared resource [@Euler2018; @Schmelzer2022].
-The community is therefore engaged in defining rules to successfully manage the commons [@Meroni2022].
-In conclusion, commons can be understood as "living social systems" that allow commoners to self-organize to address shared problems [@Bollier2019].
+Commons can assume various forms, because "they can arise whenever a community decides it wishes to manage a resource in a collective manner, with a special regard for equitable access, use and sustainability" [@Bollier2014, p.19].
+The variety of definitions can be resumed through three key points.
+First, commons allow to manage shared resources [@Ostrom1990] and to find solution for share needs of the population [@Euler2018; @Euler2019].
+Second, commons are managed by a self-organized community of users [@Ostrom1990], i.e.
+the commoners.
+This community is a "social network of mutual aid, solidarity, and practices of human exchange that are not reduced to the market form" [@DeAngelis2003, p.1].
+Moreover, commoners' organization is usually local, egalitarian, integrative, and fair [@Gidwani2011].
+Third, the community's social practices are called "commoning" and, thanks to this process, commoners create institutions to govern the commons [@Euler2018; @Schmelzer2022].
+Finally, although commons are often thought just as a shared resource, the other two aspects are also essential in defining them.
+Therefore, it is important to consider the commons as the integration of the resource, the community (i.e.
+the commoners) and its social practices (i.e.
+commoning) [@Bollier2014].
+These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look at the people who form it.
 
-These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look at the people who form it.
 More specifically, in order for a commons[^1] to be successful, its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998].
@@
 Secondly, in a commons, every member faces a conflict between individual, short-term interests and collective, long-term ones [@Hardin1968].
-Act for the common good requires a personal sacrifice, and therefore the temptation to pursue the individual interest is constantly present.
-For these reasons, we need to understand the factors that affect cooperation, and how we can improve it.
+Since acting for the common good requires a personal sacrifice, the temptation to pursue the individual interest is constantly present.
+Giving the role that commons could play in addressing the environmental and social problems, we need to understand the factors that affect cooperation, and how we can improve it.
+In fact, despite its importance, the reasons why individual choose to cooperate have not been extensively studied in commons scientific literature.
+At the same time, social dilemma experiments (i.e.
+artificial decision making situations, where personal and collective interests are at odds) allowed to identify several factors that could impact cooperation [e.g.
+@VanLange2013].
+Since commons and social dilemmas share some structural characteristics [@Hardin1968; @Dawes1980], the aim of the current scoping review is to gain insight into cooperation in commons through social dilemma literature.
 
@@
 
-In the existing literature, there are several explications of why people adopt or not cooperative behaviours in commons.
-For instance, the Rational Choice Theory predicts that people are too self-interested to cooperate in such contexts.
-As a consequence, they will inevitably destroy the shared resource, unless an external institution forces them to cooperate [@DeCaro2021; @Hardin1968].
-However, there are some less pessimistic theories that predict that people can transcend their personal interest and successfully cooperate in commons.
-An example is the Greed Efficiency Fairness hypothesis, which posits that the individuals' greed to pursue their narrow interests is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
+<!-- the whole structure has been changed according to Lilla's and Steffi's suggestions + Ostrom's principles explained more in details -->
+
+One of the first paper about cooperation in commons was Hardin's "The tragedy of the commons" [-@Hardin1968].
+In this article, Hardin argues that commons' members are rational beings who seek to maximize their personal interest by over-exploiting the common resource.
+This would inevitably lead to the destruction of the resource, unless an external institution regulates the access, or the resource is privatized.
+Therefore, according to Hardin, people benefiting from a common resource cannot successfully manage it without external interventions.
+
+However, some years later, Elinor Ostrom's seminal work [-@Ostrom1990] falsified Hardin's predictions about people's inability to manage a common resource and their greed to maximize their self-interest.
+In fact, Ostrom observed several real-life commons, and showed that some of them were very successfully managed by the community of users without the intervention of an external authority.
+Based on her observations, she established seven design principles that are present in all the observed successfull commons, plus an eight one for more complex cases.[^2] By "design principle", Ostrom means "an essential element or condition that helps to account for the success of these institutions" [@Ostrom1990, p.
+90].
+
+[^2]: Since the eight principle is not relevant for the current paper, it will not be detailed.
+
+The first principle posits that clearly defined boundaries are needed: it must be clear which is the shared resource, and who can benefit from it, otherwise, "no one knows what is being managed or for whom" (p.
+91).
+Second, the rules must be congruent with the local conditions, i.e.
+they must reflect the specific attributs of the particular resource.
+Thirdly, individuals affected by the operational rules must be able to participate in modifying them.
+This ensure that the rules fit well to the local conditions and allows to promptly adapt them when needed.
+The fourth and fifth principles concern a monitoring and a graduate sanction system.
+Interestingly, these systems are successfully implemented by commoners them-selves, that can assume the roles of monitor or punisher, with no need of an external institution.
+In fact,
+
+-   everybody has a self-interest in monitoring the others
+
+-   no one will abuse of the sanctions because they know that they could be in the same situation so their are comprehensive + being caught has already a negative effect on reputation
+
+1.  Monitoring + graduated sanctions (4 and 5) =\> these two systems are implemented by commoners them-selves, not by external institutions
+    1.
+Monitoring = low cost, because it is in everybody's self interest to monitor others + being a good monitor and catch somebody's infraction can make a person gain in prestige and status + material benefits if an infraction is caught (ex: part of the fine) + monitoring necessary to adopt a contingent strategy (if I cooperate, I want to be sure that the others do not exploit my work)
+    2.  Not enourmous sanctions needed, because being caught is already negative for reputation
+2.
+Conflict resolution mechanism (6) =\> individuals following rules for a long period of time = inevitably some infractions, so it is essential to have somewhere to discuss when conflicts arise =\> give the possibility to explain the mistake, so that compliace to rules does not drop
+3.
+Minimal recognition of the right to organize (7) =\> external authorities (such governement) should not challenge the commoners' right to organize (if they do it, the rules of appropriators are not seen as valid and therefore more difficultly compliable)
+
+These principles were not present in Hardin's example, where the hypothetical commoners made decisions in a context without local organization or established norms.
+Therefore, Hardin's scenario should not be considered a commons, but an open access regime [@Ostrom2008; @Bollier2014], and this can contribute to explain his negative predictions about cooperation.
+
+At the same time, psychology is so far absent from the discussion
+
+-   psychology is absent so far in the discussion, even though there are theories and experimental paradigms that are highliy relevant to the topic.
+On the theory side, there is....[the first paragraph with the different Theories] On the experimental side, there are classical social psychological experiments that...
+
+Secondly, Hardin assumed, in line with the Rational Choice Theory, that all the commoners wanted to maximize their personal interest [@Wittel2023].
+However, there are several theories less pessimistic than the RCT about human nature.
+For instance, the Greed Efficiency Fairness hypothesis posits that the individuals' greed to pursue their narrow interests is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
 Similarly, according to the Humanistic Rational Choice Theory, the desire to maintain basic social-psychological needs motivates people to cooperate [@DeCaro2021].
-Finally, cooperating in commons can also be a self-presentation strategy [@VanVugt2010a], since showing altruistic behaviours has a positive effect on reputation [@Roberts1998].
+Moreover, cooperating can also be a self-presentation strategy [@VanVugt2010a], since showing altruistic behaviours has a positive effect on reputation [@Roberts1998].
 
-On a more practical level, @Ostrom1990 reported several cases of successful commons, where individuals managed to create a system to ensure cooperation.
-Based on her observations, she established eight design principles that distinguish successful from unsuccessful commons.
-First, commons need clearly defined boundaries to determine who has access to the shared resource, and the governing rules must take into account the local conditions.
-Moreover, people affected by these rules must be able to participate in modifying them.
-A monitoring and a graduated sanctions system must also be implemented, as well as low-cost conflict resolution arena.
-Finally, external authorities must not challenge the commons' members' right to self-organize[^2] [@Ostrom1990].
+Finally, the laboratory study of social dilemmas also largely contributed to the investigation of this topic, by allowing researchers to identify several factors that shape cooperation [e.g.
+@VanLange2013].
+In general, these studies falsified RCT by demonstrating that, in social dilemmas, people cooperated more than predicted, and that their behaviour was impacted by variables that should not play a role according to the theory [@Ostrom1998].
+Moreover, research based on different fields has convincingly demonstrated that people can engage in collective actions to sustainably manage shared resources [@Poteete2010a].
 
-[^2]: The last principle is valid only for commons that are part of a larger system, and is about nested enterprises: all the governance activities should be organized in multiple layers of nested enterprises.
-
-There are therefore several studies that focused on commons and on how they can be successful, but social psychological and quantitative perspectives are missing from this literature.
-In fact, to the authors' knowledge, there are few studies that investigated the causal effect of individual and group factors on people's willingness to cooperate in a real-life commons [e.g.
-@Noonan2016].
-
-At the same time, an experimental approach is very popular in the laboratory study of social dilemmas, which identified several factors that shape cooperation [e.g.
-@VanLange2013].
-In these experiments, people face a conflict between personal and collective interest: each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
-At the same time, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
-Since many of the current global problems have a social dilemma structure, this topic has been extensively studied in different fields such as psychology, economy, biology, or mathematics [@VanLange2013].
-Social dilemmas are very useful to gain insights into how cooperation works, because they can easily be implemented in a laboratory setting, and they provide a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
+CONCLUSION: PSYCHOLOGY OFFER A SECOND EXPLANAITION OF WHY THERE IS NOT ALWAYS A TRAGEDY OF THE COMMONS = PEOPLE DO NOT ONLY WANT TO MAXIMISE THEIR PERSONAL INTEREST, AND SEVERAL "IRRATIONAL" FACTORS IMPACT THE WAY IN WHICH THEY INTERACT WITH OTHERS
 
@@
 However, some studies found that punishments are more efficient than rewards [e.g.
-@Milinski], while others came to the opposite conclusion [e.g.
+@Milinski2012], while others came to the opposite conclusion [e.g.
 @Chen2022].

### 2024-01-03 scoping_review_short.Rmd
intro + method + results okay

@@
   Private ownership and commodification of resources are central aspects of the current capitalistic social organization.
-This has detrimental effects both on social and environmental levels.
-Commons represent an alternative to this system, therefore they could be the needed change toward a more sustainable society and economy.
+Commons represent an alternative to this system, therefore they could be part of the solution to attain more sustainable society and economy.
 However, for a commons to be successful, its members must cooperate, i.e.
@@
 On the other hand, cooperation has been extensively studied in social dilemma experiments, where personal and collective interests are at odds.
-Since social dilemma experiments and commons share some structural characteristics, we could gain insights into cooperation in commons and how to promote it thanks to the social dilemmas literature.
+Since social dilemma and commons share some structural characteristics, we could gain insights into cooperation in commons and how to promote it thanks to the social dilemmas literature.
   The goal of the current scoping review is to identify the factors that impact cooperation in social dilemma situations, in order to better understand what could shape cooperation in commons.
@@
 
-<!-- change of the initial paragraph and of the definition -->
+<!--# change of the initial paragraph and of the definition + adding the last paragraph with an overview of the goal of the paper -->
 
-In recent years, the interest in alternative ways of social organization increased drastically due to the social and ecological crises we are facing [@Euler2018].
-Commons could be an integral part of the path to attain a more sustainable and fair social organization [@Schmelzer2022].
-In fact, they are a way of organizing resources beyond the classic private and public model [@Ostrom1990] and they are not organized around market competition [@Euler2019].
-Commons express "a broader conception of property, referring to social goods [...] which a community, not the state or any individual, collectively owns, manages, and controls" [@Federici2011, p.
+Commons allow to organize resources beyond the classic private and public model [@Ostrom1990] and they are not organized around market competition [@Euler2019].
+They express "a broader conception of property, referring to social goods [...] which a community, not the state or any individual, collectively owns, manages, and controls" [@Federici2011, p.
 41].
-Giving their characteristics, commons represent an option to the capitalistic system [@Euler2019] and its detrimental effects on natural resources and human well-being.
+Giving their characteristics, commons represent an option to the capitalistic system, which is the main responsible for the current social and ecological crises [@Euler2019; @Wittel2023].
+Therefore, they could be an integral part of the path to attain a more sustainable and fair social organization [@Schmelzer2022], and, for this reason, the interest in commons has recently increased [@Federici2019].
 
@@
 The variety of definitions can be resumed through three key points.
-First, commons allow to manage shared resources [@Ostrom1990] and to find solution for share needs of the population [@Euler2018; @Euler2019].
+First, commons allow to manage shared resources [@Ostrom1990] and to find solution for shared needs of the population [@Euler2018; @Euler2019].
 Second, commons are managed by a self-organized community of users [@Ostrom1990], i.e.
@@
 commoning) [@Bollier2014].
-These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look at the people who form it.
+For this reason, it is essential to have a closer look at the individuals who are part of commons.
 
@@
 Giving the role that commons could play in addressing the environmental and social problems, we need to understand the factors that affect cooperation, and how we can improve it.
-In fact, despite its importance, the reasons why individual choose to cooperate have not been extensively studied in commons scientific literature.
-At the same time, social dilemma experiments (i.e.
-artificial decision making situations, where personal and collective interests are at odds) allowed to identify several factors that could impact cooperation [e.g.
-@VanLange2013].
-Since commons and social dilemmas share some structural characteristics [@Hardin1968; @Dawes1980], the aim of the current scoping review is to gain insight into cooperation in commons through social dilemma literature.
 
@@
 
+Despite its importance, cooperation has not been much investigated in commons scientific literature.
+At the same time, other disciplines such as psychology extensively studied it.
+More specifically, social dilemma experiments allowed to identify several factors that impact cooperation [e.g.
+@VanLange2013].
+For this reason, the current scoping review is aimed at gaining insight into cooperation in commons through social dilemma literature.
+In the next section, we give an overview about the existing research about cooperation in commons, afterwards we will detail the research questions.
+
 ## Cooperating in commons
 
-<!-- the whole structure has been changed according to Lilla's and Steffi's suggestions + Ostrom's principles explained more in details -->
+<!--# the whole structure has been changed according to Lilla's and Steffi's suggestions + Ostrom's principles explained more in details -->
 
-One of the first paper about cooperation in commons was Hardin's "The tragedy of the commons" [-@Hardin1968].
+One of the first papers about cooperation in commons was Hardin's "The tragedy of the commons" [-@Hardin1968].
 In this article, Hardin argues that commons' members are rational beings who seek to maximize their personal interest by over-exploiting the common resource.
@@
 
-However, some years later, Elinor Ostrom's seminal work [-@Ostrom1990] falsified Hardin's predictions about people's inability to manage a common resource and their greed to maximize their self-interest.
-In fact, Ostrom observed several real-life commons, and showed that some of them were very successfully managed by the community of users without the intervention of an external authority.
-Based on her observations, she established seven design principles that are present in all the observed successfull commons, plus an eight one for more complex cases.[^2] By "design principle", Ostrom means "an essential element or condition that helps to account for the success of these institutions" [@Ostrom1990, p.
-90].
+However, research in different disciplines has convincingly demonstrated that people can engage in collective actions to sustainably manage shared resources, thus falsifying Hardin's predictions [@Poteete2010a].
+Among these studies, the most important is Elinor Ostrom's seminal work [-@Ostrom1990], where she studied several real-life commons, some of them successfully managed by the community of users without the intervention of an external authority.
+Based on her observations, she established seven design principles that are present in all the successful commons, plus an eighth one for more complex cases.[^2]
 
-[^2]: Since the eight principle is not relevant for the current paper, it will not be detailed.
+[^2]: Since the eighth principle is not relevant for the current paper, it will not be detailed.
 
-The first principle posits that clearly defined boundaries are needed: it must be clear which is the shared resource, and who can benefit from it, otherwise, "no one knows what is being managed or for whom" (p.
+The first principle posits that boundaries are essential: it must be clear which is the shared resource, and who can benefit from it, otherwise, "no one knows what is being managed or for whom" (p.
 91).
 Second, the rules must be congruent with the local conditions, i.e.
-they must reflect the specific attributs of the particular resource.
-Thirdly, individuals affected by the operational rules must be able to participate in modifying them.
+they must reflect the specific attributes of the particular resource.
+Thirdly, individuals affected by the rules must be able to participate in modifying them.
 This ensure that the rules fit well to the local conditions and allows to promptly adapt them when needed.
 The fourth and fifth principles concern a monitoring and a graduate sanction system.
-Interestingly, these systems are successfully implemented by commoners them-selves, that can assume the roles of monitor or punisher, with no need of an external institution.
-In fact,
-
--   everybody has a self-interest in monitoring the others
-
--   no one will abuse of the sanctions because they know that they could be in the same situation so their are comprehensive + being caught has already a negative effect on reputation
-
-1.  Monitoring + graduated sanctions (4 and 5) =\> these two systems are implemented by commoners them-selves, not by external institutions
-    1.
-Monitoring = low cost, because it is in everybody's self interest to monitor others + being a good monitor and catch somebody's infraction can make a person gain in prestige and status + material benefits if an infraction is caught (ex: part of the fine) + monitoring necessary to adopt a contingent strategy (if I cooperate, I want to be sure that the others do not exploit my work)
-    2.  Not enourmous sanctions needed, because being caught is already negative for reputation
-2.
-Conflict resolution mechanism (6) =\> individuals following rules for a long period of time = inevitably some infractions, so it is essential to have somewhere to discuss when conflicts arise =\> give the possibility to explain the mistake, so that compliace to rules does not drop
-3.
-Minimal recognition of the right to organize (7) =\> external authorities (such governement) should not challenge the commoners' right to organize (if they do it, the rules of appropriators are not seen as valid and therefore more difficultly compliable)
+Interestingly, these systems are successfully implemented by commoners themselves, with no need of an external institution.
+In fact, in order to know that the best strategy is to follow the rules, one must be sure that the others are also complying to them.
+For this reason, it is in everybody's self-interest to monitor other commoners.
+Similarly, the graduate sanction system can be easily self-regulated: even if punishing is usually profitable for the punisher, fines are naturally small for the first infraction and get higher only if the person persists in breaking the rules.
+In fact, since infractions are often due to extreme situations, punishers tend to be sympathetic because it could happen to them too.
+Linked to the previous principle, the sixth posits that people must have access to low-cost conflict resolution mechanisms, since, in a situation like a commons, disagreements between members are inevitable.
+Conflict resolution arenas give the rule-breaker the possibility to explain the mistake, and ensure that compliance to rules does not drop after every infraction.
+Finally, according to the seventh principle, external authorities should not challenge the commoners' right to self-organize and should recognize the commons' institutions.
 
 These principles were not present in Hardin's example, where the hypothetical commoners made decisions in a context without local organization or established norms.
-Therefore, Hardin's scenario should not be considered a commons, but an open access regime [@Ostrom2008; @Bollier2014], and this can contribute to explain his negative predictions about cooperation.
+Therefore, Hardin's scenario should not be considered a commons, but an open access regime [@Ostrom2008; @Bollier2014], and this can partly explain his negative predictions about cooperation.
 
-At the same time, psychology is so far absent from the discussion
-
--   psychology is absent so far in the discussion, even though there are theories and experimental paradigms that are highliy relevant to the topic.
-On the theory side, there is....[the first paragraph with the different Theories] On the experimental side, there are classical social psychological experiments that...
-
-Secondly, Hardin assumed, in line with the Rational Choice Theory, that all the commoners wanted to maximize their personal interest [@Wittel2023].
-However, there are several theories less pessimistic than the RCT about human nature.
+At the same time, an individual perspective is so far absent from the discussion, although it provides further theoretical and experimental evidences against Hardin's predictions.
+First, there are several theories that offer an optimistic view of human ability to manage a shared resource.
 For instance, the Greed Efficiency Fairness hypothesis posits that the individuals' greed to pursue their narrow interests is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991].
-Similarly, according to the Humanistic Rational Choice Theory, the desire to maintain basic social-psychological needs motivates people to cooperate [@DeCaro2021].
+Similarly, according to the Humanistic Rational Choice Theory, cooperation can be seen as the rational option when the institution is accepted and perceived as legitimate, and when there is a strong group cohesion [@DeCaro2021].
 Moreover, cooperating can also be a self-presentation strategy [@VanVugt2010a], since showing altruistic behaviours has a positive effect on reputation [@Roberts1998].
 
-Finally, the laboratory study of social dilemmas also largely contributed to the investigation of this topic, by allowing researchers to identify several factors that shape cooperation [e.g.
+Secondly, on the experimental level, the laboratory study of social dilemmas also largely contributed to the investigation of cooperation, by identifying several factors that impact it [e.g.
 @VanLange2013].
-In general, these studies falsified RCT by demonstrating that, in social dilemmas, people cooperated more than predicted, and that their behaviour was impacted by variables that should not play a role according to the theory [@Ostrom1998].
-Moreover, research based on different fields has convincingly demonstrated that people can engage in collective actions to sustainably manage shared resources [@Poteete2010a].
+A typical constellation in these experiments (often also referred as "public good games" or "common resource experiments") is that people face a conflict between personal and collective interest.
+Each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do.
+At the same time, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].
+Social dilemma experiments are very useful for gaining insight into cooperation, because they are easily implemented in a laboratory, and provide a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].
+In general, these studies demonstrated that people are able to cooperate, and that their behaviour is impacted by variables that should not play a role from a rational point of view [@Ostrom1998].
 
-CONCLUSION: PSYCHOLOGY OFFER A SECOND EXPLANAITION OF WHY THERE IS NOT ALWAYS A TRAGEDY OF THE COMMONS = PEOPLE DO NOT ONLY WANT TO MAXIMISE THEIR PERSONAL INTEREST, AND SEVERAL "IRRATIONAL" FACTORS IMPACT THE WAY IN WHICH THEY INTERACT WITH OTHERS
+Finally, to the best of our knowledge, there are no studies that investigated with experimental designs the causal effects of individual and group factors on people's willingness to cooperate in real-life commons.
+The aim of the current review is to lay the foundation to fill this gap in the literature.
 
 ## Current review
+
+<!--# here I do not agree with Vincent and Lilla, who proposed to divide the three reasons to combine SD and commons based on the authors:1) the arguments are not completely separated: e.g.
+the fact that SD and commons share the basic conflict between personal and collective interest is the reason why commons are considered a specific kind of SD2) for the first argument I cited Hardin and Dawes not because they both said that SD and commons have the same characteristics, but because they defined the conflict in commons and SD, respectively (reading the two definitions is easy to make the link): for this reason, I would not consider them as the same "line" of research -->
 
@@
 For this reason, commons can be considered as a particular case of social dilemma.
-In fact, @Kopelman2002 used the term of "commons dilemma" to define situations where a non-cooperative behaviour can seriously endanger the future of the shared resource.
-Moreover, commons have been classified by @Cumming2018 as "take-some dilemmas", a specific kind of social dilemma where people are tempted to increase their personal benefit by taking more than their fair share from a shared resource.
+In fact, @Kopelman2002 used the term of "commons dilemma" to define situations where a non-cooperative behaviour can seriously endanger the future of a shared resource.
+Commons have also been classified by @Cumming2018 as "take-some dilemmas", a specific kind of social dilemma where people are tempted to increase their personal benefit by taking more than their fair share from a shared resource.
 Moreover, cooperation and defection in social dilemma laboratory experiments can predict people's behaviour in a real-life commons [e.g.
@@
 
-The current paper synthesizes existing research about cooperation in social dilemmas, to provide a set of factors that impact cooperative behaviours in commons.
+Based on this evidence, the current paper synthesizes existing research about cooperation in social dilemmas, to provide a set of factors that impact cooperative behaviours in commons.
 This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation beyond artificial laboratory settings.
-Other studies already used a social dilemma framework to study real-life commons [e.g.
-@Hartl2022].
-While these studies usually focused on just one particular case, the current review is seeking to extend this approach by using social dilemma literature to gain a global understanding of cooperation in commons.
 
-This scoping review has two main goals.
-The first is to identify factors on the individual level that can shape cooperation in commons.
-Moreover, since it has been widely demonstrated that commoners can successfully self-organize to govern a commons [@Ostrom1990; @Larsson2016], the second goal is to understand which strategies groups can implement to encourage their members to cooperate.
+Some works already went in a similar direction.
+For instance, @Hartl2022 used a social dilemma framework to study real-life commons.
+However, these authors focused on just one particular commons, while the current review provides more general results.
+Moreover, through a literature review, @Kopelman2002 identified several individual and situational factors that affect cooperation in commons dilemma.
+However, they restrained their review to papers published in peer-reviewed psychological journals.
+In the current review, we do not exclude any discipline beforehand, and this allows to provide a more complete overview of the factors impacting cooperation.
+
+<!--# About the discussion with Steffi: Kopelman just focused on psychology, so it was interesting to insert it here to say that we are extending these results -->
+
+In conclusion, the current review is seeking to extend what has already been done by using social dilemma literature to gain a global understanding of cooperation in commons.
+The first goal is to identify factors on the individual level that can shape cooperation in commons.
+The second goal is to understand which strategies groups can implement to encourage their members to cooperate, since it has been widely demonstrated that commoners can successfully self-organize to govern a commons [@Ostrom1990].
+This leads to the three research questions:
+
+1.  Which individual factors affect people's cooperation in social dilemmas?
+2.  Which group factors affect people's cooperation in social dilemmas?
+3.  Which moderating effects exist between the different factors?
+
+<!--# Discussion with Steffi: goals = broader, questions = more specific for this reason in the goals I speak about commons (and strategies), while on the questions is SD (and factors) -->
 
 # Methods
+
+Due to the highly exploratory nature of the paper, a scoping review seemed more adapted to our goals than a systematic review.
+In fact, scoping reviews allow to collect the existing evidence on a specific topic, and to identify key factors linked to the main concept [@Munn2022].
 
@@
 The key phrases were "social dilemma", "public good", "common resource", and "commons", and each of them was paired with each one of the following: "cooperation", "conflicts", "reciprocity", and "trust".
+To define these phrases, we screened key literature to identify (1) synonyms for "social dilemmas" and "commons", and (2) words that were frequently associated with "cooperation".
 We carried out the research during the month of August, 2023.
-According to @Munn2022, the type of source was not a selection criterion, therefore journal articles, conference papers and book chapters could be included, to have an overview as complete as possible about the existing literature on the topic.
+Following the recommendations of @Munn2022, the type of source was not a selection criterion, therefore journal articles, conference papers and book chapters could be included, to have an overview as complete as possible about the existing literature on the topic.
 Moreover, we did not use any chronological or geographical limitations, once again to provide a broader vision.
-However, we implemented some selection criteria concerning the papers' methodology.
-First, we only selected papers written in English.
-Moreover, we focused on studies with human participants (or theoretical articles), so we excluded researches using an agent-based model.
-Secondly, among experimental or correlative studies, we only selected cases with adult participants.
 
@@
 Deleting the duplicates reduced them to 4586.
-Based on titles and abstracts, we eliminated 4333 articles, leaving 253 texts to examine.
-After a full-text evaluation of the remaining papers, we selected 89 for the present review.
+Based on titles and abstracts, we eliminated 4333 articles which were clearly not related to the topic[^3], leaving 253 texts to examine.
+During the full-text evaluation, we applied different criteria.
+First, we only selected papers written in English.
+Secondly, to be included, a paper must investigate one or more factors that impact cooperation in social dilemmas or in commons.
+Moreover, we focused on studies with human participants (or theoretical articles), so we excluded researches using an agent-based model.
+Finally, among experimental or correlative studies, we only selected cases with adult participants.
+Through the application of these criteria, we selected 89 papers for the present review.
 Figure 1 resumes this selection process.
 
-![Figure 1. Overview of the selection process.](images/figure1-01.png)
+[^3]: For instance, during the initial research, we found the article "International cooperation on financial market regulation" [@Abendschein2021] because, among its keywords, there were "public good" and "cooperation".
+However, the title already informed us that it would not allow us to answer the research questions.
+
+<!--# add somewhere that qualitative studies are ok? -->
+
+![Figure 1. Overview of the selection process.](images/figure1-03.png)
+
+<!--# for the figure: "Papers", but not all of them are papers, maybe should I use "Texts"? -->
+
+# Results
+
+In this section we will firstly describe the characteristics of the included papers.
+Next, we will present the identified factors that impact cooperation, that can be at the individual or at the group level.
 
@@
 
-The 89 included papers were published between 1984 and 2023, with a median of 2015.
++---------------------------+--------------+---------------+-------------+-------------------+---------------+--------+
+|                           | Experimental | Correlational | Qualitative | Literature review | Meta-analysis | Total  |
++---------------------------+--------------+---------------+-------------+-------------------+---------------+--------+
+| Lab-based social dilemmas | 52           | 7             | 1           | 7                 | 6             | 73     |
++---------------------------+--------------+---------------+-------------+-------------------+---------------+--------+
+| Lab-based commons         | 5            | 0             | 0           | 0                 | 0             | 5      |
++---------------------------+--------------+---------------+-------------+-------------------+---------------+--------+
+| Real-life social dilemmas | 2            | 5             | 0           | 0                 | 0             | 7      |
++---------------------------+--------------+---------------+-------------+-------------------+---------------+--------+
+| Real-life commons         | 0            | 3             | 0           | 1                 | 0             | 4      |
++---------------------------+--------------+---------------+-------------+-------------------+---------------+--------+
+| Total                     | 59           | 15            | 1           | 8                 | 6             | 89     |
++---------------------------+--------------+---------------+-------------+-------------------+---------------+--------+
+
+: Table 1. Description of the selected papers.
+
+Table 1 provides an overview of the 89 selected papers.
+The publication year ranges from 1984 to 2023, with a median of 2015.
 Almost all the selected texts were journal articles, with the only exception being a book chapter.
-Most of them were experimental studies (*N*=60), followed by literature review and meta-analysis (*N*=14) and correlative studies[^3] (*N*=14).
+Most of them were experimental studies (*N*=59), followed by correlative studies[^4] (*N*=14), and literature review and meta-analysis (*N*=14).
 The remaining paper was a qualitative study.
 
-[^3]: Studies where at least one variable is manipulated by researchers are part of the category "experimental studies", while "correlative studies" refers to papers using quantitative analysis, but without manipulations.
+[^4]: Studies where at least one variable is manipulated by researchers are part of the category "experimental studies", while "correlative studies" refers to papers using quantitative analysis, but without manipulations.
 
@@
 We identified two dimensions in the reviewed papers: setting (lab-based vs real-life) and context (social dilemma vs commons).
-There were papers in all four combinations of these dimentions, with the most represented category being "lab-based social dilemma" (*N*=75), namely highly controlled laboratory experiments where participants had to take cooperative decision.
+There were papers in all four combinations of these dimensions, with the most represented category being "lab-based social dilemma" (*N*=73).
+In these experiments, participants had to take cooperative decision in a highly controlled laboratory setting.
 This was followed by "real-life social dilemma" (*N*=7), which investigated cooperation in different real-life situations with a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998].
-Finally, "real-life commons" refers to studies of cooperation where participants were members of a commons in their everyday life, while "lab-based commons" refers to studies with a laboratory social dilemma paradigm, but with clear references to a concrete commons [e.g.
-@Mosler1993].
+Finally, "lab-based commons" (*N*=5) are studies with a laboratory social dilemma paradigm, but with clear references to a concrete commons [e.g.
+@Mosler1993], while "real-life commons" (*N*=4) refers to studies of cooperation where participants were members of a commons in their everyday life.
 
@@
 
-Finally, most of the studies were conducted in Europe (*N*=40) (especially in Germany (*N*=12) and in the Netherlands (*N*=8)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=7, of which *N*=6 in China).
+Most of the studies were conducted in Europe (*N*=40) (especially in Germany (*N*=12) and in the Netherlands (*N*=8)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=7, of which *N*=6 in China).
 Moreover, six studies were set in more than one country, and fourteen were meta-analysis or literature reviews.
@@
 
-A resume of the papers' description is provided in Table 1.
+### Operationalization of cooperation
 
-# Individual factors
+The way cooperation was operationalized was deeply connected to the study's setting.
+In fact, experiments based in laboratory often observed participants' distribution of resources between themselves and a group account to quantify their cooperation.
+The most used method (*N*=33) was to endow participants with an amount of a resource (often real or fictive money), and see which part they invested in a public account, from which the whole group could benefit.
+Otherwise, researchers observed which amount of the resource participants took for themselves from a collective pool (*N*=7), or how much they gave to an interaction partner (*N*=4).[^5] Another method often used in laboratory studies was to give participants the choice between cooperation and defection (*N*=18).
+Interestingly, in laboratory settings, words like "cooperation" or "defection" were rarely used during the instructions, to avoid responses dictated by social desirability.
+
+[^5]: The use of real money allowed to provide a real consequence for the decisions taken in the laboratory.
+For the same reason, the studies that used fictive money often informed participants that their final sum would be converted in real money at the end of the experiment.
+
+In studies with real-life settings, the operationalization of cooperation was more often based on observed behaviours (*N*=10).
+For instance, @Rompf2017 used the amount of recycling behaviours as proxy of cooperation, while in @VanLange1998 cooperation was the habits of taking public transports to commute.
+
+## Individual factors
 
 Our analysis identified five individuals factors that impact cooperation: gender, social status, group identification, values and personality traits, and trust.
-In the following sections, we describe their principal effects on cooperation, and provide an overview of the moderators of each effect.
-More details about moderators are included in Appendix A.
+In the following sections, we describe their principal effects on cooperation, and provide an overview of the moderators of each effect presented in the reviewed papers.
+A resume of the different individual factors is provided in Table 2, while more details about moderators are included in Appendix A.
 
-## Gender
+<!--# in the text: tables with the name of factor, the papers, the main effect and a list of moderatorsin Annexe: same table, but with more details for each moderator effect is it useful to put in both tables the analyzed papers for each factor?-->
+
++---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+| Individual factors                                            | Analyzed papers                                                                                                                                                                          | General effect on cooperation                                                                   | Moderators                                                       |
++===============================================================+==========================================================================================================================================================================================+=================================================================================================+==================================================================+
+| Gender                                                        | *N*=11\                                                                                                                                                                                  | Ambiguous                                                                                       | -   Other participants' characteristics                          |
+|                                                               | @Dorrough2019; @Peshkovskaya2017; @Balliet2011; @Spadaro2023; @Sell2009; @Gomez-Ruiz2020; @Colman2018; @Peshkovskaya2019; @Barrero-Amortegui2021; @Simpson2003; @Irwin2015               |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Group composition                                            |
+|                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Underlying motives                                           |
++---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+| Social status                                                 | *N*=6\                                                                                                                                                                                   | Ambiguous                                                                                       | -   Intra-class solidarity                                       |
+|                                                               | @Aksoy2019; @Kingsley2016; @VanLange2013; @Chen2022; @Camera2020; @VanKlingeren2021                                                                                                      |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Group composition                                            |
++---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+| Group identification                                          | *N*=14\                                                                                                                                                                                  | Strongly identified individuals cooperate more with the in-group than low-identified ones       | -   Individual contributions                                     |
+|                                                               | @Arora2016; @Noonan2016; @Gomez-Ruiz2020; @VanVugt2009; @Zhang2019; @Chen2007; @Wit1992; @Dorrough2015; @Aksoy2019; @Puurtinen2009; @Nockur2020; @Kramer1984; @Jackson2011; @Jackson2012 |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Intergroup competition                                       |
+|                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Super-ordinate identity                                      |
++---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+| Social Value Orientation and other values/personality factors | *N*=5 (SVO)\                                                                                                                                                                             | Pro-social individuals cooperate more than pro-self                                             | -   Incentives                                                   |
+|                                                               | @Balliet2009; @Emonds2011; @VanLange1998; @DeKwaadsteniet2008; @Lu2019                                                                                                                   |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          | Pro-environmental values are positively correlated to cooperation                               | -   Uncertainty about the number of members                      |
+|                                                               | *N*=9 (other factors)\                                                                                                                                                                   |                                                                                                 |                                                                  |
+|                                                               | @Sussman2016; @Fosgaard2019; @Kieslich2014; @Hilbig2018; @Kocher2017; @Schlosser2018; @Liu2009a; @Probst1999; @Chen2007                                                                  | Left-wingers are more cooperative than right-wingers                                            | -   Deliberation                                                 |
+|                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          | Individuals scoring high in humility and honesty cooperate more than those scoring low          | -   Inter- vs independent self                                   |
+|                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          | Individuals with high self-control, or with a high level of justice sensitivity, cooperate more | -   Perceived social norms                                       |
++---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+| Trust                                                         | *N*=10\                                                                                                                                                                                  | People with high levels of trust cooperate more than people with low levels                     | -   Degree of conflict between personal and collective interests |
+|                                                               | @Balliet2013; @Lubke2021; @VanLange2013; @Kocher2015; @Smith2013; @Chaudhuri2002; @Oyediran2018; @Sturm2019; @Franzen2019; @Rompf2017                                                    |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Uncertainty about others' intentions                         |
+|                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
+|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Perceived costs and benefits of the cooperative behaviour    |
++---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+
+: Table 2. Resume of individual factors.
+
+<!--# about Steffi's comment to first introduce the identified moderator effects and then give more details: since in the text I am not going to give a lot of details, wouldn't it be like a repetition?
+For instance:the following moderators are important: X, Y, Z.
+Men cooperate more when X, Y, while women cooperate more when Z -->
+
+### Gender
 
@@
 
-The effect of gender on cooperation is therefore subjected to several moderators, since the situation in which women and men interact is essential to determine which gender will cooperate more.
-For instance, men are more cooperative when they know other participants [@Peshkovskaya2017], when they feel part of a team [@Gomez-Ruiz2020] or when they interact repeatedly with the same group [@Balliet2011].
-The partners' gender is also an important moderator.
-Men-only groups are more cooperative than women-only [@Colman2018; @Peshkovskaya2019], while women cooperate more in mixed groups [@Balliet2011; @Peshkovskaya2019].
+The effect of gender on cooperation is therefore subjected to several moderators.
+For instance, men are more cooperative than women when they know other participants or can socialize before the cooperative interaction [@Peshkovskaya2017].
+Moreover, men, but not women, increased their cooperation when they feel part of a team [@Gomez-Ruiz2020], or when they interact repeatedly with the same group [@Balliet2011].
+
+Moreover, men-only groups are more cooperative than women-only [@Colman2018; @Peshkovskaya2019], while women cooperate more in mixed groups [@Balliet2011; @Peshkovskaya2019].
 In general, groups with a majority of women display the highest levels of cooperation [@Spadaro2023], even if this effect of group composition can be moderated by other factors [e.g.
 @Barrero-Amortegui2021].
-Moreover, men are more sensitive to greed incentives than women , and thus they cooperate less in situations with strong temptations to free-ride are present [@Simpson2003].
-On the other hand, women's principal motive in cooperative interaction is avoiding to be exploited, and that is why they cooperate less if they don't trust other participants or if they believe than others provide small contributions [@Irwin2015; @Dorrough2019].
+Finally, men are more sensitive to greed incentives than women , and thus they cooperate less in situations with strong temptations to free-ride are present [@Simpson2003].
+On the other hand, women are more sensitive to the fear of being exploited.
+In fact, their cooperation is linked to their trust in other participants [@Irwin2015; @Dorrough2019].
 
 Lastly, gender differences in cooperation could be partly explained by social status, where women represent the low-status group [@Sell2009].
-For this reason, it is important to gain insights into how social status impacts cooperation.
+For this reason, it is also important to gain insights into how social status impacts cooperation.
 
-## Social status
+<!--# Vincent's comment: Since Sell & Kuipers (2009) made a claim about social status (under the gender category) , I was expecting to see support or opposition to their claim.They did not really make a claim about an expected result, that is why I didn't start the following section with their citation -->
+
+### Social status
 
@@
 
-## Group identification
+### Group identification
 
 Social identity has a strong, positive effect on cooperation: the more individuals identify with a group, the more they cooperate with other members of the group [@VanVugt2009], for instance by providing more voluntary activities for the collective good [@Noonan2016].
-In fact, humans have a very developed sense of belonging, and when they strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they value more group-related goal [@Arora2016].
+In fact, humans have a very developed sense of belonging and, when they strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they value more group-related goal [@Arora2016].
 A strong identification also maintains high levels of cooperation over time [@Zhang2019].
-Finally, further confirmations of the strength of this effect are the fact that it is the same for individualist and collectivist people [@Chen2007] and that group identification can be easily implemented in a laboratory experiment and still have a strong effect on cooperation [@Wit1992].
+Finally, the strength of the effect of social identification on cooperation is further confirmed by two evidences.
+First, the effect is the same for individualist and collectivist people [@Chen2007]; secondly, inducing group identification needs only small nudges, and this does not diminish its effect [e.g.
+@Wit1992].
 
-In general, people cooperate more with other in-group than with out-group members [@Dorrough2015; @Aksoy2019], but the individual differences in the strength of identification can lead to inequalities in cooperation.
+In general, people cooperate more with in-group than with out-group members [@Dorrough2015; @Aksoy2019], but the individual differences in the strength of identification can lead to inequalities in cooperation.
 In fact, individuals who strongly identify with their group can even compensate, by cooperating more, for other in-group members' defection [@VanVugt2009; @Arora2016].
@@
 Finally, social identification can also moderate other factors' impact on the willingness to cooperate, such as monetary incentives [@VanVugt2009] or a previous group failure [@Jackson2011; @Jackson2012].
+In both cases, these factors have a bigger impact on the cooperativeness of low-identified individuals than of high-identified ones.
 
-## Values and personality traits
+### Values and personality traits
 
 Personal values and personality traits play an important role in predicting cooperative behaviour [@Hilbig2018].
-One of the most studied is the Social Value Orientation (SVO), that divides people in pro-social and pro-self based on how much they value their own and others' outcomes in situations of interdependence [@Balliet2009].
+One of the most studied is the Social Value Orientation (SVO), which allows to distinguish between individuals who prioritize their own interest ("pro-self") and those who prioritize the group's interest ("pro-social") [@Balliet2009].
 The effect of SVO on cooperation has been widely demonstrated: in a meta-analysis, 81 out of the 82 papers examined reported that pro-social cooperated significantly more than pro-self [@Balliet2009].
@@
 There are several moderators to this main effect.
-For instance, when economic incentives to cooperation are present, pro-self individuals attain a level of cooperation similar to pro-social's one [@Emonds2011; @Balliet2009].
-Similarly, in a study about commuting habits, the extent to which the cooperative behaviour (i.e.
-choosing to commute by public transportation or carpooling) was perceived as efficient impacted pro-self individual's decision more than pro-social's [@VanLange1998].
-Another moderator is the uncertainity about the group's size: if the uncerainty is high pro-social, but not pro-self, increse their level of cooperation [@DeKwaadsteniet2008].
+First, when economic incentives to cooperation are present, pro-self individuals attain a level of cooperation similar to pro-social's one [@Emonds2011; @Balliet2009].
+More generally, pro-self individuals value more the personal benefits of the cooperative behaviour than pro-social [@VanLange1998].
+A second moderator is the uncertainty about the group's size: if the uncertainty is high pro-social, but not pro-self, increase their level of cooperation [@DeKwaadsteniet2008].
 Finally, pro-self increase their cooperation if they have the possibility to deliberate about the situation [@Lu2019].
 
-Other studies also focused on how much people are self- or social-orientation impact cooperation by using other constructs.
+Other studies also focused on how people's self- or social-orientation impacts cooperation without directly measuring SVO.
 More cooperative individuals have an interdependent definition of the self [@Liu2009a] and see themselves as part of the group [@Probst1999].
@@
 
-## Trust and beliefs about others' contribution
+### Trust and beliefs about others' contributions
 
 Trust can be defined as the "expectations of others' benevolent motives in situations that involve a conflict between self and collective interests" [@Balliet2013, p.1].
-There are two categories of trust: first, dispositional trust is an individual general trait that can be assessed with a personality scale.
-Secondly, state trust is linked to the context and represent the expectations about a partner's behaviour in a specific situation [@Balliet2013].
+There are two categories of trust: first, dispositional trust is an individual, general trait that can be assessed with a personality scale.
+Second, state trust is linked to the context and represent the expectations about a partner's behaviour in a specific situation [@Balliet2013].
 The two are positively correlated [@Lubke2021], and both have a positive effect on cooperation [@VanLange2013; @Balliet2013].
-
 Several studies have confirmed this relationship.
@@
 The enhancing effect of trust on cooperation has also been demonstrated in real-life studies [see for example @Sturm2019; @Franzen2019].
-Finally, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
 
+Concerning moderation effects, trust matters more in situations involving a large, rather than small, conflict between personal and collective interests [@Balliet2013], and when people are uncertain about others' intentions [@VanLange2013].
 People can also display different levels of trust in the "reliability, effectiveness and legitimacy of public institutions" [@Rompf2017, p.
 2].
-Institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied motivates people to comply with norms.
+Institutional trust is associated with the probability of cooperating, because knowing that sanctions can be efficiently applied motivates people to comply with norms.
 
-# Organizational factors
+## Organizational factors
 
@@
 As for the individual factors, in the following sections we detail the main effects of each factor, and we provide an overview of possible moderators.
-More details can be found in Appendix A.
+A remsume of the main effects can be found in Table 3, while more details about the moderators in Appendix A.
 
-## Incentives
++-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+| Organizational factor | Analyzed papers                                                                 | General effect on cooperation                                                  | Moderators                                                    |
++=======================+=================================================================================+================================================================================+===============================================================+
+| Incentives            | *N*=18\                                                                         | Punishment and reward systems have a positive effect on cooperation            | -   Cost of implementation                                    |
+|                       | @Balliet2011a; @VanDijk2015; @Pfattheicher2018; @Nockur2021;                    |                                                                                |                                                               |
+|                       | @Egas2008; @Milinski2012; @Kingsley2016; @Chen2022; @Xiao2016; @Rockenbach2019; |                                                                                | -   Type of interaction                                       |
+|                       | @VanDijk2015; @VanVugt2009; @Schlosser2018; @Irwin2014; @Mulder2006;            |                                                                                |                                                               |
+|                       | @Jacquet2011; @Nelissen2013; @Maier-Rigaud2010                                  |                                                                                | -   Other participants' characteristics and group homogeneity |
+|                       |                                                                                 |                                                                                |                                                               |
+|                       |                                                                                 |                                                                                | -   Context                                                   |
+|                       |                                                                                 |                                                                                |                                                               |
+|                       |                                                                                 |                                                                                | -   Organization                                              |
+|                       |                                                                                 |                                                                                |                                                               |
+|                       |                                                                                 |                                                                                | -   Type of incentives                                        |
++-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+| Communication         | *N*=11\                                                                         | Having the possibility to communicate with other members increases cooperation | -   Group size                                                |
+|                       | @Balliet2010; @Bicchieri2002; @Janssen2014;                                     |                                                                                |                                                               |
+|                       | @Koessler2021; @Adams2022; @Hopthrow2005; @Kumakawa2013; @Torsvik2011;          |                                                                                | -   Type of communication                                     |
+|                       | @Feinberg2014; @Feinberg2012; @Giardini2021                                     |                                                                                |                                                               |
+|                       |                                                                                 |                                                                                | -   Content                                                   |
+|                       |                                                                                 |                                                                                |                                                               |
+|                       |                                                                                 |                                                                                | -   Timing                                                    |
++-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+| Social norms          | *N*=8\                                                                          | Cooperative social norms increase cooperation                                  | -   Anonymity                                                 |
+|                       | @VonBorgstede2018; @Thogersen2008; @Rege2004;                                   |                                                                                |                                                               |
+|                       | @Arora2012; @VanLange2013; @Bardsley2005a; @Weber2008; @Bicchieri2002           |                                                                                |                                                               |
++-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+| Anonymity             | *N*=10\                                                                         | Individuals cooperate more in non-anonymous situations than in anonymous ones  | -   Personal costs and benefits                               |
+|                       | @Wang2017; @Rege2004; @VanVugt2010a; @Butz2021;                                 |                                                                                |                                                               |
+|                       | @Romano2016; @VonBorgstede2018; @Jiang2021; @Mosler1993;                        |                                                                                |                                                               |
+|                       | @Przepiorka2020; @Koessler2021a                                                 |                                                                                |                                                               |
++-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
 
-Cooperation can be modified by introducing incentive systems, that can be either punishments or rewards.
-Both have a positive effect on cooperation [@Balliet2011a].
-However, some studies found that punishments are more efficient than rewards [e.g.
+: Table 3. Resume of organizational factors
+
+### Incentives
+
+Introducing a punishment or a reward system can increase cooperation [@Balliet2011a].
+Both system have a positive effect on cooperation, but it is not clear which one works better: some studies found that punishments are more efficient than rewards [e.g.
 @Milinski2012], while others came to the opposite conclusion [e.g.
 @Chen2022].
+In general, punishments have been more investigated than rewards [@VanDijk2015], and a possible explanation of their success is that, when a punishment system is present, participants perceive the situation as more fair [@Nockur2021].
 
-Several factors moderate the main effect of incentives on cooperation.
-A meta-analysis found that both rewards and punishments are more effective if their implementation is costly rather than free, and during iterated, rather than single, interactions [@Balliet2011a].
-Moreover, punishments work better in groups where all members have the same income [@Kingsley2016], because in heterogeneous groups a form of solidarity between low-status members arises and encourages free-riding [@Chen2022].
-Punishments are also more effective if participants are friends [@Balliet2011a] and when only cooperators have the power to punish defectors [@Xiao2016].
-Finally, the link between behaviour and outcome must be clear [@Xiao2016], and the punishment must have a significant consequence [@Egas2008].
+Several factors moderate the main effect of incentives[^6] on cooperation.
+For instance, they are more effective if their implementation is costly rather than free, and during iterated, rather than single, interactions [@Balliet2011a].
+Moreover, punishments work better in groups where all members have the same income [@Kingsley2016; @Chen2022], when participants are friends [@Balliet2011a], and when only cooperators have the power to punish defectors [@Xiao2016].
+Additionnally, the link between behaviour and outcome must be clear [@Xiao2016], and the punishments must have a significant consequence [@Egas2005].
+Finally, to be more effective, punishments should be applied with carefulness [@Rockenbach2019].
 
-In general, there are more studies on punishments than on rewards [@VanDijk2015].
-When a punishment system is present, participants' perceive the situation as more fair [@Nockur2021].
-However, punishments must be applied with carefulness.
-Ideally, groups should not punish in the early stages of the interaction, and have a norm of when and how to punish [@Rockenbach2019].
-Moreover, a punishment system could entail a second-order social dilemma, since cooperators are better-off by not investing resources into punishing, if all others do [@Milinski2012].
-Also, if there are no rules about who can punish, non-cooperators can punish cooperators as a form of retaliation [@Xiao2016; @VanDijk2015].
-A democratic punishment system, where a fine is given only if a majority agree, could solve this problem [@Pfattheicher2018].
+[^6]: "Incentives" is used when results apply to both punishments and rewards. Otherwise, the kind of system is explicitly mentioned.
 
@@
 Therefore, if they are removed, cooperation drops [@Irwin2014; @Mulder2006].
+Moreover, a punishment system could entail a second-order social dilemma, since cooperators are better-off by not investing resources into punishing, if all others do [@Milinski2012].
+A democratic punishment system, where a fine is given only if a majority agree, could solve this problem [@Pfattheicher2018].
 
@@
 An ostracism system where participants can vote to exclude other members is also very effective [@Maier-Rigaud2010].
-In conclusion, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
+Interestingly, social sanctions can be even more efficient than economic ones, because cooperation do not drop after their removal [@Nelissen2013].
 
-## Communication
+### Communication
 
 Communication between members has a general positive effect on cooperation [e.g.
-@Balliet2010], because it allows to shape a cooperative social norms [@Janssen2014; @Bicchieri2002] and to reach a consensus about the best strategy for the group [@Hopthrow2005].
-In fact, when communication is used to foster a common social identity, promote cooperative social norms and ensure that every member publicly commits, cooperation is higher [@Adams2022].
+@Balliet2010], because it allows to shape a cooperative social norm [@Janssen2014; @Bicchieri2002] and to reach an agreement about the best strategy for the group [@Hopthrow2005].
 
-Concerning the moderation effects, oral communication is more powerful than written messages, and communication has a stronger impact in large, rather than small, groups [@Balliet2010].
+Concerning the moderation effects, communication between members has a stronger impact in large, rather than small, groups, and oral communication is more powerful than written messages [@Balliet2010].
 Moreover, if communicating requires a personal cost, its effect is weaker than if communication is free [@Janssen2014].
-The content of the message is also essential: to be effective, communication must allow participants to become aware of the problem faced by the group, identify different strategies and agree on the one to use.
-In addition, casual chit-chat also plays a very important role in increasing cooperation [@Koessler2021].
-Finally, communication before or during the cooperative interaction have both a positive impact on cooperation [@Balliet2010], while knowing that it will be possible to communicate after the interaction does not enhance cooperation [@Kumakawa2013], and can even have a negative effect [@Torsvik2011].
+The content of the message is also essential: to be effective, communication must allow participants to become aware of the problem faced by the group, identify different solutions and agree on the one to adopt [@Koessler2021].
+Communication has also a stronger effect when it is used to foster a common social identity, promote cooperative social norms, and ensure that every member publicly commits [@Adams2022].
+Finally, communicating before or during the cooperative interaction has a positive impact on cooperation [@Balliet2010], while knowing that it will be possible to communicate after the interaction does not enhance cooperation [@Kumakawa2013], and can even have a negative effect [@Torsvik2011].
+
+<!--# Lilla's comment: or to have a good reputation in the gossip?
+Did the authors specifically find that it’s about not being a target?
+In the study, participants could decide to exclude a member of the group based on reputational information.
+The excluded member could not participate in the following round of the game, and therefore not gain.
+For this reason, in this specific study the issue was not to be the target of a negative gossip -->
 
@@
 
-## Social Norms
+### Social Norms
 
 Social norms can provide a guide on how to behave, especially when there is uncertainty about others' behaviour like in cooperative situations [@VonBorgstede2018].
-Both injunctive (what others approve) and descriptive (how others actually behave) norms impact cooperative behaviours [@Thogersen2008].
-Moreover, social norms help to maintain cooperation, because individuals who do not respect them are susceptible to social sanctions [@Rege2004].
-
+Both injunctive (what others approve of) and descriptive (how others actually behave) norms impact cooperative behaviours [@Thogersen2008].
 Social norms shape cooperation because, when taking a decision, people ask themselves: "What does a person like me do in a situation like this?" [@Arora2012].
@@
 
-Finally, social norms can be modified by participants' behaviour.
+The main moderator of this main effect is anonymity: if behaviours are observable, people comply more to social norms and, therefore, cooperate more [@Rege2004].
+Interestingly, social norms can be modified by participants' behaviour.
 For instance, the presence of consistent cooperators (i.e.
@@
 
-## Anonymity
+### Anonymity
 
@@
 
+<!--# Lilla's comment: could you give a number here?
+is small e.g.
++- 10 and large +- 100?Since it was an experiment, they used 2 as small and 20 as big, so I don't think that it is really relevant here?
+-->
+
 Therefore, reducing anonymity in cooperative interaction could significantly improve cooperation.
 A possible way to do this is to reduce the group's size, because larger groups lead to de-individuation and it is thus more difficult to identify defectors [@Romano2016].
-In fact, cooperation levels are higher in small, compared to large, groups [@Jiang2021].
+In fact, cooperation levels are higher in smaller, compared to larger, groups [@Jiang2021].
 Anonymity can also be reduced by making people publicly promise to cooperate.
@@
 
+<!--# Put principles in the same order as presented in the introduction -->
+
 Moreover, some of the factors can be related to Ostrom's principles to successfully manage a common resource [@Ostrom1990].
@@
 The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they worry about others' approval [@Nelissen2013; @Rege2004].
-On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^4]
+On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^7]
 
-[^4]: Principles 2, 7 and 8 refer to elements that are not pertinent to the current review, and therefore do not match any of the factors identified.
+[^7]: Principles 2, 7 and 8 refer to elements that are not pertinent to the current review, and therefore do not match any of the factors identified.
 

### 2024-01-05 scoping_review_short.Rmd
third version, 05.01

@@
 
+<!--# PROBLEM: all my research questions are about social dilemmas, and the idea was to use this litterature to better understand cooperation in commons, however I also included papers that studied commons (in the search, one of the key words was "commons" => solution (?): in the methods section say that I also included commons literature for X,Y reasons (more completeness?
+see the rapport between the amount of SD and commons studies?) -->
+
 # Methods
@@
 The most used method (*N*=33) was to endow participants with an amount of a resource (often real or fictive money), and see which part they invested in a public account, from which the whole group could benefit.
-Otherwise, researchers observed which amount of the resource participants took for themselves from a collective pool (*N*=7), or how much they gave to an interaction partner (*N*=4).[^5] Another method often used in laboratory studies was to give participants the choice between cooperation and defection (*N*=18).
+Otherwise, researchers observed which amount of the resource participants took for themselves from a collective pool (*N*=7), or how much they gave to another participant (*N*=4).[^5] Another method often used in laboratory studies was to give participants the choice between cooperation and defection (*N*=18).
 Interestingly, in laboratory settings, words like "cooperation" or "defection" were rarely used during the instructions, to avoid responses dictated by social desirability.
@@
 
-<!--# in the text: tables with the name of factor, the papers, the main effect and a list of moderatorsin Annexe: same table, but with more details for each moderator effect is it useful to put in both tables the analyzed papers for each factor?-->
+<!--# in the text: tables with the name of factor, the papers, the main effect and a list of moderatorsin Annexe: same table, but with more details for each moderator effect is it useful to put in both tables the analyzed papers for each factor?for the word count: useful to put all the authors just in the Annexe table, and in the text letting only N=11-->
 
@@
 | Gender                                                        | *N*=11\                                                                                                                                                                                  | Ambiguous                                                                                       | -   Other participants' characteristics                          |
-|                                                               | @Dorrough2019; @Peshkovskaya2017; @Balliet2011; @Spadaro2023; @Sell2009; @Gomez-Ruiz2020; @Colman2018; @Peshkovskaya2019; @Barrero-Amortegui2021; @Simpson2003; @Irwin2015               |                                                                                                 |                                                                  |
-|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Group composition                                            |
-|                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
+|                                                               | @Dorrough2019; @Peshkovskaya2017; @Balliet2011; @Spadaro2023; @Sell2009; @Gomez-Ruiz2020; @Colman2018; @Peshkovskaya2019; @Barrero-Amortegui2021; @Simpson2003; @Irwin2015               |                                                                                                 | -   Group composition                                            |
 |                                                               |                                                                                                                                                                                          |                                                                                                 | -   Underlying motives                                           |
@@
 | Social status                                                 | *N*=6\                                                                                                                                                                                   | Ambiguous                                                                                       | -   Intra-class solidarity                                       |
-|                                                               | @Aksoy2019; @Kingsley2016; @VanLange2013; @Chen2022; @Camera2020; @VanKlingeren2021                                                                                                      |                                                                                                 |                                                                  |
-|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Group composition                                            |
+|                                                               | @Aksoy2019; @Kingsley2016; @VanLange2013; @Chen2022; @Camera2020; @VanKlingeren2021                                                                                                      |                                                                                                 | -   Group composition                                            |
 +---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
 | Group identification                                          | *N*=14\                                                                                                                                                                                  | Strongly identified individuals cooperate more with the in-group than low-identified ones       | -   Individual contributions                                     |
-|                                                               | @Arora2016; @Noonan2016; @Gomez-Ruiz2020; @VanVugt2009; @Zhang2019; @Chen2007; @Wit1992; @Dorrough2015; @Aksoy2019; @Puurtinen2009; @Nockur2020; @Kramer1984; @Jackson2011; @Jackson2012 |                                                                                                 |                                                                  |
-|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Intergroup competition                                       |
-|                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
+|                                                               | @Arora2016; @Noonan2016; @Gomez-Ruiz2020; @VanVugt2009; @Zhang2019; @Chen2007; @Wit1992; @Dorrough2015; @Aksoy2019; @Puurtinen2009; @Nockur2020; @Kramer1984; @Jackson2011; @Jackson2012 |                                                                                                 | -   Intergroup competition                                       |
 |                                                               |                                                                                                                                                                                          |                                                                                                 | -   Super-ordinate identity                                      |
@@
 | Social Value Orientation and other values/personality factors | *N*=5 (SVO)\                                                                                                                                                                             | Pro-social individuals cooperate more than pro-self                                             | -   Incentives                                                   |
-|                                                               | @Balliet2009; @Emonds2011; @VanLange1998; @DeKwaadsteniet2008; @Lu2019                                                                                                                   |                                                                                                 |                                                                  |
-|                                                               |                                                                                                                                                                                          | Pro-environmental values are positively correlated to cooperation                               | -   Uncertainty about the number of members                      |
-|                                                               | *N*=9 (other factors)\                                                                                                                                                                   |                                                                                                 |                                                                  |
-|                                                               | @Sussman2016; @Fosgaard2019; @Kieslich2014; @Hilbig2018; @Kocher2017; @Schlosser2018; @Liu2009a; @Probst1999; @Chen2007                                                                  | Left-wingers are more cooperative than right-wingers                                            | -   Deliberation                                                 |
+|                                                               | @Balliet2009; @Emonds2011; @VanLange1998; @DeKwaadsteniet2008; @Lu2019                                                                                                                   |                                                                                                 | -   Uncertainty about the number of members                      |
+|                                                               |                                                                                                                                                                                          | Pro-environmental values are positively correlated to cooperation                               | -   Deliberation                                                 |
+|                                                               | *N*=9 (other factors)\                                                                                                                                                                   |                                                                                                 | -   Inter- vs independent self                                   |
+|                                                               | @Sussman2016; @Fosgaard2019; @Kieslich2014; @Hilbig2018; @Kocher2017; @Schlosser2018; @Liu2009a; @Probst1999; @Chen2007                                                                  | Left-wingers are more cooperative than right-wingers                                            | -   Perceived social norms                                       |
 |                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
-|                                                               |                                                                                                                                                                                          | Individuals scoring high in humility and honesty cooperate more than those scoring low          | -   Inter- vs independent self                                   |
+|                                                               |                                                                                                                                                                                          | Individuals scoring high in humility and honesty cooperate more than those scoring low          |                                                                  |
 |                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
-|                                                               |                                                                                                                                                                                          | Individuals with high self-control, or with a high level of justice sensitivity, cooperate more | -   Perceived social norms                                       |
+|                                                               |                                                                                                                                                                                          | Individuals with high self-control, or with a high level of justice sensitivity, cooperate more |                                                                  |
 +---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
 | Trust                                                         | *N*=10\                                                                                                                                                                                  | People with high levels of trust cooperate more than people with low levels                     | -   Degree of conflict between personal and collective interests |
-|                                                               | @Balliet2013; @Lubke2021; @VanLange2013; @Kocher2015; @Smith2013; @Chaudhuri2002; @Oyediran2018; @Sturm2019; @Franzen2019; @Rompf2017                                                    |                                                                                                 |                                                                  |
-|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Uncertainty about others' intentions                         |
-|                                                               |                                                                                                                                                                                          |                                                                                                 |                                                                  |
+|                                                               | @Balliet2013; @Lubke2021; @VanLange2013; @Kocher2015; @Smith2013; @Chaudhuri2002; @Oyediran2018; @Sturm2019; @Franzen2019; @Rompf2017                                                    |                                                                                                 | -   Uncertainty about others' intentions                         |
 |                                                               |                                                                                                                                                                                          |                                                                                                 | -   Perceived costs and benefits of the cooperative behaviour    |
@@
 
-## Organizational factors
+## Group factors
 
-On the organizational level, we identified four factors from the reviewed papers: incentives, communication, social norms and anonymity.
+On the group level, we identified four factors from the reviewed papers: incentives, communication, social norms and anonymity.
 As for the individual factors, in the following sections we detail the main effects of each factor, and we provide an overview of possible moderators.
@@
 
-+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
++-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
 | Organizational factor | Analyzed papers                                                                                                                                                                                                                                                  | General effect on cooperation                                                  | Moderators                                                    |
-+=======================+=================================================================================+================================================================================+===============================================================+
++=======================+==================================================================================================================================================================================================================================================================+================================================================================+===============================================================+
 | Incentives            | *N*=18\                                                                                                                                                                                                                                                          | Punishment and reward systems have a positive effect on cooperation            | -   Cost of implementation                                    |
-|                       | @Balliet2011a; @VanDijk2015; @Pfattheicher2018; @Nockur2021;                    |                                                                                |                                                               |
-|                       | @Egas2008; @Milinski2012; @Kingsley2016; @Chen2022; @Xiao2016; @Rockenbach2019; |                                                                                | -   Type of interaction                                       |
-|                       | @VanDijk2015; @VanVugt2009; @Schlosser2018; @Irwin2014; @Mulder2006;            |                                                                                |                                                               |
-|                       | @Jacquet2011; @Nelissen2013; @Maier-Rigaud2010                                  |                                                                                | -   Other participants' characteristics and group homogeneity |
-|                       |                                                                                 |                                                                                |                                                               |
+|                       | @Balliet2011a; @VanDijk2015; @Pfattheicher2018; @Nockur2021; @Egas2008; @Milinski2012; @Kingsley2016; @Chen2022; @Xiao2016; @Rockenbach2019; @VanDijk2015; @VanVugt2009; @Schlosser2018; @Irwin2014; @Mulder2006; @Jacquet2011; @Nelissen2013; @Maier-Rigaud2010 |                                                                                | -   Type of interaction                                       |
+|                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Other participants' characteristics and group homogeneity |
 |                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Context                                                   |
-|                       |                                                                                 |                                                                                |                                                               |
 |                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Organization                                              |
-|                       |                                                                                 |                                                                                |                                                               |
 |                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Type of incentives                                        |
-+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
++-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
 | Communication         | *N*=11\                                                                                                                                                                                                                                                          | Having the possibility to communicate with other members increases cooperation | -   Group size                                                |
-|                       | @Balliet2010; @Bicchieri2002; @Janssen2014;                                     |                                                                                |                                                               |
-|                       | @Koessler2021; @Adams2022; @Hopthrow2005; @Kumakawa2013; @Torsvik2011;          |                                                                                | -   Type of communication                                     |
-|                       | @Feinberg2014; @Feinberg2012; @Giardini2021                                     |                                                                                |                                                               |
+|                       | @Balliet2010; @Bicchieri2002; @Janssen2014; @Koessler2021; @Adams2022; @Hopthrow2005; @Kumakawa2013; @Torsvik2011; @Feinberg2014; @Feinberg2012; @Giardini2021                                                                                                   |                                                                                | -   Type of communication                                     |
 |                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Content                                                   |
-|                       |                                                                                 |                                                                                |                                                               |
 |                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Timing                                                    |
-+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
++-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
 | Social norms          | *N*=8\                                                                                                                                                                                                                                                           | Cooperative social norms increase cooperation                                  | -   Anonymity                                                 |
-|                       | @VonBorgstede2018; @Thogersen2008; @Rege2004;                                   |                                                                                |                                                               |
-|                       | @Arora2012; @VanLange2013; @Bardsley2005a; @Weber2008; @Bicchieri2002           |                                                                                |                                                               |
-+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+|                       | @VonBorgstede2018; @Thogersen2008; @Rege2004; @Arora2012; @VanLange2013; @Bardsley2005a; @Weber2008; @Bicchieri2002                                                                                                                                              |                                                                                |                                                               |
++-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
 | Anonymity             | *N*=10\                                                                                                                                                                                                                                                          | Individuals cooperate more in non-anonymous situations than in anonymous ones  | -   Personal costs and benefits                               |
-|                       | @Wang2017; @Rege2004; @VanVugt2010a; @Butz2021;                                 |                                                                                |                                                               |
-|                       | @Romano2016; @VonBorgstede2018; @Jiang2021; @Mosler1993;                        |                                                                                |                                                               |
-|                       | @Przepiorka2020; @Koessler2021a                                                 |                                                                                |                                                               |
-+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+|                       | @Wang2017; @Rege2004; @VanVugt2010a; @Butz2021; @Romano2016; @VonBorgstede2018; @Jiang2021; @Mosler1993; @Przepiorka2020; @Koessler2021a                                                                                                                         |                                                                                |                                                               |
++-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
 
@@
 The aim of the present paper was to synthesize the existing literature about cooperation in social dilemmas, in order to identify factors that could impact cooperative behaviours in commons.
-Through a scoping review approach, we identified nine factors, both at the individual and group level.
-Our results seem to be in line with others findings about cooperation in commons.
-For instance, factors such as gender, social status, SVO, incentives, and communication were also found by @Kopelman2002 in their review about lab-based commons, and their effects were the same as the ones reported in the current paper.
+More specifically, we aimed at identifying factors at the individual and group level that affect people's cooperation, as well as the moderating effects existing between them.
+Through a scoping review approach, we identified five individual, and four group factors.
 
-<!--# Put principles in the same order as presented in the introduction -->
+<!--# in general I have some doubts about the order: what I did now is to follow the order of the research questions, namely: individual, group, moderationsHowever, I could not "include" the individual factors on the theories used in the introduction, while the group factors fit well in Ostrom principles.
+I find therefore strange to start from the factors that are less linked to the previous theories.
+At the same time it is normal that I did not find a lot of theories on individual factors for the introduction, because that's the gap that I foundSO: maybe it could be useful to change the order of the research questions and of the results?
+-->
 
-Moreover, some of the factors can be related to Ostrom's principles to successfully manage a common resource [@Ostrom1990].
-For instance, the clearly defined boundaries can strengthen commoners' social identification, since only when an in- and an out-group exist social identity is salient and therefore an identification is possible [@Tajfel1974].
-Even if Ostrom developed this principle on a more organizational level, its secondary effect of creating a social identity can also contribute to improve cooperation.
-Secondly, communication is essential for the principle about the creation and modification of norms [@Bicchieri2002], and for the one about the arenas to solve conflicts.
-Finally, the principles concerning the monitoring and the graduated sanction systems underline the importance of incentives.
-The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they worry about others' approval [@Nelissen2013; @Rege2004].
-On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^7]
+## Individual factors
 
-[^7]: Principles 2, 7 and 8 refer to elements that are not pertinent to the current review, and therefore do not match any of the factors identified.
+<!--# discussion with Steffi: since in the introduction I did not use any theory to explain the specific individual and group factors that I found (I still didn't know what I was going to find), I used some new theories in the discussion to show that my results make sense -->
 
-Ostrom's principles are especially related to factors at the organizational level.
-This is understandable when considering her economic approach to the study of the commons.
-However, taking into account the social dynamics and the characteristics of the commoners is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011].
-For this reason, this paper went a step further and identified five individual characteristics affecting the efficiency of commons.
-Although less studied in commons literature, these individual factors are consistent with existing theories.
+The factors on the individual level were: gender, social status, social identification, SVO and other values and personality traits, and trust.
+In the following paragraph we will discuss their effects on cooperation, and the implications for the study of commons.
 
-First, the reported positive effects of trust on cooperation is explained through the principle of reciprocity, that posits that individuals cooperate more facing cooperative partners [@Fehr2002; @VanLange1999].
+First, the reviewed results about gender did not provide a clear conclusion about its effect on cooperation.
+A possible explanation is that every experimental paradigm can trigger differently the participants' gender identity [@Sell2009], and this impacts the way in which they decide to behave.
+Gender effect on cooperation is therefore very dependent on the context.
+For instance, factors such as other participants' gender, or the overall group composition determine whether men or women are more cooperative.
+For this reason, when studying commoners' cooperation, it is essential to take into account the effects that gender could have.
+
+The second identified factors is social status, and, once again, we obtained contradictory findings about its effect on cooperation.
+However, our analysis revealed that members of low-status groups show solidarity with other low-status individuals, while this does not happen in high-status groups.
+This is consistent with the existing literature on social status.
+First, there are structural differences between high- and low-status group's dynamic, that make high-status members more individualistic than low-status [@Lorenzi-Cioldi2002].
+Second, high-status individuals display more system justification (i.e.
+they perceive the social system as fair) and more Social Dominance Orientation (i.e.
+they have a preference for inequality between social groups) than low-status [@Caricati2012; @Vargas-Salfate2018].
+This is negatively correlated with concern about others and altruism [@Pratto1994].
+For this reason, social status must also be taken into account when investigating cooperation, since the solidarity dynamics described above influence individuals' behaviours.
+
+Third, we found a strong positive effect of social identification: the more individuals identify with their group, the more they are likely to act for the group's good.
+<!--# question: when I recall results in the discussion, do I need to put again the citations?
+--> This is in line with the Social Identity Theory [@Tajfel1974], which posits that people's identity is also composed by their group affiliations.
+Therefore, the strongest the identification with a group, the more personal interests are aligned with group's ones.
+Also, within a social group, individuals perceive themselves as more similar to other members, and therefore they are more susceptible to adopt collective goals and behaviours [@Turner1984; @Fritsche2018].
+Thus, for a group's success, its members' identification is essential: for instance, strongly identified individuals are less likely to leave a group in case of failure or difficulties [@Ellemers1997].
+Given its importance, strengthen the commoners' social identification could significantly improve their cooperation for the commons' good.
+Moreover, priming a common social identity is quite simple [e.g.
+@Kramer1984; @Zhang2019]: therefore, this could allow to enhance cooperation in an easy and cheap way.
+
+Fourth, Social Value Orientation also impacts cooperation.
+More specifically, individuals with a pro-social orientation cooperate more than those pro-self oriented.
+In fact, pro-social value more equality in outcomes, while for pro-self is the personal gain which is more important [@VanLange1999].
+In addition to SVO, there are other values and personality traits which impact cooperation, such as political orientation, justice sensitivity, and self-control.
+Interestingly, although personality trait are usually stable, it is possible to modify values and attitudes, for example by making the participant elaborate about them [@Petty1995].
+This technique could therefore be used to improve cooperation in commons.
+
+The last individual factor, trust, has also a clear effect on cooperation: the more individuals trust other members, the more they cooperate.
+This effect is explained through the principle of reciprocity,<!--# Lilla: reciprocity is problematic because I never mention it in the results, and that I should add it as explanation.
+However, in the results part I mentioned only what came out of the papers, and explications are included only if mentioned in one of the papers--> that posits that individuals cooperate more facing cooperative partners [@Fehr2002; @VanLange1999].
 Since in real-life situations it is not always possible to know exactly others' willingness to contribute, trust (i.e.
 beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012].
-Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can be successful.
+For this reason, improving reciprocal trust between members of a commons can be a powerful tool to enhance cooperation.
 
-Secondly, the influence of SVO on cooperation is due to the difference between pro-social and pro-self in the importance accorded to the relative benefits.
-More specifically, pro-social value more others' outcome and equality in outcomes than pro-self [@VanLange1999].
-Moreover, the difference in weights accorded to the personal and others' outcome seem to be the only dissimilarity between pro-social and pro-self, because they process the cooperative interaction in the same way [@Fiedler2013].
+In conclusion, individuals factors have a great impact on cooperation, although, to the best of our knowledge, just a few papers investigated them in the commons literature [e.g.
+@Nightingale2011; @Singh2017].
+This scoping review contributed to this trend, showing that we cannot assume that, in a same situation, everybody behaves in the same way.
+Therefore, an individual-centered approach can provide great insights into cooperation in commons.
 
-The reviewed results did not provide a clear conclusion about gender effect on cooperation.
-However, existing theories would predict that women cooperate more than men, because, according to gender stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012].
-In fact, groups partly composed by women display more solidarity and collaboration than all-men groups [@Westermann2005].
-However, every experimental paradigm can trigger the participants' gender identity differently [@Sell2009], and for this reason this effect is subjected to several moderators.
+## Group factors
 
-Concerning social status, the analyzed studies showed that usually members of low-status groups cooperated more and showed more solidarity with others low-status members than high-status.
-Although this effect has not been extensively studied, these results seem to be consistent with the existing literature on social status.
-First, there are structural differences between high- and low-status group's dynamic, that make high-status members more individualistic than low-status [@Lorenzi-Cioldi2002].
-High-status individuals also display more system justification and more Social Dominance Orientation than low-status [@Caricati2012; @Vargas-Salfate2018]: they see the social system as fair and they have a preference for inequality between social groups.
-This is negatively correlated with concern about others and altruism [@Pratto1994].
+<!--# I put the principle in the same order as they are presented in the introduction, but I wonder if it is not better to follow the order of presentation of the different factors as I did in the previous section?
+-->
 
-The last individual factor was group identification, and the reviewed results showed that the more individuals identify with their group, the more they are likely to act for the group's good.
-In fact, according to the Social Identity Theory, people's identity is also composed by their group affiliations, and the stronger they identify with a social group, the more important this group becomes for their identity and the more their personal interests aligns with group's ones [@Tajfel1974].
-Also, within a social group, individuals perceive themselves as more similar to other members, and therefore they are more susceptible to adopt collective goals and behaviours [@Turner1984; @Fritsche2018].
-Moreover, strongly identified people are less likely to leave a group in case of failure or difficulties [@Ellemers1997].
-Thus, a strong identification is essential for a group's success.
-In-group identification is also essential to engage in collective actions [@VanZomeren2008], and it is the main predictor of pro-environmental actions in the Social Identity Model of Pro-Environmental Action [SIMPEA, @Fritsche2018].
+We identified four factors at the group level: incentives, communication, social norms, and anonymity.
+This factors will be discussed within Ostrom's seven design principles for a successful management of a common-pool resource [-@Ostrom1990].
+Moreover, we will address their implications for the study of commons.
 
-## Factors' interactions
+Ostrom's first principle about the need of clearly defined boundaries is linked to anonymity, since to define who has and who hasn't access to the resource commoners have to know each-other.
+Moreover, communication is also important to reach an agreement on the exact boundaries of the shared resource.
+The second and third principles posit that rules must be adapted to the resource condition, and that commoners must be able to participate in modifying them.
+What Ostrom calls "rules" is very close to social norms, and, once again, communication is essential to shape and adapt them according to the condition of the resource.
+The fourth and fifth principles are about a monitoring and a graduate sanction system, and they underline the importance of incentives, that can be both social or material.
+In fact, a monitor that discovers an infraction gains prestige by being a good member of the commons, while the rule-breaker loses it.
+At the same time, the monitor can often keep a portion of the violator's harvest.
+Moreover, these two systems discourage free-riding because commoners know that their actions can be observed by others.
+Finally, the sixth principle about arenas for conflict resolution is linked to communication.[^7]
 
-Until now, the identified factors have been discussed separately.
-However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.
+[^7]: Since Ostrom's seventh principle concerns external authorities and institutions, the current scoping review did not find any evidence in its support.
+
+The main implication of these results is that a classical work of commons literature, as it is Ostrom's seminal book, is confirmed with findings coming from other disciplines and (mostly) from experimental studies.
+This shows that integrating this approach on the study of cooperation in commons is pertinent, and can give additional interesting insights on the topic.
+
+## Moderation effects between factors
+
+<!--# mention the main factors identified? in that case, reformulate to have the main ones as main subject of each paragraph -->
+
+Until now, the identified factors have been discussed separately. However, their impacts are often interconnected. In this section, we will show how they are linked to each other.
+
 For instance, there are gender differences in trust and SVO: trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019], and women are more prevalent between pro-social and less between pro-self [@VanLange1999].
@@
 Therefore, pro-self individuals show less cooperation in part because they expect others not to cooperate.
+
+<!--# in the precent version I did not have a specific research question about how factors are connected to each-other, so this part fitted well: I took the results and completed them with related literatureHowever, now that I do have a research question about the moderation, it feels strange to add new results in this part.
+Should I take here only the moderation effects identified in the results section?
+Or maybe should I start from what I found to further develop on other moderators?
+-->
 
@@
 At the same time, group identification also moderates other effects.
-First, as a consequence of the Social Identity Theory, high-identified individuals are more willing to comply to the group's norms and to pursue the group's goal [@Tajfel1974].
+First, consistent with the Social Identity Theory, high-identified individuals are more willing to comply to the group's norms and to pursue the group's goal [@Tajfel1974].
 Therefore, they need less cooperation-enhancing measures such as incentives [@VanVugt2009] or non-anonymous conditions [@Barreto2000].
@@
 
-## Theoretical implications
+The fact that factors are connected to each other means that their effect on cooperation can be either direct or indirect, via the moderation of other factors.
+This has important practical implications: first, it shows that, when implementing a strategy aimed at improving cooperation in commons, not all the factors need to be explicitly addressed.
+For instance, encouraging participants to communicate also improves their mutual trust, helps them to shape social norms, and increases their identification in the group.
+Second, these connections allow us to identify four central factors, namely trust, communication, group identification and anonymity.
+These "core" elements can be used as starting point for future researches about cooperation in commons, as well as for behavioural interventions to improve cooperation.
+On the theoretical level, the fact that individual and group factors are linked shows that integrating an individual perspective to the commons literature is important, and it can contribute to gain a better understanding of why people do (not) cooperate in commons.
 
-The analyzed papers showed that people often cooperate.
-This contradicts the Rational Choice Theory (RCT), who posits that individuals are too self interested to sacrifice their personal benefit to the greater good, unless if forced to do so.
-Our general results are therefore consistent with the existing literature, since RCT has already been refuted by experimental studies, who demonstrated that cooperation was higher than predicted in social dilemmas, and that it was impacted by variables that should not play a role according to this theory [@Ostrom1998].
+# Conclusions, limitations and future perspectives
 
-Moreover, this review also corroborated the lack of quantitative studies about cooperation in real-life commons: of the 89 analyzed papers, just three had these characteristics, and they all were correlative.
+Beyond the specific factors, this review showed that people often cooperate.
+This contradict Hardin's [-@Hardin1968] assumptions that rational individuals are too self-interested to cooperate in a situation where individual and group interests are at odds.
+Our results are therefore consistent with the existing literature, namely with theories such as the Greed Efficience Fairness Hypothesis [@Wilke1991], the Humanistic Rational Choice Theory [@DeCaro2021], or the theory of competitive altruism [@Roberts1998], which posit that cooperation is possible.
+Moreover, several experimental studies have already demonstrated that cooperation was higher than predicted in social dilemmas, and that it was impacted by variables that should not play a role from a rational point of view [@Ostrom1998].
+
+Moreover, this review made an important contribution to the study of commons through social dilemma experiments.
+In fact, previous studies using the same approach focused either on a specific commons [e.g.
+@Hartl2022] or on a specific discipline [@Kopelman2002].
+We extended these results by studying cooperation in general, and by not excluding any scientific field.
+
+Third, we also identify a lack of quantitative studies about cooperation in real-life commons: of the 89 analyzed papers, just three had these characteristics, and they all were correlative.
 Therefore, they could not draw a causal link between the investigated factors and cooperative behaviours.
@@
 
-## Practical implications
-
-This review can be used as a guide for commons members to design campaigns or activities to improve cooperation.
-In fact, some of the identified factors can be manipulated in order to create better conditions for cooperation to arise.
-Moreover, since the different elements are linked, they can impact cooperation both directly and indirectly, via mediation or moderation effects.
-Based on the quantity of connections with other elements, the factors that seem to have a stronger effect are trust, communication, group identification and accountability of actions.
-Therefore, interventions based on this elements can be very powerful tools to improve cooperation in commons.
-On the other hand, some individual factor cannot be manipulated, but must be taken into account when designing an intervention.
-For instance, commons' composition in terms of gender and social status can have a large influence on the overall cooperation.
-
-# Limitations and future perspectives
-
-To conclude, this review summarized existing researches about cooperation in social dilemmas, and therefore provided a set of factors that can help better understanding cooperative behaviours in commons.
-It also highlighted a lack of quantitative studies about this topic in real-life commons.
-It is, however, not without limitations.
-
+Concerning the review's limitations, we could identify three.
 First, there is a lack of representation of the global population.
-In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Global North.
-The current results apply therefore to Western societies and should not be generalized to Global South.
+In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from occidental countries.
+The current results apply therefore to Western societies and should not be generalized to other cultures.
 In fact, there are cultural differences in individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989].
@@
 @Kuwabara2014].
-It is therefore likely that cooperation relies on different mechanisms in Global South and North: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.
+It is therefore likely that, in different cultures, cooperation relies on different mechanisms: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.
 
-Moreover, our aim was to use results of social dilemma researches to gain a better understanding of commons, therefore most of the included studies had a laboratory setting.
+Secondly, our aim was to use results of social dilemma researches to gain a better understanding of commons, therefore most of the included studies had a laboratory setting.
 In fact, this kind of setting is very useful to study social dilemmas because it provides a standard paradigm [@Balliet2011].
-However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and specific ecological conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015].
+However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and specific conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015].
 Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings.

### 2024-01-08 scoping_review_short.Rmd
final 3rd version - 08.01.24

@@
 commoning) [@Bollier2014].
-For this reason, it is essential to have a closer look at the individuals who are part of commons.
+It is therefore essential to have a closer look at the individuals who are part of commons.
 
@@
 For this reason, the current scoping review is aimed at gaining insight into cooperation in commons through social dilemma literature.
-In the next section, we give an overview about the existing research about cooperation in commons, afterwards we will detail the research questions.
+In the next section, we will give an overview about the existing research about cooperation in commons, afterwards we will detail the research questions.
 
@@
 
-However, research in different disciplines has convincingly demonstrated that people can engage in collective actions to sustainably manage shared resources, thus falsifying Hardin's predictions [@Poteete2010a].
-Among these studies, the most important is Elinor Ostrom's seminal work [-@Ostrom1990], where she studied several real-life commons, some of them successfully managed by the community of users without the intervention of an external authority.
+However, research in different disciplines has often obtained opposite findings, namely that people can engage in collective actions to sustainably manage shared resources [@Poteete2010a].
+Among these researches, the most important is Elinor Ostrom's seminal work [-@Ostrom1990], where she studied several real-life commons, some of them successfully managed by the community of users without the intervention of an external authority.
 Based on her observations, she established seven design principles that are present in all the successful commons, plus an eighth one for more complex cases.[^2]
@@
 The fourth and fifth principles concern a monitoring and a graduate sanction system.
-Interestingly, these systems are successfully implemented by commoners themselves, with no need of an external institution.
+Interestingly, these systems are successfully implemented by commoners themselves, with no need for an external institution.
 In fact, in order to know that the best strategy is to follow the rules, one must be sure that the others are also complying to them.
@@
 
-Secondly, on the experimental level, the laboratory study of social dilemmas also largely contributed to the investigation of cooperation, by identifying several factors that impact it [e.g.
+Secondly, on the experimental level, the laboratory study of social dilemmas largely contributed to the investigation of cooperation, by identifying several factors that impact it [e.g.
 @VanLange2013].
@@
 
-Based on this evidence, the current paper synthesizes existing research about cooperation in social dilemmas, to provide a set of factors that impact cooperative behaviours in commons.
+Based on this evidence, the current paper synthesizes existing research about cooperation in social dilemmas, and provides a set of factors that impact cooperative behaviours in commons.
 This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation beyond artificial laboratory settings.
@@
 <!--# PROBLEM: all my research questions are about social dilemmas, and the idea was to use this litterature to better understand cooperation in commons, however I also included papers that studied commons (in the search, one of the key words was "commons" => solution (?): in the methods section say that I also included commons literature for X,Y reasons (more completeness?
-see the rapport between the amount of SD and commons studies?) -->
+see the rapport between the amount of SD and commons studies?)or, in your opinion, this doesn't cause any problem on the logic of the paper?
+-->
 
@@
 However, the title already informed us that it would not allow us to answer the research questions.
-
-<!--# add somewhere that qualitative studies are ok? -->
 
@@
 Our analysis identified five individuals factors that impact cooperation: gender, social status, group identification, values and personality traits, and trust.
-In the following sections, we describe their principal effects on cooperation, and provide an overview of the moderators of each effect presented in the reviewed papers.
+In the following sections, we describe their main effects on cooperation, and provide an overview of the moderators of each effect presented in the reviewed papers.
 A resume of the different individual factors is provided in Table 2, while more details about moderators are included in Appendix A.
 
-<!--# in the text: tables with the name of factor, the papers, the main effect and a list of moderatorsin Annexe: same table, but with more details for each moderator effect is it useful to put in both tables the analyzed papers for each factor?for the word count: useful to put all the authors just in the Annexe table, and in the text letting only N=11-->
-
-+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
++---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
 | Individual factors                                            | Analyzed papers       | General effect on cooperation                                                                   | Moderators                                                       |
-+===============================================================+==========================================================================================================================================================================================+=================================================================================================+==================================================================+
-| Gender                                                        | *N*=11\                                                                                                                                                                                  | Ambiguous                                                                                       | -   Other participants' characteristics                          |
-|                                                               | @Dorrough2019; @Peshkovskaya2017; @Balliet2011; @Spadaro2023; @Sell2009; @Gomez-Ruiz2020; @Colman2018; @Peshkovskaya2019; @Barrero-Amortegui2021; @Simpson2003; @Irwin2015               |                                                                                                 | -   Group composition                                            |
++===============================================================+=======================+=================================================================================================+==================================================================+
+| Gender                                                        | *N*=11                | Ambiguous                                                                                       | -   Other participants' characteristics                          |
+|                                                               |                       |                                                                                                 | -   Group composition                                            |
 |                                                               |                       |                                                                                                 | -   Underlying motives                                           |
-+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
++---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
 | Social status                                                 | *N*=6\                | Ambiguous                                                                                       | -   Intra-class solidarity                                       |
-|                                                               | @Aksoy2019; @Kingsley2016; @VanLange2013; @Chen2022; @Camera2020; @VanKlingeren2021                                                                                                      |                                                                                                 | -   Group composition                                            |
-+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+|                                                               |                       |                                                                                                 | -   Group composition                                            |
++---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
 | Group identification                                          | *N*=14\               | Strongly identified individuals cooperate more with the in-group than low-identified ones       | -   Individual contributions                                     |
-|                                                               | @Arora2016; @Noonan2016; @Gomez-Ruiz2020; @VanVugt2009; @Zhang2019; @Chen2007; @Wit1992; @Dorrough2015; @Aksoy2019; @Puurtinen2009; @Nockur2020; @Kramer1984; @Jackson2011; @Jackson2012 |                                                                                                 | -   Intergroup competition                                       |
+|                                                               |                       |                                                                                                 | -   Intergroup competition                                       |
 |                                                               |                       |                                                                                                 | -   Super-ordinate identity                                      |
-+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
-| Social Value Orientation and other values/personality factors | *N*=5 (SVO)\                                                                                                                                                                             | Pro-social individuals cooperate more than pro-self                                             | -   Incentives                                                   |
-|                                                               | @Balliet2009; @Emonds2011; @VanLange1998; @DeKwaadsteniet2008; @Lu2019                                                                                                                   |                                                                                                 | -   Uncertainty about the number of members                      |
-|                                                               |                                                                                                                                                                                          | Pro-environmental values are positively correlated to cooperation                               | -   Deliberation                                                 |
-|                                                               | *N*=9 (other factors)\                                                                                                                                                                   |                                                                                                 | -   Inter- vs independent self                                   |
-|                                                               | @Sussman2016; @Fosgaard2019; @Kieslich2014; @Hilbig2018; @Kocher2017; @Schlosser2018; @Liu2009a; @Probst1999; @Chen2007                                                                  | Left-wingers are more cooperative than right-wingers                                            | -   Perceived social norms                                       |
++---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+| Social Value Orientation and other values/personality factors | *N*=5 (SVO)           | Pro-social individuals cooperate more than pro-self                                             | -   Incentives                                                   |
+|                                                               |                       |                                                                                                 | -   Uncertainty about the number of members                      |
+|                                                               | *N*=9 (other factors) | Pro-environmental values are positively correlated to cooperation                               | -   Deliberation                                                 |
+|                                                               |                       |                                                                                                 | -   Inter- vs independent self                                   |
+|                                                               |                       | Left-wingers are more cooperative than right-wingers                                            | -   Perceived social norms                                       |
 |                                                               |                       |                                                                                                 |                                                                  |
@@
 |                                                               |                       | Individuals with high self-control, or with a high level of justice sensitivity, cooperate more |                                                                  |
-+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
-| Trust                                                         | *N*=10\                                                                                                                                                                                  | People with high levels of trust cooperate more than people with low levels                     | -   Degree of conflict between personal and collective interests |
-|                                                               | @Balliet2013; @Lubke2021; @VanLange2013; @Kocher2015; @Smith2013; @Chaudhuri2002; @Oyediran2018; @Sturm2019; @Franzen2019; @Rompf2017                                                    |                                                                                                 | -   Uncertainty about others' intentions                         |
++---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
+| Trust                                                         | *N*=10                | People with high levels of trust cooperate more than people with low levels                     | -   Degree of conflict between personal and collective interests |
+|                                                               |                       |                                                                                                 | -   Uncertainty about others' intentions                         |
 |                                                               |                       |                                                                                                 | -   Perceived costs and benefits of the cooperative behaviour    |
-+---------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
++---------------------------------------------------------------+-----------------------+-------------------------------------------------------------------------------------------------+------------------------------------------------------------------+
 
@@
 As for the individual factors, in the following sections we detail the main effects of each factor, and we provide an overview of possible moderators.
-A remsume of the main effects can be found in Table 3, while more details about the moderators in Appendix A.
+A resume of the main effects is provided in Table 3, while more details about the moderators in Appendix A.
 
-+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
++-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
 | Organizational factor | Analyzed papers | General effect on cooperation                                                  | Moderators                                                    |
-+=======================+==================================================================================================================================================================================================================================================================+================================================================================+===============================================================+
-| Incentives            | *N*=18\                                                                                                                                                                                                                                                          | Punishment and reward systems have a positive effect on cooperation            | -   Cost of implementation                                    |
-|                       | @Balliet2011a; @VanDijk2015; @Pfattheicher2018; @Nockur2021; @Egas2008; @Milinski2012; @Kingsley2016; @Chen2022; @Xiao2016; @Rockenbach2019; @VanDijk2015; @VanVugt2009; @Schlosser2018; @Irwin2014; @Mulder2006; @Jacquet2011; @Nelissen2013; @Maier-Rigaud2010 |                                                                                | -   Type of interaction                                       |
++=======================+=================+================================================================================+===============================================================+
+| Incentives            | *N*=18          | Punishment and reward systems have a positive effect on cooperation            | -   Cost of implementation                                    |
+|                       |                 |                                                                                | -   Type of interaction                                       |
 |                       |                 |                                                                                | -   Other participants' characteristics and group homogeneity |
@@
 |                       |                 |                                                                                | -   Type of incentives                                        |
-+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
-| Communication         | *N*=11\                                                                                                                                                                                                                                                          | Having the possibility to communicate with other members increases cooperation | -   Group size                                                |
-|                       | @Balliet2010; @Bicchieri2002; @Janssen2014; @Koessler2021; @Adams2022; @Hopthrow2005; @Kumakawa2013; @Torsvik2011; @Feinberg2014; @Feinberg2012; @Giardini2021                                                                                                   |                                                                                | -   Type of communication                                     |
++-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+| Communication         | *N*=11          | Having the possibility to communicate with other members increases cooperation | -   Group size                                                |
+|                       |                 |                                                                                | -   Type of communication                                     |
 |                       |                 |                                                                                | -   Content                                                   |
 |                       |                 |                                                                                | -   Timing                                                    |
-+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
-| Social norms          | *N*=8\                                                                                                                                                                                                                                                           | Cooperative social norms increase cooperation                                  | -   Anonymity                                                 |
-|                       | @VonBorgstede2018; @Thogersen2008; @Rege2004; @Arora2012; @VanLange2013; @Bardsley2005a; @Weber2008; @Bicchieri2002                                                                                                                                              |                                                                                |                                                               |
-+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
-| Anonymity             | *N*=10\                                                                                                                                                                                                                                                          | Individuals cooperate more in non-anonymous situations than in anonymous ones  | -   Personal costs and benefits                               |
-|                       | @Wang2017; @Rege2004; @VanVugt2010a; @Butz2021; @Romano2016; @VonBorgstede2018; @Jiang2021; @Mosler1993; @Przepiorka2020; @Koessler2021a                                                                                                                         |                                                                                |                                                               |
-+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
++-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+| Social norms          | *N*=8           | Cooperative social norms increase cooperation                                  | -   Anonymity                                                 |
++-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
+| Anonymity             | *N*=10          | Individuals cooperate more in non-anonymous situations than in anonymous ones  | -   Personal costs and benefits                               |
++-----------------------+-----------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+
 
@@
 
-### Social Norms
+### Social norms
 
@@
 The second identified factors is social status, and, once again, we obtained contradictory findings about its effect on cooperation.
-However, our analysis revealed that members of low-status groups show solidarity with other low-status individuals, while this does not happen in high-status groups.
+At the same time, our analysis revealed that members of low-status groups show solidarity with other low-status individuals, while this does not happen in high-status groups.
 This is consistent with the existing literature on social status.
@@
 Moreover, priming a common social identity is quite simple [e.g.
-@Kramer1984; @Zhang2019]: therefore, this could allow to enhance cooperation in an easy and cheap way.
+@Kramer1984; @Zhang2019]: this could allow to enhance cooperation in an easy and cheap way.
 
@@
 In addition to SVO, there are other values and personality traits which impact cooperation, such as political orientation, justice sensitivity, and self-control.
-Interestingly, although personality trait are usually stable, it is possible to modify values and attitudes, for example by making the participant elaborate about them [@Petty1995].
+Interestingly, although personality traits are usually stable, it is possible to modify values and attitudes, for example by making the participant elaborate about them [@Petty1995].
 This technique could therefore be used to improve cooperation in commons.
@@
 
-<!--# in the precent version I did not have a specific research question about how factors are connected to each-other, so this part fitted well: I took the results and completed them with related literatureHowever, now that I do have a research question about the moderation, it feels strange to add new results in this part.
+<!--# in the precent version I did not have a specific research question about how factors are connected to each-other, so this part fitted well: I took the results and completed them with related literatureNow that I do have a research question about the moderation, it feels strange to add new results in this part.
 Should I take here only the moderation effects identified in the results section?
@@
 First, there is a lack of representation of the global population.
-In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from occidental countries.
+In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Western countries.
 The current results apply therefore to Western societies and should not be generalized to other cultures.
-In fact, there are cultural differences in individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989].
+In fact, there are cultural differences in individualism and collectivism: generally, North American and European are more individualistic, while South American, African and Asian are more collective [@Triandis1989].
 These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g.
 @Kuwabara2014].
-It is therefore likely that, in different cultures, cooperation relies on different mechanisms: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.
+It is therefore likely that, in different cultures, cooperation relies on different mechanisms: comparative studies should be conducted in order to reach a global understanding of cooperation.
 
@@
 In fact, this kind of setting is very useful to study social dilemmas because it provides a standard paradigm [@Balliet2011].
-However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and specific conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015].
+However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and real-life conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015].
 Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings.
@@
 In conclusion, a successful commons relies on the cooperation of its members, but this topic has not yet been extensively studied.
-Thus, further researches are needed to address the limitations of the current review and to reach a deeper understanding of this topic.
+This review started to fill the gap, but further researches are still needed to address the limitations of the current paper and to reach a deeper understanding of this topic.
 
